### 2017-01-13 Tech1.tex
Adding Tech file to the repository

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified July 2011
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \defcommand, or \renewcommand.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to latex@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format: two column (default)
% and draft.
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
% sw    SPACE WEATHER

% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below.)

\documentclass[draft,jgrga]{AGUTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OPTIONAL:
% To produce a two-columned version:
% \documentclass[grl]{AGUTeX}

% Two-columned format can be used to estimate the number of pages
% for the final published PDF.

% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OPTIONAL:
% To create numbered lines:

% If you don't already have lineno.sty, you can download it from
% http://www.ctan.org/tex-archive/macros/latex/contrib/ednotes/
% (or search the internet for lineno.sty ctan), available at TeX
%Archive Network (CTAN).
% Take care that you always use the latest version.

% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:
% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:
\usepackage{amsmath, amsthm, amssymb}
 \usepackage{lineno}
 \linenumbers*[1]

 %\usepackage{lineno}
 %\linenumbers*[1]

%  To add line numbers to lines with equations:

%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables
%
% When submitting articles through the GEMS system:
% COMMENT OUT ANY COMMANDS THAT INCLUDE GRAPHICS.
% (See FIGURES section near the end of the file.)
%
% DO NOT USE \psfrag or \subfigure commands.
%
%  Figures and tables should be placed AT THE END OF THE ARTICLE,
%  after the references.
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
 \usepackage{graphicx}
 \usepackage{ulem}
\usepackage{color}
  %
%  Uncomment the following command to allow illustrations to print
%   when using Draft:
  \setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
\authorrunninghead{STERN ET AL.}

% Shorter version of title entered in capital letters:
%\titlerunninghead{Remote and local affects of large Antarctic icebergs}
%\titlerunninghead{Effects of iceberg calving size}
\titlerunninghead{THE EFFECTS OF ICEBERG CALVING SIZE}

% Author mailing address: please repeat this command for
% each author and alphabetize authors:

\authoraddr{A. A. Stern, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{A. Adcroft, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{O. Sergienko, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{G. Marquez, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{R. Hallberg, Geophysical Fluid Dynamics Laboratory, Princeton University}

%
\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

%\title{Remote and local effects of large Antarctic icebergs}
%OR\\
%\title{The effect of calving-size distribution on sea-ice formation around Antarctica}
\title{Modeling ice shelf cavities and calving tabular icebergs}
%\title{The effects of iceberg calving-size distribution in a global climate model}
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
%

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

%Use \author{\altaffilmark{}} and \altaffiltext{}

 %\altaffilmark will produce footnote;
% matching \altaffiltext will appear at bottom of page.

 \authors{A.A. Stern,\altaffilmark{1} , A. Adcroft\altaffilmark{1}
   and O. Sergienko \altaffilmark{1} , G. Marquez\altaffilmark{1}, R. Hallberg\altaffilmark{1}}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

% >> Do NOT include any \begin...\end commands within
% >> the body of the abstract.

\begin{abstract}
The calving of giant icebergs is an important process in the Antarctic freshwater cycle. Iceberg calving can significantly alter the geometry of an ice shelf cavity, potentially affecting the circulation within the cavity. Furthermore, giant icebergs which break away can drift across large distance, altering ocean circulation, sea ice distributions and bottom water formation. 
However the despite its importance, the current generation of numerical models is unable to represent this process in a physically realistic way.
In this study we develop a model of an ice shelf cavity using a Lagrangian ice shelf. The ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds. This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs. 
The model developed in the manuscript is referred to as the Lagrangian Iceberg/Ice Shelf Model (LIISM). This paper provides a description of the LIISM model and discusses a number of the technical elements involved in building a Lagrangian ice shelf. 
To test the model, the LIISM is used to model an idealized ice shelf cavity which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). Results from static ice shelf experiments compare well to results using a more traditional Eularian ice shelf cavity. 
The novel capabilities of the  LIISM are demonstrated by modeling a tabular iceberg breaking away from the idealized ice shelf.

\end{abstract}
%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%
% The body of the article must start with a \begin{article} command
%
\clearpage
\vspace{10mm}
\textbf{Key Points:}\\

% \end{article} must follow the references section, before the figures
%  and tables.
\begin{article}
%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%
\section{Introduction}
%\subsection{Key points for writing introduction}
%
%1) Physical processes that affect the ocean circulation around Antarctica (involving ice shelf cavities /tabular icebergs). 
%
%2) Why is it important that we are about to model these regions correctly, and tabular icebergs?
%
%3) What are the significant efforts that have been made thus far towards correctly modeling ice shelf cavities / Antarctic fresh water fluxes.
%
%4) What is missing - and what we intend to add
%
%5) Similar things which have been done in the past (if there are any)
%
%6) Short summary and paper description.
%
%\subsection{Introduction}
Floating ice shelves cover vast regions of the Antarctic polar oceans. These massive platforms of ice extend deep into the water column, applying large pressures to surface of the ocean, which is often hundreds of meters below global sea level. Beneath the ice shelves, both the bottom topography and the ice shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}. The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice shelf cavities, and gives the ocean within the ice shelves cavities a unique character.

In addition to suppressing the depth of ocean surface, the ice shelves also melt (and break), thus providing a freshwater flux into the ice shelf cavities. 
Ice shelf melting and breaking are key components in the Antarctic meltwater system, and affect the ocean hydrography and biology both inside and outside of the ice shelf cavities. Some elements of the this Antarctic meltwater system are discussed in the following paragraphs.

Within the ice shelf cavities, the input of buoyant meltwater into the ocean creates rising density plumes, which are guided along the ice shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}. The strength of the circulation within the cavity feeds back onto the ice shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice shelf melt \citep{Lewis1986, Jacobs2011}.

The Antarctic ice shelves are also characterized by large infrequent calving events where massive pieces of the ice shelves break off, to create giant tabular icebergs. Observational estimates suggest that approximately half of Antarctic ice shelf decay is due to iceberg calving, while the other half occurs through ice shelf melting \citep{Depoorter2013, Rignot2013}. Calving icebergs' sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}. After calving, icebergs slowly drift away from their mother glaciers, often becoming stuck in sea ice, or become grounded along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}. Giant tabular icebergs also extend deep into the water column, and have to potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.

Melt water from both ice shelf melt and iceberg melt impact the ocean hydrography outside of the ice shelf cavities, influencing sea ice production and bottom water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}. The long distances traveled by giant icebergs before melting means that their meltwater impact is often felt hundreds of kilometers away from their calving origins \citep{Stern2016}. Melt water injection (and the accompanying upwelling) from ice shelves and icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}. The increased productivity associated with free floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.
%either increasing it by providing nutrients to the surface ocean, or decreasing by changing sea ice conditions

In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic meltwater system described in the previous paragraphs. This increased interest has led to accelerated efforts to accurately model Antarctic ice shelf cavities \citep{Asay-Davis2016}.  Modeling the ocean beneath the ice shelves presents a unique set of challenges, since (i) the presence of ice shelves provides a rigid upper boundary for the ocean model which is not encountered elsewhere in the ocean, and (ii) melting and breaking ice shelves imply a changing ocean boundary conditions which present numerous numerical difficulties.

The earliest models of ocean ice shelf cavities were developed using a static ice shelf with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}. In these models, ice shelf melting was represented through salinity and temperature fluxes, while the ice shelf geometry remained unchanged. Later models of ice shelf cavities allowed the ice shelf geometry to evolve as the ice shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}. More recently, dynamic ice shelf models have been coupled the ocean cavity, allowing the study of grounding line migration, which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}. As far as we know, all models of ice shelf cavities to date have neglected ice shelf breaking and iceberg detachment.

In parallel to these efforts to develop ice shelf cavity models, a number of iceberg drift models have been developed, and have been included in some global General Circulation Models \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}. These iceberg drift models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt. Since icebergs are treated as point particles, the iceberg drift models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such iceberg drift models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}. These models are not suitable for modeling larger tabular icebergs, which feel the ocean over many grid cells, depress the ocean surface and change circulation patterns \citep{Stern2016}. They also not suitable for studying  the local effects that icebergs have on the surrounding ocean. For this reason, tabular icebergs (L $>$ 5km) are currently not represented in the iceberg drift models used in climate models, even though observations suggest that tabular icebergs account for  the vast majority of the total Southern Hemisphere icebergs mass \citep{Tournadre2016}.

The ice shelf cavity models and iceberg drift models described above have been developed separately from one another, and have not been designed to be used together in a physically consistent way.  As such, it has not been possible to model the calving of tabular icebergs away from an ice shelf, which is an important part of the Antarctic climate system.  The goal of this study is to develop a model which combines features of the ice shelf cavity models and the iceberg drift models, to create an ice shelf cavity model that is able to calve tabular icebergs. To do this, we create an ice shelf model out of Lagrangian elements which are `bonded' together by numerical bonds. In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break' away from an existing ice shelf, thus changing the geometry of the ice shelf cavity. Modeling iceberg calving in a physically consistent way allows us to study the ocean response to iceberg detachment (see Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top}, for example). Also, by allowing icebergs protrude deep into the water column we can study the ocean dynamics around individual tabular icebergs (which was not possible in iceberg drift models).

%Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top} show an example of a tabular icebergs detaching from an idealized ice shelf. As the icebergs moves away from the ice shelf, it perturbs the water column. Details of this simulation are described further in Sections 3 and 4.
In all simulation in this study, the shape of the calving iceberg is prescribed. The question of how to correctly prescribe a calving law is undoubtably a very important question, which has rightfully received much attention in recent years \citep{Benn2007, Alley2008, Levermann2012}. \citet{Bassis2013}, for example, used a DEM model to study the generation and propagation of cracks within an ice shelf (not coupled to a dynamic ocean model).  In this study, we bypass the question of how to correctly calve icebergs or break bonds. Instead we focus on developing a framework to model the ocean to response to ice shelf breaking and the presence of tabular icebergs. This framework of representing ice shelves using a Lagrangian grid might be a step towards including giant tabular icebergs in climate models. Including ice fracture into this model will be a later step.

The model developed in this study is referred to at the Lagrangian Iceberg/Ice Shelf Model (LIISM). Section 2 gives a description of many of the key aspects of the LIISM. Since this model is a new approach to modeling ice shelf cavities, we present many of the technical elements involved in constructing the model. Those readers who are more interested in the model capabilities, should skip directly to the model results in the later sections. In Section 3 and 4, the LIISM model is used to simulate the circulation beneath an idealized ice shelf. The LIISM model results are validated by comparing them to an existing ice shelf model.  We then we move beyond the capabilities of the existing ice shelf model by allowing a piece of the ice shelf to break away becoming a tabular icebergs, and consider the ocean response to this calving event.

%A prerequisite of a complete model of an ice shelf cavity with a calving ice shelf is an understanding of the physical processes involved in iceberg calving. The importance of this problem for projecting sea level has meant that the search for a ``calving law" has received much attention in recent years. However, even with a theory of ice shelf breaking, there are still significant technical barriers preventing us from modeling icebergs calving away from ice shelves in a dynamically consistent way. In this paper, we d

%This work bears some similarity to [Basis et al], who used a DEM model to model the generation and propagation of cracks within an ice shelf. The present study is distinct from [Basis et al] in that (i) we  focus on the ocean's response to iceberg calving and thus our DEM model is coupled to a fully dynamic ocean model, (ii) the element in our DEM model are of scale > 1 km, while those in Basis were much smaller (1 meter), since we focus on the large scale oceanography, rather than the small scale fracture mechanics. Finally, we do not model the breaking in iceberg bonds and ice dynamics. However, including bonds between ice elements in our model means that modeling ice shelf breaking is a natural extension to this work.

%This same constraint is present in previous iceberg models, and has meant that those models have only been able to represent smaller icebergs (e.g. icebergs with area less than $3.5km^{2}$ in \citet{Gladstone2001, Martin2010}). However, as mentioned above, satellite observations of iceberg size show that more than 80(?) percent of Southern Hemispheric icebergs mass is stored in icebergs with areas greater than $3.5km^{2}$  \citep{Tournadre2016}, which motivates the including of larger icebergs in climate models.

\section{Model description}
%, which can be used to model small icebergs, tabular icebergs, sea ice and ice shelf cavities
In this section we describe many key elements of the LIISM.  The LIISM is a Lagrangian/particle-based model in that the objects of the model are Lagrangian elements. Each element represents a mass of ice which is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time. The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element. The elements are forced by oceanic and atmospheric forces, which are provided by the user or are determined by coupling the LIISM to an ocean/atmosphere model. The elements also interact with one another and can be bonded together to form larger structures. In different contexts, the LIISM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
In this latter case, the LIISM model can be categorized as a discrete element model (DEM). 
% in the sense that large structures are constructed from smaller independent Lagrangian elements.

The LIISM model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}. When run with the correct set of runtime flags, the model runs as a traditional iceberg drift model.
%
%In this section, we discuss the equations of motion governing the element movement and the thermodynamic equations governing the decay of the elements. The also discuss the interactive forces

\subsection{Equations of motion}
The elements drift in the ocean, forced by atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force and a force due to the sea surface slope.  When these ice elements move alone (without interactions with other elements), they can be thought of as representation of small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).

In addition to the environmental forces, the elements in the LIISM model experience interactive forces due to the presence of other elements. Two types of interactive forces are included between elements. The first force is repulsive force which is applied to elements to prevent them from moving too close to one another. This repulsive force prevents icebergs from piling up on top of one another. The second interactive force is a force due to numerical `bonds', and is only applied if two elements are `bonded' together. When two elements are bonded, each element feels an attractive force that prevents the elements from moving too far apart from one another. The interactive forces between two bonded elements are defined such that in the absence of other forces the elements come to rest adjacent to one another, with no overlap of the iceberg areas.

The momentum equation for each element is given by 
\begin{equation}
\label{Iceberg_mom_eq}
M \frac{D \vec{u}}{Dt}=\vec{F}_{A} + \vec{F}_{W}+ \vec{F}_{R}+\vec{F}_{C} +\vec{F}_{SS}+\vec{F}_{SI}+\vec{F}_{IA} ,
\end{equation}
where $\frac{D}{Dt}$ is the total (Lagrangian) derivative, $M$ is the mass of the element, $\vec{u}$ is the velocity of the element, and the terms on the right hand side give the forces on the element due to air drag $(\vec{F}_{A})$, water drag $(\vec{F}_{W})$, sea ice drag $(\vec{F}_{SI})$, Coriolis force $(\vec{F}_{C})$, wave radiation force $(\vec{F}_{R})$, sea surface slope $(\vec{F}_{SS})$, and interactions with other elements ($\vec{F}_{IA}$). The environmental forces are the same as those presented in \citet{Martin2010}, and are provided for completeness in Appendix A.  The details of the interactive forces are provided in below.

\subsection{Interactive Forces}
The interactive force on an element is calculated by adding together the interactions with all other elements, such that the interactive force on element $i$, $(\vec{F}_{IA})_{i}$ is given by:
\begin{equation}
\label{F_interaction_i}
(F_{IA})_{i}= \Sigma_{j \neq i} (F_{IA})_{ij},
\end{equation}
where $(F_{IA})_{ij}$ is the force on element $i$ by element $j$. Both bonded an repulsive interactions are modeled using elastic stresses with frictional damping. The elastic component of the force is a function of the distance between the two elements, while the  frictional damping force depends on the relative velocity of the two elements.

To describe the forces between two elements, we begin by introducing some notation.  Let $\vec{x_{i}}$, $\vec{x_{j}}$ be the positions of elements i and j. The distance between elements i and j is
\begin{equation}
\label{distance}
d_{ij}= | \vec{x_{i}} - \vec{x_{j}}|.
\end{equation}
We then define the interaction diameter of an element by 
\begin{equation}
\label{Diameter}
D_{i}=2 \sqrt{\frac{A_{i}}{\pi}},
\end{equation}
where $A_{i}$ is the planar surface area of element i. Using this, we define the critical interactive length scale, 
\begin{equation}
L_{ij}=\frac{D_{i} + D_{j}}{2},
\label{eq:Interaction_crit}
\end{equation}
which governs interactions between elements i and j. 
Repulsive forces are only applied when $d_{i,j} \textless L_{i,j}$, while bonded forces are only applied when the when $d_{i,j} \textgreater L_{i,j}$ and a bond exists between element i and j.  Bond and repulsive forces are designed to such that in the absence of other forces, bonded particles will settle in an equilibrium position where elements are separated by the critical interaction length scale $L_{i,j}$.
% (see schematic in Figure \ref{fig:Interactive_forces}).

To aid in notation, we define a bond matrix $B_{ij}$ such that $B_{ij}=1$ if elements i and j are bonded together and  $B_{ij}=0$ otherwise. Using this notation, the interactive force $(\vec{F_{IA}})_{ij}$ on an element i by an element j is given by
\begin{equation}
\label{F_interactione}
(\vec{F_{IA}})_{ij}= \left\{%
  \begin{array}{ll}
   (\vec{F_{e}})_{ij} + (\vec{F_{d}})_{ij}
    & \mbox{if $d_{ij} \leq L_{ij} $ }\\
 %     & \mbox{if $|x_{i} -x_{j}| \leq \frac{1}{2}(D_{i}+D_{j}) $ }\\
    (\vec{F_{e}})_{ij} + (\vec{F_{d}})_{ij}
 %     & \mbox{if $|x_{i} -x_{j}| > \frac{1}{2}(D_{i}+D_{j}) \textrm{ and } B_{ij}=1 $ }\\
       & \mbox{if $d_{ij} >  L_{ij}  \textrm{ and } B_{ij}=1 $ }\\
      0
 %     & \mbox{if $|x_{i} -x_{j}| > \frac{1}{2}(D_{i}+D_{j}) \textrm{ and } B_{ij}=0 $ }.\\
      & \mbox{if $d_{ij} > L_{ij} \textrm{ and } B_{ij}=0 $ }.\\
  \end{array}
\right.
\end{equation}
$(\vec{F_{e}})_{ij}$ and $(\vec{F_{d}})_{ij}$ are the elastic and frictional damping components of the interactive force between elements i and j.
The elastic force $(\vec{F_{e}})_{ij}$ between elements is given by
\begin{equation}
\label{F_elastic}
(\vec{F_{e}})_{ij}= -\kappa_{e}  \bigg( d_{i,j}-L_{i,j} \bigg) T_{i,j} \vec{r},
\end{equation}
where $\vec{r}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, and $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j. We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F_{IA}})_{ij}=-(\vec{F_{IA}})_{ji}$). This is in contrast to some other DEM models in the literature (e.g. \citet{Li2014}). The minimum thickness is preferred to the average thickness, since this means that the for two bonded elements a fixed distance apart, acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero. 
%
%Since ice elements are able to melt entirely, the repulsive forces between elements need to be carefully defined so that they are stable even for very small elements with mass approaching zero. We define the elastic repulsive force $(F_{r})_{ij}$ between elements i and j as
%\begin{equation}
%\label{F_elastic}
%(F_{r})_{ij}= -\kappa_{r} A_{o}(i,j) T_{i,j}\vec{r},
%\end{equation}
%where $A_{o}(i,j)$ is the overlap area of the two circles centered at $\vec{x_{i}}$ and $\vec{x_{j}}$, with diameter $D_{i}$ and $D_{j}$ (see Figure \ref{fig:Interactive_forces}), respectively, and $\kappa_{r}$ is the repulsive spring constant. We choose $(F_{r})_{ij}$ to be proportional to the overlap area between the interactive circles surrounding each element so that the acceleration due to this repulsive force is bounded, even as the element mass approaches zero.   This consideration is not needed for the bonded force, since element bonds will be broken when elements are smaller than a threshold size. 
%[Should we use a bonded force given by  $(F_{b})_{ij}= -\kappa_{b}  \bigg( d_{i,j}-L_{i,j}) \bigg)^{2} T_{i,j} \vec{r}$ rather? Come back to this.]

The frictional damping force has components that damp both the relative radial velocity and relative transverse velocities of the two elements. If $\vec{r}^{\perp}$ is the direction vector perpendicular to $\vec{r}$, and $P_{\vec{r}}$ and $P_{\vec{r^{\perp}}}$ are the projection matrices that project onto $\vec{r}$ and $\vec{r}^{\perp}$ respectively, then the frictional damping force is given by
\begin{equation}
\label{F_damping} 
%(F_{d})_{ij}=   -C_{r}|(u_{i} -u_{j}) \cdot \vec{r}   | \vec{r}  - C_{t}|(u_{i} -u_{j})\cdot  \vec{r}^{\perp} | \vec{r}^{\perp})
(\vec{F_{d}})_{ij}=   \Bigg (-c_{r} P_{\vec{r}}  - c_{t} P_{\vec{r}^{\perp}} \Bigg ) \cdot (\vec{u_{i}} -\vec{u_{j}} ) 
\end{equation}
Here $c_{r}$ and $c_{t}$ are the radial and transverse drag coefficients. For the simulation below, we set $c_{r}=2\sqrt{\kappa_{e} }$ and  $c_{t}=\frac{1}{4}c_{r}$ so that the radial elastic force is critically damped, and the transverse damping is sub critical. The damping forces are implemented using an implicit time stepping scheme, to avoid stability issues for very small elements (details found in Appendix B).

The effectiveness of the repulsive forces can be seen in Figure \ref{fig:Regular_Uncoupled_sim} which shows an uncoupled simulation where ice elements drift westward into a bay, and eventually come to rest with minimal overlap between elements. The effectiveness of the numerical bonds is demonstrated in Figure \ref{fig:Uncoupled_sim} tabular icebergs (constructed from many ice elements bonded together) and individual icebergs (unbonded elements) drift together towards a convex coast line. When the tabular icebergs arrive at the coast, they bump into the coastline and begin to rotate, influencing the paths of the other icebergs. In this example we see that modeling large structures using small elements bonded together, allows us to achieve large-scale structure and rotational motion, without having to include an equation for the angular momentum of the elements (as discussed in \citet{Jakobsen2001}).

\subsection{Element geometry and packing}
Elements are packed differently depending on the shape of the elements. For all simulations in this study, we use elements whose surface areas are equally-sized regular hexagons. In order to pack these elements together, the hexagonal elements are initially arranged in a staggered lattice, with each element bonded to the adjacent elements (see Figure  \ref{fig:Hex_intersections}a). In this arrangement, each element (away from the edges) is bonded to six other elements. The bonds between elements form a pattern of equilateral triangles, which give the larger structure rigidity.

Some experiments were also performed using rectangular elements, arranged in a regular (non-staggered) lattice. In this case, each element forms four bonds with adjacent elements. However, the resultant structures were found to be much less rigid and tended to collapse when sufficient forces was applied. For this reason, hexagonal elements were preferred.

\subsection{Ocean-ice and ice-ocean coupling}
The LIISM model is coupled to the ocean model via a two-way synchronous coupling, meaning that ocean model fields are passed to the LIISM model and the LIISM model fields are passed back to the ocean model at every time step. Passing fields between the two models involves interpolating fields between the Eulerian grid of the ocean model and the `Lagrangian grid' of the LIISM model (i.e.: onto the ice elements).

The coupling from the ocean model to the LIISM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LIISM model, to be used in the momentum and thermodynamics equations of the ice elements. Within the LIISM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme. The LIISM model is not sensitive to the chosen interpolation scheme.

%More care needs to be taken when passing fields back from the LIISM model to the ocean model. 
The coupling in the other direction, from the LIISM model to the ocean model, is more complex.
The LIISM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean boundary condition by applying a no slip boundary condition and frictional velocity beneath the ice. Fields from the LIISM model are interpolated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model. Since the LIISM model applies large pressures to the ocean surface, the ocean model is sensitive to the interpolation scheme used to map the LIISM fields to the ocean grid. Sudden jumps to the ocean surface pressure can trigger tsunamis within the ocean model, making the ocean model become unstable.

The interpolation of the LIISM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LIISM model (see Section 2.3). Fields are `spread' to the ocean model by exactly calculating what fraction of an element's surface area lies in a particular grid box, and dividing the field in proportion to this fraction.
%While the position of a particular element might be inside one ocean grid cell, the implied shape of the element will often intersect other ocean grid cells. 
For example, consider an element which has a hexagonal surface area in the LIISM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b). In this situation, the mass of the element is divided between these four ocean cells in proportion to the overlap area between the hexagonal element and the grid cell (this fraction is shown by the colors in \ref{fig:Hex_intersections}b). An advantage of this approach is that there are no jumps in pressure as an element moves from one grid cell to another.

The numerical calculation of the intersection between hexagons and the ocean grid is simplified by dividing the hexagon into 6 equilateral triangles. This method allows for the intersection to be found even when the hexagon is not aligned with the grid. The LIISM model can be run using hexagonal or rectangular elements.

The field-spreading scheme is coded with the restriction that an element's area can only intersect a maximum of four ocean grid cells at a time. A consequence of this is that this sets a limit on the maximum size of elements that can be represented using this model, i.e.: the longest horizontal dimension of an ice element must be smaller than the ocean grid spacing. Larger ice structures are constructed by bonding together smaller elements.

\subsection{Thermodynamics}
The ice elements decay according to a number of melt parameterizations.  As the ice elements melt, their mass decreases, and the appropriate salt, mass and heat fluxes are passed to the ocean. In this section we described the melt parametrization for bonded, unbonded and partially bonded elements.

As mentioned above, ice elements which do not interact with other elements are modeled identically to the point particle icebergs described in \citet{Martin2010}. These elements melt according to three semi-empirical parametrization for melt commonly used in previous iceberg studies \citep{Gladstone2001,Martin2010}.  Three types of iceberg melting are used: basal melt, $M_{b}$, melt due to wave erosion, $M_{e}$ and melt due to buoyant convection, $M_{v}$. $M_{e}$ and $M_{v}$ are applied to the sides of the ice element, while $M_{b}$ is applied at the ice element base. The details of $M_{b}$. $M_{v}$ and $M_{e}$ are given in Appendix A.

When multiple elements are bonded together to form larger structures, it is no long appropriate to use the parameterizations for melt developed for individual point-particle icebergs. An element which is completely surrounded by other elements, is meant to represent a piece of ice in the middle of a large structure, and hence will not experience a melt at its sides due to wave erosion or buoyant convection. Also, the iceberg basal melt rate, $M_{b}$ described above is based on boundary layer theory of flow past a finite plate, and is only appropriate for basal surfaces where the distance from the leading edge is sufficiently small \citep{Eckert1950, Weeks1973}. For an element in the interior of large structures, the distance from the edge of the structure is large, and so using $M_{b}$ for the basal melt is not appropriate. Instead, the basal melt, $M_{s}$ is determined using the three equation model for basal melt, which is a typical melting parametrization beneath used beneath ice shelves \citep{Holland1999}.% (see Appendix A).

When using both individual elements and bonded elements in the same simulation, we determine which melt rate parameterizations to use based on the amount of bonds that each element has. An element which is in the center of a large structure will form the maximum number of bonds, while unbonded elements form zero bonds. If maximum number of bonds that an element can form (given the shape of the element) is $N_{max}$, and the number bonds that an element has is $N_{b}$, then the side melt and bottom melt for that element are given by
\begin{equation}
M_{side}=\frac{(N_{max}-N_{b})}{N_{max}}  (M_{v} +M_{e})
\end{equation}
and
\begin{equation}
M_{bottom}=\frac{(N_{max}-N_{b})}{N_{max}}M_{b} +\frac{N_{b}}{N_{max}}M_{s}
\end{equation}
respectively.  In this way, elements with no bonds, melt like point particle icebergs, elements at the center of large structures melt like ice shelves, and elements at the sides of large structures have a combination of iceberg side and basal melt, and ice shelf melt.

\subsection{Algorithms and computational efficiency}
Including interactions between elements leads to an increase in the computational complexity of the model. In this subsection we comment on some of the algorithmic procedures that have been used to increase the computational efficiency. Readers who are not interested in this more technical side of the model should skip this section.
\subsubsection{Time stepping}
The ice elements in the LIISM model are advected using a semi-implicit velocity Verlet time-stepping scheme. The velocity verlet time stepping scheme is commonly used in DEM models in video games because it is computational efficient and has desirable stability properties \citep{Jakobsen2001}. This time stepping scheme was preferred to the Runge-Kutta  4, which was used in the iceberg model of \citet{Martin2010} since, the Verlet time stepping only requires one calculation of the interactive forces per time step (while the Runge-Kutta scheme requires the interactive forces to be calculated four times). Since the calculation of the interactive forces is one of the most computationally expensive part of the algorithm, the Verlet scheme leads to a significant increase in the speed of the model. We note that the Verlet scheme used in the LIISM contains a small modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability). The details of this time stepping schemed are outline in Appendix B.
\subsubsection{Interactions and Bonds}
At every time step, we calculate the force on each element due to interactions with every other element. In principle, this involves order $n^{2}$ operations (for n elements). However, since each element only has repulsive interactions with elements that are less than one ocean grid cell away, and each element only has bonded interactions with a small number of other elements, we are able to reduce the complexity of the system.

The complexity reduction is achieved by storing the element data in an efficient way that prevents having to search through all element pairs to check if they are close to one another or are bonded with one another. The data storage system works as follows: pointers to the memory structures containing each element are are stored in linked list data structures, which allow elements to be added and removed from the lists easily without restructuring the entire list. Instead of using one list for all the elements on a processor, we use a separate linked list for each ocean grid cell. When an element moves between ocean grid cells, it is removed from its original list and added to the list corresponding to its new ocean grid cell. Since the area of elements has to be smaller than the area of an ocean grid cell, the critical interaction critical interaction length scale (equation \ref{eq:Interaction_crit}) is less than the length of a grid cell. This means that elements only experience repulsive forces with elements in the same ocean grid cell, or in one of the 8 adjacent cells. Limiting the possible repulsive interactions to elements in the 9 linked lists substantially reduces the computational time needed to calculate the total interactive force.

Bonded interactions are handled slightly differently. Each bond is assigned a piece of memory. Each ice element contains a linked list of each of its bonds (typically up to six bonds per element). At each time step, the code traverses the lists of bonded elements, and adds a bonded force corresponding to these bond. The bonded force is only applied if $\vec{r}_{i,j} > L_{ij}$, to avoid double counting an interaction. Having a list of bonds stored with each element reduces the computational complexity of bonded interactions from order $n^{2}$ to order n. Handling bonded attractive forces separately to the repulsive and non-bonded forces means that we do not need to check whether two elements are bonded, which further increases the computational efficiency.

\subsubsection{Parallelization and halos}
The LIISM model runs on multiple processors in parallel. When elements move from an ocean cell on one processor to an ocean cell on a second processor, the memory has to be passed from one processor the next, added and removed to the appropriate lists and the memory has to be allocated and deallocated correctly. Element interactions across the edge of processors are handled using computational halos. A computational halo is a copy of the edge of a one processor which is appended to the edge of a second processor, so that the first processor can `see' the second processor during a time step. Before a time step, elements at the edges of each processor are copied onto the halos of adjacent processors so that they can be used in calculating the interactive forces. After each time step, these halos and removed, and the process is repeated. These halo updates are one of the most computationally expensive parts of the LIISM model.

Keeping track of pairs of bonded elements that move across a processor edge requires a lot of book keeping since bonds have to be severed and reconnected. Details of how the bonds are broken and reconnected across processor boundaries are provided in Appendix~C.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Experiment Setup}
%The introduction of Lagrangian elements, numerical bond and appropriate interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice shelf cavities which undergo large calving events, and create giant tabular icebergs.

%We demonstrate this capability in an experimental setup using an idealized ice shelf. For these experiments the LIISM model is coupled to the MOM6 ocean model.
% This section contains a description of the experimental setup and numerical experiments performed. The results of these simulations are presented in Section 4.

 %In the examples below, the LIISM model is firstly used in uncoupled mode to model the movement of freely drifting icebergs. Secondly, the coupled LIISM with static ice elements is used to model an idealized ice shelf cavity. Finally, the fully-coupled LIISM is used to model a tabular iceberg which calves off of this ice shelf.

%\subsection{Uncoupled simulation}
%We begin by demonstrating the LIISM model uncoupled to the ocean. For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide. Land points are arranged in a semi-circle, in the west of the domain, as shown by the black dots in Figure \ref{fig:Uncoupled_sim}.  Three hundred ice elements are initialized with diameters uniformly sampled from the interval [0 40km], and positioned randomly at positions with $x \leq 300$km. These ice elements can be thought to represent interacting sea ice flows or icebergs. Three `tabular icebergs' are initialized by arranging ice elements in a staggered lattices with adjacent elements bonded together, as described in Section 2.4. The three tabular icebergs contain 25, 16 and 4 elements, respectively. Each of the elements that make up the tabular icebergs has a diameter of 40km. All elements have an initial thickness of 10m.
%
%The simulation is forced by an imposed westward ocean current of u=0.1m/s. Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero. The initial setup is shown in Figure \ref{fig:Uncoupled_sim}a.

%\subsection{Coupled Ocean-Ice simulations}
%\subsection{Description of idealized ice shelf cavity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \section{Experiment Setup}
The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice shelf cavities which undergo large calving events. We demonstrate this capability by performing numerical experiments with the LIISM model coupled to the MOM6 ocean model [reference]. 
%This section describes the experimental setup of these numerical experiments. The results are shown in Section 4.

\subsection{MISOMIP configuration}
In order for our simulations to be easily comparable to previous models of ice shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
%For this experiment, we use the ice shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
The MISOMIP configuration was developed as a standardize configuration to allow for the comparison between various ocean-ice coupled models. The configuration consists of an idealized ice shelf in a rectangular domain. The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650km. The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_exp}a and \ref{fig:ISOMIP_exp}b respectively, with the grounding line position drawn in for reference. The configuration is the same as that of the Ocean0 setup in the MISOMIP, with three changes made:
\begin{enumerate}
\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
\item The ice shelf is configured to be symmetric about its center line. This was achieved by using the average of the left and right flank of the ice shelf thickness. 
\end{enumerate}
These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.

The LIISM model is coupled to the MOM6 ocean model. 
The ocean model is run in layered mode, with a horizontal resolution of $\Delta x = 2$ km, and 36 vertical layers. 
%The ocean model is run in using vertical coordinate system which is a hybrid between a sigma level and a z-level model. In particular, model layers bend underneath the ice shelf as they would in a sigma model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model. The coordinate system was achieve using ALE regridding remapping scheme.The model used a horizontal resolution of 2km, and 36 vertical layers.
Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1. The simulation is initially at rest, with horizontally uniform initial ocean temperature and salinity profiles that vary linearly between specified surface and bottom values. The initial surface temperature and salinity are  $T_{t}=-1.9^{\circ}$C and $S_{t}=33.8$ psu, respectively. The initial temperature and salinity at the depth $H_{ocean}$ are $T_{b}=1.0^{\circ}$C and $S_{b}=34.7$ psu. The maximum ocean depth is $H_{ocean}=720$ m.  A sponge layer is used on the northern boundary of which relaxes back to the initial temperature and salinity with a relaxation time scale of $\tau=0.1$ days. Melting is set to zero for cells where the ocean column thickness is less than 10m to avoid using more energy to melt ice than is present in the water column.

%\textbf{Initializing Lagrangian elements:}\\
\subsection{Initializing Lagrangian elements:}
Ice elements in the LIISM model are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3). The apothem of the hexagons is initially set to $A=0.85$ km. Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2A<\Delta x$). The initial mass of the ice elements is determined by preprocessing inversion, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3. Boundary points are filled in using extra ice elements of appropriate thickness.

When the model is run, the average ice draft in an ocean grid cell, is calculated from the total mass of ice elements in that grid cell by assuming that the ice elements are in hydrostatic balance. The total mass is found by summing up over all ice elements located in that grid cell, while allowing elements to spread their mass across neighboring grid cells (as discussed in Section 2.3). Figure \ref{fig:ISOMIP_exp}b shows the draft of the ice shelf above the ice shelf cavity in the coupled static ice shelf simulation using this interpolation method, while Figure \ref{fig:ISOMIP_exp}c shows the draft which is calculated without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses). When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_exp}c). The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_exp}b). In simulations without mass spreading, irregularities in ice draft cause irregularities in the ocean surface pressure, which cause spurious motion in the ocean (not shown). This is much reduced or absent when mass spreading is used.

\subsection{Static ice shelf experiment}
In the first experiment, we use a static ice shelf where the velocity of all ice elements is set to zero. In this experiment, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as was done in the Ocean0 setup in the MISOMIP \citep{Asay-Davis2016}). In this setup, ice shelf melting generates a temperature and salinity flux into the ocean, but does not change the thickness of the ice shelf. This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice shelf advection.

Results of the static ice shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice shelf model \citep{Goldberg2012}, coupled to the same ocean model. The simulations in the Lagrangian and Eularian are compared after 5 years of models time.

%Another set of experiments were performed using a static ice shelf which decays as it melts. The results over a 5 year period were fairly similar to the non-decaying shelf, and are not shown.

% \subsection{Decaying ice shelf experiment}
%In the second experiment, the LIISM ice shelf is allowed to decay as the ice melts. This setup provides a more challenging test of the ocean-ice coupling, as the ocean responds to a moving lateral boundary. For this experiment, we increase the temperature of initial temperature profile and the sponge layer by 4 degrees, to make the ice shelf decay more rapidly.

 \subsection{Tabular iceberg calving}
In the next set of experiments, we demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice shelf models. These simulations model a large tabular iceberg being calved from the edge of the ice shelf. The tabular iceberg drifts in the ocean, submerged in the water column, where it influences the ocean circulation.

The tabular iceberg simulations are initialized using the final ocean state of the static ice shelf experiment. For these situations, all ice elements initially within a 15km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held are stationary.  The three tabular iceberg simulations are performed:

\begin{enumerate}
\item
\textbf{Tabular iceberg with fixed velocity}:\\
In this simulation, the velocity of the non-stationary elements is fixed to u=0m/s, v=0.01m/s. This simulation allows us to study the response of the ocean to disturbance caused by a tabular iceberg moving through the water (with an fixed velocity). This simulation is not fully coupled since the velocity of the elements is prescribed.
\item
\textbf{Tabular iceberg with bonded elements}:\\
 All non-stationary ice elements are bonded together by the numerical bonds. This experiments is fully-coupled in that the ice elements are driven the ocean, and the pressure exerted by the ice elements drives ocean flow. In order to make the iceberg drift away from the ice shelf, we imposed a zonal wind stress of $\tau_{x}$ = 0.1 $\frac{N}{m^{2}}$. .
\item
\textbf{Tabular iceberg with unbonded elements}:\\
This simulation is identical to the bonded elements simulation, except that all the numerical bonds are broken, so that the elements are free to move away from one another.
\end{enumerate}

%\section{Results}
%\subsection{Uncoupled simulation}
%Figure \ref{fig:Uncoupled_sim} shows the results of the uncoupled simulation described in subsection 3.1. The figure shows snapshots of the positions of ice elements at after t=0, 300, 600 and 900 days.  During the simulation, the ice elements drift westward with the prescribed ocean current until the reach the land boundary on the western side of the domain.  Once the elements reach the western coastline, the elements become trapped against the coast and can not move further. When new elements approach the elements at the coast, they interact with the elements already at the coast, and are repulsed. The elements eventually settle in an equilibrium position where there is minimal overlap between elements.
%
%The tabular icebergs also drift westward towards the coast. The elements within the tabular icebergs which arrive first at the coastline  bump up against the coastline (or elements already at the coast). This interaction causes the tabular icebergs to rotate, and change directions. The tabular icebergs continue to drift and interact with other elements until they too settle into an equilibrium position and come to rest. The rotation of the tabular icebergs confirms the this solid body rotation can me modeled using elements and bonds, without having to include an equation for the angular momentum of the elements (as discussed in \citet{Jakobsen2001}).
%
%Comparing the northern and southern halves of the simulation shows how large tabular icebergs can interfere with the trajectories and movement of smaller icebergs (or sea ice flows). These types of interactions will likely play an important role in ice choked fjords [reference] and Antarctic coastal regions [reference].

\section{Results}

%\subsection{Coupled simulation}
\subsection{Static ice shelf experiment}

%\subsubsection{Comparison with Eularian ice shelf model}
\textbf{Comparison of LIISM and Eularian ice shelf model}\\
The results from coupled ocean-ice simulation in the MISOMIP configuration using LIISM are compared to the results using an Eulerian ice shelf model in the same configuration. The ice draft in the Eulerian ice shelf model is initialized using the field shown in Figure \ref{fig:ISOMIP_exp}b. Figures \ref{fig:Melt_comparison} show the time-averaged melt rates of both the Lagrangian and Eulerian ice shelf models, averaged over the first 5 years of the simulation.

The melt rates of the Eulerian and Lagrangian models are very similar with slight difference showing up at the grounding line and ice front (Figure \ref{fig:Melt_comparison}). The slight difference at the grounding line are a result of the fact that elements in the LIISM model are smaller than a grid cell in length. This means that ice element near the grounding line may be ungrounded in the LIISM model, while the grid cell is considered grounded in the Eularian model. At the ice front, the Eularian model has a straight ice front, while the LIISM model has a staggered ice front, which is a result of the staggered hexagonal packing.

The small changes in melt at the grounding line and ice front drive slight changes to the circulation beneath the ice shelf, which in turn lead to small difference in the temperature and salinity profiles over time. This is seen by comparing the time-averaged ocean salinity profiles for the Lagrangian and Eularian ice shelves (Figure \ref{fig:Salt_comparison} ) and also  by comparing the the time-averaged barotropic stream function of the two simulations (see Figures \ref{fig:Bt_comparison}) and in the supplementary material).
The differences between the Eularian and Lagrangian simulations are small compared to the wide spread of difference seen in the MISOMIP inter comparison. This is unsurprising, since the LIISM and Eularian ice shelves are coupled to the same ocean model and pass similar fields to the ocean model.

The similarity of the Lagrangian and Eulerian ice shelf models shows that the LIISM model coupled to an ocean model is able to model sub ice shelf cavities as well as the Eularian model does. This is a good starting point for moving beyond the capabilities of the Eularian model.

%\subsection{Decaying ice shelf experiment}
%In the decaying ice shelf experiment, the ice shelf is allowed to decay as it melts. As the ice shelf melts, it decays and the pressure on the top layer of the ocean model decreases (Figure \ref{fig:Decaying_shelf}). The ice shelf decays most rapidly near to the grounding line. Grounding line migration due to melt does not take place since melting is set to zero where the ocean thickness is less that 10m.

%As the ice shelf melts, there is a mass flux into the ocean. The integrated sea surface height north of the ice shelf does not change during the course of the simulation, since the extra mass flux into the ocean, is exactly offset by a decrease mass of the ice shelf, as expected.

\subsection{Tabular iceberg calving}

%\subsubsection{Tabular iceberg with fixed velocity}
\textbf{Tabular iceberg with fixed velocity}\\
The fixed iceberg velocity calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.  After the iceberg calves, it moves northwards away from the ice shelf with a prescribed velocity. After the iceberg has calved away from the ice shelf, we observed a warming of the surface waters near the near the ice front and iceberg edge. This surface warming is caused by an upwelling of the warmer waters from beneath the ice shelf and iceberg. As the icebergs drifts away from the ice front, these warmer waters remain in the wake of the iceberg (Figures \ref{fig:Calving_fixed_top}). The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color near to tabular iceberg in the Southern Ocean [reference],  suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface. The motion of the iceberg also drives barotropic velocities through out the water column, which disturb the initial stratification of the water column (Figures \ref{fig:Calving_fixed_side}).

%\subsubsection{Fully coupled tabular iceberg}
\textbf{Fully coupled tabular iceberg}\\
The necessity of bonds between ice elements is demonstrated by comparing two simulations where an iceberg calves, and is allowed to evolve freely with the flow. In the Bonded simulation, the elements in the calved iceberg are bonded together, while in the Unbonded simulation the all bonds between elements in the tabular iceberg are broken.

%The motions of elements in the tabular iceberg in these two simulations are rather different. 
In the Bonded simulation, the ice element in the tabular iceberg remain close to one another, and the tabular iceberg retains its shape (Figure \ref{fig:Bond_vs_No_bond}a,c). The elements are forced by the melt-water-driven current at the ice front, which moves towards the north-west (see Figure \ref{fig:static_solo} in the supplementary material). This current, together with the Coriolis force, cause the iceberg to rotate before moving away from the ice shelf (Figure \ref{fig:Bond_vs_No_bond}a).

In the Unbonded simulation, the ice elements in tabular iceberg are not constrained to move together. Instead, the elements spread out and drift towards the north-west for the same reason discussed above. Since the ice elements are not closely, packed together, they apply a smaller pressure to the ocean surface, spread over a larger area (Figure \ref{fig:Bond_vs_No_bond}c). The type of behavior could be relevant in simulating ice shelf disintegrations, rather than tabular iceberg calving.

 \section{Discussion}
1) How do we get this into a big coupled climate model - what is still needed? Bond breaking, ice growing
2) Mention lagrangian sea ice

\section{Appendix A}
\subsection{Environmental forces on ice elements}
The non-interactive forces on an ice element are as described in \citep{Martin2010}, and are repeated here for completeness. 
The force on an element due to air (a), ocean (o) and sea ice (si) drag are given by
\begin{equation}
(\vec{F}_{a}) = \rho_{a} (0.5 c_{a,v} W F + c_{a,h} L W) | \vec{u}_{a} - \vec{u}|(\vec{u}_{a} - \vec{u}),
\end{equation}
\begin{equation}
(\vec{F}_{o}) = \rho_{o} (0.5 c_{o,v} W (D-T_{si})F + c_{o,h} L W) | \vec{u}_{o} - \vec{u}|(\vec{u}_{o} - \vec{u}),
\end{equation}
\begin{equation}
(\vec{F}_{si}) = \rho_{si} (0.5 c_{si,v} W T_{si}F + c_{si,h} L W) | \vec{u}_{si} - \vec{u}|(\vec{u}_{si} - \vec{u}).
\end{equation}
Here $\rho_{a}$, $\rho_{o}$, $\rho_{si}$, are the density of air, ocean and sea ice, respectively. $c_{a,v}$, $c_{o,v}$ and $c_{si,v}$ are the vertical drag coefficients with air, ocean and sea ice, while $c_{a,h}$, $c_{o,h}$ and $c_{si,h}$ are the respective horizontal drag coefficients. Here $\vec{u}_{a}$, $\vec{u}_{o}$, $\vec{u}_{si}$, are the velocities air, ocean and sea ice, respectively. L, W, T, F and D are the length, width, thickness, freeboard and draft of the ice element. The element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$, where $\rho$ is the ice element density.

The  wave radiation force $(\vec{F}_{R})$ is given by
\begin{equation}
\vec{F}_{R} = \frac{1}{2}\rho_{o} c_{r} g a \textrm{ min}(a,F)  \textrm{ } 2\frac{WL}{W+L} \frac{\vec{v}_{a}}{|\vec{v}_{a} |}
\end{equation}
where g is the acceleration due to gravity, a is the wave amplitude empirically related to the wind speed by  $a=0.010125|\vec{v}_{a} -  \vec{v}_{o}| $, and $c_{wd}$ is the wave drag coefficient defined as 
\begin{equation}
c_{wd}=0.06 \textrm{ min} \Bigg( \textrm{ max} \Bigg[0,\frac{L-L_{c}}{L_{t}-L_{c} } \Bigg]  , 1    \Bigg), 
\end{equation}
where $L_{w}=0.32|\vec{v}_{a} -  \vec{v}_{o}|^{2}$ is an empirical wave length, $L_{c}=0.125 L_{w}$ is the cutoff length, and  $L_{t}=0.25 L_{w}$ is the upper limit.

The pressure gradient force is approximated as a force due to sea surface slope and given by
\begin{equation}
\vec{F}_{SS} = -M g \vec{\nabla} \eta
   \end{equation}
where $\eta$ is the sea surface height.

\subsection{Melt rate parametrization}
As discussed in Section 2.5, unbounded ice elements in the LIISM model decay according to parameterizations for iceberg decay typically used in iceberg drift models \citep{Martin2010}, while ice elements within larger ice structures have only a basal melt given by the three equation model \citep{Holland1999} .

For unbonded ice elements, the element thickness decays at due to basal melt at a rate $M_{b}$, while the length and width of the elements decay as a result of melt due to wave erosion, $M_{e}$ and melt due to buoyant convection, $M_{v}$. Following \citet{Martin2010}, the basal melt rate, wave erosion melt rate, and buoyant convection melt rate are parameterized by 
\begin{equation}
M_{b} = 0.58 | \vec{v} - \vec{v}_{0}|^{0.8} \frac{\tilde{T}_{0} - \tilde{T}}{L^{0.2}}
\end{equation}
\begin{equation}
M_{e} = \frac{1}{12} S_{s} \Bigg(  1 + \cos{[\pi A_{i}^{3}]}  \Bigg) \Bigg( \tilde{T}_{0} +2 \Bigg ),
\end{equation}
\begin{equation}
M_{v} =  \Bigg(7.62 \times 10^{-3}  \Bigg )   \tilde{T}_{0} + \Bigg( 1.29 \times 10^{-3} \Bigg)\tilde{T}_{0}^{2}.
\end{equation}
$\tilde{T}$ is the effective iceberg temperature and is set to $\tilde{T}=4^{\circ}$C, $\tilde{T}_{0}$ is the temperature at the top of the ocean,  $A_{i}$ is the sea ice area fraction, and $S_{s}$ is the sea state, which is given by the Beaufort scale
\begin{equation}
S_{s} =  \frac{2}{3}  | \vec{u}_{a} - \vec{u}_{o} |^{\frac{1}{2}}  +\frac{1}{10}   | \vec{u}_{a} -\vec{u}_{o} |
\end{equation}
All three melt rates are in units of meters per day.

For elements inside larger structures, the melt due to wave erosion  and melt due to buoyant convection are set to zero, and the basal melt, $M_{s}$ is given by the standard three equation model \citep{Holland1999}. 
%\begin{equation}
%M_{s} =\frac{ 1}{L_{ice} \rho_{ice} }    \rho_{o} c_{po}\gamma_{T}  \Bigg(  T_{o} -T_{f}(S_{o},p_{o})  \Bigg)
%\end{equation}
%where $T_{o}$, $S_{o}$, $p_{o}$ are the ocean mixed layer temperature, salinity and pressure.  $T_{f}(S_{ml}, p_{ml})$ is the salinity and pressure dependent freezing point of sea water at salinity $S_{o}$ and pressure $p_{o}$. $\gamma_{T}$ is the turbulent transfer coefficient given by
%\begin{equation}
%\gamma_{T}=\frac{1}{\Gamma_{Turb} +\Gamma^{T}_{Molec}}
%\end{equation}

\section{Appendix B}
\subsection{Modified Verlet Algorithm}
The LIISM model uses a version velocity verlet algorithm, which has been modified to allow part of the forcing to be calculated implicitly. The traditional velocity verlet algorithm is commonly used in molecular dynamics, as it is simple to implement, second order accurate and computationally efficient \citep{Swope1982, Omelyan2002}.
Here we modify the tradition scheme to allow for the drag forces to be modeled implicitly, which prevents large accelerations for element's whose mass approaches zero. 
To do this, we modify the traditional verlet algorithm to include both an implicit and explicit acceleration, $a(t)=a_{exp}(t)+a_{imp}(t)$. The explicit acceleration, $a_{exp}(t)$ includes all forcing terms which depend only on the previous time step, while the implicit acceleration, $a_{imp}(t)$  includes forcing terms which depend on the current time step (in particular the drag and Coriolis forces).

%1) $ x(t_{n+1}) = x(t_{n}) + u(t_{n}) \Delta t  + \frac{1}{2} \Delta t^{2} a(t_{n}) $.\\
%2) Calculate $a(t_{n+1})$\\
%3) $u(t_{n+1}) = u(t_{n}) + \frac{\Delta t}{2} \Bigg(a(t_{n}) + a(t_{n+1}) \Bigg)$\\
%Note that in step 2, $a(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other quantites evaluated at time $t_{n}$.

Using a time step of $\Delta t$ and the notation $t_{n+1}= t_{n} + (\Delta t)$, the modified velocity verlet scheme can be written as:\\
1) $ x(t_{n+1}) = x(t_{n}) + u(t_{n}) \Delta t  + \frac{1}{2} \Delta t^{2} \Bigg(a_{exp}(t_{n}) + a_{imp}(t_{n} )\Bigg) $.\\
2) Calculate $a_{exp}(t_{n+1})$ and  $a_{imp}(t_{n+1})$\\
3) $u(t_{n+1}) = u(t_{n}) + \frac{\Delta t}{2} \Bigg(a_{exp}(t_{n}) + a_{exp}(t_{n+1}) \Bigg) +  (\Delta t) a_{imp}(t_{n+1})$\\
This scheme reduces to the traditional velocity verlet when $a_{imp}$ is set to zero. Note that at step 2, $a_{exp}(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other qualities evaluated at time $t_{n}$, while $a_{imp}(t_{n+1})$ additionally depends on $u(t_{n+1})$ (and needs to be solved implicitly). For this reason, steps 2 and 3 need to be solved simultaneously, as described in the next section.

 In equation (1), the forces due to ocean drag, atmospheric drag and sea ice drag are treated implicitly. The force due to sea surface slope and wave radiation are treated explicitly. The Coriolis term is handled using Crank-Nicolson scheme so that half of the effect is implicit and half is explicit. The elastic part of the interactive forces is treated explicitly, while the interactive damping is handled semi-implicitly in that the drag force on element A by element B depends on the velocity of elements A and B evaluated at time $t_{n+1}$ and $t_{n}$, respectively.

 %A full description of how the scheme is implemented is provided below.

 \subsection{Solving for the velocity implicitly}
Since this modified scheme contains some forcing terms which are handled implicitly, steps 2 and 3 need to be solved together.  We demonstrate how this is done, using a simplified one-dimensional version of equation (1), neglecting the atmospheric drag, sea ice drag and Coriolis force, so that the only implicitly treated term is the ocean drag. We also define an explicit force $F_{exp}$, which accounts for all forces not proportional the element velocity. With these simplifications, the implicit and explicit accelerations are
 \begin{equation}
a_{exp} =\frac{1}{M} ( \vec{F}_{exp} )
\end{equation}
 \begin{equation}
a_{imp} =\frac{1}{M} (F_{W})
\end{equation}
The ocean drag force at time $t_{n+1}$ is modeled (mostly) implicitly as 
\begin{equation}
\label{eq:Drag}
F_{W}(t_{n+1}) = c_{w} |u_{w}(t_{n}) -u(t_{n}) | (u_{w}(t_{n}) -u(t_{n+1}) )  
\end{equation}
%The consequences of the drag not being fully implicit are discussed below. 
Step 3 of the modified velocity verlet scheme can be rewritten by introducing an intermediate velocity $u^{*}$, which only depends on the velocity and acceleration at time $t_{n}$,
 \begin{equation}
 u^{*}(t_{n}) =  u(t_{n})  + \frac{1}{2} (\Delta t) a(t_{n}). 
 \end{equation}
Using this, the updated velocity (Step 3) can be written 
 %\begin{equation}
 %x(t_{n+1}) = x(t_{n}) + v^{*}(t_{n}) \Delta t 
 % \end{equation}
 \begin{equation}
u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2} a_{exp}(t_{n+1})+  (\Delta t) a_{imp}(t_{n+1}).
 \end{equation}

Including the forcing terms into this equations gives
 \begin{equation}
u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}     \Bigg(  c_{w} |u_{w}(t_{n}) -u(t_{n}) | (u_{w}(t_{n}) -u(t_{n+1}) )   \Bigg)
 \end{equation}
Solving for $u(t_{n+1})$ in terms of quantities which only depend on the previous time step gives
 \begin{equation}
u(t_{n+1}) = \frac{u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}    \Bigg(  c_{w} |u_{w}(t_{n}) -u(t_{n}) | (u_{w}(t_{n}) )   \Bigg)}{  \Bigg( 1+  \frac{\Delta t}{M}       c_{w} |u_{w}(t_{n}) -u(t_{n}) |    \Bigg)}
 \end{equation}
Once the $u(t_{n+1})$  has been found, it can be used to calculated the explicit and implicit accelerations, which are required for the next time step.

Finally, we note that the the drag term (equation \ref{eq:Drag}) is not entirely implicit, since the element velocity inside the absolute value is evaluated at time $t_{n}$, rather than at time $t_{n+1}$. This is done so that we can solve for the updated velocity exactly. One consequence of this is that it gives rise to a small oscillation in the element velocity. This oscillation is addressed by using a predictive corrective scheme: once you have solved for a first guess of the velocity at time $t_{n+1}$, this estimate of the velocity is used to update the estimate of the drag force (i.e.: inside the absolute value signs). Using the updated drag, you can now repeat the process described above to find an improved estimate of the velocity. We found that two iterations were sufficient to remove the unwanted oscillation.

The procedure described in this section is easily extended to include more forcing terms and two dimensions (where it involves inverting a $2 \times 2$ matrix).

\section{Appendix C}
\textbf{Connecting bonds across processor boundaries}\\
When a bonded element moves off the edge of a processor, the bond needs to be broken. When the element is copied into the halo of the processor, the bond needs to be reconnected.., and then reconnected when the element is copied back

 The basics of the bond bookkeeping work as follows. Consider an element A and an element B that are bonded together. As mentioned above, each element has a copy of the bond which is stored with the element. Let A-B be the bond stored by element A, and B-A be the bond stored by element B. Bond A-B contains a pointer which points to element B and bond B-A contains a pointer which points to element A.

Consider a situation where element A and B are originally on Processor 1, and then element B moves to Processor 2. When this occurs, the memory assigned to element B on processor 1 is removed, and is allocated on Processor 2. This means that the pointer to element B in bond A-B (stored in element A on Processor 1) is no longer assigned. Similarly, the pointer to element A in bond B-A (stored in element B on Processor 2) is no longer assigned. Before the next time step, a halo update occurs, so that the there is a copy of element A in the halo of Processor 2 and a copy of element B in the halo of Processor 1. After the halo update, the bonds A-B and B-A have to be reconnected on both Processor 1 and 2. To aid in reconnecting the bonds, a copy of the grid cell number of element B is stored in the bond A-B and a copy of the grid cell number of element A is stored in the bond B-A. We refer to this as the `most recent address'. Before a bond is moved from one processor to another, the `most recent address' is updated, so that the bond can be reconnected later. To reconnect bond A-B on Processor 1 (for example), we find the most recent address of element B, and search through the list of elements in the grid cell corresponding to the most recent address of element B until element B is found. The pointer to element B in bond A-B is reassigned and the bond is said to be connected.

Once all bonds are reconnected, a bond quality control is done where we loop through all bonds and check that they are working properly. To check that a bond is working properly is a four step process. For example, consider the bond A-B stored in element A on Processor 1. To check the quality of this bond A-B, we use the following four steps:
\begin{enumerate}
\item Check that the pointer to element B is assigned on bond A-B (stored on element A).
\item Check that the corresponding bond B-A exists on element B.
\item Check that a pointer to element A exists in this bond B-A.
\item Check that the element A which is being pointed to is the same element A where you started.
\end{enumerate}
All four of these tests must pass in order to make sure that the memory is correctly assigned. A useful tool in this process is that each element is assigned a unique number so that elements are easily identified.

\clearpage

\section{Possibly add}
\subsection{Lagrangian sea ice mode}
The addition of interactive forces between elements, means that the LIISM model can be used as a Lagrangian sea ice model, following [Li et al, 2014]. In this formulation, each element represents a collection of sea ice flows.

\subsection{Orientation}
We can get the orientation of iceberg by considering the bonds that they form.

\subsubsection{DEM vs SPH}
Note that there is some ambiguity in the literature about the definition of a Discrete Element Model. In one view, to qualify as a Discrete Element Model since we do not evolve the angular momentum of the elements. 
Since elements are allows to overlap briefly, this method could be considered an example of a Smooth Particle Hydrodynamics model. 
This same repulsive force is similar to that used by  [Li et al] in the context of sea ice interactions.

\newpage
\begin{thebibliography}{9}
\expandafter\ifx\csname natexlab\endcsname\relax
  \def\natexlab#1{#1}\fi
\expandafter\ifx\csname selectlanguage\endcsname\relax
  \def\selectlanguage#1{\relax}\fi
%
\bibitem[Asay-Davis et al (2016)]{Asay-Davis2016}
Asay-Davis, X. S., S. L. Cornford, B. K. Galton-Fenzi, R. M. Gladstone, G. H. Gudmundsson, D. M. Holland, P. R. Holland, and D. F. Martin (2016), Experimental design for three interrelated marine ice sheet and ocean model intercomparison projects: MISMIP v. 3 (MISMIP+), ISOMIP v. 2 (ISOMIP+) and MISOMIP v. 1 (MISOMIP1). {\it Geoscientific Model Development} 9, no. 7: 2471.
%
\bibitem[Arrigo et al (2002)]{Arrigo2002}
Arrigo, K. R., G. L. van Dijken,  D. G. Ainley, M. A. Fahnestock, and T. Markus (2002). Ecological impact of a large Antarctic iceberg. {\it Geophys. Res. Let.}, 29(7).

\bibitem[Alley et al (2008)]{Alley2008}
Alley, R. B., H. J. Horgan, I. Joughin, K. M. Cuffey, T. K. Dupont, B. R. Parizek, S. Anandakrishnan, and J. Bassis (2008), A simple law for ice-shelf calving. {\it Science} 322, no. 5906, 1344-1344.

\bibitem[Bassis and Jacobs (2013)]{Bassis2013}
Bassis, J. N., and S. Jacobs (2013), Diverse calving patterns linked to glacier geometry. {\it Nature Geoscience}, 6(10), 833-836.

\bibitem[Benn et all (2007)]{Benn2007}
Benn, D. I., C. R. Warren, and R. H. Mottram (2007). Calving processes and the dynamics of calving glaciers. {\it Earth-Science Reviews}, 82(3), 143-179.

\bibitem[Bigg et al (1997)]{Bigg1997}
Bigg, G. R., Wadley, M. R., Stevens, D. P., and Johnson, J. A. (1997), Modelling the dynamics and thermodynamics of icebergs. {\it Cold Regions Science and Technology}, 26(2), 113-135.

\bibitem[Biddle et al (2015)]{Biddle2015}
Biddle, L. C., J. Kaiser, K. J. Heywood, A. F. Thompson and A. Jenkins (2015), Ocean glider observations of iceberg-enhanced biological productivity in the northwestern Weddell Sea, {\it Geophys. Res. Lett.}, 42, 459Ð465.

\bibitem[De Rydt and Gudmundsson (2016)]{De_Rydt2006}
De Rydt, J., and G. H. Gudmundsson (2016), Coupled ice shelf?ocean modeling and complex grounding line retreat from a seabed ridge. {\it J. of Geophys. Res.: Earth Surface}, 121(5), 865-880.
%
\bibitem[Dunne et al (2012)]{Dunne2012}
Dunne, J.P., J.G. John,, A.J. Adcroft, S.M. Griffies, R.W. Hallberg, E. Shevliakova, R.J. Stouffer, W. Cooke, K.A. Dunne, M.J Harrison, and J.P. Krasting (2012), GFDL's ESM2 global coupled climate-carbon Earth System Models. Part I: Physical formulation and baseline simulation characteristics. {\it J. of Climate}, 25(19), 6646-6665.
%
\bibitem[Depoorter et al (2013)]{Depoorter2013}
Depoorter, M. A., J. L. Bamber, J. A. Griggs, J. T. M. Lenaerts, Stefan RM Ligtenberg, M. R. van den Broke, and G. Moholdt (2013), Calving fluxes and basal melt rates of Antarctic ice shelves. {\it Nature}, 502(7469), 89-92.

\bibitem[Determan and Gerdes (1994)]{Determan1994}
Determan J.,  Gerdes R. (1994), Melting and freezing beneath ice shelves: implications from a three-dimensional ocean-circulation model. {\it  Ann. Glaciol.}, 20, 413-419.

\bibitem[Dowdeswell and Bamber (2007)]{Dowdeswell2007}
Dowdeswell, J. A., and J. L. Bamber (2007). Keel depths of modern Antarctic icebergs and implications for sea-floor scouring in the geological record. {\it Marine Geology}, 243(1), 120-131.

\bibitem[Eckert (1950)]{Eckert1950}
Eckert, E. R. G. (1950). Introduction to the Transfer of Heat and Mass. McGraw-Hill.

\bibitem[Gladstone et al (2001)]{Gladstone2001}
Gladstone, R. M., G. R. Bigg, and K. W. Nicholls. (2001), Iceberg trajectory modeling and meltwater injection in the Southern Ocean (1978Ð2012). {\it J. of Geophys. Res.: Oceans}, 106(C9), 19903-19915.

\bibitem[Goldberg et al (2012)]{Goldberg2012}
Goldberg, D. N., C. M. Little, O. V. Sergienko, A. Gnanadesikan, R. Hallberg, and M. Oppenheimer (2012), Investigation of land ice?ocean interaction with a fully coupled ice?ocean model: 1. Model description and behavior. {\it J. of Geophys. Res.: Earth Surface}, 117(F2).
%
\bibitem[Gladish et al (2012)]{Gladish2012}
Gladish, C. V., D. M. Holland, P. R. Holland, and S. F. Price (2012), Ice-shelf basal channels in a coupled ice/ocean model. {\it J. of Glaciol.}, 58(212), 1227-1244.

\bibitem[Grosfeld et al (1997)]{Grosfeld1997}
Grosfeld K., R. Gerdes, J. Determan (1997), Thermohaline circulation and interaction between ice shelf cavities and the adjacent open ocean. {\em J. Phys. Oceanogr.,  \textbf{102}, C7, 15959-15610}.

\bibitem[Grosfeld and SandhŠger (2004)]{Grosfeld2004}
Grosfeld, K., and H. SandhŠger, (2004). The evolution of a coupled ice shelfÐocean system under different climate states. {\it Global and Planetary Change}, 42(1), 107-132.

\bibitem[Holland and Jenkins (2001)]{Holland2001}
Holland D. M.,  Jenkins A. (2001), Adaptation of an isopycnic coordinate ocean model for the study of circulation beneath ice shelves. {\it Mon. Wea. Rev}., 129, 1905-1927.

\bibitem[Holland and Feltham (2006)]{Holland2006}
Holland P. R. and  D. L. Feltham (2006), The effects of rotation and ice shelf topography on frazil-laden Ice Shelf Water plumes. {\it  J. Phys. Oceanogr.,}  36, 2312-2327.

\bibitem[Holland and Jenkins (1999)]{Holland1999}
Holland, D. M., and A. Jenkins (1999), Modeling thermodynamic ice-ocean interactions at the base of an ice shelf. {J. of Phys. Oceanogr.} 29.8, 1787-1800.

\bibitem[Hellmer and Olbers (1989)]{Hellmer1989}
Hellmer H.H.,  Olbers D. J. (1989), A two-dimensional model for the thermohaline circulation under an ice shelf. {\it  Antarctic Science},  1, 325- 336.

\bibitem[Jakobsen (2001)]{Jakobsen2001}
Jakobsen, T. (2001). Advanced character physics. {\it In Game Developers Conference}, Vol. 3.

\bibitem[Jenkins et al (2010)]{Jenkins2010}
Jenkins, A., P. Dutrieux, S. S. Jacobs, S. D. McPhail, J. R. Perrett, A. T. Webb, and D. White (2010), Observations beneath Pine Island Glacier in West Antarctica and implications for its retreat. {it Nature Geo.}, 3(7), 468-472.

\bibitem[Jacobs et al (2011)]{Jacobs2011}
Jacobs, S. S., A. Jenkins, C. F. Giulivi, and P. Dutrieux (2011). Stronger ocean circulation and increased melting under Pine Island Glacier ice shelf. {Nature Geo.}, 4(8), 519-523.

\bibitem[Jongma et al (2009)]{Jongma2009}
Jongma, J. I., E. Driesschaert, T. Fichefet, H. Goosse, and H. Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104Ð113.

\bibitem[Lewis and Perkin (1986)]{Lewis1986}
Lewis E.L. and R.G. Perkin (1986), Ice pumps and their rates. {\it J. of Geophys. Res.}, 91, 11756-11762.

\bibitem[Losch (2008)]{Losch2008}
Losch, M. (2008). Modeling ice shelf cavities in az coordinate ocean general circulation model. {\it J. of Geophys. Res.: Oceans}, 113(C8).

\bibitem[Li et al (2014)]{Li2014}
Li, B., H. Li, Y. Liu, A. Wang and S. Ji (2014), A modified discrete element model for sea ice dynamics. {\it Acta Oceanologica Sinica}, 33(1), 56-63.

\bibitem[Lichey and Hellmer (2001)]{Lichey2001}
Lichey, C., and H. H. Hellmer (2001). Modeling giant-iceberg drift under the influence of sea ice in the Weddell Sea, Antarctica. {\it J. of Glaciol.}, 47(158), 452-460.

\bibitem[Levermann et al (2012)]{Levermann2012}
Levermann, A., T. Albrecht, R. Winkelmann, M. A. Martin, M. Haseloff, and I. Joughin. (2012), Kinematic first-order calving law implies potential for abrupt ice-shelf retreat. {\it The Cryosphere}, 6(2), 273-286.

\bibitem[Martin and Adcroft (2010)]{Martin2010}
Martin, T., and Adcroft, A. (2010), Parameterizing the fresh-water flux from land ice to ocean with interactive icebergs in a coupled climate model. {\it Ocean Modelling}, 34(3), 111-124.
%
\bibitem[Marsh et al (2015)]{Marsh2015}
Marsh, R., V. O. Ivchenko, N. Skliris, S. Alderson, G. R. Bigg, G. Madec, A. T. Blaker  Y. Aksenov, B. Sinha, A.C. Coward, and J.L. Sommer (2015), NEMOÐICB (v1. 0): interactive icebergs in the NEMO ocean model globally configured at eddy-permitting resolution. {\it Geoscientific Model Development} 8, no. 5 (2015): 1547-1562.

\bibitem[MacAyeal (1984)]{MacAyeal1984}
MacAyeal D.R. (1984), Thermohaline Circulation Below the Ross Ice Shelf: A Consequence of Tidally Induced Vertical Mixing and Basal Melting. {\it J. Geophys. Res.}, 89, 597-606 
%
\bibitem[Nicholls (1996)]{Nicholls1996}
Nicholls K.W. (1996), Temperature variability beneath Ronne Ice Shelf, Antarctica, from thermistor cables. {\it J. Phys. Oceanogr.},  11, 1199-1210.
%
\bibitem[Nicholls et al (2009)]{Nicholls2009}
Nicholls KW, {\O}sterhus S, Makinson K (2009), Ice-Ocean processes over the continental shelf of the southern Weddell Sea, Antarctica: a review. {\it Rev. Geophys.} 47(3).

\bibitem[Omelyan et al (2002)]{Omelyan2002}
Omelyan, I. P., M. I. Mryglod, and R. Folk (2002), Optimized Verlet-like algorithms for molecular dynamics simulations. {\it Physical Review E}, 65(5), 056706.

\bibitem[Rignot et al (2013)]{Rignot2013}
Rignot, E., S. Jacobs, J. Mouginot, and B. Scheuchl (2013), Ice-shelf melting around Antarctica. {\it Science}, 341, no. 6143 (2013): 266-270.

\bibitem[Robinson et al (2012)]{Robinson2012}
Robinson, N. J., M. J. M. Williams, P. J. Barrett, and A. R. Pyne (2010), Observations of flow and ice-ocean interaction beneath the McMurdo
Ice Shelf, Antarctica, {\it J. Geophys. Res.}, 115, C03025

\bibitem[Sergienko (2013)]{Sergienko2013}
Sergienko, O. V. (2013). Basal channels on ice shelves. {\it J. of Geophys. Res.: Earth Surface}, 118(3), 1342-1355.

\bibitem[Silva et al (2006)]{Silva2006}
Silva, T. A. M., Bigg, G. R., and Nicholls, K. W. (2006), Contribution of giant icebergs to the Southern Ocean freshwater flux. {J. of Geophys. Res.: Oceans}, 111(C3).

\bibitem[Smith et al (2007)]{Smith2007}
Smith, K., B. Robison, J. Helly, R. Kaufmann, H. Ruhl, H., T. Shaw, and M. Vernet (2007), Free-drifting icebergs: Hotspots of chemical and biological enrichment in the Weddell Sea, {\it Science}, 317, 478Ð482.

\bibitem[Stern et al (2014)]{Stern2014}
Stern, A. A., D. M. Holland,  P. R. Holland, A. Jenkins and J. Sommeria (2014), The effect of geometry on ice shelf ocean cavity ventilation: a laboratory experiment. {\it Experiments in Fluids}, 55(5), 1-19.

\bibitem[Stern et al (2015)]{Stern2015}
Stern, A.A., Johnson, E., Holland, D.M., Wagner, T.J., Wadhams, P., Bates, R., Abrahamsen, E.P., Nicholls, K.W., Crawford, A., Gagnon, J. and Tremblay, J.E. (2015), Wind-driven upwelling around grounded tabular icebergs. {\it J. of Geophys. Res.: Oceans}, 120(8), 5820-5835.

\bibitem[Stern et al (2016)]{Stern2016}
Stern, A. A., A. Adcroft, and O. Sergienko (2016), The effects of Antarctic iceberg calving?size distribution in a global climate model. {\it J. of Geophys. Res.: Oceans}, 121(8), 5773-5788.

\bibitem[Swope et al (1982)]{Swope1982}
Swope, W. C., H. C. Andersen, P. H. Berens, and K. R. Wilson (1982), A computer simulation method for the calculation of equilibrium constants for the formation of physical clusters of molecules: Application to small water clusters. {\it The Journal of Chemical Physics} 76, no. 1, 637-649.

\bibitem[Tournadre et al (2016)]{Tournadre2016}
Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. RŽmy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.

\bibitem[Vernet et al (2012)]{Vernet2012}
Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38Ð39

\bibitem[Weeks and Campbell  (1973)]{Weeks1973}
Weeks, W. F., and  W. J. Campbell (1973). Icebergs as a fresh-water source: an appraisal. {\it J. of Glaciol.}, 12(65), 207-233.

\end{thebibliography}

 \clearpage
 \end{article}

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp_layers}
\caption{ {Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
%FIgure created by \end{center}
\end{center}
\label{fig:Calving_fixed_side}
\end{figure}
  \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp}
\caption{ {Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Calving_fixed_top}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Diagrams/Interactive forces.pdf}
%\caption{ {Schematic of interactive forces}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:Interactive_forces}
%\end{figure}
 %\clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Regular_towards_coast}
\caption{ {Positions of ice elements at time t=0, 200, 400, 600 days for the simulation. The size of the dots shows the surface area (and interaction diameter) of each ice element. Land points are shown by black circles. }}
\end{center}
%FIgure created by \end{center}
\label{fig:Regular_Uncoupled_sim}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Tabular_and_regular_towards_coast_manual}
\caption{ {Positions of ice elements at time t=0, 300, 600, 900 days for the simulation. The size of the dots shows the surface area (and interaction diameter) of each ice element. Bonds between ice elements are plotted in magenta. Three tabular icebergs are shown, with 25, 16 and 4 elements respectively. Land points are shown by black circles. }}
\end{center}
%FIgure created by \end{center}
\label{fig:Uncoupled_sim}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
\caption{ {(a) Intersection of hexagonal element and ocean grid is used to find weights to spread LIISM properties to the ocean grid. (b) Hexagonal elements are initialized in a staggered lattice as shown. Adjacent elements are bonded together. The centers of bonded elements are plotted in pink. The element bonds form equilateral triangles which give the larger structure rigidity. The black circles shows to the interactive length scales used in element interactions.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Hex_intersections}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_D_spread_mass_mass.png}
\caption{ {(a) Ocean bottom topography in ISOMIP configuration. (b) Ice shelf draft used in static shelf experiment. The ice draft is calculated from the ice mass in an ocean grid cell, which is found by spreading ice mass across ocean cells accounting for the size of each element (as explained in Section ?). (c) Same as in panel (b), except that the interpolation does not account for iceberg size, and instead treats elements as point masses.}}
\end{center}
%FIgure created by \end{center}
\label{fig:ISOMIP_exp}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
\caption{ {Results of the static ice shelf experiment using the LIISM model. The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
\end{center}
%FIgure created by \end{center}
\label{fig:static_solo_melt}
\end{figure} 
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
\caption{ {Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
\end{center}
%FIgure created by \end{center}
\label{fig:Bt_comparison}
\end{figure}
 \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/melting_shelf_temp_layers.png}
%\caption{ {Temperature section at $y=\frac{L_{y}}{2}$ for the decaying ice shelf simulation (using the LIISM ice shelf) at time (a) t=0, (b) t=100(?), (c) t=200 days. As the ice shelf melts, it decays and the pressure at the ocean surface decreases. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:Decaying_shelf}
%\end{figure}

%\clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_salt_layers.png}
\caption{ {Calving of tabular iceberg with the LIISM model fully coupled to the ocean for simulations with and without bonds between ice elements. The top row show the aveage draft of ice above the ocean in each grid cell for the simulation (a) with and (b) without bonds. The bottom row shows the corresponding temperature section at $y=\frac{L_{y}}{2}$ for the simulation (a) with and (b) without bonds.  All snapshots are taken at time t= 30 days.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Bond_vs_No_bond}
\end{figure}

  \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_spread_area.png}
%\caption{ {Need to update this Figure. Also, I should try using orientation with the Bonds.}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

% \clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_salt_layers.png}
%\caption{ {}}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

%\clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_u_layers.png}
%\caption{ {Need to update this Figure. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}

%\clearpage

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_v_layers.png}
%\caption{ {Need to update this Figure. }}
%\end{center}
%FIgure created by \end{center}
%\label{fig:}
%\end{figure}
\clearpage
\section{Supplementary Figures}
\clearpage

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_salt_layers.png}
\caption{ {Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model salinity fields.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Salt_comparison}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_melt.png}
\caption{ {Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model melt fields.}}
\end{center}
%FIgure created by \end{center}
\label{fig:Melt_comparison}
\end{figure}
 \clearpage

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_vo_uo_sst.png}
\caption{ {Results of the static ice shelf experiment using the LIISM model. The three panels show 5 year time average of the (a) meridional velocity, (b) zonal velocity and (c) ocean temperature in the top layer of the simulation (at the surface or directly below the ice shelf).}}
\end{center}
%FIgure created by \end{center}
\label{fig:static_solo}
\end{figure} 
 \clearpage

 \end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-01-17 Tech1.tex

@@
 \subsection{MISOMIP configuration}
-In order for our simulations to be easily comparable to previous models of ice shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
+In order for our (pre-calving) simulations to be easily comparable to previous models of ice shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
 %For this experiment, we use the ice shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
@@
 Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
-The simulation is initially at rest, with horizontally uniform initial ocean temperature and salinity profiles that vary linearly between specified surface and bottom values.
+The simulation is initially at rest, with horizontally uniform initial ocean temperature  (Figure \ref{fig:static_solo_temp_temp_v}a) and salinity profiles that vary linearly between specified surface and bottom values.
 The initial surface temperature and salinity are  $T_{t}=-1.9^{\circ}$C and $S_{t}=33.8$ psu, respectively.
@@
 Ice elements in the LIISM model are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
-The apothem of the hexagons is initially set to $A=0.85$ km.
+The apothem of the gridded hexagons are initially set to $A=0.85$ km.
 Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2A<\Delta x$).
-The initial mass of the ice elements is determined by preprocessing inversion, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
-Boundary points are filled in using extra ice elements of appropriate thickness.
-
-When the model is run, the average ice draft in an ocean grid cell, is calculated from the total mass of ice elements in that grid cell by assuming that the ice elements are in hydrostatic balance.
-The total mass is found by summing up over all ice elements located in that grid cell, while allowing elements to spread their mass across neighboring grid cells (as discussed in Section 2.3).
-Figure \ref{fig:ISOMIP_exp}b shows the draft of the ice shelf above the ice shelf cavity in the coupled static ice shelf simulation using this interpolation method, while Figure \ref{fig:ISOMIP_exp}c shows the draft which is calculated without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
+Gaps along the boundary are filled in with using smaller elements so that the total ice shelf area is preserved.
+The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
+
+Figure \ref{fig:ISOMIP_exp}c shows what the ice shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
+Figure \ref{fig:ISOMIP_exp}b shows the draft after spreading the mass across grid cells.
 When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_exp}c).
 The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_exp}b).
-In simulations without mass spreading, irregularities in ice draft cause irregularities in the ocean surface pressure, which cause spurious motion in the ocean (not shown).
-This is much reduced or absent when mass spreading is used.
 
@@
 
-The tabular iceberg simulations are initialized using the final ocean state of the static ice shelf experiment.
+The tabular iceberg simulations are initialized using the ocean state from the end of the static ice shelf experiment (after 5 years).
 For these situations, all ice elements initially within a 15km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held are stationary.
@@
 \section{Results}
+
+%\subsection{Mass spreading}
+%When the model is run, the average ice draft in an ocean grid cell, is calculated from the total mass of ice elements in that grid cell by assuming that the ice elements are in hydrostatic balance.
+The total mass is found by summing up over all ice elements located in that grid cell, while allowing elements to spread their mass across neighboring grid cells (as discussed in Section 2.3).
+Figure \ref{fig:ISOMIP_exp}b shows the draft of the ice shelf above the ice shelf cavity in the coupled static ice shelf simulation using this interpolation method, while Figure \ref{fig:ISOMIP_exp}c shows the draft which is calculated without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
+When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_exp}c).
+The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_exp}b).
+In simulations without mass spreading, irregularities in ice draft cause irregularities in the ocean surface pressure, which cause spurious motion in the ocean (not shown).
+This is much reduced or absent when mass spreading is used.
 
@@
 \begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_temp_temp_v.png}
+\caption{ {Results of the static ice shelf experiment using the LIISM model.
+Panels show a cross section of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field, and  (c) meridional velocity after 5 years of simulation.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:static_solo_temp_temp_v}
+\end{figure} 
+ \clearpage
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
@@
 
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_vo_uo_sst.png}
+%\caption{ {Results of the static ice shelf experiment using the LIISM model.
+The three panels show 5 year time average of the (a) meridional velocity, (b) zonal velocity and (c) ocean temperature in the top layer of the simulation (at the surface or directly below the ice shelf).}}
+%\end{center}
+%\label{fig:static_solo}
+%\end{figure} 
+ %\clearpage
+
+ \section{ALE versions}
+
  \begin{figure}
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_vo_uo_sst.png}
-\caption{ {Results of the static ice shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) meridional velocity, (b) zonal velocity and (c) ocean temperature in the top layer of the simulation (at the surface or directly below the ice shelf).}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
+\caption{ {ALE z , Results of the static ice shelf experiment using the LIISM model.
+Panels show a cross section of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field, and  (c) meridional velocity after 5 years of simulation.}}
 \end{center}
 %FIgure created by \end{center}
-\label{fig:static_solo}
+\label{fig:static_solo_temp_temp_v}
 \end{figure} 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+\caption{ {ALE Results of the static ice shelf experiment using the LIISM model.
+The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:static_solo_melt}
+\end{figure} 
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
+\caption{ {ALE Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Bt_comparison}
+\end{figure}
+ \clearpage
+
  \end{document}

### 2017-01-17 Tech1.tex

@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp_layers}
-\caption{ {Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp_layers}
+\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
 %FIgure created by \end{center}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp}
-\caption{ {Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp}
+\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
 \end{center}
@@
 (b) Ice shelf draft used in static shelf experiment.
-The ice draft is calculated from the ice mass in an ocean grid cell, which is found by spreading ice mass across ocean cells accounting for the size of each element (as explained in Section ?).
+The ice draft is calculated from the ice mass in an ocean grid cell, which is found by spreading ice mass across ocean cells accounting for the size of each element (as explained in Section 2.3).
 (c) Same as in panel (b), except that the interpolation does not account for iceberg size, and instead treats elements as point masses.}}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_temp_temp_v.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
 \caption{ {Results of the static ice shelf experiment using the LIISM model.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
 \caption{ {Results of the static ice shelf experiment using the LIISM model.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
-\caption{ {Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
+\caption{ {ALE Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
 \end{center}
@@
 \label{fig:Bt_comparison}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_spread_area.png}
+\caption{ {}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_temp.png}
+\caption{ {}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_melt_m_per_year.png}
+\caption{ {}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
+\caption{ {}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
+\caption{ {}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:}
 \end{figure}
@@
 
- \section{ALE versions}
-
- \begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
-\caption{ {ALE z , Results of the static ice shelf experiment using the LIISM model.
-Panels show a cross section of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field, and  (c) meridional velocity after 5 years of simulation.}}
+ \section{Layer versions}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp_layers}
+\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
+%FIgure created by \end{center}
+\end{center}
+\label{fig:Calving_fixed_side}
+\end{figure}
+  \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp}
+\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Calving_fixed_top}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_temp_temp_v.png}
+\caption{ {Layered: Results of the static ice shelf experiment using the LIISM model.
+Panels show snapshots of cross sections of the (a) temperature field after 1 time step, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity after 5 years.}}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {ALE Results of the static ice shelf experiment using the LIISM model.
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+\caption{ {Layer: Results of the static ice shelf experiment using the LIISM model.
 The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\caption{ {ALE Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
+\caption{ {Layer: Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
 \end{center}

### 2017-01-19 Tech1.tex
More work on manuscript. Looking good

@@
 The LIISM model is coupled to the MOM6 ocean model. 
-The ocean model is run in layered mode, with a horizontal resolution of $\Delta x = 2$ km, and 36 vertical layers. 
-%The ocean model is run in using vertical coordinate system which is a hybrid between a sigma level and a z-level model.
+The ocean model is run in using vertical coordinate system which is a hybrid between a sigma level and a z-level coordinate.
 In particular, model layers bend underneath the ice shelf as they would in a sigma model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
-The coordinate system was achieve using ALE regridding remapping scheme.The model used a horizontal resolution of 2km, and 36 vertical layers.
+The coordinate system was achieve using ALE regridding-remapping scheme.
+The model used a horizontal resolution of 2km, and 36 vertical layers.
+All simulation were repeated using the ocean model is run layered mode (select results are shown in the supplementary material). 
 Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
@@
 
-\subsection{Static ice shelf experiment}
+\subsection{Numerical experiment}
+\begin{enumerate}
+\item
+\textbf{Static ice shelf experiment:}\\
+%\subsection{Static ice shelf experiment}
 In the first experiment, we use a static ice shelf where the velocity of all ice elements is set to zero.
@@
 
-Results of the static ice shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice shelf model \citep{Goldberg2012}, coupled to the same ocean model.
+Results of the static ice shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_exp}b).
 The simulations in the Lagrangian and Eularian are compared after 5 years of models time.
@@
 
- \subsection{Tabular iceberg calving}
-In the next set of experiments, we demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice shelf models.
-These simulations model a large tabular iceberg being calved from the edge of the ice shelf.
-The tabular iceberg drifts in the ocean, submerged in the water column, where it influences the ocean circulation.
-
-The tabular iceberg simulations are initialized using the ocean state from the end of the static ice shelf experiment (after 5 years).
-For these situations, all ice elements initially within a 15km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held are stationary.
-The three tabular iceberg simulations are performed:
-
-\begin{enumerate}
 \item
-\textbf{Tabular iceberg with fixed velocity}:\\
-In this simulation, the velocity of the non-stationary elements is fixed to u=0m/s, v=0.01m/s.
+ \textbf{Tabular iceberg calving:}\\
+% \subsection{Tabular iceberg calving}
+Next, we preform a numerical experiment which demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice shelf models.
+In this experiments we break off a large piece of the the ice shelf and allow it to drift into the ocean as a tabular iceberg.
+
+All ice elements initially within a 14.4 km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held are stationary.
+Ice elements less than 12 km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
+A ring of elements whose distance from the ice front center is $\geq$ 12 km, but $\leq$14.4 km are allowed to move freely, but have all their bonds removed.
+Elements in this half annulus represent fragments of the ice shelf with calve into small pieces during a large calving event, and also allow the giant icebergs to move away from the ice shelf cavity more easily.
+
+A wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice shelf cavity.
+Perturbation experiments were run using other wind stress values.
+In this experiment, the ice is allowed to decay as it melts.
+The tabular iceberg calving experiment is initialized using the ocean state from the end of the static ice shelf experiment (after 5 years).
+
+\end{enumerate}
+
+%\begin{enumerate}
+%\item
+%\textbf{Tabular iceberg with fixed velocity}:\\
+%In this simulation, the velocity of the non-stationary elements is fixed to u=0m/s, v=0.01m/s.
 This simulation allows us to study the response of the ocean to disturbance caused by a tabular iceberg moving through the water (with an fixed velocity).
 This simulation is not fully coupled since the velocity of the elements is prescribed.
-\item
-\textbf{Tabular iceberg with bonded elements}:\\
- All non-stationary ice elements are bonded together by the numerical bonds.
+%\item
+%\textbf{Tabular iceberg with bonded elements}:\\
+ %All non-stationary ice elements are bonded together by the numerical bonds.
 This experiments is fully-coupled in that the ice elements are driven the ocean, and the pressure exerted by the ice elements drives ocean flow.
@@
 .
-\item
-\textbf{Tabular iceberg with unbonded elements}:\\
-This simulation is identical to the bonded elements simulation, except that all the numerical bonds are broken, so that the elements are free to move away from one another.
-\end{enumerate}
+%\item
+%\textbf{Tabular iceberg with unbonded elements}:\\
+%This simulation is identical to the bonded elements simulation, except that all the numerical bonds are broken, so that the elements are free to move away from one another.
+%\end{enumerate}
 
@@
 \subsection{Static ice shelf experiment}
+The LIISM results from the static ice shelf experiment fit well within the current understanding of ice-shelf cavity circulations base on ice shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
+The initial water temperatures inside the domain are warmer than the in-situ freezing point, and cause melting at the ice-shelf base.
+The melt water entering the domain is more buoyant than the water around it, and rises  along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_temp_v}b, c).
+As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_temp_v}b).
+This injection of buoyancy at depth drives a clockwise circulation outside of the ice shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice shelf melt.
+
+The highest melt rates are seen within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
+These elevated melt rates are caused by the presence of of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line.
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice shelf front.
 
 %\subsubsection{Comparison with Eularian ice shelf model}
-\textbf{Comparison of LIISM and Eularian ice shelf model}\\
-The results from coupled ocean-ice simulation in the MISOMIP configuration using LIISM are compared to the results using an Eulerian ice shelf model in the same configuration.
-The ice draft in the Eulerian ice shelf model is initialized using the field shown in Figure \ref{fig:ISOMIP_exp}b.
-Figures \ref{fig:Melt_comparison} show the time-averaged melt rates of both the Lagrangian and Eulerian ice shelf models, averaged over the first 5 years of the simulation.
-
+\textbf{Comparison of LIISM and Eularian ice shelf models}\\
+The LIISM results from the static ice shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
+To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice shelf model using an identical configuration.
+The results show that two simulations have similar circulations (Figures \ref{fig:Bt_comparison}), melt rates and temperature/salinity profiles (see supplementary materials).
+The differences between the barotropic stream function of the two simulations (for example) are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with difference vertical coordinate systems [double check that this is correct].
+
+The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model.
+Recall that the role of the ice shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iiI) alter the upper ocean boundary condition below the ice shelf.
+The agreement agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LIISM model, and that the LIISM is able able to model sub ice shelf cavities as well as the Eularian model does.
+This is a good starting point for moving beyond the capabilities of the Eularian model.
+
+%Figures \ref{fig:Melt_comparison} show the time-averaged melt rates of both the Lagrangian and Eulerian ice shelf models, averaged over the first 5 years of the simulation.
 The melt rates of the Eulerian and Lagrangian models are very similar with slight difference showing up at the grounding line and ice front (Figure \ref{fig:Melt_comparison}).
@@
 
-The small changes in melt at the grounding line and ice front drive slight changes to the circulation beneath the ice shelf, which in turn lead to small difference in the temperature and salinity profiles over time.
+%The small changes in melt at the grounding line and ice front drive slight changes to the circulation beneath the ice shelf, which in turn lead to small difference in the temperature and salinity profiles over time.
 This is seen by comparing the time-averaged ocean salinity profiles for the Lagrangian and Eularian ice shelves (Figure \ref{fig:Salt_comparison} ) and also  by comparing the the time-averaged barotropic stream function of the two simulations (see Figures \ref{fig:Bt_comparison}) and in the supplementary material).
-The differences between the Eularian and Lagrangian simulations are small compared to the wide spread of difference seen in the MISOMIP inter comparison.
-This is unsurprising, since the LIISM and Eularian ice shelves are coupled to the same ocean model and pass similar fields to the ocean model.
-
-The similarity of the Lagrangian and Eulerian ice shelf models shows that the LIISM model coupled to an ocean model is able to model sub ice shelf cavities as well as the Eularian model does.
-This is a good starting point for moving beyond the capabilities of the Eularian model.
 
@@
 \subsection{Tabular iceberg calving}
+The tabular iceberg calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.
+After the iceberg calves (referred to at time t=0 days), the iceberg drifts to the northward east, driven by the wind and steered by the Coriolis force (Figure \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
+After the iceberg has calved away from the ice shelf, we observed a warming of the surface waters near the near the ice front and iceberg edge (Figure \ref{fig:SST_Collapse}).
+This surface warming is caused by an upwelling of the warmer waters from beneath the ice shelf and iceberg.
+As the icebergs drifts away from the ice front, these warmer waters remain in the wake of the iceberg.
+The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color near to tabular iceberg in the Southern Ocean \citep{Duprat2016}, suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface.
+
+The motion of the iceberg disturbs the ocean surface which drives ocean velocities through out the water column \ref{fig:Velocity_section_Collapse}.
+The elevated velocities around the tabular iceberg lead to increased vertical mixing in the vicinity of the iceberg, which alters the stratification of the water column (Figure \ref{fig:Temperature_section_Collapse}).
+
+The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg \ref{fig:Collapse_solo_melt}.
+Large melt rates are observed at the new ice shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving calving has created an ice cliff at the edge of the ice shelf and iceberg.
+These sharp ice fronts allows for large ocean currents (Figure \ref{fig:Collapse_solo_melt}c), which drive the elevated melt rates.
+This will smooth out the ice front over time, and make it less sharp.
+While this is likely a real phenomena that could be observed in the real world, we should be wary of the modeled velocities at ice cliffs, since large changes in ice shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
+
+As mentioned above, the direction (and speed) of the iceberg drift is largely determined by the wind speed and direction.
+Perturbation experiments using different wind stresses showed that the iceberg drifted to the north east for positive zonal and to the north west for negative zonal velocities.
+For wind stresses less that $\tau= ???$ the iceberg did not move away from the ice shelf.
+While this result is partly an artifact of the artificial shape of the calving iceberg, it is also consistent with \citet{Bassis2013} who noted that calving is a two step process consisting of (i) ice shelf breaking and (ii) iceberg detachment.
+The results here suggest that strong wind may be required to drive large tabular icebergs away from their mother glaciers.
+
+Finally, we note that the numerical bond in the LIISM model are in fact needed in order to allow the tabular iceberg to retains its shape.
+Comparing the iceberg calving simulation with an identical simulation with all numerical bonds removed shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
+In this case, the model behavior is more similar to an ice shelf disintegration and does not create a cohesive tabular iceberg.
 
 %\subsubsection{Tabular iceberg with fixed velocity}
-\textbf{Tabular iceberg with fixed velocity}\\
-The fixed iceberg velocity calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.
+%\textbf{Tabular iceberg with fixed velocity}\\
+%The fixed iceberg velocity calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.
 After the iceberg calves, it moves northwards away from the ice shelf with a prescribed velocity.
@@
 %\subsubsection{Fully coupled tabular iceberg}
-\textbf{Fully coupled tabular iceberg}\\
-The necessity of bonds between ice elements is demonstrated by comparing two simulations where an iceberg calves, and is allowed to evolve freely with the flow.
+%\textbf{Fully coupled tabular iceberg}\\
+%The necessity of bonds between ice elements is demonstrated by comparing two simulations where an iceberg calves, and is allowed to evolve freely with the flow.
 In the Bonded simulation, the elements in the calved iceberg are bonded together, while in the Unbonded simulation the all bonds between elements in the tabular iceberg are broken.
@@
 %The motions of elements in the tabular iceberg in these two simulations are rather different. 
-In the Bonded simulation, the ice element in the tabular iceberg remain close to one another, and the tabular iceberg retains its shape (Figure \ref{fig:Bond_vs_No_bond}a,c).
+%In the Bonded simulation, the ice element in the tabular iceberg remain close to one another, and the tabular iceberg retains its shape (Figure \ref{fig:Bond_vs_No_bond}a,c).
 The elements are forced by the melt-water-driven current at the ice front, which moves towards the north-west (see Figure \ref{fig:static_solo} in the supplementary material).
@@
 
-In the Unbonded simulation, the ice elements in tabular iceberg are not constrained to move together.
+%In the Unbonded simulation, the ice elements in tabular iceberg are not constrained to move together.
 Instead, the elements spread out and drift towards the north-west for the same reason discussed above.
@@
  \section{Discussion}
-1) How do we get this into a big coupled climate model - what is still needed? Bond breaking, ice growing
-2) Mention lagrangian sea ice
+In order to accurately project future sea level, it is likely that we will need to develop fully-coupled global general climate models (GCM's) with dynamic ice-shelf cavities which are able to melt, break and interact with the ocean in physically realistic ways.
+In the sections above, we have seen that constructing ice shelves out of Lagrangian elements is a potentially useful method for introducing breakable ice shelves and tabular icebergs into climate models.
+In this section we briefly discuss a few of the things which still need to be done in order to introduce this technology into next generation GCM's.
+
+One element which is missing from the LIISM ice shelf is that the ice shelf is not dynamic.
+Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice shelf geometry to change over time.
+Much progress has been made in modeling ice-shelf flows in an Eularian framework \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
+A challenge will be to develop similar ice dynamics models in a Lagrangian framework.
+This can perhaps be achieved using smooth particle hydrodynamics (SPH) methods, which allow partial differential equations to be solved on a Lagrangian gird \citep{Liu2010, Pan2013}.
+However, it is presently unclear how one would evolve the numerical bonds over time, so the bonds could still be used to hold the ice shelf and tabular icebergs together.
+This may involve performing a regridding of the ice element or a regridding of the numerical bonds after several ice time steps, or perhaps allowing the numerical bonds to break and form in a dynamic way.
+
+The other major innovation which will need to be introduced is a method for breaking numerical bonds.
+This is essentially equivalent to determining a ice shelf calving law, and is a famously difficult problem.
+One possible way that this could be done is to break bonds when the elastic stress in the bond is larger than a given yield stress of that bond.
+The yield stress in the bond would likely be proportional to the ice thickness.
+The bond strength could also evolve dynamically as bonds get `damaged'.
+The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eularian ice shelf studies \citep{Pralong2005, Borstad2012}.
+
+In addition to these two problems, more work needs to be done to determine the interaction between tabular icebergs and sea ice, as the presence of sea ice can arrest the motion of tabular icebergs and the presence of icebergs likely affects sea ice formation and dynamics.
+A possible path towards this is to model sea ice using a Lagrangian grid \citep{Hopkins1996, Li2014}, and to treat sea ice - iceberg interactions in the same way that iceberg - iceberg interactions are treated in this study.
+A number of preliminary experiments have been run using the LIISM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
+Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
+These will need to be considered in order to model the primary productivity around tabular icebergs.
+
+Finally, there are a number of open questions associated with introducing giant tabular icebergs into climate models: (i) how to correctly link tabular icebergs' melt water fluxes to ocean biology, (ii) how to deal with giant calving events in small ensemble simulations where one calving even can skew the ensemble statistics, (iii) how to introduce tabular icebergs into models which do not use a fully dynamic ice sheet, and (iv) how to model iceberg breakup and fracturing.
+These and other questions will need to be answered in order to achieve physically realistic climate models with tabular icebergs and breaking ice shelves.
+
+%How do we grow icebergs?
 
@@
 
+\bibitem[Borstad et al (2012)]{Borstad2012}
+Borstad, C.
+P., A.
+Khazendar, E.
+Larour, M.
+Morlighem, E.
+Rignot, M.
+P.
+Schodlok, and H.
+Seroussi (2012), A damage mechanics assessment of the Larsen B ice shelf prior to collapse: Toward a physically-based calving law, {\it Geophys.
+Res.
+Lett.}, 39, L18502
+
 \bibitem[Biddle et al (2015)]{Biddle2015}
@@
 Res.
-Lett.}, 42, 459Ð465.
+Lett.}, 42, 459–465.
 
@@
 \bibitem[Dowdeswell and Bamber (2007)]{Dowdeswell2007}
-Dowdeswell, J. A., and J. L. Bamber (2007). Keel depths of modern Antarctic icebergs and implications for sea-floor scouring in the geological record. {\it Marine Geology}, 243(1), 120-131.
+Dowdeswell, J. A., and J. L. Bamber (2007), Keel depths of modern Antarctic icebergs and implications for sea-floor scouring in the geological record. {\it Marine Geology}, 243(1), 120-131.
+
+\bibitem[Duprat et al (2016)]{Duprat2016}
+Duprat, L. P., G. R. Bigg, and D. J. Wilton (2016), Enhanced Southern Ocean marine productivity due to fertilization by giant icebergs. {\it Nature Geoscience.}
 
@@
 Nicholls.
-(2001), Iceberg trajectory modeling and meltwater injection in the Southern Ocean (1978Ð2012).
+(2001), Iceberg trajectory modeling and meltwater injection in the Southern Ocean (1978–2012).
 {\it J.
@@
 
-\bibitem[Grosfeld and SandhŠger (2004)]{Grosfeld2004}
-Grosfeld, K., and H. SandhŠger, (2004). The evolution of a coupled ice shelfÐocean system under different climate states. {\it Global and Planetary Change}, 42(1), 107-132.
+\bibitem[Grosfeld and Sandhäger (2004)]{Grosfeld2004}
+Grosfeld, K., and H. Sandhäger, (2004). The evolution of a coupled ice shelf–ocean system under different climate states. {\it Global and Planetary Change}, 42(1), 107-132.
 
@@
 Hellmer H.H.,  Olbers D. J. (1989), A two-dimensional model for the thermohaline circulation under an ice shelf. {\it  Antarctic Science},  1, 325- 336.
+
+\bibitem[Hopkins (1996)]{Hopkins1996}
+Hopkins, M. A. (1996). On the mesoscale interaction of lead ice and floes. {\it J. of Geophys. Res.: Oceans}, 101(C8), 18315-18326.
 
@@
 Goosse, and H.
-Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104Ð113.
+Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104–113.
 
@@
 Li, B., H. Li, Y. Liu, A. Wang and S. Ji (2014), A modified discrete element model for sea ice dynamics. {\it Acta Oceanologica Sinica}, 33(1), 56-63.
+
+\bibitem[Liu and Liu (2010)]{Liu2010}
+Liu, M. B. and G. R. Liu (2010), Smoothed particle hydrodynamics (SPH): an overview and recent developments. {\it Archives of computational methods in engineering}, 17(1), 25-76.
 
@@
 Coward, and J.L.
-Sommer (2015), NEMOÐICB (v1.
+Sommer (2015), NEMO–ICB (v1.
 0): interactive icebergs in the NEMO ocean model globally configured at eddy-permitting resolution.
@@
 Ice Shelf, Antarctica, {\it J. Geophys. Res.}, 115, C03025
+
+\bibitem[Pan et al (2013)]{Pan2013}
+Pan, W.,  A. M. Tartakovsky, and J. J. Monaghan (2013). Smoothed particle hydrodynamics non-Newtonian model for ice-sheet and ice-shelf dynamics. {\it J. of Comp. Phys.}, 242, 828-842.
+
+\bibitem[Pralong and Funk (2005)]{Pralong2005}
+Pralong, A., and M. Funk (2005), Dynamic damage model of crevasse opening and application to glacier calving, {\it J. Geophys. Res.}, 110, B01309.
 
@@
 Shaw, and M.
-Vernet (2007), Free-drifting icebergs: Hotspots of chemical and biological enrichment in the Weddell Sea, {\it Science}, 317, 478Ð482.
+Vernet (2007), Free-drifting icebergs: Hotspots of chemical and biological enrichment in the Weddell Sea, {\it Science}, 317, 478–482.
 
@@
 \bibitem[Tournadre et al (2016)]{Tournadre2016}
-Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. RŽmy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.
+Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. Rémy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.
 
 \bibitem[Vernet et al (2012)]{Vernet2012}
-Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38Ð39
+Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38–39
 
@@
  \end{article}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp_layers}
-\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-%FIgure created by \end{center}
-\end{center}
-\label{fig:Calving_fixed_side}
-\end{figure}
-  \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp}
-\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:Calving_fixed_top}
-\end{figure}
- \clearpage
 
@@
 \caption{ {Results of the static ice shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
+The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation at the base of the ice shelf.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_spread_area.png}
-\caption{ {}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
+\caption{ {Fraction of grid cell covered by ice (using the LIISM ice shelf) (a) t=15, (b) t=30, and (c) t=60 days after calving.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Spread_area}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
+\caption{ {Temperature section at $x=70 $km for the tabular iceberg calving simulation (a) t=15, (b) t=30, and (c) t=60 days after calving.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Temperature_section_Collapse}
 \end{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_temp.png}
-\caption{ {}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_melt_m_per_year.png}
-\caption{ {}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
+\caption{ {Sea surface temperature for the tabular iceberg calving simulation (a) t=15, (b) t=30, and (c) t=60 days after calving. Regions with ice area fraction = 1 area plotted in white.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:SST_Collapse}
 \end{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
+\caption{ {Meridional velocity section at $x=70 $km for the tabular iceberg calving simulation (a) t=15, (b) t=30, and (c) t=60 days after calving.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Velocity_section_Collapse}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg_calved.png}
+\caption{ {Results of the tabular iceberg calving simulation 60 days after the iceberg calves.
+The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$ at the base of the ice shelf.
+Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Collapse_solo_melt}
 \end{figure}
@@
 %\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%                       Supplementary Figures                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage
@@
 %FIgure created by \end{center}
-\label{fig:Salt_comparison}
+%\label{fig:Salt_comparison}
 \end{figure}
@@
 %FIgure created by \end{center}
-\label{fig:Melt_comparison}
+%\label{fig:Melt_comparison}
 \end{figure}
@@
 
+ \begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp_layers}
+\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
+%FIgure created by \end{center}
+\end{center}
+%\label{fig:Calving_fixed_side}
+\end{figure}
+  \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp}
+\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
+\end{center}
+%FIgure created by \end{center}
+%\label{fig:Calving_fixed_top}
+\end{figure}
+ \clearpage
+
  \section{Layer versions}
@@
 \end{center}
-\label{fig:Calving_fixed_side}
+%\label{fig:Calving_fixed_side}
 \end{figure}
@@
 %FIgure created by \end{center}
-\label{fig:Calving_fixed_top}
+%\label{fig:Calving_fixed_top}
 \end{figure}
@@
 %FIgure created by \end{center}
-\label{fig:static_solo_temp_temp_v}
+%\label{fig:static_solo_temp_temp_v}
 \end{figure} 
@@
 %FIgure created by \end{center}
-\label{fig:static_solo_melt}
+\label{fig:}
 \end{figure} 
@@
 %FIgure created by \end{center}
-\label{fig:Bt_comparison}
+%\label{fig:Bt_comparison}
 \end{figure}

### 2017-01-25 Tech1.tex
Changes to matlab scripts, matlab figures and Text

@@
 Iceberg calving can significantly alter the geometry of an ice shelf cavity, potentially affecting the circulation within the cavity.
-Furthermore, giant icebergs which break away can drift across large distance, altering ocean circulation, sea ice distributions and bottom water formation.
-However the despite its importance, the current generation of numerical models is unable to represent this process in a physically realistic way.
+Giant icebergs which break away can drift across large distance, altering regional ocean circulation, sea ice distributions and bottom water formation.
+However, despite its importance, the current generation of numerical models is unable to represent this process in a physically realistic way.
 In this study we develop a model of an ice shelf cavity using a Lagrangian ice shelf.
@@
 To test the model, the LIISM is used to model an idealized ice shelf cavity which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-Results from static ice shelf experiments compare well to results using a more traditional Eularian ice shelf cavity.
+Results from static ice shelf experiments compare well to results using a more traditional Eularian ice shelf modles.
 The novel capabilities of the  LIISM are demonstrated by modeling a tabular iceberg breaking away from the idealized ice shelf.
@@
 In addition to suppressing the depth of ocean surface, the ice shelves also melt (and break), thus providing a freshwater flux into the ice shelf cavities. 
-Ice shelf melting and breaking are key components in the Antarctic meltwater system, and affect the ocean hydrography and biology both inside and outside of the ice shelf cavities.
-Some elements of the this Antarctic meltwater system are discussed in the following paragraphs.
-
+%Perhaps remove this line....:
+This melting and breaking of Antarctic ice shelves is a key component in the Antarctic meltwater system.
+%, and affect the ocean hydrography and biology both inside and outside of the ice shelf cavities. %Some elements of this Antarctic meltwater system are discussed in the following paragraphs. 
+%
 Within the ice shelf cavities, the input of buoyant meltwater into the ocean creates rising density plumes, which are guided along the ice shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
@@
 Melt water injection (and the accompanying upwelling) from ice shelves and icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}.
-The increased productivity associated with free floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.
+The increased productivity associated with free-floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.
 %either increasing it by providing nutrients to the surface ocean, or decreasing by changing sea ice conditions
@@
 
-The earliest models of ocean ice shelf cavities were developed using a static ice shelf with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
+The earliest models of ocean ice shelf cavities were developed using a static ice shelves with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
 In these models, ice shelf melting was represented through salinity and temperature fluxes, while the ice shelf geometry remained unchanged.
@@
 To do this, we create an ice shelf model out of Lagrangian elements which are `bonded' together by numerical bonds.
-In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break' away from an existing ice shelf, thus changing the geometry of the ice shelf cavity.
-Modeling iceberg calving in a physically consistent way allows us to study the ocean response to iceberg detachment (see Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top}, for example).
+In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break away' from an existing ice shelf, thus changing the geometry of the ice shelf cavity.
+Modeling iceberg calving in a physically consistent way allows us to study the ocean response to iceberg detachment.
+%(see Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top}, for example).  
 Also, by allowing icebergs protrude deep into the water column we can study the ocean dynamics around individual tabular icebergs (which was not possible in iceberg drift models).
 
-%Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top} show an example of a tabular icebergs detaching from an idealized ice shelf.
-As the icebergs moves away from the ice shelf, it perturbs the water column.
-Details of this simulation are described further in Sections 3 and 4.
 In all simulation in this study, the shape of the calving iceberg is prescribed.
 The question of how to correctly prescribe a calving law is undoubtably a very important question, which has rightfully received much attention in recent years \citep{Benn2007, Alley2008, Levermann2012}.
-\citet{Bassis2013}, for example, used a DEM model to study the generation and propagation of cracks within an ice shelf (not coupled to a dynamic ocean model).
+\citet{Bassis2013}, for example, used a discrete element model (DEM) model to study the generation and propagation of cracks within an ice shelf (not coupled to an ocean model).
 In this study, we bypass the question of how to correctly calve icebergs or break bonds.
-Instead we focus on developing a framework to model the ocean to response to ice shelf breaking and the presence of tabular icebergs.
+Instead we focus on developing a framework to model the ocean response to ice shelf breaking and the presence of tabular icebergs.
 This framework of representing ice shelves using a Lagrangian grid might be a step towards including giant tabular icebergs in climate models.
@@
 Since this model is a new approach to modeling ice shelf cavities, we present many of the technical elements involved in constructing the model.
-Those readers who are more interested in the model capabilities, should skip directly to the model results in the later sections.
+Those readers who are more interested in the model capabilities, should skip directly to the numerical experiments presented in the later sections.
 In Section 3 and 4, the LIISM model is used to simulate the circulation beneath an idealized ice shelf.
-The LIISM model results are validated by comparing them to an existing ice shelf model.
-We then we move beyond the capabilities of the existing ice shelf model by allowing a piece of the ice shelf to break away becoming a tabular icebergs, and consider the ocean response to this calving event.
+The LIISM model results are validated by comparing them to an existing Eularian ice-shelf model.
+We then we move beyond the capabilities of the existing ice shelf model by allowing a piece of the ice shelf to break away, becoming a tabular icebergs, and consider the ocean response to this calving event.
 
@@
 %, which can be used to model small icebergs, tabular icebergs, sea ice and ice shelf cavities
-In this section we describe many key elements of the LIISM.
-The LIISM is a Lagrangian/particle-based model in that the objects of the model are Lagrangian elements.
+%In this section we describe many key elements of the LIISM.  
+The LIISM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
 Each element represents a mass of ice which is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time.
 The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element.
-The elements are forced by oceanic and atmospheric forces, which are provided by the user or are determined by coupling the LIISM to an ocean/atmosphere model.
+The elements are forced by oceanic and atmospheric forces, which are provided by the user, or are determined by coupling the LIISM to an ocean/atmosphere model.
 The elements also interact with one another and can be bonded together to form larger structures.
 In different contexts, the LIISM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
-In this latter case, the LIISM model can be categorized as a discrete element model (DEM). 
+%In this latter case, the LIISM model can be categorized as a discrete element model (DEM). 
 % in the sense that large structures are constructed from smaller independent Lagrangian elements.
@@
 The elements drift in the ocean, forced by atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force and a force due to the sea surface slope.
-When these ice elements move alone (without interactions with other elements), they can be thought of as representation of small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).
+When these ice elements move alone (without interactions with other elements), they can be thought of as representing of small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).
 
@@
 where $(F_{IA})_{ij}$ is the force on element $i$ by element $j$.
-Both bonded an repulsive interactions are modeled using elastic stresses with frictional damping.
+Both bonded and repulsive interactions are modeled using elastic stresses with frictional damping.
 The elastic component of the force is a function of the distance between the two elements, while the  frictional damping force depends on the relative velocity of the two elements.
@@
 where $\vec{r}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, and $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
-We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F_{IA}})_{ij}=-(\vec{F_{IA}})_{ji}$).
-This is in contrast to some other DEM models in the literature (e.g.
-\citet{Li2014}).
+We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F}_{IA})_{ij}=-(\vec{F}_{IA})_{ji}$).
+%This is in contrast to some other DEM models in the literature (e.g. \citet{Li2014}). 
 The minimum thickness is preferred to the average thickness, since this means that the for two bonded elements a fixed distance apart, acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero.
@@
 
-The effectiveness of the repulsive forces can be seen in Figure \ref{fig:Regular_Uncoupled_sim} which shows an uncoupled simulation where ice elements drift westward into a bay, and eventually come to rest with minimal overlap between elements.
-The effectiveness of the numerical bonds is demonstrated in Figure \ref{fig:Uncoupled_sim} tabular icebergs (constructed from many ice elements bonded together) and individual icebergs (unbonded elements) drift together towards a convex coast line.
+The effectiveness of the repulsive forces can be seen in Figure \ref{fig:Regular_Uncoupled_sim}, which shows an uncoupled (ice only) simulation where ice elements drift westward into a bay, and eventually come to rest with minimal overlap between elements.
+The effectiveness of the numerical bonds is demonstrated in Figure \ref{fig:Uncoupled_sim}, where tabular icebergs (constructed from many ice elements bonded together) and individual icebergs (unbonded elements) drift together towards a convex coast line.
 When the tabular icebergs arrive at the coast, they bump into the coastline and begin to rotate, influencing the paths of the other icebergs.
 In this example we see that modeling large structures using small elements bonded together, allows us to achieve large-scale structure and rotational motion, without having to include an equation for the angular momentum of the elements (as discussed in \citet{Jakobsen2001}).
+Animations of these simulations can be found in the supplementary materials.
 
@@
 
-The coupling from the ocean model to the LIISM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LIISM model, to be used in the momentum and thermodynamics equations of the ice elements.
+The coupling from the ocean model to the LIISM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LIISM model, to be used in the momentum and thermodynamic equations of the ice elements.
 Within the LIISM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme.
@@
 The coupling in the other direction, from the LIISM model to the ocean model, is more complex.
-The LIISM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean boundary condition by applying a no slip boundary condition and frictional velocity beneath the ice.
+The LIISM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean by applying a no-slip boundary condition and frictional velocity beneath the ice.
 Fields from the LIISM model are interpolated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model.
@@
 The interpolation of the LIISM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LIISM model (see Section 2.3).
-Fields are `spread' to the ocean model by exactly calculating what fraction of an element's surface area lies in a particular grid box, and dividing the field in proportion to this fraction.
+Fields are `spread' to the ocean model grid by exactly calculating what fraction of an element's surface area lies in a particular grid box, and dividing the field in proportion to this fraction.
 %While the position of a particular element might be inside one ocean grid cell, the implied shape of the element will often intersect other ocean grid cells. 
-For example, consider an element which has a hexagonal surface area in the LIISM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
+For example, consider a hexagonal element in the LIISM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
 In this situation, the mass of the element is divided between these four ocean cells in proportion to the overlap area between the hexagonal element and the grid cell (this fraction is shown by the colors in \ref{fig:Hex_intersections}b).
@@
 This method allows for the intersection to be found even when the hexagon is not aligned with the grid.
-The LIISM model can be run using hexagonal or rectangular elements.
+%The LIISM model can be run using hexagonal or rectangular elements.
 
@@
 The complexity reduction is achieved by storing the element data in an efficient way that prevents having to search through all element pairs to check if they are close to one another or are bonded with one another.
-The data storage system works as follows: pointers to the memory structures containing each element are are stored in linked list data structures, which allow elements to be added and removed from the lists easily without restructuring the entire list.
+The data storage system works as follows: pointers to the memory structures containing each element are stored in linked list data structures, which allow elements to be added and removed from the lists easily without restructuring the entire list.
 Instead of using one list for all the elements on a processor, we use a separate linked list for each ocean grid cell.
 When an element moves between ocean grid cells, it is removed from its original list and added to the list corresponding to its new ocean grid cell.
-Since the area of elements has to be smaller than the area of an ocean grid cell, the critical interaction critical interaction length scale (equation \ref{eq:Interaction_crit}) is less than the length of a grid cell.
+Since the area of elements has to be smaller than the area of an ocean grid cell, the critical interaction length scale (equation \ref{eq:Interaction_crit}) is less than the length of a grid cell.
 This means that elements only experience repulsive forces with elements in the same ocean grid cell, or in one of the 8 adjacent cells.
-Limiting the possible repulsive interactions to elements in the 9 linked lists substantially reduces the computational time needed to calculate the total interactive force.
+Limiting the possible repulsive interactions to elements in these 9 linked lists substantially reduces the computational time needed to calculate the total interactive force.
 
@@
 The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice shelf cavities which undergo large calving events.
-We demonstrate this capability by performing numerical experiments with the LIISM model coupled to the MOM6 ocean model [reference].
+We demonstrate this capability by performing numerical experiments with the LIISM model coupled to the MOM6 ocean model \citep{Hallberg2013}.
 %This section describes the experimental setup of these numerical experiments. The results are shown in Section 4.
@@
 %For this experiment, we use the ice shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
-The MISOMIP configuration was developed as a standardize configuration to allow for the comparison between various ocean-ice coupled models.
+The MISOMIP configuration was developed as a standardized configuration to allow for a comparison between various ocean-ice coupled models.
 The configuration consists of an idealized ice shelf in a rectangular domain.
 The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650km.
-The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_exp}a and \ref{fig:ISOMIP_exp}b respectively, with the grounding line position drawn in for reference.
+The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference.
 The configuration is the same as that of the Ocean0 setup in the MISOMIP, with three changes made:
@@
 \item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
-\item The ice shelf is configured to be symmetric about its center line. This was achieved by using the average of the left and right flank of the ice shelf thickness. 
+\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$).
+This was achieved by using the average of the left and right flanks of the ice shelf thickness.
 \end{enumerate}
@@
 The LIISM model is coupled to the MOM6 ocean model. 
-The ocean model is run in using vertical coordinate system which is a hybrid between a sigma level and a z-level coordinate.
+The ocean model is run in using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
 In particular, model layers bend underneath the ice shelf as they would in a sigma model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
-The coordinate system was achieve using ALE regridding-remapping scheme.
+The coordinate system was achieve using ALE regridding-remapping scheme \citep{White2009}.
 The model used a horizontal resolution of 2km, and 36 vertical layers.
-All simulation were repeated using the ocean model is run layered mode (select results are shown in the supplementary material). 
+All simulation were repeated using the ocean model is run layered mode (results were similar and are not presented here).
+%(select results are shown in the supplementary material). 
 Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
@@
 The maximum ocean depth is $H_{ocean}=720$ m.
-A sponge layer is used on the northern boundary of which relaxes back to the initial temperature and salinity with a relaxation time scale of $\tau=0.1$ days.
-Melting is set to zero for cells where the ocean column thickness is less than 10m to avoid using more energy to melt ice than is present in the water column.
+A sponge layer is used on the northern boundary, which relaxes back to the initial temperature and salinity with a relaxation time scale of $\tau=0.1$ days.
+Melting is set to zero for ocean cells where the ocean column thickness is less than 10m to avoid using more energy to melt ice than is present in the water column.
 
@@
 Ice elements in the LIISM model are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
-The apothem of the gridded hexagons are initially set to $A=0.85$ km.
-Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2A<\Delta x$).
-Gaps along the boundary are filled in with using smaller elements so that the total ice shelf area is preserved.
+The sides of the gridded hexagons are initialized with length $S=0.98$ km.
+Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
+Gaps along the boundaries are filled in using smaller elements so that the total ice shelf area is preserved.
 The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
 
-Figure \ref{fig:ISOMIP_exp}c shows what the ice shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
-Figure \ref{fig:ISOMIP_exp}b shows the draft after spreading the mass across grid cells.
-When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_exp}c).
-The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_exp}b).
+Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
+Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
+When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
+The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
 
@@
 In the first experiment, we use a static ice shelf where the velocity of all ice elements is set to zero.
-In this experiment, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as was done in the Ocean0 setup in the MISOMIP \citep{Asay-Davis2016}).
+In this experiment, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as in the Ocean0 experiement in the MISOMIP \citep{Asay-Davis2016}).
 In this setup, ice shelf melting generates a temperature and salinity flux into the ocean, but does not change the thickness of the ice shelf.
@@
 
-Results of the static ice shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_exp}b).
-The simulations in the Lagrangian and Eularian are compared after 5 years of models time.
+Results of the static ice shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_mass_and_topog}b).
+Results from the static ice shelf experiment are analyzed after 5 years of model spinup.
 
@@
 Next, we preform a numerical experiment which demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice shelf models.
-In this experiments we break off a large piece of the the ice shelf and allow it to drift into the ocean as a tabular iceberg.
+In this experiments we break off a large piece of the ice shelf and allow it to drift into the ocean as a tabular iceberg.
 
@@
 Ice elements less than 12 km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
-A ring of elements whose distance from the ice front center is $\geq$ 12 km, but $\leq$14.4 km are allowed to move freely, but have all their bonds removed.
-Elements in this half annulus represent fragments of the ice shelf with calve into small pieces during a large calving event, and also allow the giant icebergs to move away from the ice shelf cavity more easily.
+A ring of elements whose distance, $d$, from the ice front center obeys $12 \textrm{ km} \leq   d \leq14.4 \textrm{ km}$, are allowed to move freely, but have all their bonds removed.
+Elements in this half annulus represent fragments of the ice shelf which calve into small pieces during a large calving event.
+Breaking the bonds of these surrounding elements allows the tabular iceberg to move away from the ice shelf cavity more easily.
 
 A wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice shelf cavity.
-Perturbation experiments were run using other wind stress values.
-In this experiment, the ice is allowed to decay as it melts.
-The tabular iceberg calving experiment is initialized using the ocean state from the end of the static ice shelf experiment (after 5 years).
-
+Perturbation experiments were performed using other wind stress values.
+
+The tabular iceberg calving experiment is initialized using the ocean state from the static ice shelf experiment after 5 years of simulation time.
+In tabular iceberg calving experiment, the ice shelf and icebergs are allowed to decay as they melt. 
 \end{enumerate}
@@
 The total mass is found by summing up over all ice elements located in that grid cell, while allowing elements to spread their mass across neighboring grid cells (as discussed in Section 2.3).
-Figure \ref{fig:ISOMIP_exp}b shows the draft of the ice shelf above the ice shelf cavity in the coupled static ice shelf simulation using this interpolation method, while Figure \ref{fig:ISOMIP_exp}c shows the draft which is calculated without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
-When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_exp}c).
-The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_exp}b).
+Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft of the ice shelf above the ice shelf cavity in the coupled static ice shelf simulation using this interpolation method, while Figure \ref{fig:ISOMIP_mass_and_topog}c shows the draft which is calculated without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
+When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
+The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
 In simulations without mass spreading, irregularities in ice draft cause irregularities in the ocean surface pressure, which cause spurious motion in the ocean (not shown).
@@
 \subsection{Static ice shelf experiment}
-The LIISM results from the static ice shelf experiment fit well within the current understanding of ice-shelf cavity circulations base on ice shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
+The LIISM results from the static ice shelf experiment fit well within the current understanding of ice-shelf cavity circulations based on ice shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
 The initial water temperatures inside the domain are warmer than the in-situ freezing point, and cause melting at the ice-shelf base.
@@
 As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_temp_v}b).
-This injection of buoyancy at depth drives a clockwise circulation outside of the ice shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice shelf melt.
-
-The highest melt rates are seen within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
-These elevated melt rates are caused by the presence of of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice shelf front.
-
+This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice shelf melt.
+
+The highest melt rates are observed within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
+These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice shelf front.\\
+\\
 %\subsubsection{Comparison with Eularian ice shelf model}
-\textbf{Comparison of LIISM and Eularian ice shelf models}\\
+\textbf{Comparison of LIISM and Eularian ice shelf model}\\
 The LIISM results from the static ice shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
-To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice shelf model using an identical configuration.
-The results show that two simulations have similar circulations (Figures \ref{fig:Bt_comparison}), melt rates and temperature/salinity profiles (see supplementary materials).
-The differences between the barotropic stream function of the two simulations (for example) are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with difference vertical coordinate systems [double check that this is correct].
-
-The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model.
-Recall that the role of the ice shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iiI) alter the upper ocean boundary condition below the ice shelf.
-The agreement agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LIISM model, and that the LIISM is able able to model sub ice shelf cavities as well as the Eularian model does.
+To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice shelf model with an identical configuration.
+The results show that two simulations have very similar circulations (Figures \ref{fig:Bt_comparison}), melt rates and temperature/salinity profiles (see supplementary materials).
+The differences between the barotropic stream functions of the two simulations (for example) are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems [double check that this is correct].
+
+The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
+Recall that the role of the ice shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iii) alter the upper ocean boundary condition below the ice shelf.
+The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LIISM model, and that the LIISM is able to model sub-ice-shelf cavities as well as the Eularian model does.
 This is a good starting point for moving beyond the capabilities of the Eularian model.
@@
 
-\subsection{Tabular iceberg calving}
+\subsection{Tabular iceberg calving experiement}
 The tabular iceberg calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.
-After the iceberg calves (referred to at time t=0 days), the iceberg drifts to the northward east, driven by the wind and steered by the Coriolis force (Figure \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
-After the iceberg has calved away from the ice shelf, we observed a warming of the surface waters near the near the ice front and iceberg edge (Figure \ref{fig:SST_Collapse}).
+After the numerical bonds are severed, the tabular iceberg and smaller ice fragments calve away from the ice shelf and begin to move.
+The tabular iceberg drifts to the northward east, driven by the wind and steered by the Coriolis force (Figure \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
+After the iceberg has moved away from the ice shelf, we observed a warming of the surface waters nearby ice front and iceberg edge (Figure \ref{fig:SST_Collapse}).
 This surface warming is caused by an upwelling of the warmer waters from beneath the ice shelf and iceberg.
-As the icebergs drifts away from the ice front, these warmer waters remain in the wake of the iceberg.
-The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color near to tabular iceberg in the Southern Ocean \citep{Duprat2016}, suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface.
-
-The motion of the iceberg disturbs the ocean surface which drives ocean velocities through out the water column \ref{fig:Velocity_section_Collapse}.
-The elevated velocities around the tabular iceberg lead to increased vertical mixing in the vicinity of the iceberg, which alters the stratification of the water column (Figure \ref{fig:Temperature_section_Collapse}).
-
-The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg \ref{fig:Collapse_solo_melt}.
-Large melt rates are observed at the new ice shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving calving has created an ice cliff at the edge of the ice shelf and iceberg.
-These sharp ice fronts allows for large ocean currents (Figure \ref{fig:Collapse_solo_melt}c), which drive the elevated melt rates.
-This will smooth out the ice front over time, and make it less sharp.
-While this is likely a real phenomena that could be observed in the real world, we should be wary of the modeled velocities at ice cliffs, since large changes in ice shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
+As the icebergs drifts away from the ice front, these warmer waters remain at the surface, mapping of the wake of the iceberg  (Figure \ref{fig:SST_Collapse}).
+The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color in the wake of tabular iceberg in the Southern Ocean \citep{Duprat2016}, suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface.
+
+The motion of the tabular iceberg disturbs the ocean surface, which drives ocean velocities through out the water column (Figure \ref{fig:Velocity_section_Collapse}).
+The elevated velocities around the tabular iceberg lead to increased vertical mixing in the vicinity of the iceberg, which alters the stratification of the water column (Figure \ref{fig:Temperature_section_Collapse}), heating the upper ocean.
+The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg (Figure \ref{fig:Collapse_solo_melt}).
+Large melt rates are observed at the newly calved ice shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving has created steep ice cliffs.
+These sharp ice fronts allow for large ocean currents (Figure \ref{fig:Collapse_solo_melt}c), which drive the elevated melt rates.
+These elevated melt rates act to smooth out the ice front over time, making the ice cliff less steep.
+While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
 
 As mentioned above, the direction (and speed) of the iceberg drift is largely determined by the wind speed and direction.
-Perturbation experiments using different wind stresses showed that the iceberg drifted to the north east for positive zonal and to the north west for negative zonal velocities.
-For wind stresses less that $\tau= ???$ the iceberg did not move away from the ice shelf.
+Perturbation experiments using different wind stresses showed that the iceberg drifts to the north east for positive zonal wind stresses and to the north west for negative zonal wind stresses.
+For wind stresses less that $\tau= ???$ the iceberg does not move away from the ice shelf.
 While this result is partly an artifact of the artificial shape of the calving iceberg, it is also consistent with \citet{Bassis2013} who noted that calving is a two step process consisting of (i) ice shelf breaking and (ii) iceberg detachment.
@@
 
-Finally, we note that the numerical bond in the LIISM model are in fact needed in order to allow the tabular iceberg to retains its shape.
-Comparing the iceberg calving simulation with an identical simulation with all numerical bonds removed shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
+Finally, we note that the numerical bonds in the LIISM model are needed in order to allow the tabular iceberg to retain its shape.
+Comparing the iceberg calving simulation with an identical simulation where all numerical bonds have been removed, shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
 In this case, the model behavior is more similar to an ice shelf disintegration and does not create a cohesive tabular iceberg.
@@
 Much progress has been made in modeling ice-shelf flows in an Eularian framework \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
-A challenge will be to develop similar ice dynamics models in a Lagrangian framework.
+A challenge will be to develop models with similar ice dynamics in a Lagrangian framework.
 This can perhaps be achieved using smooth particle hydrodynamics (SPH) methods, which allow partial differential equations to be solved on a Lagrangian gird \citep{Liu2010, Pan2013}.
 However, it is presently unclear how one would evolve the numerical bonds over time, so the bonds could still be used to hold the ice shelf and tabular icebergs together.
-This may involve performing a regridding of the ice element or a regridding of the numerical bonds after several ice time steps, or perhaps allowing the numerical bonds to break and form in a dynamic way.
+This may involve performing a regridding of the ice element or a regridding of the numerical bonds after severa time steps, or perhaps allowing the numerical bonds to break and form in a dynamic way.
 
 The other major innovation which will need to be introduced is a method for breaking numerical bonds.
-This is essentially equivalent to determining a ice shelf calving law, and is a famously difficult problem.
+This is essentially equivalent to determining an ice shelf calving law, and is a famously difficult problem.
 One possible way that this could be done is to break bonds when the elastic stress in the bond is larger than a given yield stress of that bond.
@@
 A number of preliminary experiments have been run using the LIISM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
-Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
+% Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
 These will need to be considered in order to model the primary productivity around tabular icebergs.
 
-Finally, there are a number of open questions associated with introducing giant tabular icebergs into climate models: (i) how to correctly link tabular icebergs' melt water fluxes to ocean biology, (ii) how to deal with giant calving events in small ensemble simulations where one calving even can skew the ensemble statistics, (iii) how to introduce tabular icebergs into models which do not use a fully dynamic ice sheet, and (iv) how to model iceberg breakup and fracturing.
-These and other questions will need to be answered in order to achieve physically realistic climate models with tabular icebergs and breaking ice shelves.
+Finally, there are a number of other open questions associated with introducing giant tabular icebergs into climate models: (i) how to correctly link tabular icebergs' melt water fluxes to ocean biology, (ii) how to deal with giant calving events in small ensemble simulations where one calving event can skew the ensemble statistics, (iii) how to introduce tabular icebergs into models which do not use a fully dynamic ice sheet, and (iv) how to model the breakup and fracture of freely-floating tabular icebergs.
+These and other questions will need to be answered in order to achieve physically realistic tabular icebergs and ice shelves in GCM's.
+The results presented in this study suggest that coupling DEM models to dynamic ocean models, presents a promising path towards a more realistic representation of breakable ice shelves and icebergs in climate models.
+%is potentially a promising path towards achieving this goal.
+% in order to represent large breakable ice shelves and icebergs
 
@@
 The non-interactive forces on an ice element are as described in \citep{Martin2010}, and are repeated here for completeness. 
-The force on an element due to air (a), ocean (o) and sea ice (si) drag are given by
+The forces on an element due to air (a), ocean (o) and sea ice (si) drag are given by
 \begin{equation}
@@
 (\vec{F}_{o}) = \rho_{o} (0.5 c_{o,v} W (D-T_{si})F + c_{o,h} L W) | \vec{u}_{o} - \vec{u}|(\vec{u}_{o} - \vec{u}),
+\label{eq:ocean_drag_eq}
 \end{equation}
@@
 $c_{a,v}$, $c_{o,v}$ and $c_{si,v}$ are the vertical drag coefficients with air, ocean and sea ice, while $c_{a,h}$, $c_{o,h}$ and $c_{si,h}$ are the respective horizontal drag coefficients.
-Here $\vec{u}_{a}$, $\vec{u}_{o}$, $\vec{u}_{si}$, are the velocities air, ocean and sea ice, respectively.
+$\vec{u}_{a}$, $\vec{u}_{o}$, $\vec{u}_{si}$, are the velocities air, ocean and sea ice, respectively.
 L, W, T, F and D are the length, width, thickness, freeboard and draft of the ice element.
@@
 
-For unbonded ice elements, the element thickness decays at due to basal melt at a rate $M_{b}$, while the length and width of the elements decay as a result of melt due to wave erosion, $M_{e}$ and melt due to buoyant convection, $M_{v}$.
+For unbonded ice elements, the element thickness decays due to basal melt at a rate $M_{b}$, while the length and width of the elements decay as a result of melt due to wave erosion, $M_{e}$, and melt due to buoyant convection, $M_{v}$.
 Following \citet{Martin2010}, the basal melt rate, wave erosion melt rate, and buoyant convection melt rate are parameterized by
@@
 \subsection{Modified Verlet Algorithm}
-The LIISM model uses a version velocity verlet algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
+The LIISM model uses a version velocity verlet time-stepping algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
 The traditional velocity verlet algorithm is commonly used in molecular dynamics, as it is simple to implement, second order accurate and computationally efficient \citep{Swope1982, Omelyan2002}.
@@
 This scheme reduces to the traditional velocity verlet when $a_{imp}$ is set to zero.
-Note that at step 2, $a_{exp}(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other qualities evaluated at time $t_{n}$, while $a_{imp}(t_{n+1})$ additionally depends on $u(t_{n+1})$ (and needs to be solved implicitly).
-For this reason, steps 2 and 3 need to be solved simultaneously, as described in the next section.
+Note that at step 2, $a_{exp}(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other quantities evaluated at time $t_{n}$, while $a_{imp}(t_{n+1})$ additionally depends on $u(t_{n+1})$, and needs to be solved implicitly).
+For this reason, steps 2 and 3 need to be solved simultaneously, as described in the next subsection.
 
@@
 The Coriolis term is handled using Crank-Nicolson scheme so that half of the effect is implicit and half is explicit.
-The elastic part of the interactive forces is treated explicitly, while the interactive damping is handled semi-implicitly in that the drag force on element A by element B depends on the velocity of elements A and B evaluated at time $t_{n+1}$ and $t_{n}$, respectively.
+The elastic part of the interactive forces is treated explicitly, while the interactive damping is handled semi-implicitly in that the drag force on element A by element B depends on the velocities of elements A and B evaluated at time $t_{n+1}$ and $t_{n}$, respectively.
 
@@
  \begin{equation}
-a_{imp} =\frac{1}{M} (F_{W})
+a_{imp} =\frac{1}{M} (F_{o})
 \end{equation}
@@
 \label{eq:Drag}
-F_{W}(t_{n+1}) = c_{w} |u_{w}(t_{n}) -u(t_{n}) | (u_{w}(t_{n}) -u(t_{n+1}) )  
-\end{equation}
+F_{W}(t_{n+1}) = \tilde{c}_{o} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) -u(t_{n+1}) ),
+\end{equation}
+where $\tilde{c}_{o}$ is the effective drag coefficient, accounting for the dimensions of the ice element (see equation \ref{eq:ocean_drag_eq}).
+
 %The consequences of the drag not being fully implicit are discussed below. 
@@
  \begin{equation}
-u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}     \Bigg(  c_{w} |u_{w}(t_{n}) -u(t_{n}) | (u_{w}(t_{n}) -u(t_{n+1}) )   \Bigg)
+u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}     \Bigg(  c_{w} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) -u(t_{n+1}) )   \Bigg)
  \end{equation}
@@
  \begin{equation}
-u(t_{n+1}) = \frac{u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}    \Bigg(  c_{w} |u_{w}(t_{n}) -u(t_{n}) | (u_{w}(t_{n}) )   \Bigg)}{  \Bigg( 1+  \frac{\Delta t}{M}       c_{w} |u_{w}(t_{n}) -u(t_{n}) |    \Bigg)}
+u(t_{n+1}) = \frac{u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}    \Bigg(  c_{w} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) )   \Bigg)}{  \Bigg( 1+  \frac{\Delta t}{M}       c_{w} |u_{o}(t_{n}) -u(t_{n}) |    \Bigg)}
  \end{equation}
@@
 Finally, we note that the the drag term (equation \ref{eq:Drag}) is not entirely implicit, since the element velocity inside the absolute value is evaluated at time $t_{n}$, rather than at time $t_{n+1}$.
-This is done so that we can solve for the updated velocity exactly.
+This is done so that we can solve for the updated velocity analytically.
 One consequence of this is that it gives rise to a small oscillation in the element velocity.
@@
 \textbf{Connecting bonds across processor boundaries}\\
-When a bonded element moves off the edge of a processor, the bond needs to be broken.
-When the element is copied into the halo of the processor, the bond needs to be reconnected.., and then reconnected when the element is copied back
-
- The basics of the bond bookkeeping work as follows.
-Consider an element A and an element B that are bonded together.
-As mentioned above, each element has a copy of the bond which is stored with the element.
+Since the LIISM model can be parallelized across multiple processors, it often happens that two elements on different processes are bonded together.
+Keeping track of numerical bonds across processor boundaries requires a lot of book keeping.
+In this section we describe the how LIISM model avoids segmentation faults by severing and reconnecting bonds at the edge of a processor during halo updates.
+
+%When a bonded element moves off the edge of a processor, the bond needs to be broken (to avoid segmentation faults).
+Before the next time step, the code performs a `halo update', and a copy of the element is written to the halo of the original processor.
+After this, the bond which was broken at the previous time step, needs to be reconnected.
+This processes of severing and reconnecting bonds requires a lot of bookkeeping, some of which are described below.
+
+The basics of the bond bookkeeping work as follows:
+consider an element A and an element B that are bonded together.
+Each element has a copy of the bond (a piece of memory which describes the bond between the two elements), which is stored with the element.
 Let A-B be the bond stored by element A, and B-A be the bond stored by element B.
@@
 For example, consider the bond A-B stored in element A on Processor 1.
-To check the quality of this bond A-B, we use the following four steps:
+To check the quality of this bond, we use the following four steps:
 \begin{enumerate}
@@
 \section{Possibly add}
-\subsection{Lagrangian sea ice mode}
-The addition of interactive forces between elements, means that the LIISM model can be used as a Lagrangian sea ice model, following [Li et al, 2014].
-In this formulation, each element represents a collection of sea ice flows.
-
 \subsection{Orientation}
-We can get the orientation of iceberg by considering the bonds that they form.
-
-\subsubsection{DEM vs SPH}
-Note that there is some ambiguity in the literature about the definition of a Discrete Element Model.
-In one view, to qualify as a Discrete Element Model since we do not evolve the angular momentum of the elements.
-Since elements are allows to overlap briefly, this method could be considered an example of a Smooth Particle Hydrodynamics model. 
-This same repulsive force is similar to that used by  [Li et al] in the context of sea ice interactions.
+Possibly add a section where we spread mass using the orientation of the icebergs.
 
@@
 \bibitem[Bigg et al (1997)]{Bigg1997}
-Bigg, G. R., Wadley, M. R., Stevens, D. P., and Johnson, J. A. (1997), Modelling the dynamics and thermodynamics of icebergs. {\it Cold Regions Science and Technology}, 26(2), 113-135.
+Bigg, G. R., Wadley, M. R., Stevens, D. P., and Johnson, J. A. (1997), Modeling the dynamics and thermodynamics of icebergs. {\it Cold Regions Science and Technology}, 26(2), 113-135.
 
@@
 \bibitem[De Rydt and Gudmundsson (2016)]{De_Rydt2006}
-De Rydt, J., and G. H. Gudmundsson (2016), Coupled ice shelf?ocean modeling and complex grounding line retreat from a seabed ridge. {\it J. of Geophys. Res.: Earth Surface}, 121(5), 865-880.
+De Rydt, J., and G. H. Gudmundsson (2016), Coupled ice shelf ocean modeling and complex grounding line retreat from a seabed ridge. {\it J. of Geophys. Res.: Earth Surface}, 121(5), 865-880.
 %
@@
 Hallberg, and M.
-Oppenheimer (2012), Investigation of land ice?ocean interaction with a fully coupled ice?ocean model: 1.
+Oppenheimer (2012), Investigation of land ice?ocean interaction with a fully coupled ice-ocean model: 1.
 Model description and behavior.
@@
 \bibitem[Grosfeld et al (1997)]{Grosfeld1997}
-Grosfeld K., R. Gerdes, J. Determan (1997), Thermohaline circulation and interaction between ice shelf cavities and the adjacent open ocean. {\em J. Phys. Oceanogr.,  \textbf{102}, C7, 15959-15610}.
+Grosfeld K., R. Gerdes, J. Determan (1997), Thermohaline circulation and interaction between ice shelf cavities and the adjacent open ocean. {\it J. Phys. Oceanogr.,  \textbf{102}, C7, 15959-15610}.
 
@@
 Grosfeld, K., and H. Sandhäger, (2004). The evolution of a coupled ice shelf–ocean system under different climate states. {\it Global and Planetary Change}, 42(1), 107-132.
+
+\bibitem[Hallberg et al (2013)]{Hallberg2013}
+Hallberg, R., A.
+Adcroft, J.
+P.
+Dunne, J.
+P., Krasting, R.
+J., and Stouffer (2013), Sensitivity of twenty-first-century global-mean steric sea level rise to ocean model formulation.
+{J.
+of Climate}, 26(9), 2947-2956.
 
@@
 
+\bibitem[White et al  (2009)]{White2009}
+White, L., A.
+Adcroft, and R.
+Hallberg (2009), High-order regridding–remapping schemes for continuous isopycnal and generalized coordinates in ocean models.
+{\it J.
+of Comp.
+Phys.}, 228(23), 8665-8692.
+
 \end{thebibliography}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Regular_towards_coast}
-\caption{ {Positions of ice elements at time t=0, 200, 400, 600 days for the simulation.
+\caption{ {Results of an ice-only LIISM simulation with no bonds between ice elements.
+Ice elements are initialized throughout the domain, as shown in panel (a).
+The elements are forced by an imposed westward ocean current of u=0.1m/s (no ocean model is used).
+Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
+The figure shows snapshots of ice element positions at time (a) t=0, (b) 200, (c) 400, (d) 600 days.
 The size of the dots shows the surface area (and interaction diameter) of each ice element.
-Land points are shown by black circles.
-}}
+Land points are shown by black circles.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Tabular_and_regular_towards_coast_manual}
-\caption{ {Positions of ice elements at time t=0, 300, 600, 900 days for the simulation.
+\caption{ {Results of an ice-only LIISM simulation using bonds between elements.
+Ice elements are initialized throughout the domain, as shown in panel (a).
+Three tabular icebergs are included, with 25, 16 and 4 elements respectively.
+The elements are forced by an imposed westward ocean current of u=0.1m/s (no ocean model is used).
+Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
+The figure shows snapshots of ice element positions at time (a) t=0, (b) 300, (c) 600, (d) 900 days.
 The size of the dots shows the surface area (and interaction diameter) of each ice element.
 Bonds between ice elements are plotted in magenta.
-Three tabular icebergs are shown, with 25, 16 and 4 elements respectively.
-Land points are shown by black circles.
-}}
+Land points are shown by black circles.}}
 \end{center}
@@
 
+%We begin by demonstrating the LIISM model uncoupled to the ocean.
+For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide.
+Land points are arranged in a semi-circle, in the west of the domain, as shown by the black dots in Figure \ref{fig:Uncoupled_sim}.
+Three hundred ice elements are initialized with diameters uniformly sampled from the interval [0 40km], and positioned randomly at positions with $x \leq 300$km.
+These ice elements can be thought to represent interacting sea ice flows or icebergs.
+Three `tabular icebergs' are initialized by arranging ice elements in a staggered lattices with adjacent elements bonded together, as described in Section 2.4.
+The three tabular icebergs contain 25, 16 and 4 elements, respectively.
+Each of the elements that make up the tabular icebergs has a diameter of 40km.
+All elements have an initial thickness of 10m.
+%
+%The simulation is forced by an imposed westward ocean current of u=0.1m/s.
+Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
+The initial setup is shown in Figure \ref{fig:Uncoupled_sim}a.
+
 \begin{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
-\caption{ {(a) Intersection of hexagonal element and ocean grid is used to find weights to spread LIISM properties to the ocean grid.
-(b) Hexagonal elements are initialized in a staggered lattice as shown.
+\caption{ {(a) Hexagonal elements are initialized in a staggered lattice as shown.
 Adjacent elements are bonded together.
@@
 The element bonds form equilateral triangles which give the larger structure rigidity.
-The black circles shows to the interactive length scales used in element interactions.}}
+The black circles shows to the interactive length scales used in element interactions.
+(b) Intersection of a hexagonal element and an ocean grid.
+The colors indicate the fraction of the hexagon that lies in each grid cell.
+These fractions are used as weights to spread LIISM properties to the ocean grid (see text for more details).}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_D_spread_mass_mass.png}
-\caption{ {(a) Ocean bottom topography in ISOMIP configuration.
+\caption{ {(a) Ocean bottom topography in MISOMIP configuration.
 (b) Ice shelf draft used in static shelf experiment.
@@
 %FIgure created by \end{center}
-\label{fig:ISOMIP_exp}
+\label{fig:ISOMIP_mass_and_topog}
 \end{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
-\caption{ {Results of the static ice shelf experiment using the LIISM model.
-Panels show a cross section of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field, and  (c) meridional velocity after 5 years of simulation.}}
+\caption{ {Results of the static ice shelf experiment using the LIISM model coupled to MOM6.
+Panels show cross sections of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity near the ice shelf base after 5 years of simulation.
+The region shown in panel (c) is indicated by the black box on panel (b),}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Results of the static ice shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation at the base of the ice shelf.}}
+\caption{ {Results of the static ice shelf experiment using the LIISM model coupled to MOM6.
+The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
+Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\caption{ {ALE Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
+\caption{ {Time-averaged barotropic stream function in the (a) Eularian and (b) Lagrangian simulations in the static ice shelf configuration.
+Panel (c) shows the difference between panels (a) and (b).
+The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_spread_area.png}
-\caption{ {Fraction of grid cell covered by ice (using the LIISM ice shelf) (a) t=15, (b) t=30, and (c) t=60 days after calving.}}
+\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment. Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Temperature section at $x=70 $km for the tabular iceberg calving simulation (a) t=15, (b) t=30, and (c) t=60 days after calving.}}
+\caption{ {Snapshots of vertical sections of ocean temperature at $x=70 $km in the LIISM tabular iceberg calving experiment. Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_temp.png}
-\caption{ {Sea surface temperature for the tabular iceberg calving simulation (a) t=15, (b) t=30, and (c) t=60 days after calving. Regions with ice area fraction = 1 area plotted in white.}}
+\caption{ {Snapshots of the sea surface temperature in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.
+Regions with ice area fraction = 1 area plotted in white.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {Meridional velocity section at $x=70 $km for the tabular iceberg calving simulation (a) t=15, (b) t=30, and (c) t=60 days after calving.}}
+\caption{ {Snapshots of vertical sections of meridional velocity at $x=70 $km in the LIISM tabular iceberg calving experiment. Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.}}
 \end{center}
@@
 \caption{ {Results of the tabular iceberg calving simulation 60 days after the iceberg calves.
-The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$ at the base of the ice shelf.
+The three panels show snapshots of the (a) melt rate, (b) top-of-ocean temperature and (c) $u^{*}$ at the base of the ice shelf.
 Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_salt_layers.png}
-\caption{ {Calving of tabular iceberg with the LIISM model fully coupled to the ocean for simulations with and without bonds between ice elements.
-The top row show the aveage draft of ice above the ocean in each grid cell for the simulation (a) with and (b) without bonds.
-The bottom row shows the corresponding temperature section at $y=\frac{L_{y}}{2}$ for the simulation (a) with and (b) without bonds.
-All snapshots are taken at time t= 30 days.}}
+\caption{ {Results from the tabular iceberg calving experiment using the LIISM model coupled to an ocean model.
+The top row shows the average draft of ice above the ocean for the simulation (a) with and (b) without numerical bonds.
+The bottom row shows the corresponding temperature section at $x=\frac{L_{x}}{2}$ for the simulation (a) with and (b) without bonds.
+All snapshots are taken at time t = 30 days.}}
 \end{center}

### 2017-01-25 calving_shelf.m

@@ -1,0 +1,228 @@
+clear all
+close all
+load 'blue_white.mat'
+path_name='/Users/alon/Desktop/files/Icebergs_clusters/Matlab_scripts/Box_experiment';
+cd(path_name)
+
+%filename='Viscous_spring_contact'
+%filename='Different_sizes_Viscous_spring_contact'
+%filename='Including_big_Bergs_with_Jacobi_5';
+%filename='All_bonds_Including_big_Bergs_with_Jacobi_5';
+%filename='Half_circle_exp_with_bergs_Jacobi_5';
+%filename='Half_circle_exp_with_little_bergs_Jacobi_5';
+%filename='Two_interacting_bergs_springs_for_land_bonds_interaction';
+%filename='Test_using_L_eff';
+%filename='Test_using_L_eff_alpha_max_10';
+%filename='Box_using_L_eff_alpha_max_10';
+%filename='Conc_on_Box_using_L_eff_alpha_max_10';
+%filename='Convex__Conc_on_alpha_max_10';
+%filename='Convex__Conc_on_alpha_mu_0';
+%filename='Convex__Conc_on_alpha_mu_1';
+%filename='Convex__Conc_on_alpha_mu_3';
+%filename='Convex_interaction_factor_mu_3';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3_take2';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3_take3';
+%filename='Convex_interaction_factor_mu_5_gamma_1_take4';
+%filename='Convex_interaction_factor_mu_5_gamma_1_take5';
+%filename='Reverse_wind_dir';
+%filename='Circular_wind_dir';
+%filename='Sea_surface_slope';
+%filename='Gridded_bergs_towards_wall';
+% %filename='Corriolis_Gridded_bergs_towards_wall';
+% %filename='Gridded_bergs_towards_wall_again';
+% filename='Gridded_bergs_towards_wall_again2';
+% filename='Gridded_bergs_towards_wall_again_stiffer';
+% filename='Gridded_bergs_towards_wall_again_stiffer_2';
+% %filename='Gridded_bergs_towards_wall_again_stiffer_Jacobi';
+% filename='Gridded_bergs_towards_wall_again_stiffer_Jacobi';
[…]

### 2017-01-25 hexagon_intersection.m

@@ -1,0 +1,115 @@
+clear all
+close all
+
+%Flags
+plot_hexagon_intersection=1;
+
+
+L=2;
+dx=0.01;
+%Initialize grid
+x=[-L:dx:L];
+y=x;
+
+
+C1=0;C2=0;C3=0;C4=0;
+
+H=0.4  %Height of hexigon
+
+x0=0.1;  %x position of center of hexigon
+y0=0.15;  %y position of center of hexigon
+S=(2/sqrt(3))*H;   %side of hexigon
+
+N=length(x);
+
+for k=1:2
+    
+    %Initialize matrix
+    Matrix=zeros(N,N);
+    
+    
+    %Define axes
+    Ax=0*ones(length(x),1);
+    Ay=0*ones(length(y),1);
+    
+    %Define 6 lines for linear programing (plus axes) - in order anticlockwise
+    L1=-sqrt(3)*x + (y0+(sqrt(3)*(S+x0)));    %upper right
+    L2= (y0+H)*ones(length(x),1);  %Top
+    L3=sqrt(3)*x + (y0+(sqrt(3)*(S-x0)));  %Upper left
+    
+    L4=sqrt(3)*x + (y0-(sqrt(3)*(S+x0)));  %Lower right
+    L5= (y0-H)*ones(length(x),1);  %Bottom
+    L6=-sqrt(3)*x + (y0-(sqrt(3)*(S-x0)));   %Lower left
+    
+    
+    A_hex=0;
+    A1=0;
+    A2=0;
+    A3=0;
+    A4=0;
+    
+    %Color in hexigon
+    for i=1:N
+        for j=1:N
+            Condition1=(y(j)< L1(i)) & (y(j)<L2(i)) & (y(j)< L3(i)) & (y(j)> L4(i)) & (y(j)>L5(i)) & (y(j)> L6(i)); %in the hexagon
+            First_Q= (y(j)>0) & (x(i)>0);
+            Second_Q= (y(j)>0) & (x(i)<0);
+            Third_Q= (y(j)<0) & (x(i)<0);
+            Forth_Q= (y(j)<0) & (x(i)>0);
+            if Condition1
+                Matrix(i,j)=1;
+                A_hex=A_hex+(dx^2);
+            end
+            if Condition1 & First_Q
+                Matrix(i,j)=1;
+                A1=A1+(dx^2);
+            end
+            if Condition1 & Second_Q
+                Matrix(i,j)=2;
+                A2=A2+(dx^2);
+                
+            end
[…]

### 2017-01-25 hexagonal_packing.m

@@ -1,0 +1,166 @@
+clear all
+close all
+
+%Flags
+plot_hexagon_intersection=1;
+
+if plot_hexagon_intersection==1
+    hexagon_intersection
+    clear all
+    plot_hexagon_intersection=1;
+end
+
+fontsize=20;
+
+L=6;
+dx=0.01;
+%Initialize grid
+x=[-L:dx:L];
+y=x;
+circ_ind=[0:0.1:2*pi];
+
+
+
+C1=0;C2=0;C3=0;C4=0;
+
+H=0.4  %Height of hexigon
+
+x0=0.1;  %x position of center of hexigon
+y0=0.15;  %y position of center of hexigon
+S=(2/sqrt(3))*H;   %side of hexigon
+
+N=length(x);
+Matrix2=zeros(N,N);
+
+berg_count=0;
+
+outer_max=6;
+inner_max=6;
+berg_pos_x=zeros(outer_max*inner_max,1);
+berg_pos_y=zeros(outer_max*inner_max,1);
+
+y_ini=0;
+x_ini=0;
+R=H;
+for outer=0:outer_max-1
+    x_start=y_ini + (sqrt(3)*R*outer);
+    y_start=mod(outer,2)*R;
+    
+    
+    for inner = 0 : inner_max-1
+        berg_count=berg_count+1;
+        berg_pos_y(berg_count)=y_start+(inner*2*R);
+        berg_pos_x(berg_count)=x_start;
+        y0=y_start+(inner*2*R);
+        x0=x_start;
+        
+        
+        %Initialize matrix
+        Matrix=zeros(N,N);
+        
+        
+        %Define axes
+        Ax=0*ones(length(x),1);
+        Ay=0*ones(length(y),1);
+        
+        %Define 6 lines for linear programing (plus axes) - in order anticlockwise
+        L1=-sqrt(3)*x + (y0+(sqrt(3)*(S+x0)));    %upper right
+        L2= (y0+H)*ones(length(x),1);  %Top
+        L3=sqrt(3)*x + (y0+(sqrt(3)*(S-x0)));  %Upper left
+        
+        L4=sqrt(3)*x + (y0-(sqrt(3)*(S+x0)));  %Lower right
+        L5= (y0-H)*ones(length(x),1);  %Bottom
+        L6=-sqrt(3)*x + (y0-(sqrt(3)*(S-x0)));   %Lower left
+        
+        
+        A_hex=0;
+        A1=0;
+        A2=0;
+        A3=0;
+        A4=0;
+        
[…]

### 2017-01-25 regular_towards_coast.m

@@ -1,0 +1,228 @@
+clear all
+close all
+load 'blue_white.mat'
+path_name='/Users/alon/Desktop/files/Icebergs_clusters/Matlab_scripts/Box_experiment';
+cd(path_name)
+
+%filename='Viscous_spring_contact'
+%filename='Different_sizes_Viscous_spring_contact'
+%filename='Including_big_Bergs_with_Jacobi_5';
+%filename='All_bonds_Including_big_Bergs_with_Jacobi_5';
+%filename='Half_circle_exp_with_bergs_Jacobi_5';
+%filename='Half_circle_exp_with_little_bergs_Jacobi_5';
+%filename='Two_interacting_bergs_springs_for_land_bonds_interaction';
+%filename='Test_using_L_eff';
+%filename='Test_using_L_eff_alpha_max_10';
+%filename='Box_using_L_eff_alpha_max_10';
+%filename='Conc_on_Box_using_L_eff_alpha_max_10';
+%filename='Convex__Conc_on_alpha_max_10';
+%filename='Convex__Conc_on_alpha_mu_0';
+%filename='Convex__Conc_on_alpha_mu_1';
+%filename='Convex__Conc_on_alpha_mu_3';
+%filename='Convex_interaction_factor_mu_3';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3_take2';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3_take3';
+%filename='Convex_interaction_factor_mu_5_gamma_1_take4';
+%filename='Convex_interaction_factor_mu_5_gamma_1_take5';
+%filename='Reverse_wind_dir';
+%filename='Circular_wind_dir';
+%filename='Sea_surface_slope';
+%filename='Gridded_bergs_towards_wall';
+% %filename='Corriolis_Gridded_bergs_towards_wall';
+% %filename='Gridded_bergs_towards_wall_again';
+% filename='Gridded_bergs_towards_wall_again2';
+% filename='Gridded_bergs_towards_wall_again_stiffer';
+% filename='Gridded_bergs_towards_wall_again_stiffer_2';
+% %filename='Gridded_bergs_towards_wall_again_stiffer_Jacobi';
+% filename='Gridded_bergs_towards_wall_again_stiffer_Jacobi';
[…]

### 2017-01-25 tabular_and_regular_towards_coast.m

@@ -1,0 +1,231 @@
+clear all
+close all
+load 'blue_white.mat'
+path_name='/Users/alon/Desktop/files/Icebergs_clusters/Matlab_scripts/Box_experiment';
+cd(path_name)
+
+%filename='Viscous_spring_contact'
+%filename='Different_sizes_Viscous_spring_contact'
+%filename='Including_big_Bergs_with_Jacobi_5';
+%filename='All_bonds_Including_big_Bergs_with_Jacobi_5';
+%filename='Half_circle_exp_with_bergs_Jacobi_5';
+%filename='Half_circle_exp_with_little_bergs_Jacobi_5';
+%filename='Two_interacting_bergs_springs_for_land_bonds_interaction';
+%filename='Test_using_L_eff';
+%filename='Test_using_L_eff_alpha_max_10';
+%filename='Box_using_L_eff_alpha_max_10';
+%filename='Conc_on_Box_using_L_eff_alpha_max_10';
+%filename='Convex__Conc_on_alpha_max_10';
+%filename='Convex__Conc_on_alpha_mu_0';
+%filename='Convex__Conc_on_alpha_mu_1';
+%filename='Convex__Conc_on_alpha_mu_3';
+%filename='Convex_interaction_factor_mu_3';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3_take2';
+%filename='Convex_interaction_factor_mu_3_gamma_0_3_take3';
+%filename='Convex_interaction_factor_mu_5_gamma_1_take4';
+%filename='Convex_interaction_factor_mu_5_gamma_1_take5';
+%filename='Reverse_wind_dir';
+%filename='Circular_wind_dir';
+%filename='Sea_surface_slope';
+%filename='Gridded_bergs_towards_wall';
+% %filename='Corriolis_Gridded_bergs_towards_wall';
+% %filename='Gridded_bergs_towards_wall_again';
+% filename='Gridded_bergs_towards_wall_again2';
+% filename='Gridded_bergs_towards_wall_again_stiffer';
+% filename='Gridded_bergs_towards_wall_again_stiffer_2';
+% %filename='Gridded_bergs_towards_wall_again_stiffer_Jacobi';
+% filename='Gridded_bergs_towards_wall_again_stiffer_Jacobi';
[…]

### 2017-01-25 Other_scripts/meltrate_comparison.sh
Added drivers to scripts so they can be run from the outside. This allowed me to create a Fig_.sh file for every figure in the paper. These have been added too.
A number of features have been added to the figurs, to make them
publication ready

@@ -1,0 +1,2 @@
+cd ../
+./static_shelf_comparison.py -fields_to_compare=plot_melt_comparison -save_figure=False 

### 2017-01-25 Scripts_for_paper_figures/Fig_BT_comparison.sh

@@ -1,0 +1,2 @@
+cd ../
+./static_shelf_comparison.py -fields_to_compare=plot_bt_stream_comparison -save_figure=True 

### 2017-01-25 Scripts_for_paper_figures/Fig_Collapse_solo_melt.sh

@@ -1,0 +1,2 @@
+cd ../
+./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -broken_shelf=True -save_figure=True  

### 2017-01-25 Scripts_for_paper_figures/Fig_SST_Collapse.sh

@@ -1,0 +1,2 @@
+cd ../
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.2  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -save_figure=True

### 2017-01-25 Scripts_for_paper_figures/Fig_Temperature_section_Collapse.sh

@@ -1,0 +1,2 @@
+cd ../
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.3 -vertical_coordinate=layers -xmin=450.0 -xmax=750.0 -dir_slice_num=10 -colorbar_units='(deg C)' -save_figure=True

### 2017-01-25 Scripts_for_paper_figures/Fig_Velocity_section_Collapse.sh

@@ -1,0 +1,2 @@
+cd ../
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=450.0 -xmax=750.0 -dir_slice_num=10 -colorbar_units='(m/s)' -save_figure=True

### 2017-01-25 Scripts_for_paper_figures/Fig_spread_area_snapshots.sh

@@ -1,0 +1,2 @@
+cd ../
+./snapshots.py -extension=icebergs_month.nc -plot_horizontal_field=True -use_ALE=True -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=Blues -field=spread_area -vmin=0.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=False -dir_slice_num=1 -colorbar_units='(non dim)' -save_figure=True

### 2017-01-25 Scripts_for_paper_figures/Fig_static_solo_melt.sh

@@ -1,0 +1,2 @@
+cd ../
+./static_shelf_solo.py -plot_horizontal_field=True -three_fields_flag=plot_melt_sst_ustar_berg -save_figure=True 

### 2017-01-25 Scripts_for_paper_figures/Fig_static_solo_temp_temp_v.sh

@@ -1,0 +1,2 @@
+cd ../
+./static_shelf_solo.py -plot_horizontal_field=False -three_fields_flag=plot_temp_temp_v -save_figure=True 

### 2017-01-25 drift_bond.py

@@ -1,0 +1,220 @@
+#!/usr/bin/env python
+
+#First import the netcdf4 library
+from netCDF4 import Dataset  # http://code.google.com/p/netcdf4-python/
+import numpy as np  # http://code.google.com/p/netcdf4-python/
+import matplotlib
+import math
+import os
+matplotlib.use("GTKAgg")
+from pylab import *
+#import matplotlib.pyplot as plt
+import pdb
+import netCDF4 as nc
+import sys
+import argparse
+from m6toolbox  import section2quadmesh
+from static_shelf_comparison import *
+
+
+##########################################################  Main Program   #########################################################################
+####################################################################################################################################################
+
+def main():
+	parser = argparse.ArgumentParser()
+	args = parser.parse_args()
+
+
+	#Plotting flags
+	save_figure=True
+
+	#General flags
+	rotated=True
+
+	#What to plot?
+	plot_horizontal_field=True
+	plot_temperature_cross_section=True
+
+	#Parameters
+	rho_ice=918.0
+	rho_water=1025.0
+
+
+	if (plot_horizontal_field is False) and  (plot_temperature_cross_section is False):
+		print 'You must select an option'
+		return
+
+
+	#Defining path
+
+	Fixed_berg_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/completed/fixed_speed_Moving_berg_trimmed_shelf/'
+	Drift_berg_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/completed/drifting_Moving_berg_trimmed_shelf/'
+	Bond_berg_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/completed/Bond_drifting_Moving_berg_trimmed_shelf/'
+
+	#Geometry files
+	ocean_geometry_filename=Fixed_berg_path +'ocean_geometry.nc'
+	ice_geometry_filename=Fixed_berg_path+'MOM_Shelf_IC.nc'
+	ISOMIP_IC_filename=Fixed_berg_path+'ISOMIP_IC.nc'
+	
+	#Berg files
[…]

### 2017-01-25 snapshots.py

@@ -19,35 +19,153 @@ from static_shelf_comparison import *
 ##########################################################  Main Program   #########################################################################
 ####################################################################################################################################################
 
-def main():
-	parser = argparse.ArgumentParser()
-	args = parser.parse_args()
+
+
+
+def parseCommandLine():
+        """
+        Parse the command line positional and optional arguments.
+        This is the highest level procedure invoked from the very end of the script.
+        """
+
+        parser = argparse.ArgumentParser(description=
+        '''
+        Plot snapshots of either surface or vertical sections, for Tech paper.
+        ''',
+        epilog='Written by Alon Stern, Dec. 2016.')
+	
+	#Adding an extra boolian type argument
+        parser.register('type','bool',str2bool) # add type keyword to registries
+
+
+
+	#Adding arguments:
+
+	#Saving figure
+	parser.add_argument('-save_figure', type='bool', default=False,
+		                        help=''' When true, the figure produced by the script is saved''')
+
+	#parser.add_argument('', type='bool', default=,
+	#	                        help='''    ''')
+
+	#General flags
+	parser.add_argument('-rotated', type='bool', default=True,
+		                        help=''' Rotates the figures so that latitude runs in the vertical (involves switching x and y. ''')
+	parser.add_argument('-use_ALE', type='bool', default=True,
+		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
+	use_ALE=True
+	parser.add_argument('-use_days_title', type='bool', default=False,
+		                        help=''' When true, the day number is used as a title for the figures. ''')
+	#What to plot?
+	parser.add_argument('-plot_horizontal_field', type='bool', default=True,
+		                        help='''    ''')
+	#Which simulation to use
[…]

### 2017-01-25 static_shelf_comparison.py

@@ -16,6 +16,62 @@ import argparse
 from m6toolbox  import section2quadmesh
 
 
+def parseCommandLine():
+        """
+        Parse the command line positional and optional arguments.
+        This is the highest level procedure invoked from the very end of the script.
+        """
+
+        parser = argparse.ArgumentParser(description=
+        '''
+        Plot snapshots of either surface or vertical sections, for Tech paper.
+        ''',
+        epilog='Written by Alon Stern, Dec. 2016.')
+	
+	#Adding an extra boolian type argument
+        parser.register('type','bool',str2bool) # add type keyword to registries
+
+
+
+	#Adding arguments:
+
+	#Saving figure
+	parser.add_argument('-save_figure', type='bool', default=False,
+		                        help=''' When true, the figure produced by the script is saved''')
+
+	#General flags
+	parser.add_argument('-rotated', type='bool', default=True,
+		                        help=''' Rotates the figures so that latitude runs in the vertical (involves switching x and y. ''')
+	parser.add_argument('-use_ALE', type='bool', default=True,
+		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
+	
+	#What to plot?
+	parser.add_argument('-fields_to_compare', type=str, default='plot_bt_stream_comparison',
+		                        help=''' This flag determine whether to plot horizontal, vertical, or special case for barotropic stream function
+					(should remove this later). Options are plot_bt_stream_comparison, plot_melt_comparison, plot_cross_section   ''')
+
+	#Which file type to use
+	parser.add_argument('-use_title_on_figure', type='bool', default=False,
+		                        help=''' When true, figure the name of the field is written as title ''')
+
+	optCmdLineArgs = parser.parse_args()
+	return optCmdLineArgs
+
+def str2bool(string):
+        if string.lower() in  ("yes", "true", "t", "1"):
+                Value=True
+        elif string.lower() in ("no", "false", "f", "0"):
+                Value=False
+        else:
[…]

### 2017-01-25 static_shelf_solo.py

@@ -20,87 +20,239 @@ from static_shelf_comparison import *
 ##########################################################  Main Program   #########################################################################
 ####################################################################################################################################################
 
-def main():
-	parser = argparse.ArgumentParser()
-	args = parser.parse_args()
+def parseCommandLine():
+        """
+        Parse the command line positional and optional arguments.
+        This is the highest level procedure invoked from the very end of the script.
+        """
+
+        parser = argparse.ArgumentParser(description=
+        '''
+        Plot snapshots of either surface or vertical sections, for Tech paper.
+        ''',
+        epilog='Written by Alon Stern, Dec. 2016.')
+	
+	#Adding an extra boolian type argument
+        parser.register('type','bool',str2bool) # add type keyword to registries
+
+
+
+	#Adding arguments:
+
+	#Saving figure
+	parser.add_argument('-save_figure', type='bool', default=False,
+		                        help=''' When true, the figure produced by the script is saved''')
+
+	#General flags
+	parser.add_argument('-rotated', type='bool', default=True,
+		                        help=''' Rotates the figures so that latitude runs in the vertical (involves switching x and y. ''')
+	parser.add_argument('-use_ALE', type='bool', default=True,
+		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
+	
+	#What to plot?
+	parser.add_argument('-plot_horizontal_field', type='bool', default=True,
+		                        help='''    ''')
+
+	#Which file type to use
+	parser.add_argument('-broken_shelf', type='bool', default=False,
+		                        help=''' When true, figure plots data after ice shelf breakoff ''')
+	
+	parser.add_argument('-three_fields_flag', type=str, default='plot_melt_sst_ustar_berg',
[…]

### 2017-01-26 snapshots.py
Added line to spread_mass_figure, added comparison of barotropic stream functions to static_shelf_comparison

@@ -277,6 +277,8 @@ def main(args):
 				plt.ylabel('y (km)',fontsize=20)
 			if n>0:
 				ax.set_yticks([])
+			if (n==2) and (args.field=='spread_area'):
+				plt.plot(np.array([xvec[10], xvec[10]]), np.array([450.0, 750.0]),'--', color='k',linewidth=3 )
 		#Creating colorbar
 		fig.subplots_adjust(right=0.85)
 		cbar_ax = fig.add_axes([0.88,0.12 , 0.025, 0.75])

### 2017-01-26 static_shelf_comparison.py

@@ -54,6 +54,9 @@ def parseCommandLine():
 	parser.add_argument('-use_title_on_figure', type='bool', default=False,
 		                        help=''' When true, figure the name of the field is written as title ''')
 
+	parser.add_argument('-only_shelf_ALE', type='bool', default=False,
+		                        help=''' When true, Figures compares Shelf ALE and Layer (must be used with use_ALE=True ''')
+
 	optCmdLineArgs = parser.parse_args()
 	return optCmdLineArgs
 
@@ -511,13 +514,21 @@ def main(args):
 	ice_geometry_filename=Shelf_path+'/MOM_Shelf_IC.nc'
 	ISOMIP_IC_filename=Shelf_path+'ISOMIP_IC.nc'
 	
+	#only used when comparing ALE and Layer
+	Layer_Shelf_path=Path+'Shelf/' + Folder_name
+
 	#Using ALE ice shelf
 	use_ALE_flag=''
 	if use_ALE is True:
+		
 		use_ALE_flag='ALE_z_'
 		Folder_name='ALE_z_' +Folder_name
 		Shelf_path=Path+'Shelf/' + Folder_name
 		Berg_path=Path+'Bergs/' + Folder_name
+
+		#Comparing Layer vs ALE
+		if args.only_shelf_ALE is True:
+			Berg_path=Layer_Shelf_path 
 	
 	#Shelf files
 	Shelf_ocean_file=Shelf_path+'00010101.ocean_month.nc'

### 2017-01-26 static_shelf_solo.py

@@ -191,7 +191,7 @@ def main(args):
 		#fig=plt.figure(figsize=(15,10))
 
 		flipped=False
-		slice_num=59
+		time_slice_num=59
 		time_slice='mean'
 		cmap='jet'
 		snapshot=True
@@ -261,14 +261,14 @@ def main(args):
 			filename=filename_list[k]
 
 			ax=plt.subplot(1,N,k+1)
-			data=load_and_compress_data(filename,field=field,time_slice=time_slice,time_slice_num=slice_num,rotated=rotated) 
+			data=load_and_compress_data(filename,field=field,time_slice=time_slice,time_slice_num=time_slice_num,rotated=rotated) 
 			plt.plot(xvec,grounding_line, linewidth=3.0,color='black')
 			if broken_shelf is False:
 				plt.plot(xvec,ice_front, linewidth=3.0,color='black')
 			if mask_open_ocean[k] == True:
 				mask_ocean_using_bergs=True
 				if mask_ocean_using_bergs is True:
-					ice_data=load_and_compress_data(Berg_iceberg_file,field='spread_area',time_slice='',time_slice_num=slice_num,\
+					ice_data=load_and_compress_data(Berg_iceberg_file,field='spread_area',time_slice='',time_slice_num=time_slice_num,\
 							rotated=rotated,direction='xy',dir_slice=None, dir_slice_num=1)
 					data=mask_ocean(data,ice_data)
 				else:
@@ -383,7 +383,7 @@ def main(args):
 
 			plot_flag=plot_flag+'_'+ field
 
-			plt.subplot(N,1,k+1)
+			ax=plt.subplot(N,1,k+1)
 
 			data=load_and_compress_data(filename,field , time_slice, time_slice_num=time_slice_num, direction='yz',\
 					dir_slice=None, dir_slice_num=20,rotated=rotated)
@@ -418,6 +418,7 @@ def main(args):
 			if k==2:
 				plt.xlabel('y (km)',fontsize=20)
 			plt.ylabel('Depth (m)',fontsize=20)
+			text(1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 		
 		#For plotting purposes
 		field=field+'_'+ vertical_coordinate

### 2017-01-26 Scripts_for_paper_figures/Fig_Temperature_section_Collapse.sh
Changed y axis to go from zero

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.3 -vertical_coordinate=layers -xmin=450.0 -xmax=750.0 -dir_slice_num=10 -colorbar_units='(deg C)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.3 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=10 -colorbar_units='(deg C)' -save_figure=True

### 2017-01-26 Scripts_for_paper_figures/Fig_Velocity_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=450.0 -xmax=750.0 -dir_slice_num=10 -colorbar_units='(m/s)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=10 -colorbar_units='(m/s)' -save_figure=True

### 2017-01-26 Scripts_for_paper_figures/Fig_static_solo_melt.sh

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -plot_horizontal_field=True -three_fields_flag=plot_melt_sst_ustar_berg -save_figure=True 
+./static_shelf_solo.py -plot_horizontal_field=True -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 

### 2017-01-26 Scripts_for_paper_figures/Fig_static_solo_temp_temp_v.sh

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -plot_horizontal_field=False -three_fields_flag=plot_temp_temp_v -save_figure=True 
+./static_shelf_solo.py -plot_horizontal_field=False -three_fields_flag=plot_temp_temp_v -time_slice=mean -save_figure=True 

### 2017-01-26 snapshots.py
Changed y axis to go from zero

@@ -236,8 +236,8 @@ def main(args):
 		fig, axes = plt.subplots(nrows=1,ncols=3)
 		fig.set_size_inches(15.0,10.0, forward=True)
 		#fig=plt.figure(figsize=(15,10),facecolor='grey')
-		ylim_min=550.
-		ylim_max=750.
+		ylim_min=550.-320.0
+		ylim_max=750.-320.0
 		for n in range(3):
 			#flipped=False
 			#field='spread_area'  ;vmin=0.0  ; vmax=1.0
@@ -278,7 +278,7 @@ def main(args):
 			if n>0:
 				ax.set_yticks([])
 			if (n==2) and (args.field=='spread_area'):
-				plt.plot(np.array([xvec[10], xvec[10]]), np.array([450.0, 750.0]),'--', color='k',linewidth=3 )
+				plt.plot(np.array([xvec[10], xvec[10]]), np.array([450.0-320., 750.0-320.]),'--', color='k',linewidth=3 )
 		#Creating colorbar
 		fig.subplots_adjust(right=0.85)
 		cbar_ax = fig.add_axes([0.88,0.12 , 0.025, 0.75])

### 2017-01-26 static_shelf_comparison.py

@@ -285,7 +285,7 @@ def switch_x_and_y(x,y):
 	
 	return [x,y]
 
-def load_static_variables(ocean_geometry_filename,ice_geometry_filename,ISOMIP_IC_filename,rotated):
+def load_static_variables(ocean_geometry_filename,ice_geometry_filename,ISOMIP_IC_filename,rotated,xy_from_zero=True):
 	# bedrock
 	depth = Dataset(ocean_geometry_filename).variables['D'][:]
 	# area under shelf 
@@ -302,6 +302,16 @@ def load_static_variables(ocean_geometry_filename,ice_geometry_filename,ISOMIP_I
 	y=Dataset(ocean_geometry_filename).variables['geolat'][:]#*1.0e3 # in m
 	xvec=Dataset(ocean_geometry_filename).variables['lonh'][:]#*1.0e3 # in m
 	yvec=Dataset(ocean_geometry_filename).variables['lath'][:]#*1.0e3 # in m
+
+	if xy_from_zero is True:
+		x_start=np.min(x)-(0.5*(xvec[2]-xvec[1]));
+		y_start=np.min(y)-(0.5*(yvec[2]-yvec[1]));
+		print 'Subtracting y,x=', x_start, y_start
+		x=x-x_start
+		y=y-y_start
+		xvec=xvec-x_start
+		yvec=yvec-y_start
+
 	if rotated is True:
 		depth=transpose_matrix(depth)
 		shelf_area=transpose_matrix(shelf_area)

### 2017-01-26 static_shelf_solo.py

@@ -71,44 +71,44 @@ def parseCommandLine():
 	parser.add_argument('-cmap', type=str, default='jet',
 		                        help='''Colormap to use when producing the figure ''')
 	
-	parser.add_argument('-field', type=str, default='temp',
-		                        help=''' Which field is being plotted  ''')
+	#parser.add_argument('-field', type=str, default='temp',
+	#	                        help=''' Which field is being plotted  ''')
 	
-	parser.add_argument('-vmin', type=float, default=0.0,
-		                        help='''Minimum value used for plotting''')
+	#parser.add_argument('-vmin', type=float, default=0.0,
+	#	                        help='''Minimum value used for plotting''')
 	
-	parser.add_argument('-vmax', type=float, default=1.0,
-		                        help='''Maximum values used for plotting''')
+	#parser.add_argument('-vmax', type=float, default=1.0,
+	#	                        help='''Maximum values used for plotting''')
 	
-	parser.add_argument('-vanom', type=float, default=0.3,
-		                        help='''This is the color scale when plot_anomaly=True. Goes from [-vanom vanom]''')
+	#parser.add_argument('-vanom', type=float, default=0.3,
+	#	                        help='''This is the color scale when plot_anomaly=True. Goes from [-vanom vanom]''')
 	
-	parser.add_argument('-flipped', type='bool', default=False,
-		                        help=''' The panel is flipped over so that it faces the other way.''')
+	#parser.add_argument('-flipped', type='bool', default=False,
+	#	                        help=''' The panel is flipped over so that it faces the other way.''')
 	
-	parser.add_argument('-mask_using_bergs', type='bool', default=False,
-		                        help='''When true, the iceberg is masked out using the iceberg file (when you only want the ocean)''')
+	#parser.add_argument('-plot_anomaly', type='bool', default=False,
+	#	                        help=''' If true, then figure plots the anomaly from the initial value, using color scale -vanom ''')
 
-	parser.add_argument('-plot_anomaly', type='bool', default=False,
-		                        help=''' If true, then figure plots the anomaly from the initial value, using color scale -vanom ''')
-
-	parser.add_argument('-vertical_coordinate', type=str, default='layers',
[…]

### 2017-01-27 Scripts_for_paper_figures/Fig_Bond_vs_No_bond.sh
updated figure Bond vs No bond scripts and figures

@@ -1,0 +1,2 @@
+cd ../
+./drift_bond.py -save_figure=True

### 2017-01-27 drift_bond.py

@@ -20,13 +20,36 @@ from static_shelf_comparison import *
 ##########################################################  Main Program   #########################################################################
 ####################################################################################################################################################
 
-def main():
-	parser = argparse.ArgumentParser()
-	args = parser.parse_args()
+def parseCommandLine():
+        """
+        Parse the command line positional and optional arguments.
+        This is the highest level procedure invoked from the very end of the script.
+        """
 
+        parser = argparse.ArgumentParser(description=
+        '''
+        Plot snapshots of either surface or vertical sections, for Tech paper.
+        ''',
+        epilog='Written by Alon Stern, Dec. 2016.')
+	
+	#Adding an extra boolian type argument
+        parser.register('type','bool',str2bool) # add type keyword to registries
+
+
+
+	#Adding arguments:
+
+	#Saving figure
+	parser.add_argument('-save_figure', type='bool', default=False,
+		                        help=''' When true, the figure produced by the script is saved''')
+
+        optCmdLineArgs = parser.parse_args()
+        return optCmdLineArgs
+
+def main(args):
 
 	#Plotting flags
-	save_figure=True
+	save_figure=args.save_figure
 
 	#General flags
 	rotated=True
@@ -47,9 +70,15 @@ def main():
 
 	#Defining path
 
+	path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/'
 	Fixed_berg_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/completed/fixed_speed_Moving_berg_trimmed_shelf/'
 	Drift_berg_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/completed/drifting_Moving_berg_trimmed_shelf/'
[…]

### 2017-01-27 Tech1.tex

@@
 %\title{The effect of calving-size distribution on sea-ice formation around Antarctica}
-\title{Modeling ice shelf cavities and calving tabular icebergs}
+\title{Modeling ice-shelf cavities and calving tabular icebergs}
 %\title{The effects of iceberg calving-size distribution in a global climate model}
@@
 The calving of giant icebergs is an important process in the Antarctic freshwater cycle.
-Iceberg calving can significantly alter the geometry of an ice shelf cavity, potentially affecting the circulation within the cavity.
+Iceberg calving can significantly alter the geometry of an ice-shelf cavity, potentially affecting the circulation within the cavity.
 Giant icebergs which break away can drift across large distance, altering regional ocean circulation, sea ice distributions and bottom water formation.
 However, despite its importance, the current generation of numerical models is unable to represent this process in a physically realistic way.
-In this study we develop a model of an ice shelf cavity using a Lagrangian ice shelf.
+In this study we develop a model of an ice-shelf cavity using a Lagrangian ice shelf.
 The ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
@@
 This paper provides a description of the LIISM model and discusses a number of the technical elements involved in building a Lagrangian ice shelf.
-To test the model, the LIISM is used to model an idealized ice shelf cavity which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-Results from static ice shelf experiments compare well to results using a more traditional Eularian ice shelf modles.
+To test the model, the LIISM is used to model an idealized ice-shelf cavity which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
+Results from static ice-shelf experiments compare well to results using a more traditional Eularian ice-shelf models.
 The novel capabilities of the  LIISM are demonstrated by modeling a tabular iceberg breaking away from the idealized ice shelf.
@@
 These massive platforms of ice extend deep into the water column, applying large pressures to surface of the ocean, which is often hundreds of meters below global sea level.
-Beneath the ice shelves, both the bottom topography and the ice shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}.
-The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice shelf cavities, and gives the ocean within the ice shelves cavities a unique character.
-
-In addition to suppressing the depth of ocean surface, the ice shelves also melt (and break), thus providing a freshwater flux into the ice shelf cavities. 
+Beneath the ice shelves, both the bottom topography and the ice-shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}.
+The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean within the ice shelves cavities a unique character.
+
+In addition to suppressing the depth of ocean surface, the ice shelves also melt (and break), thus providing a freshwater flux into the ice-shelf cavities. 
 %Perhaps remove this line....:
@@
 %
-Within the ice shelf cavities, the input of buoyant meltwater into the ocean creates rising density plumes, which are guided along the ice shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
-The strength of the circulation within the cavity feeds back onto the ice shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice shelf melt \citep{Lewis1986, Jacobs2011}.
+Within the ice-shelf cavities, the input of buoyant meltwater into the ocean creates rising density plumes, which are guided along the ice-shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
+The strength of the circulation within the cavity feeds back onto the ice-shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice-shelf melt \citep{Lewis1986, Jacobs2011}.
 
 The Antarctic ice shelves are also characterized by large infrequent calving events where massive pieces of the ice shelves break off, to create giant tabular icebergs.
-Observational estimates suggest that approximately half of Antarctic ice shelf decay is due to iceberg calving, while the other half occurs through ice shelf melting \citep{Depoorter2013, Rignot2013}.
+Observational estimates suggest that approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
 Calving icebergs' sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}.
@@
 
-Melt water from both ice shelf melt and iceberg melt impact the ocean hydrography outside of the ice shelf cavities, influencing sea ice production and bottom water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
+Melt water from both ice-shelf melt and iceberg melt impact the ocean hydrography outside of the ice-shelf cavities, influencing sea ice production and bottom water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
 The long distances traveled by giant icebergs before melting means that their meltwater impact is often felt hundreds of kilometers away from their calving origins \citep{Stern2016}.
@@
 In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic meltwater system described in the previous paragraphs.
-This increased interest has led to accelerated efforts to accurately model Antarctic ice shelf cavities \citep{Asay-Davis2016}.
+This increased interest has led to accelerated efforts to accurately model Antarctic ice-shelf cavities \citep{Asay-Davis2016}.
 Modeling the ocean beneath the ice shelves presents a unique set of challenges, since (i) the presence of ice shelves provides a rigid upper boundary for the ocean model which is not encountered elsewhere in the ocean, and (ii) melting and breaking ice shelves imply a changing ocean boundary conditions which present numerous numerical difficulties.
 
-The earliest models of ocean ice shelf cavities were developed using a static ice shelves with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
-In these models, ice shelf melting was represented through salinity and temperature fluxes, while the ice shelf geometry remained unchanged.
-Later models of ice shelf cavities allowed the ice shelf geometry to evolve as the ice shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}.
-More recently, dynamic ice shelf models have been coupled the ocean cavity, allowing the study of grounding line migration, which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
-As far as we know, all models of ice shelf cavities to date have neglected ice shelf breaking and iceberg detachment.
-
-In parallel to these efforts to develop ice shelf cavity models, a number of iceberg drift models have been developed, and have been included in some global General Circulation Models \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
+The earliest models of ocean ice-shelf cavities were developed using a static ice shelves with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
+In these models, ice-shelf melting was represented through salinity and temperature fluxes, while the ice-shelf geometry remained unchanged.
+Later models of ice-shelf cavities allowed the ice-shelf geometry to evolve as the ice shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}.
+More recently, dynamic ice-shelf models have been coupled the ocean cavity, allowing the study of grounding line migration, which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
+As far as we know, all models of ice-shelf cavities to date have neglected ice-shelf breaking and iceberg detachment.
+
+In parallel to these efforts to develop ice-shelf cavity models, a number of iceberg drift models have been developed, and have been included in some global General Circulation Models \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
 These iceberg drift models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
@@
 
-The ice shelf cavity models and iceberg drift models described above have been developed separately from one another, and have not been designed to be used together in a physically consistent way.
+The ice-shelf cavity models and iceberg drift models described above have been developed separately from one another, and have not been designed to be used together in a physically consistent way.
 As such, it has not been possible to model the calving of tabular icebergs away from an ice shelf, which is an important part of the Antarctic climate system.
-The goal of this study is to develop a model which combines features of the ice shelf cavity models and the iceberg drift models, to create an ice shelf cavity model that is able to calve tabular icebergs.
-To do this, we create an ice shelf model out of Lagrangian elements which are `bonded' together by numerical bonds.
-In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break away' from an existing ice shelf, thus changing the geometry of the ice shelf cavity.
+The goal of this study is to develop a model which combines features of the ice-shelf cavity models and the iceberg drift models, to create an ice-shelf cavity model that is able to calve tabular icebergs.
+To do this, we create an ice-shelf model out of Lagrangian elements which are `bonded' together by numerical bonds.
+In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break away' from an existing ice shelf, thus changing the geometry of the ice-shelf cavity.
 Modeling iceberg calving in a physically consistent way allows us to study the ocean response to iceberg detachment.
@@
 In this study, we bypass the question of how to correctly calve icebergs or break bonds.
-Instead we focus on developing a framework to model the ocean response to ice shelf breaking and the presence of tabular icebergs.
+Instead we focus on developing a framework to model the ocean response to ice-shelf breaking and the presence of tabular icebergs.
 This framework of representing ice shelves using a Lagrangian grid might be a step towards including giant tabular icebergs in climate models.
@@
 Section 2 gives a description of many of the key aspects of the LIISM.
-Since this model is a new approach to modeling ice shelf cavities, we present many of the technical elements involved in constructing the model.
+Since this model is a new approach to modeling ice-shelf cavities, we present many of the technical elements involved in constructing the model.
 Those readers who are more interested in the model capabilities, should skip directly to the numerical experiments presented in the later sections.
@@
 The LIISM model results are validated by comparing them to an existing Eularian ice-shelf model.
-We then we move beyond the capabilities of the existing ice shelf model by allowing a piece of the ice shelf to break away, becoming a tabular icebergs, and consider the ocean response to this calving event.
+We then we move beyond the capabilities of the existing ice-shelf model by allowing a piece of the ice shelf to break away, becoming a tabular icebergs, and consider the ocean response to this calving event.
 
@@
 respectively.
-In this way, elements with no bonds, melt like point particle icebergs, elements at the center of large structures melt like ice shelves, and elements at the sides of large structures have a combination of iceberg side and basal melt, and ice shelf melt.
+In this way, elements with no bonds, melt like point particle icebergs, elements at the center of large structures melt like ice shelves, and elements at the sides of large structures have a combination of iceberg side and basal melt, and ice-shelf melt.
 
@@
  \section{Experiment Setup}
-The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice shelf cavities which undergo large calving events.
+The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice-shelf cavities which undergo large calving events.
 We demonstrate this capability by performing numerical experiments with the LIISM model coupled to the MOM6 ocean model \citep{Hallberg2013}.
@@
 \subsection{MISOMIP configuration}
-In order for our (pre-calving) simulations to be easily comparable to previous models of ice shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
-%For this experiment, we use the ice shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
+In order for our (pre-calving) simulations to be easily comparable to previous models of ice-shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
+%For this experiment, we use the ice-shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
 The MISOMIP configuration was developed as a standardized configuration to allow for a comparison between various ocean-ice coupled models.
@@
 \item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$).
-This was achieved by using the average of the left and right flanks of the ice shelf thickness.
+This was achieved by using the average of the left and right flanks of the ice-shelf thickness.
 \end{enumerate}
@@
 Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
-Gaps along the boundaries are filled in using smaller elements so that the total ice shelf area is preserved.
+Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
 The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
 
-Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
+Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
 Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
-When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
+When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice-shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
 The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
@@
 \item
-\textbf{Static ice shelf experiment:}\\
+\textbf{Static ice-shelf experiment:}\\
 %\subsection{Static ice shelf experiment}
@@
 In this experiment, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as in the Ocean0 experiement in the MISOMIP \citep{Asay-Davis2016}).
-In this setup, ice shelf melting generates a temperature and salinity flux into the ocean, but does not change the thickness of the ice shelf.
-This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice shelf advection.
-
-Results of the static ice shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_mass_and_topog}b).
-Results from the static ice shelf experiment are analyzed after 5 years of model spinup.
+In this setup, ice-shelf melting generates a temperature and salinity flux into the ocean, but does not change the thickness of the ice shelf.
+This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
+
+Results of the static ice-shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_mass_and_topog}b).
+Results from the static ice-shelf experiment are analyzed after 5 years of model spinup.
 
@@
 % \subsection{Tabular iceberg calving}
-Next, we preform a numerical experiment which demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice shelf models.
+Next, we preform a numerical experiment which demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice-shelf models.
 In this experiments we break off a large piece of the ice shelf and allow it to drift into the ocean as a tabular iceberg.
@@
 Elements in this half annulus represent fragments of the ice shelf which calve into small pieces during a large calving event.
-Breaking the bonds of these surrounding elements allows the tabular iceberg to move away from the ice shelf cavity more easily.
-
-A wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice shelf cavity.
+Breaking the bonds of these surrounding elements allows the tabular iceberg to move away from the ice-shelf cavity more easily.
+
+A wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice-shelf cavity.
 Perturbation experiments were performed using other wind stress values.
 
-The tabular iceberg calving experiment is initialized using the ocean state from the static ice shelf experiment after 5 years of simulation time.
+The tabular iceberg calving experiment is initialized using the ocean state from the static ice-shelf experiment after 5 years of simulation time.
 In tabular iceberg calving experiment, the ice shelf and icebergs are allowed to decay as they melt. 
@@
 %\subsection{Coupled simulation}
-\subsection{Static ice shelf experiment}
-The LIISM results from the static ice shelf experiment fit well within the current understanding of ice-shelf cavity circulations based on ice shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
+\subsection{Static ice-shelf experiment}
+The LIISM results from the static ice-shelf experiment fit well within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
 The initial water temperatures inside the domain are warmer than the in-situ freezing point, and cause melting at the ice-shelf base.
@@
 As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_temp_v}b).
-This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice shelf melt.
+This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice-shelf melt.
 
@@
 These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice shelf front.\\
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front.\\
 \\
 %\subsubsection{Comparison with Eularian ice shelf model}
-\textbf{Comparison of LIISM and Eularian ice shelf model}\\
-The LIISM results from the static ice shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
-To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice shelf model with an identical configuration.
+\textbf{Comparison of LIISM and Eularian ice-shelf model}\\
+The LIISM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
+To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice-shelf model with an identical configuration.
 The results show that two simulations have very similar circulations (Figures \ref{fig:Bt_comparison}), melt rates and temperature/salinity profiles (see supplementary materials).
@@
 The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
-Recall that the role of the ice shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iii) alter the upper ocean boundary condition below the ice shelf.
+Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iii) alter the upper ocean boundary condition below the ice shelf.
 The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LIISM model, and that the LIISM is able to model sub-ice-shelf cavities as well as the Eularian model does.
@@
 
-\subsection{Tabular iceberg calving experiement}
-The tabular iceberg calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.
+\subsection{Tabular iceberg calving experiment}
+The tabular iceberg calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf (see animations of  in the supplementary materials).
 After the numerical bonds are severed, the tabular iceberg and smaller ice fragments calve away from the ice shelf and begin to move.
@@
 The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg (Figure \ref{fig:Collapse_solo_melt}).
-Large melt rates are observed at the newly calved ice shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving has created steep ice cliffs.
+Large melt rates are observed at the newly calved ice-shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving has created steep ice cliffs.
 These sharp ice fronts allow for large ocean currents (Figure \ref{fig:Collapse_solo_melt}c), which drive the elevated melt rates.
 These elevated melt rates act to smooth out the ice front over time, making the ice cliff less steep.
-While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
+While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice-shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
 
@@
 For wind stresses less that $\tau= ???$ the iceberg does not move away from the ice shelf.
-While this result is partly an artifact of the artificial shape of the calving iceberg, it is also consistent with \citet{Bassis2013} who noted that calving is a two step process consisting of (i) ice shelf breaking and (ii) iceberg detachment.
+While this result is partly an artifact of the artificial shape of the calving iceberg, it is also consistent with \citet{Bassis2013} who noted that calving is a two step process consisting of (i) ice-shelf breaking and (ii) iceberg detachment.
 The results here suggest that strong wind may be required to drive large tabular icebergs away from their mother glaciers.
@@
 Comparing the iceberg calving simulation with an identical simulation where all numerical bonds have been removed, shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
-In this case, the model behavior is more similar to an ice shelf disintegration and does not create a cohesive tabular iceberg.
+In this case, the model behavior is more similar to an ice-shelf disintegration and does not create a cohesive tabular iceberg.
 
@@
 One element which is missing from the LIISM ice shelf is that the ice shelf is not dynamic.
-Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice shelf geometry to change over time.
+Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice-shelf geometry to change over time.
 Much progress has been made in modeling ice-shelf flows in an Eularian framework \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
@@
 The other major innovation which will need to be introduced is a method for breaking numerical bonds.
-This is essentially equivalent to determining an ice shelf calving law, and is a famously difficult problem.
+This is essentially equivalent to determining an ice-shelf calving law, and is a famously difficult problem.
 One possible way that this could be done is to break bonds when the elastic stress in the bond is larger than a given yield stress of that bond.
@@
 The bond strength could also evolve dynamically as bonds get `damaged'.
-The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eularian ice shelf studies \citep{Pralong2005, Borstad2012}.
+The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eularian ice-shelf studies \citep{Pralong2005, Borstad2012}.
 
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_D_spread_mass_mass.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_spread_mass_mass.png}
 \caption{ {(a) Ocean bottom topography in MISOMIP configuration.
-(b) Ice shelf draft used in static shelf experiment.
+(b) ice-shelf draft used in static shelf experiment.
 The ice draft is calculated from the ice mass in an ocean grid cell, which is found by spreading ice mass across ocean cells accounting for the size of each element (as explained in Section 2.3).
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
-\caption{ {Results of the static ice shelf experiment using the LIISM model coupled to MOM6.
-Panels show cross sections of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity near the ice shelf base after 5 years of simulation.
+\caption{ {Results of the static ice-shelf experiment using the LIISM model coupled to MOM6.
+Panels show cross sections of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity near the ice-shelf base after 5 years of simulation.
 The region shown in panel (c) is indicated by the black box on panel (b),}}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Results of the static ice shelf experiment using the LIISM model coupled to MOM6.
+\caption{ {Results of the static ice-shelf experiment using the LIISM model coupled to MOM6.
 The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\caption{ {Time-averaged barotropic stream function in the (a) Eularian and (b) Lagrangian simulations in the static ice shelf configuration.
+\caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration.
 Panel (c) shows the difference between panels (a) and (b).
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment. Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
+\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse}} and \ref{fig:Velocity_section_Collapse}.}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Snapshots of vertical sections of ocean temperature at $x=70 $km in the LIISM tabular iceberg calving experiment. Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.}}
+\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The position of the vertical transects is shown by the dashed lines in Figure \ref{ig:Spread_area}c.}}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Collapse_temp.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp.png}
 \caption{ {Snapshots of the sea surface temperature in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
 Regions with ice area fraction = 1 area plotted in white.}}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {Snapshots of vertical sections of meridional velocity at $x=70 $km in the LIISM tabular iceberg calving experiment. Snapshots are taken (a) 15, (b) 30, and (c) 60 days after calving.}}
+\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The position of the transects is shown by the dashed line in Figure \ref{fig:Spread_area}c.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg_calved.png}
-\caption{ {Results of the tabular iceberg calving simulation 60 days after the iceberg calves.
+\caption{ {Results of the tabular iceberg calving simulation 30 days after the iceberg calves.
 The three panels show snapshots of the (a) melt rate, (b) top-of-ocean temperature and (c) $u^{*}$ at the base of the ice shelf.
@@
 
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ |c c c c| }
+\hline
+Parameter & Symbol & Value &  Unit \\
+\hline
+Domain Length &  $L_{x}$ & 80  & km \\
+Domain Width &  $L_{y}$ & 480  & km \\
+Viscosity &  $3.3\times 10^{9}$ & 209 & 104 \\
+Time step &  $1.8\times 10^{10}$& 426  & 104\\
+Class 5 &  $3.8\times 10^{10}$ & 518 & 104 \\
+Class 6 &  $7.5\times 10^{10}$ & 728  & 104\\
+Class 7 &  $1.2\times 10^{11}$ & 920  & 104 \\
+Class 8 &  $2.2\times 10^{11}$ & 1246  & 104\\
+Class 9 &  $3.9\times 10^{11}$ & 1659 & 104 \\
+Class 10 & $7.4\times 10^{11}$ &  2285  & 104\\
+%Class 1 &  $8.8\times 10^{7}$ & 60  & 0.0026 & 40 & 2000 \\
+%Class 2 &  $4.1\times 10^{8}$ & 100 & 0.0072 & 67 & 200\\
+%Class 3 &  $3.3\times 10^{9}$ & 200  & 0.029 &133 & 50 \\
+%Class 4 &  $1.8\times 10^{10}$& 350 &  0.12 &175  & 20 \\
+%Class 5 &  $3.8\times 10^{10}$ & 500  & 0.18 &250 & 10\\
+%Class 6 &  $7.5\times 10^{10}$ & 700   & 0.35 &250 & 5\\
+%Class 7 &  $1.2\times 10^{11}$ & 900  & 0.56 &250  & 2 \\
+%Class 8 &  $2.2\times 10^{11}$ & 1200  & 1.0&250 & 1 \\
+%Class 9 &  $3.9\times 10^{11}$ & 1600 & 1.8&250 & 1  \\
+%Class 10 & $7.4\times 10^{11}$ &  2200 & 3.5 &250  &1\\
+\hline
+\end{tabular}
+%\caption{Description of the iceberg calving classes used in the model.
+{\it Mass}, {\it Length}, {\it Area} and {\it Th} refer to the iceberg mass, length, area, and thickness at the time of calving.
+{\it Scaling} is the number of icebergs represented by one Lagrangian point particle.
+The iceberg mass and thickness for each class are the same as those reported in \citet{Gladstone2001}.
+The iceberg area and length for each class is calculated from the iceberg mass and thickness by assuming that the icebergs are cuboids with a length to width ratio of 1.5, using an iceberg density $\rho_{i}=850$kg/$\textrm{m}^{3}$.}
+% Note that the areas of the iceberg classes (calculated from the iceberg lengths and masses given in \citep{Gladstone2001}) are not monotonically increasing.
+\label{table:parameters2}
+\end{center}
+\end{table}
+
+\clearpage
+
 %\begin{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_salt_layers.png}
-\caption{ {Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model salinity fields.}}
+\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model salinity fields.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_melt.png}
-\caption{ {Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model melt fields.}}
+\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian Ice shelf model melt fields.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_temp_temp_v.png}
-\caption{ {Layered: Results of the static ice shelf experiment using the LIISM model.
+\caption{ {Layered: Results of the static ice-shelf experiment using the LIISM model.
 Panels show snapshots of cross sections of the (a) temperature field after 1 time step, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity after 5 years.}}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Layer: Results of the static ice shelf experiment using the LIISM model.
+\caption{ {Layer: Results of the static ice-shelf experiment using the LIISM model.
 The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
-\caption{ {Layer: Comparison of Eulerian ice shelf model and Lagrangian Ice shelf model barotropic stream function}}
+\caption{ {Layer: Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model barotropic stream function}}
 \end{center}

### 2017-01-27 Tech1.tex
Updated text, added parameter table.

@@
 The coordinate system was achieve using ALE regridding-remapping scheme \citep{White2009}.
-The model used a horizontal resolution of 2km, and 36 vertical layers.
+The model used a horizontal resolution of 2km, and 72 vertical layers.
 All simulation were repeated using the ocean model is run layered mode (results were similar and are not presented here).
@@
 The maximum ocean depth is $H_{ocean}=720$ m.
-A sponge layer is used on the northern boundary, which relaxes back to the initial temperature and salinity with a relaxation time scale of $\tau=0.1$ days.
+A sponge layer is used on the northern boundary, which relaxes back to the initial temperature and salinity with a relaxation time scale of $T_{sponge}=0.1$ days.
 Melting is set to zero for ocean cells where the ocean column thickness is less than 10m to avoid using more energy to melt ice than is present in the water column.
@@
 As mentioned above, the direction (and speed) of the iceberg drift is largely determined by the wind speed and direction.
-Perturbation experiments using different wind stresses showed that the iceberg drifts to the north east for positive zonal wind stresses and to the north west for negative zonal wind stresses.
-For wind stresses less that $\tau= ???$ the iceberg does not move away from the ice shelf.
+Perturbation experiments using different wind stresses showed that for sufficiently large winds, the iceberg drifts to the north east when the zonal component of the wind stresses is positive, and to the north west when the zonal component of the wind stress is negative.
+For a purely zonal wind stress with $\tau_{x} \leq 0.01 \frac{\textrm{N}}{\textrm{m}^{2}}$, the iceberg does not move away from the ice shelf.
+When the wind is purely offshore ($\tau_{x} = 0.0 \frac{\textrm{N}}{\textrm{m}^{2}}$), a meridional wind stress $\tau_{y} \geq 0.05 \frac{\textrm{N}}{\textrm{m}^{2}}$ is needed to move the tabular iceberg away from the ice shelf.
 While this result is partly an artifact of the artificial shape of the calving iceberg, it is also consistent with \citet{Bassis2013} who noted that calving is a two step process consisting of (i) ice-shelf breaking and (ii) iceberg detachment.
-The results here suggest that strong wind may be required to drive large tabular icebergs away from their mother glaciers.
+The results here suggest that strong (cross-shore) winds may be required to drive large tabular icebergs away from their mother glaciers.
 
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_salt_layers.png}
-\caption{ {Results from the tabular iceberg calving experiment using the LIISM model coupled to an ocean model.
-The top row shows the average draft of ice above the ocean for the simulation (a) with and (b) without numerical bonds.
-The bottom row shows the corresponding temperature section at $x=\frac{L_{x}}{2}$ for the simulation (a) with and (b) without bonds.
-All snapshots are taken at time t = 30 days.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_temp_layers.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_salt_layers.png}
+\caption{ {Results from the tabular iceberg calving experiment with and without iceberg bonds.
+The top row shows the fractional ice cover for the simulations (a) with and (b) without numerical bonds.
+The bottom row shows the corresponding vertical temperature section at $x=58 $km for the simulation (c) with and (d) without bonds.
+The location of the vertical transects in panels (c) and (d) are shown by the dashed lines in panels (a) and (b), respectively.
+All snapshots are taken at time t = 30 days.
+The simulations uses wind stress $\vec{\tau}=< 0.0, 0.05 >.$}}
 \end{center}
@@
 Domain Width &  $L_{y}$ & 480  & km \\
-Viscosity &  $3.3\times 10^{9}$ & 209 & 104 \\
-Time step &  $1.8\times 10^{10}$& 426  & 104\\
-Class 5 &  $3.8\times 10^{10}$ & 518 & 104 \\
-Class 6 &  $7.5\times 10^{10}$ & 728  & 104\\
-Class 7 &  $1.2\times 10^{11}$ & 920  & 104 \\
-Class 8 &  $2.2\times 10^{11}$ & 1246  & 104\\
-Class 9 &  $3.9\times 10^{11}$ & 1659 & 104 \\
-Class 10 & $7.4\times 10^{11}$ &  2285  & 104\\
+Horizontal Resolution &  $\Delta x$ & 2  & km \\
+Number of vertical layers &  $N_{l}$ & 72  & non-dim\\
+Horizontal Viscosity &  $\nu_{H}$ & 6.0 & $\frac{m^{2}}{s}$ \\
+Diapycnal Viscosity &  $\nu_{V} $ & $10^{-3}$ & $\frac{m^{2}}{s}$ \\
+Horizontal Diffusivity & $ \epsilon_{H}$ & 1.0 & $ \frac{m^{2}}{s}$ \\
+Diapycnal Diffusivity &  $\epsilon_{V} $ & $5 \times 10^{-5}$ & $\frac{m^{2}}{s}$ \\
+Initial Surface Temperature &  $ T_{t}$& -1.9   & $ ^{o} C$\\
+Initial Bottom Temperature &  $ T_{b}$&  1.0  & $ ^{o} C$\\
+Initial Surface Salinity &  $ S_{t}$& 33.8   & psu\\
+Initial Bottom Salinity &  $ S_{b}$&  34.7  & psu\\
+Maximum Ocean depth &  $H_{ocean} $ & 720 & m \\
+Relaxation Time of Sponge Layer &  $T_{sponge}$ & 0.1  & days\\
+%Background Frictional Velocity Below Ice &  $u^{*}_{bg}$ & 0.0  & 104 \\
+%Drag Coefficient Below Ice&  c_{d} & $0.0025$  & (non dim)\\
+%Class 9 &  $3.9\times 10^{11}$ & 1659 & 104 \\
+Time Step for Static Shelf Experiment & $dt_{Static}$ &  1000  & s\\
+Time Step for Iceberg Calving Experiment & $dt_{Calving}$ &  10  & s\\
 %Class 1 &  $8.8\times 10^{7}$ & 60  & 0.0026 & 40 & 2000 \\

### 2017-02-08 Icebergs_only.tex
Adding iceberg only version of the paper

--- 2017-01-27 Tech1.tex
@@
 %\titlerunninghead{Effects of iceberg calving size}
-\titlerunninghead{THE EFFECTS OF ICEBERG CALVING SIZE}
+\titlerunninghead{Modeling tabular icebergs}
 
@@
 %\title{The effect of calving-size distribution on sea-ice formation around Antarctica}
-\title{Modeling ice-shelf cavities and calving tabular icebergs}
+\title{Modeling tabular icebergs coupled to an ocean model}
 %\title{The effects of iceberg calving-size distribution in a global climate model}
@@
 \begin{abstract}
-The calving of giant icebergs is an important process in the Antarctic freshwater cycle.
-Iceberg calving can significantly alter the geometry of an ice-shelf cavity, potentially affecting the circulation within the cavity.
-Giant icebergs which break away can drift across large distance, altering regional ocean circulation, sea ice distributions and bottom water formation.
-However, despite its importance, the current generation of numerical models is unable to represent this process in a physically realistic way.
-In this study we develop a model of an ice-shelf cavity using a Lagrangian ice shelf.
-The ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
-This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-The model developed in the manuscript is referred to as the Lagrangian Iceberg/Ice Shelf Model (LIISM).
-This paper provides a description of the LIISM model and discusses a number of the technical elements involved in building a Lagrangian ice shelf.
-To test the model, the LIISM is used to model an idealized ice-shelf cavity which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-Results from static ice-shelf experiments compare well to results using a more traditional Eularian ice-shelf models.
-The novel capabilities of the  LIISM are demonstrated by modeling a tabular iceberg breaking away from the idealized ice shelf.
-
+The calving of giant icebergs from the Antarctic ice shelves accounts for approximately half of Antarctic ice-shelf decay.
+After calving these tabular icebergs drift across large distances, altering regional ocean circulation, bottom water formation and local rates biological primary productivity.
+Freshwater fluxes from sub-marine melting can affect large-scale sea-ice distributions, which feedback onto the greater climate system.
+However, despite their importance, the current generation of numerical models is unable to represent giant tabular icebergs a physically realistic way.
+In this study we develop novel method to model giant tabular icebergs. Tabular icebergs are constructed out of Lagrangian elements which are bonded together by numerical bonds. 
+These numerical bonds hold the ice element together and allow the individual elements to move as a unit.
+By breaking these bonds, we can simulate the  ocean response to giant iceberg detaching away from an ice shelf (also constructed from Lagrangian elements) or the fracturing of a large iceberg into smaller pieces.
+This paper provides a description and demonstration of the Lagrangian tabular-iceberg model and discusses a number of the technical elements involved its development.
+%We demonstrate the capabilities of the model by modeling a tabular iceberg breaking away an idealized ice shelf.
 \end{abstract}
@@
 %\subsection{Introduction}
-Floating ice shelves cover vast regions of the Antarctic polar oceans.
-These massive platforms of ice extend deep into the water column, applying large pressures to surface of the ocean, which is often hundreds of meters below global sea level.
-Beneath the ice shelves, both the bottom topography and the ice-shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}.
-The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean within the ice shelves cavities a unique character.
-
-In addition to suppressing the depth of ocean surface, the ice shelves also melt (and break), thus providing a freshwater flux into the ice-shelf cavities. 
-%Perhaps remove this line....:
-This melting and breaking of Antarctic ice shelves is a key component in the Antarctic meltwater system.
-%, and affect the ocean hydrography and biology both inside and outside of the ice shelf cavities. %Some elements of this Antarctic meltwater system are discussed in the following paragraphs. 
-%
-Within the ice-shelf cavities, the input of buoyant meltwater into the ocean creates rising density plumes, which are guided along the ice-shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
-The strength of the circulation within the cavity feeds back onto the ice-shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice-shelf melt \citep{Lewis1986, Jacobs2011}.
-
-The Antarctic ice shelves are also characterized by large infrequent calving events where massive pieces of the ice shelves break off, to create giant tabular icebergs.
-Observational estimates suggest that approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
-Calving icebergs' sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}.
+
+The Antarctic ice shelves are characterized by large infrequent calving events where massive pieces of the ice shelves break off, to create giant tabular icebergs.
+Observational estimates suggest that over the past 30 years approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
 After calving, icebergs slowly drift away from their mother glaciers, often becoming stuck in sea ice, or become grounded along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}.
-Giant tabular icebergs also extend deep into the water column, and have to potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
-
-Melt water from both ice-shelf melt and iceberg melt impact the ocean hydrography outside of the ice-shelf cavities, influencing sea ice production and bottom water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
+Giant tabular icebergs extend deep into the water column, and have to potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
+Iceberg sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while the far less numerous giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}.
+
+Freshwater fluxes from iceberg melt impact ocean hydrography, influencing sea-ice production and bottom-water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
 The long distances traveled by giant icebergs before melting means that their meltwater impact is often felt hundreds of kilometers away from their calving origins \citep{Stern2016}.
-Melt water injection (and the accompanying upwelling) from ice shelves and icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}.
+Melt water injection (and the accompanying upwelling) from icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}.
 The increased productivity associated with free-floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.
@@
 
-In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic meltwater system described in the previous paragraphs.
-This increased interest has led to accelerated efforts to accurately model Antarctic ice-shelf cavities \citep{Asay-Davis2016}.
-Modeling the ocean beneath the ice shelves presents a unique set of challenges, since (i) the presence of ice shelves provides a rigid upper boundary for the ocean model which is not encountered elsewhere in the ocean, and (ii) melting and breaking ice shelves imply a changing ocean boundary conditions which present numerous numerical difficulties.
-
-The earliest models of ocean ice-shelf cavities were developed using a static ice shelves with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
-In these models, ice-shelf melting was represented through salinity and temperature fluxes, while the ice-shelf geometry remained unchanged.
-Later models of ice-shelf cavities allowed the ice-shelf geometry to evolve as the ice shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}.
-More recently, dynamic ice-shelf models have been coupled the ocean cavity, allowing the study of grounding line migration, which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
-As far as we know, all models of ice-shelf cavities to date have neglected ice-shelf breaking and iceberg detachment.
-
-In parallel to these efforts to develop ice-shelf cavity models, a number of iceberg drift models have been developed, and have been included in some global General Circulation Models \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
-These iceberg drift models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
-Since icebergs are treated as point particles, the iceberg drift models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such iceberg drift models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
-These models are not suitable for modeling larger tabular icebergs, which feel the ocean over many grid cells, depress the ocean surface and change circulation patterns \citep{Stern2016}.
-They also not suitable for studying  the local effects that icebergs have on the surrounding ocean.
-For this reason, tabular icebergs (L $>$ 5km) are currently not represented in the iceberg drift models used in climate models, even though observations suggest that tabular icebergs account for  the vast majority of the total Southern Hemisphere icebergs mass \citep{Tournadre2016}.
-
-The ice-shelf cavity models and iceberg drift models described above have been developed separately from one another, and have not been designed to be used together in a physically consistent way.
-As such, it has not been possible to model the calving of tabular icebergs away from an ice shelf, which is an important part of the Antarctic climate system.
-The goal of this study is to develop a model which combines features of the ice-shelf cavity models and the iceberg drift models, to create an ice-shelf cavity model that is able to calve tabular icebergs.
-To do this, we create an ice-shelf model out of Lagrangian elements which are `bonded' together by numerical bonds.
-In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break away' from an existing ice shelf, thus changing the geometry of the ice-shelf cavity.
-Modeling iceberg calving in a physically consistent way allows us to study the ocean response to iceberg detachment.
-%(see Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top}, for example).  
-Also, by allowing icebergs protrude deep into the water column we can study the ocean dynamics around individual tabular icebergs (which was not possible in iceberg drift models).
-
-In all simulation in this study, the shape of the calving iceberg is prescribed.
-The question of how to correctly prescribe a calving law is undoubtably a very important question, which has rightfully received much attention in recent years \citep{Benn2007, Alley2008, Levermann2012}.
-\citet{Bassis2013}, for example, used a discrete element model (DEM) model to study the generation and propagation of cracks within an ice shelf (not coupled to an ocean model).
-In this study, we bypass the question of how to correctly calve icebergs or break bonds.
-Instead we focus on developing a framework to model the ocean response to ice-shelf breaking and the presence of tabular icebergs.
-This framework of representing ice shelves using a Lagrangian grid might be a step towards including giant tabular icebergs in climate models.
-Including ice fracture into this model will be a later step.
-
-The model developed in this study is referred to at the Lagrangian Iceberg/Ice Shelf Model (LIISM).
-Section 2 gives a description of many of the key aspects of the LIISM.
-Since this model is a new approach to modeling ice-shelf cavities, we present many of the technical elements involved in constructing the model.
-Those readers who are more interested in the model capabilities, should skip directly to the numerical experiments presented in the later sections.
-In Section 3 and 4, the LIISM model is used to simulate the circulation beneath an idealized ice shelf.
-The LIISM model results are validated by comparing them to an existing Eularian ice-shelf model.
-We then we move beyond the capabilities of the existing ice-shelf model by allowing a piece of the ice shelf to break away, becoming a tabular icebergs, and consider the ocean response to this calving event.
+In recent years, there has been an increased interest in iceberg drift and decay.
+This surge of interest has been driven by (i) the need to understand polar freshwater cycles in order to create realistic climate forecasts and sea level projections \citep{Silva2006, Shepherd2007, Rignot2013}, (ii) the increased use of high-latitudes iceberg-filled waters for shipping lanes and offshore hydrocarbon exploration \citep{Pizzolato2014, Unger2014, Henderson2016}.
+The increased interest in icebergs has led to the development of numerical models of iceberg drift and decay \citep{Mountain1980, Bigg1997, Gladstone2001, Kubat2005}, some of which have been included in global General Circulation Models \citep{Martin2010, Marsh2015}.
+These iceberg models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
+Since icebergs are treated as point particles, the iceberg models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such iceberg models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
+These models are not suitable for modeling larger tabular icebergs (or smaller icebergs at fine scales), where the size and structure of the iceberg may be an important feature in determining their drift and decay \citep{Stern2016}.
+They also are not suitable for studying the local effects that icebergs have on the surrounding ocean.
+For this reason, tabular icebergs (L $>$ 5km) are currently not represented in the iceberg models used in climate models, even though observations suggest that tabular icebergs account for  the vast majority of the total Southern Hemisphere icebergs mass \citep{Tournadre2016}.
+Similarly, operational iceberg models are often inadequate for projecting iceberg drift at fine scales \citep{Turnbull2015}.
+
+The goal of this study is to develop a new iceberg model where tabular icebergs are explicitly resolved in the ocean.
+In this model, icebergs are no longer treated as point particles that feel the ocean at one point, but rather the icebergs have structure, depress the ocean surface, and can feel the ocean across multiple ocean grid cells.
+To do this, we create tabular icebergs out of many Lagrangian elements which are `bonded' together by numerical bonds.
+The numerical bonds hold the ice elements together and allow a collection elements to move as a unit.
+By manually breaking these bonds, we can simulate iceberg calving, allowing us to study the ocean response to giant iceberg detaching from an ice shelf or the fracturing of a large iceberg into smaller pieces.
+
+The discrete element model (DEM) developed in this study is referred to at the Lagrangian Tabular Iceberg Model (LTAM).
+Section 2 gives a description of many of the key aspects of the LTAM.
+Since this model is a new approach to modeling iceberg, we present many of the technical elements involved in constructing the model.
+In Section 3 and 4, we demonstrate the capabilities of the model by simulating a tabular iceberg detaching from an idealized ice shelf.
 
@@
 %, which can be used to model small icebergs, tabular icebergs, sea ice and ice shelf cavities
-%In this section we describe many key elements of the LIISM.  
-The LIISM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
+%In this section we describe many key elements of the LTAM.  
+The LTAM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
 Each element represents a mass of ice which is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time.
 The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element.
-The elements are forced by oceanic and atmospheric forces, which are provided by the user, or are determined by coupling the LIISM to an ocean/atmosphere model.
+The elements are forced by oceanic and atmospheric forces, which are provided by the user, or are determined by coupling the LTAM to an ocean/atmosphere model.
 The elements also interact with one another and can be bonded together to form larger structures.
-In different contexts, the LIISM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
-%In this latter case, the LIISM model can be categorized as a discrete element model (DEM). 
+The angular momentum of the elements is not model explicitly, instead rotational motion of larger structures emerge as a consequence of bond orientation.
+In different contexts, the LTAM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
+%In this latter case, the LTAM model can be categorized as a discrete element model (DEM). 
 % in the sense that large structures are constructed from smaller independent Lagrangian elements.
 
-The LIISM model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}.
+The LTAM model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}.
 When run with the correct set of runtime flags, the model runs as a traditional iceberg drift model.
@@
 The elements drift in the ocean, forced by atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force and a force due to the sea surface slope.
-When these ice elements move alone (without interactions with other elements), they can be thought of as representing of small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).
-
-In addition to the environmental forces, the elements in the LIISM model experience interactive forces due to the presence of other elements.
+When these ice elements move alone (without interactions with other elements), they can be thought of as representing individual (or clusters of) small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).
+
+In addition to the environmental forces, the elements in the LTAM model experience interactive forces due to the presence of other elements.
 Two types of interactive forces are included between elements.
@@
 \end{equation}
-We then define the interaction diameter of an element by 
+When calculating the interactive forces between elements, the elements are assumed to be circular. We define the interaction diameter of an element by 
 \begin{equation}
@@
 which governs interactions between elements i and j. 
-Repulsive forces are only applied when $d_{i,j} \textless L_{i,j}$, while bonded forces are only applied when the when $d_{i,j} \textgreater L_{i,j}$ and a bond exists between element i and j.
-Bond and repulsive forces are designed to such that in the absence of other forces, bonded particles will settle in an equilibrium position where elements are separated by the critical interaction length scale $L_{i,j}$.
+Repulsive forces are only applied when $d_{i,j} \textless L_{i,j}$, while for $d_{i,j} \textgreater L_{i,j}$ attractive bonded forces are applied when a bond exists between element i and j.
+Bond and repulsive forces are designed such that in the absence of other forces, bonded particles will settle in an equilibrium position where elements are separated by the critical interaction length scale $L_{i,j}$.
 % (see schematic in Figure \ref{fig:Interactive_forces}).
@@
 \subsection{Element geometry and packing}
-Elements are packed differently depending on the shape of the elements.
-For all simulations in this study, we use elements whose surface areas are equally-sized regular hexagons.
-In order to pack these elements together, the hexagonal elements are initially arranged in a staggered lattice, with each element bonded to the adjacent elements (see Figure  \ref{fig:Hex_intersections}a).
+For purposes of packing, we assume that elements have surface areas which are shaped as equally-sized regular hexagons (note that the elements are assumed to be circular for proposes of interactions, but are assumed to be hexagonal for packing purposes).
+When packing these elements together, the hexagonal elements are initially arranged in a staggered lattice, with each element bonded to the adjacent elements (see Figure  \ref{fig:Hex_intersections}a).
 In this arrangement, each element (away from the edges) is bonded to six other elements.
 The bonds between elements form a pattern of equilateral triangles, which give the larger structure rigidity.
+The circular shape of elements (used for interactions) is inscribed within the hexagonal shape used for packing (Figure  \ref{fig:Hex_intersections}a).
+The centers of adjacent elements are initially separated by a distance $d_{i,j}=L_{i,j}=2A_{p}$, where $A_{p}$ is the length the apothems of the hexagons.
 
@@
 However, the resultant structures were found to be much less rigid and tended to collapse when sufficient forces was applied.
-For this reason, hexagonal elements were preferred.
+For this reason, hexagonal elements are used here.
 
 \subsection{Ocean-ice and ice-ocean coupling}
-The LIISM model is coupled to the ocean model via a two-way synchronous coupling, meaning that ocean model fields are passed to the LIISM model and the LIISM model fields are passed back to the ocean model at every time step.
-Passing fields between the two models involves interpolating fields between the Eulerian grid of the ocean model and the `Lagrangian grid' of the LIISM model (i.e.: onto the ice elements).
-
-The coupling from the ocean model to the LIISM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LIISM model, to be used in the momentum and thermodynamic equations of the ice elements.
-Within the LIISM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme.
-The LIISM model is not sensitive to the chosen interpolation scheme.
-
-%More care needs to be taken when passing fields back from the LIISM model to the ocean model. 
-The coupling in the other direction, from the LIISM model to the ocean model, is more complex.
-The LIISM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean by applying a no-slip boundary condition and frictional velocity beneath the ice.
-Fields from the LIISM model are interpolated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model.
-Since the LIISM model applies large pressures to the ocean surface, the ocean model is sensitive to the interpolation scheme used to map the LIISM fields to the ocean grid.
+The LTAM model is coupled to the ocean model via a two-way synchronous coupling, meaning that ocean model fields are passed to the LTAM model and the LTAM model fields are passed back to the ocean model at every time step.
+Passing fields between the two models involves interpolating fields between the Eulerian grid of the ocean model and the `Lagrangian grid' of the LTAM model (i.e.: onto the ice elements).
+
+The coupling from the ocean model to the LTAM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LTAM model, to be used in the momentum and thermodynamic equations of the ice elements.
+Within the LTAM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme.
+The LTAM model is not sensitive to the chosen interpolation scheme.
+
+%More care needs to be taken when passing fields back from the LTAM model to the ocean model. 
+The coupling in the other direction, from the LTAM model to the ocean model, is more complex.
+The LTAM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean by applying a no-slip boundary condition and frictional velocity beneath the ice.
+Fields from the LTAM model are interpolated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model.
+Since the LTAM model applies large pressures to the ocean surface, the ocean model is sensitive to the interpolation scheme used to map the LTAM fields to the ocean grid.
 Sudden jumps to the ocean surface pressure can trigger tsunamis within the ocean model, making the ocean model become unstable.
 
-The interpolation of the LIISM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LIISM model (see Section 2.3).
+The interpolation of the LTAM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LTAM model (see Section 2.3).
 Fields are `spread' to the ocean model grid by exactly calculating what fraction of an element's surface area lies in a particular grid box, and dividing the field in proportion to this fraction.
 %While the position of a particular element might be inside one ocean grid cell, the implied shape of the element will often intersect other ocean grid cells. 
-For example, consider a hexagonal element in the LIISM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
+For example, consider a hexagonal element in the LTAM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
 In this situation, the mass of the element is divided between these four ocean cells in proportion to the overlap area between the hexagonal element and the grid cell (this fraction is shown by the colors in \ref{fig:Hex_intersections}b).
@@
 This method allows for the intersection to be found even when the hexagon is not aligned with the grid.
-%The LIISM model can be run using hexagonal or rectangular elements.
+%The LTAM model can be run using hexagonal or rectangular elements.
 
@@
 
-When multiple elements are bonded together to form larger structures, it is no long appropriate to use the parameterizations for melt developed for individual point-particle icebergs.
+When multiple elements are bonded together to form larger structures, it is no longer appropriate to use the parameterizations for melt developed for individual point-particle icebergs.
 An element which is completely surrounded by other elements, is meant to represent a piece of ice in the middle of a large structure, and hence will not experience a melt at its sides due to wave erosion or buoyant convection.
@@
 In this subsection we comment on some of the algorithmic procedures that have been used to increase the computational efficiency.
-Readers who are not interested in this more technical side of the model should skip this section.
-\subsubsection{Time stepping}
-The ice elements in the LIISM model are advected using a semi-implicit velocity Verlet time-stepping scheme.
-The velocity verlet time stepping scheme is commonly used in DEM models in video games because it is computational efficient and has desirable stability properties \citep{Jakobsen2001}.
-This time stepping scheme was preferred to the Runge-Kutta  4, which was used in the iceberg model of \citet{Martin2010} since, the Verlet time stepping only requires one calculation of the interactive forces per time step (while the Runge-Kutta scheme requires the interactive forces to be calculated four times).
-Since the calculation of the interactive forces is one of the most computationally expensive part of the algorithm, the Verlet scheme leads to a significant increase in the speed of the model.
-We note that the Verlet scheme used in the LIISM contains a small modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
-The details of this time stepping schemed are outline in Appendix B.
+
 \subsubsection{Interactions and Bonds}
@@
 The data storage system works as follows: pointers to the memory structures containing each element are stored in linked list data structures, which allow elements to be added and removed from the lists easily without restructuring the entire list.
-Instead of using one list for all the elements on a processor, we use a separate linked list for each ocean grid cell.
+Instead of using one list for all the elements on a processor (as was done in the original code \citep{Martin2010}), we use a separate linked list for each ocean grid cell.
 When an element moves between ocean grid cells, it is removed from its original list and added to the list corresponding to its new ocean grid cell.
@@
 
-Bonded interactions are handled slightly differently.
+Bonded interactions are handled differently.
 Each bond is assigned a piece of memory.
@@
 At each time step, the code traverses the lists of bonded elements, and adds a bonded force corresponding to these bond.
-The bonded force is only applied if $\vec{r}_{i,j} > L_{ij}$, to avoid double counting an interaction.
+The bonded force is only applied if $d_{i,j} > L_{ij}$, to avoid double counting an interaction.
 Having a list of bonds stored with each element reduces the computational complexity of bonded interactions from order $n^{2}$ to order n.
@@
 \subsubsection{Parallelization and halos}
-The LIISM model runs on multiple processors in parallel.
+The LTAM model runs on multiple processors in parallel.
 When elements move from an ocean cell on one processor to an ocean cell on a second processor, the memory has to be passed from one processor the next, added and removed to the appropriate lists and the memory has to be allocated and deallocated correctly.
@@
 After each time step, these halos and removed, and the process is repeated.
-These halo updates are one of the most computationally expensive parts of the LIISM model.
+These halo updates are one of the most computationally expensive parts of the LTAM model.
 
@@
 Details of how the bonds are broken and reconnected across processor boundaries are provided in Appendix~C.
+
+\subsubsection{Time stepping}
+The ice elements in the LTAM model are advected using a semi-implicit velocity Verlet time-stepping scheme.
+The velocity verlet time stepping scheme is commonly used in DEM models in video games because it is computational efficient and has desirable stability properties \citep{Jakobsen2001}.
+This time stepping scheme was preferred to the Runge-Kutta  4, which was used in the iceberg model of \citet{Martin2010} since, the Verlet time stepping only requires one calculation of the interactive forces per time step (while the Runge-Kutta scheme requires the interactive forces to be calculated four times).
+Since the calculation of the interactive forces is one of the most computationally expensive part of the algorithm, the Verlet scheme leads to a significant increase in the speed of the model.
+We note that the Verlet scheme used in the LTAM contains a small modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
+The details of this time stepping schemed are outline in Appendix B.
 
@@
 
-%We demonstrate this capability in an experimental setup using an idealized ice shelf. For these experiments the LIISM model is coupled to the MOM6 ocean model.
+%We demonstrate this capability in an experimental setup using an idealized ice shelf. For these experiments the LTAM model is coupled to the MOM6 ocean model.
 % This section contains a description of the experimental setup and numerical experiments performed. The results of these simulations are presented in Section 4.
 
- %In the examples below, the LIISM model is firstly used in uncoupled mode to model the movement of freely drifting icebergs.
-Secondly, the coupled LIISM with static ice elements is used to model an idealized ice shelf cavity.
-Finally, the fully-coupled LIISM is used to model a tabular iceberg which calves off of this ice shelf.
+ %In the examples below, the LTAM model is firstly used in uncoupled mode to model the movement of freely drifting icebergs.
+Secondly, the coupled LTAM with static ice elements is used to model an idealized ice shelf cavity.
+Finally, the fully-coupled LTAM is used to model a tabular iceberg which calves off of this ice shelf.
 
 %\subsection{Uncoupled simulation}
-%We begin by demonstrating the LIISM model uncoupled to the ocean.
+%We begin by demonstrating the LTAM model uncoupled to the ocean.
 For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide.
@@
  \section{Experiment Setup}
-The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice-shelf cavities which undergo large calving events.
-We demonstrate this capability by performing numerical experiments with the LIISM model coupled to the MOM6 ocean model \citep{Hallberg2013}.
+The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we now have the tools to model giant tabular icebergs submerged in the ocean.
+We demonstrate this capability by performing a simulation of a tabular iceberg drifting away from an idealized ice shelf.
+This simulation is performed using the LTAM model coupled to the MOM6 ocean model \citep{Hallberg2013}.
 %This section describes the experimental setup of these numerical experiments. The results are shown in Section 4.
 
-\subsection{MISOMIP configuration}
-In order for our (pre-calving) simulations to be easily comparable to previous models of ice-shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
-%For this experiment, we use the ice-shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
-The MISOMIP configuration was developed as a standardized configuration to allow for a comparison between various ocean-ice coupled models.
+ \subsection{Model configuration}
+We initialized our simulation using the experimental setup created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
 The configuration consists of an idealized ice shelf in a rectangular domain.
-The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650km.
+The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650 km.
 The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference.
@@
 
-The LIISM model is coupled to the MOM6 ocean model. 
-The ocean model is run in using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
-In particular, model layers bend underneath the ice shelf as they would in a sigma model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
+%\textbf{Initializing Lagrangian elements:}\\
+\subsection{Initializing Lagrangian elements:}
+The idealized ice shelf is constructed out of Lagrangian ice elements.
+Ice elements are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
+The sides of the gridded hexagons are initialized with length $S=0.98$ km.
+Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
+Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
+The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
+
+Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
+Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
+When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice-shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
+The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
+
+\subsection{Ocean model setup}
+The LTAM model is coupled to the MOM6 ocean model.
+The ocean model is run using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
+In particular, model layers bend underneath the ice shelf as they would in a sigma-coordinate model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
 The coordinate system was achieve using ALE regridding-remapping scheme \citep{White2009}.
-The model used a horizontal resolution of 2km, and 72 vertical layers.
-All simulation were repeated using the ocean model is run layered mode (results were similar and are not presented here).
+The model uses a horizontal resolution of 2km, and 72 vertical layers.
+All simulation were repeated using the ocean model run layered mode (results were similar and are not presented here).
 %(select results are shown in the supplementary material). 
 Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
-The simulation is initially at rest, with horizontally uniform initial ocean temperature  (Figure \ref{fig:static_solo_temp_temp_v}a) and salinity profiles that vary linearly between specified surface and bottom values.
+The simulation is initially at rest, with horizontally uniform initial ocean temperature and salinity profiles that vary linearly between specified surface and bottom values.
 The initial surface temperature and salinity are  $T_{t}=-1.9^{\circ}$C and $S_{t}=33.8$ psu, respectively.
@@
 
-%\textbf{Initializing Lagrangian elements:}\\
-\subsection{Initializing Lagrangian elements:}
-Ice elements in the LIISM model are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
-The sides of the gridded hexagons are initialized with length $S=0.98$ km.
-Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
-Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
-The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
-
-Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
-Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
-When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice-shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
-The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
-
-\subsection{Numerical experiment}
-\begin{enumerate}
-\item
-\textbf{Static ice-shelf experiment:}\\
-%\subsection{Static ice shelf experiment}
-In the first experiment, we use a static ice shelf where the velocity of all ice elements is set to zero.
-In this experiment, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as in the Ocean0 experiement in the MISOMIP \citep{Asay-Davis2016}).
-In this setup, ice-shelf melting generates a temperature and salinity flux into the ocean, but does not change the thickness of the ice shelf.
-This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
-
-Results of the static ice-shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_mass_and_topog}b).
-Results from the static ice-shelf experiment are analyzed after 5 years of model spinup.
-
-%Another set of experiments were performed using a static ice shelf which decays as it melts. The results over a 5 year period were fairly similar to the non-decaying shelf, and are not shown.
-
-% \subsection{Decaying ice shelf experiment}
-%In the second experiment, the LIISM ice shelf is allowed to decay as the ice melts.
-This setup provides a more challenging test of the ocean-ice coupling, as the ocean responds to a moving lateral boundary.
-For this experiment, we increase the temperature of initial temperature profile and the sponge layer by 4 degrees, to make the ice shelf decay more rapidly.
-
-\item
- \textbf{Tabular iceberg calving:}\\
+\subsection{Spinup and iceberg calving:}
 % \subsection{Tabular iceberg calving}
-Next, we preform a numerical experiment which demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice-shelf models.
-In this experiments we break off a large piece of the ice shelf and allow it to drift into the ocean as a tabular iceberg.
-
-All ice elements initially within a 14.4 km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held are stationary.
+The model is spun up for 5 years with all ice elements being held stationary.
+After spinup, a giant tabular iceberg is 'broken off' from the ice shelf, and allowed to drift into the open ocean.
+This is achieved by allowing all ice elements initially within a 14.4 km radius of the center of the ice front to move freely while the other ice elements continue to be held stationary.
 Ice elements less than 12 km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
@@
 Perturbation experiments were performed using other wind stress values.
-
-The tabular iceberg calving experiment is initialized using the ocean state from the static ice-shelf experiment after 5 years of simulation time.
-In tabular iceberg calving experiment, the ice shelf and icebergs are allowed to decay as they melt. 
-\end{enumerate}
 
@@
 
-\section{Results}
+\section{Model Results}
 
@@
 %\subsection{Coupled simulation}
-\subsection{Static ice-shelf experiment}
-The LIISM results from the static ice-shelf experiment fit well within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
-The initial water temperatures inside the domain are warmer than the in-situ freezing point, and cause melting at the ice-shelf base.
-The melt water entering the domain is more buoyant than the water around it, and rises  along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_temp_v}b, c).
-As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_temp_v}b).
-This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice-shelf melt.
-
-The highest melt rates are observed within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
-These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front.\\
-\\
-%\subsubsection{Comparison with Eularian ice shelf model}
-\textbf{Comparison of LIISM and Eularian ice-shelf model}\\
-The LIISM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
-To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice-shelf model with an identical configuration.
-The results show that two simulations have very similar circulations (Figures \ref{fig:Bt_comparison}), melt rates and temperature/salinity profiles (see supplementary materials).
-The differences between the barotropic stream functions of the two simulations (for example) are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems [double check that this is correct].
-
-The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
-Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iii) alter the upper ocean boundary condition below the ice shelf.
-The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LIISM model, and that the LIISM is able to model sub-ice-shelf cavities as well as the Eularian model does.
-This is a good starting point for moving beyond the capabilities of the Eularian model.
 
@@
 The melt rates of the Eulerian and Lagrangian models are very similar with slight difference showing up at the grounding line and ice front (Figure \ref{fig:Melt_comparison}).
-The slight difference at the grounding line are a result of the fact that elements in the LIISM model are smaller than a grid cell in length.
-This means that ice element near the grounding line may be ungrounded in the LIISM model, while the grid cell is considered grounded in the Eularian model.
-At the ice front, the Eularian model has a straight ice front, while the LIISM model has a staggered ice front, which is a result of the staggered hexagonal packing.
+The slight difference at the grounding line are a result of the fact that elements in the LTAM model are smaller than a grid cell in length.
+This means that ice element near the grounding line may be ungrounded in the LTAM model, while the grid cell is considered grounded in the Eularian model.
+At the ice front, the Eularian model has a straight ice front, while the LTAM model has a staggered ice front, which is a result of the staggered hexagonal packing.
 
@@
 
-\subsection{Tabular iceberg calving experiment}
-The tabular iceberg calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf (see animations of  in the supplementary materials).
-After the numerical bonds are severed, the tabular iceberg and smaller ice fragments calve away from the ice shelf and begin to move.
+%\subsection{Tabular iceberg calving experiment}
+
+During spinup, injection of positive buoyancy due to melting at the base of the ice shelf drives a circulation within the domain (not shown).
+The circulation compares well with an identical experiment run using an Eularian ice shelf model \citep{Goldberg2012}  (a detailed comparison of the Lagrangian and Eularian ice shelf models is presented in a separate study, and is not shown here).
+
+After spinup, the numerical bonds are severed, and the tabular iceberg and smaller ice fragments calve away from the ice shelf and begin to move (see animations in the supplementary materials).
 The tabular iceberg drifts to the northward east, driven by the wind and steered by the Coriolis force (Figure \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
@@
 These elevated melt rates act to smooth out the ice front over time, making the ice cliff less steep.
-While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice-shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
+While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
 
@@
 
-Finally, we note that the numerical bonds in the LIISM model are needed in order to allow the tabular iceberg to retain its shape.
+Finally, we note that the numerical bonds in the LTAM model are needed in order to allow the tabular iceberg to retain its shape.
 Comparing the iceberg calving simulation with an identical simulation where all numerical bonds have been removed, shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
@@
 
- \section{Discussion}
-In order to accurately project future sea level, it is likely that we will need to develop fully-coupled global general climate models (GCM's) with dynamic ice-shelf cavities which are able to melt, break and interact with the ocean in physically realistic ways.
-In the sections above, we have seen that constructing ice shelves out of Lagrangian elements is a potentially useful method for introducing breakable ice shelves and tabular icebergs into climate models.
-In this section we briefly discuss a few of the things which still need to be done in order to introduce this technology into next generation GCM's.
-
-One element which is missing from the LIISM ice shelf is that the ice shelf is not dynamic.
-Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice-shelf geometry to change over time.
-Much progress has been made in modeling ice-shelf flows in an Eularian framework \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
-A challenge will be to develop models with similar ice dynamics in a Lagrangian framework.
-This can perhaps be achieved using smooth particle hydrodynamics (SPH) methods, which allow partial differential equations to be solved on a Lagrangian gird \citep{Liu2010, Pan2013}.
-However, it is presently unclear how one would evolve the numerical bonds over time, so the bonds could still be used to hold the ice shelf and tabular icebergs together.
-This may involve performing a regridding of the ice element or a regridding of the numerical bonds after severa time steps, or perhaps allowing the numerical bonds to break and form in a dynamic way.
-
-The other major innovation which will need to be introduced is a method for breaking numerical bonds.
-This is essentially equivalent to determining an ice-shelf calving law, and is a famously difficult problem.
-One possible way that this could be done is to break bonds when the elastic stress in the bond is larger than a given yield stress of that bond.
-The yield stress in the bond would likely be proportional to the ice thickness.
-The bond strength could also evolve dynamically as bonds get `damaged'.
-The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eularian ice-shelf studies \citep{Pralong2005, Borstad2012}.
-
-In addition to these two problems, more work needs to be done to determine the interaction between tabular icebergs and sea ice, as the presence of sea ice can arrest the motion of tabular icebergs and the presence of icebergs likely affects sea ice formation and dynamics.
-A possible path towards this is to model sea ice using a Lagrangian grid \citep{Hopkins1996, Li2014}, and to treat sea ice - iceberg interactions in the same way that iceberg - iceberg interactions are treated in this study.
-A number of preliminary experiments have been run using the LIISM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
-% Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
-These will need to be considered in order to model the primary productivity around tabular icebergs.
-
-Finally, there are a number of other open questions associated with introducing giant tabular icebergs into climate models: (i) how to correctly link tabular icebergs' melt water fluxes to ocean biology, (ii) how to deal with giant calving events in small ensemble simulations where one calving event can skew the ensemble statistics, (iii) how to introduce tabular icebergs into models which do not use a fully dynamic ice sheet, and (iv) how to model the breakup and fracture of freely-floating tabular icebergs.
-These and other questions will need to be answered in order to achieve physically realistic tabular icebergs and ice shelves in GCM's.
-The results presented in this study suggest that coupling DEM models to dynamic ocean models, presents a promising path towards a more realistic representation of breakable ice shelves and icebergs in climate models.
-%is potentially a promising path towards achieving this goal.
-% in order to represent large breakable ice shelves and icebergs
-
-%How do we grow icebergs?
+ \section{Summary}
+In study above we have presented a novel method that can be used to representing tabular icebergs in numerical ocean models.
+In this framework, tabular icebergs (or ice shelves) are constructed out of Lagrangian particles which are held together by numerical bonds.
+In this way icebergs are not treated as point particles (as in previous iceberg models), but rather are explicitly resolved in the ocean.
+This allows the icebergs to apply pressure to the ocean surface over a wide area (larger than a grid cell), and affect circulation patterns in a way that is more physically realistic.
+
+A demonstration of the tabular iceberg model was performed using an idealized semi-circular iceberg drifting away from an idealized ice shelf.
+The results showed that explicitly resolving the iceberg in the ocean allowed for a complex interaction between the tabular iceberg and the surrounding ocean.
+In our setup, the tabular iceberg is driven way from the ice shelf by ocean currents, wind stress, and the Coriolis force.
+As the iceberg moves through the water, it disturbs the ocean surface, driving barotropic ocean currents.
+The motion of the iceberg and melt beneath the iceberg also drive upwelling along the sides of the iceberg, which entrains ambient water and causes a warming of the surface ocean in the wake of the iceberg.
+The changing ocean conditions feed back onto the iceberg, affecting its motion and melt rates.
+The highest melt rates are observed at edge of the iceberg which has the steepest ice cliff.
+These have the effect of smoothing out the ice edge over time.
+Simulations without using numerical bonds showed that these bonds are essential for allowing the iceberg to move as a unit.
+We also saw that by breaking these numerical bonds we can simulate iceberg fracture, which is important process which rapidly increases the rate of iceberg decay.
+
+The model presented here is potentially a step towards including tabular icebergs in global general climate models (GCM's).
+However, before this can be done, there are a number of other outstanding questions to be resolved.
+Firstly, it is currently unclear how and when one would introduce tabular icebergs into climate simulations, especially if the GCM does not use an active ice shelf from which the tabular icebergs can calve.
+For simulations with ice shelves, a calving law would be needed to decide when to release the tabular iceberg into the ocean.
+The question of what calving law to use is a topic of ongoing research \citep{Benn2007, Alley2008, Levermann2012, Bassis2013} and is still unresolved.
+One potential way bypass this problem would be to run hindcast simulations using historically observed calving events.
+Another question is how and when to break the bonds within the freely floating icebergs to simulation iceberg breakup.
+Without a rule for iceberg breakup, the tabular icebergs would likely drift to unrealistically low latitudes.
+There are also a number of outstanding questions involving the interaction between tabular icebergs and sea ice, ocean biogeochemistry and iceberg grounding.
+None-the-less, the technical framework described in this article is potentially a using step towards including tabular icebergs in global general climate models (GCM's).
 
@@
 \subsection{Melt rate parametrization}
-As discussed in Section 2.5, unbounded ice elements in the LIISM model decay according to parameterizations for iceberg decay typically used in iceberg drift models \citep{Martin2010}, while ice elements within larger ice structures have only a basal melt given by the three equation model \citep{Holland1999} .
+As discussed in Section 2.5, unbounded ice elements in the LTAM model decay according to parameterizations for iceberg decay typically used in iceberg drift models \citep{Martin2010}, while ice elements within larger ice structures have only a basal melt given by the three equation model \citep{Holland1999} .
 
 For unbonded ice elements, the element thickness decays due to basal melt at a rate $M_{b}$, while the length and width of the elements decay as a result of melt due to wave erosion, $M_{e}$, and melt due to buoyant convection, $M_{v}$.
-Following \citet{Martin2010}, the basal melt rate, wave erosion melt rate, and buoyant convection melt rate are parameterized by
+Following \citet{Gladstone2001} and \citet{Martin2010}, the basal melt rate, wave erosion melt rate, and buoyant convection melt rate are parameterized by
 \begin{equation}
@@
 \subsection{Modified Verlet Algorithm}
-The LIISM model uses a version velocity verlet time-stepping algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
+The LTAM model uses a version velocity verlet time-stepping algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
 The traditional velocity verlet algorithm is commonly used in molecular dynamics, as it is simple to implement, second order accurate and computationally efficient \citep{Swope1982, Omelyan2002}.
 Here we modify the tradition scheme to allow for the drag forces to be modeled implicitly, which prevents large accelerations for element's whose mass approaches zero. 
-To do this, we modify the traditional verlet algorithm to include both an implicit and explicit acceleration, $a(t)=a_{exp}(t)+a_{imp}(t)$.
-The explicit acceleration, $a_{exp}(t)$ includes all forcing terms which depend only on the previous time step, while the implicit acceleration, $a_{imp}(t)$  includes forcing terms which depend on the current time step (in particular the drag and Coriolis forces).
+To do this, we modify the traditional verlet algorithm to include both an implicit and explicit acceleration, $a=a^{exp} +a^{imp}$.
+The explicit acceleration, $a^{exp}$ includes all forcing terms which depend only on the previous time step, while the implicit acceleration, $a^{imp}$  includes forcing terms which depend on the current time step (in particular the drag and Coriolis forces).
 
@@
 
-Using a time step of $\Delta t$ and the notation $t_{n+1}= t_{n} + (\Delta t)$, the modified velocity verlet scheme can be written as:\\
-1) $ x(t_{n+1}) = x(t_{n}) + u(t_{n}) \Delta t  + \frac{1}{2} \Delta t^{2} \Bigg(a_{exp}(t_{n}) + a_{imp}(t_{n} )\Bigg) $.\\
-2) Calculate $a_{exp}(t_{n+1})$ and  $a_{imp}(t_{n+1})$\\
-3) $u(t_{n+1}) = u(t_{n}) + \frac{\Delta t}{2} \Bigg(a_{exp}(t_{n}) + a_{exp}(t_{n+1}) \Bigg) +  (\Delta t) a_{imp}(t_{n+1})$\\
-This scheme reduces to the traditional velocity verlet when $a_{imp}$ is set to zero.
-Note that at step 2, $a_{exp}(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other quantities evaluated at time $t_{n}$, while $a_{imp}(t_{n+1})$ additionally depends on $u(t_{n+1})$, and needs to be solved implicitly).
-For this reason, steps 2 and 3 need to be solved simultaneously, as described in the next subsection.
+Using a time step of $\Delta t$, and subscripts to denote the time step (so that $t_{n+1}= t_{n} + \Delta t$), the modified velocity verlet scheme can be written as:\\
+1) $ x_{n+1} = x_{n} + u_{n} \Delta t  + \frac{1}{2} \Delta t^{2} \Bigg(a^{exp}_{n} + a^{imp}_{n} \Bigg) $.\\
+2) Calculate $a^{exp}_{n+1}$, which is a function of $x_{n+1}$, and other quantities measured at time $t_{n}$. \\
+3) Calculate $a^{imp}_{n+1}$ and $u_{n+1} = u_{n} + \frac{\Delta t}{2} \Bigg(a^{exp}_{n} + a^{exp}_{n+1} \Bigg) +  (\Delta t) a^{imp}_{n+1}$\\
+This scheme reduces to the traditional velocity verlet when $a^{imp}$ is set to zero.
+Note that $a^{exp}_{n+1} = a^{exp}_{n+1}(x_{n+1}, t_{n})$ is an explicit function of  $x_{n+1}$ and other quantities evaluated at time $t_{n}$, while $a^{imp}_{n+1}=a^{imp}_{n+1}(u_{n+1}, x_{n+1}, t_{n})$ additionally depends on $u_{n+1}$, and needs to be solved implicitly.
+For this reason, in step 3 $a^{imp}_{n+1}$ and $u_{n+1}$ need to be solved simultaneously, as described in the next subsection.
 
@@
 We demonstrate how this is done, using a simplified one-dimensional version of equation (1), neglecting the atmospheric drag, sea ice drag and Coriolis force, so that the only implicitly treated term is the ocean drag.
-We also define an explicit force $F_{exp}$, which accounts for all forces not proportional the element velocity.
+In this demonstration, we use a superscript to denote the ocean drag force, $F^{o}$ and ocean velocity, $u^{o}$ to avoid confusion with the subscripts indicating time step.
+We also define an explicit force $F^{exp}$, which accounts for all forces not proportional the element velocity.
 With these simplifications, the implicit and explicit accelerations are
  \begin{equation}
-a_{exp} =\frac{1}{M} ( \vec{F}_{exp} )
-\end{equation}
- \begin{equation}
-a_{imp} =\frac{1}{M} (F_{o})
+a^{exp} =\frac{1}{M} ( \vec{F}^{exp} )
+\end{equation}
+ \begin{equation}
+a^{imp} =\frac{1}{M} (F^{o})
 \end{equation}
@@
 \label{eq:Drag}
-F_{W}(t_{n+1}) = \tilde{c}_{o} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) -u(t_{n+1}) ),
-\end{equation}
-where $\tilde{c}_{o}$ is the effective drag coefficient, accounting for the dimensions of the ice element (see equation \ref{eq:ocean_drag_eq}).
+F^{o}_{n+1} = \tilde{c}^{o} |u^{o}_{n} -u_{n} | (u^{o}_{n} -u_{n+1} ),
+\end{equation}
+where $\tilde{c}^{o}$ is the effective drag coefficient, accounting for the dimensions of the ice element (see equation \ref{eq:ocean_drag_eq}).
 
@@
  \begin{equation}
- u^{*}(t_{n}) =  u(t_{n})  + \frac{1}{2} (\Delta t) a(t_{n}). 
+ u^{*}_{n} =  u_{n}  + \frac{1}{2} (\Delta t) a_{n}. 
  \end{equation}
@@
  \begin{equation}
-u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2} a_{exp}(t_{n+1})+  (\Delta t) a_{imp}(t_{n+1}).
+u_{n+1} = u^{*}_{n} + \frac{\Delta t}{2} a^{exp}_{n+1}+  (\Delta t) a^{imp}_{n+1}.
  \end{equation}
@@
  \begin{equation}
-u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}     \Bigg(  c_{w} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) -u(t_{n+1}) )   \Bigg)
+u_{n+1} = u^{*}_{n} + \frac{\Delta t}{2M} ( F^{exp} _{n+1}) +   \frac{\Delta t}{M}     \Bigg(  c_{w} |u^{o}_{n} -u_{n} | (u^{o}_{n} -u_{n+1} )   \Bigg)
  \end{equation}
@@
  \begin{equation}
-u(t_{n+1}) = \frac{u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}    \Bigg(  c_{w} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) )   \Bigg)}{  \Bigg( 1+  \frac{\Delta t}{M}       c_{w} |u_{o}(t_{n}) -u(t_{n}) |    \Bigg)}
- \end{equation}
-Once the $u(t_{n+1})$  has been found, it can be used to calculated the explicit and implicit accelerations, which are required for the next time step.
+u_{n+1} = \frac{u^{*}_{n} + \frac{\Delta t}{2M} ( F^{exp}_{n+1}) +   \frac{\Delta t}{M}    \Bigg(  c_{w} |u^{o}_{n} -u_{n} | (u^{o}_{n} )   \Bigg)}{  \Bigg( 1+  \frac{\Delta t}{M}       c_{w} |u^{o}_{n} -u_{n} |    \Bigg)}
+ \end{equation}
+Once the $u_{n+1}$  has been found, it can be used to calculated the explicit and implicit accelerations, which are required for the next time step.
 
@@
 \textbf{Connecting bonds across processor boundaries}\\
-Since the LIISM model can be parallelized across multiple processors, it often happens that two elements on different processes are bonded together.
+Since the LTAM model can be parallelized across multiple processors, it often happens that two elements on different processes are bonded together.
 Keeping track of numerical bonds across processor boundaries requires a lot of book keeping.
-In this section we describe the how LIISM model avoids segmentation faults by severing and reconnecting bonds at the edge of a processor during halo updates.
+In this section we describe the how LTAM model avoids segmentation faults by severing and reconnecting bonds at the edge of a processor during halo updates.
 
@@
 
+\bibitem[Henderson and Loe (2016)]{Henderson2016}
+Henderson J., J. S. P. Loe (2016), The Prospects andChallenges for Arctic Oil Development. {\it Oil, Gas and Energy Law Journal (OGEL)}, 14 (2)
+
 \bibitem[Hopkins (1996)]{Hopkins1996}
 Hopkins, M. A. (1996). On the mesoscale interaction of lead ice and floes. {\it J. of Geophys. Res.: Oceans}, 101(C8), 18315-18326.
+
+\bibitem[Gaskill and Rochester (1984)]{Gaskill1984}
+Gaskill, H. S., and J. Rochester (1984). A new technique for iceberg drift prediction. {\it Cold Reg. Sci. Technol.}, 8(3), 223-234.
 
@@
 
+\bibitem[Kubat et al (2005)]{Kubat2005}
+Kubat I., M. Sayed, S. Savage, T. Carrieres (2005), An operational model of iceberg drift {\it Int. J. Off. Polar Eng.}, 15 (2), 125–131
+
 \bibitem[Lewis and Perkin (1986)]{Lewis1986}
@@
 {\it The Cryosphere}, 6(2), 273-286.
+
+\bibitem[Mountain (1980)]{Mountain1980}
+Mountain, D. G. (1980). On predicting iceberg drift. {\it Cold Reg. Sci. Technol.}, 1(3-4), 273-282.
 
@@
 
+\bibitem[Pizzolato et al (2012)]{Pizzolato2014}
+Pizzolato,  L., S.
+E.
+Howell, C.
+Derksen, J.
+Dawson, L.
+Copland (2014), Changing sea ice conditions and marine transportation activity in Canadian Arctic waters between 1990 and  2012, {\it Climatic  Change}  123  (2),  161173.
+
 \bibitem[Pan et al (2013)]{Pan2013}
@@
 Vernet (2007), Free-drifting icebergs: Hotspots of chemical and biological enrichment in the Weddell Sea, {\it Science}, 317, 478–482.
+
+\bibitem[Shepherd and Wingham (2007)]{Shepherd2007}
+Shepherd, A., and D. Wingham (2007). Recent sea-level contributions of the Antarctic and Greenland ice sheets. {\it Science}, 315(5818), 1529-1532.
 
@@
 
+\bibitem[Turnbull et al (2015)]{Turnbull2015}
+Turnbull I.D., N. Fournier, M. Stolwijk, T. Fosnaes, D. McGonigal (2015), Operational iceberg drift forecasting in Northwest Greenland, {\it Cold Reg. Sci. Technol.} 110, 1-18
+
+\bibitem[Unger (2014)]{Unger2014}
+Unger, J. D., 2014. Regulating the Arctic Gold Rush:  Recommended Regulatory Reforms to Protect Alaska's ArcticEnvironment from Offshore Oil Drilling Pollution . {\it Alaska L. Rev}, 31
+
 \bibitem[Vernet et al (2012)]{Vernet2012}
@@
 \end{thebibliography}
-
- \clearpage
- \end{article}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Diagrams/Interactive forces.pdf}
-%\caption{ {Schematic of interactive forces}}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:Interactive_forces}
-%\end{figure}
- %\clearpage
 
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Regular_Uncoupled_sim}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Uncoupled_sim}
@@
  \clearpage
-
-%We begin by demonstrating the LIISM model uncoupled to the ocean.
-For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide.
-Land points are arranged in a semi-circle, in the west of the domain, as shown by the black dots in Figure \ref{fig:Uncoupled_sim}.
-Three hundred ice elements are initialized with diameters uniformly sampled from the interval [0 40km], and positioned randomly at positions with $x \leq 300$km.
-These ice elements can be thought to represent interacting sea ice flows or icebergs.
-Three `tabular icebergs' are initialized by arranging ice elements in a staggered lattices with adjacent elements bonded together, as described in Section 2.4.
-The three tabular icebergs contain 25, 16 and 4 elements, respectively.
-Each of the elements that make up the tabular icebergs has a diameter of 40km.
-All elements have an initial thickness of 10m.
-%
-%The simulation is forced by an imposed westward ocean current of u=0.1m/s.
-Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
-The initial setup is shown in Figure \ref{fig:Uncoupled_sim}a.
 
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Hex_intersections}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:ISOMIP_mass_and_topog}
-\end{figure}
- \clearpage
-
- \begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
-\caption{ {Results of the static ice-shelf experiment using the LIISM model coupled to MOM6.
-Panels show cross sections of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity near the ice-shelf base after 5 years of simulation.
-The region shown in panel (c) is indicated by the black box on panel (b),}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:static_solo_temp_temp_v}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Results of the static ice-shelf experiment using the LIISM model coupled to MOM6.
-The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
-Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:static_solo_melt}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration.
-Panel (c) shows the difference between panels (a) and (b).
-The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:Bt_comparison}
 \end{figure}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Spread_area}
@@
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The position of the vertical transects is shown by the dashed lines in Figure \ref{ig:Spread_area}c.}}
+The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:Spread_area}c.}}
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Temperature_section_Collapse}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:SST_Collapse}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Velocity_section_Collapse}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Collapse_solo_melt}
@@
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/melting_shelf_temp_layers.png}
-%\caption{ {Temperature section at $y=\frac{L_{y}}{2}$ for the decaying ice shelf simulation (using the LIISM ice shelf) at time (a) t=0, (b) t=100(?), (c) t=200 days.
-As the ice shelf melts, it decays and the pressure at the ocean surface decreases.
-}}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:Decaying_shelf}
-%\end{figure}
-
-%\clearpage
-
 \begin{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_temp_layers.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_salt_layers.png}
 \caption{ {Results from the tabular iceberg calving experiment with and without iceberg bonds.
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:Bond_vs_No_bond}
@@
  \clearpage
-
-\begin{table}[h!]
-\begin{center}
-\begin{tabular}{ |c c c c| }
-\hline
-Parameter & Symbol & Value &  Unit \\
-\hline
-Domain Length &  $L_{x}$ & 80  & km \\
-Domain Width &  $L_{y}$ & 480  & km \\
-Horizontal Resolution &  $\Delta x$ & 2  & km \\
-Number of vertical layers &  $N_{l}$ & 72  & non-dim\\
-Horizontal Viscosity &  $\nu_{H}$ & 6.0 & $\frac{m^{2}}{s}$ \\
-Diapycnal Viscosity &  $\nu_{V} $ & $10^{-3}$ & $\frac{m^{2}}{s}$ \\
-Horizontal Diffusivity & $ \epsilon_{H}$ & 1.0 & $ \frac{m^{2}}{s}$ \\
-Diapycnal Diffusivity &  $\epsilon_{V} $ & $5 \times 10^{-5}$ & $\frac{m^{2}}{s}$ \\
-Initial Surface Temperature &  $ T_{t}$& -1.9   & $ ^{o} C$\\
-Initial Bottom Temperature &  $ T_{b}$&  1.0  & $ ^{o} C$\\
-Initial Surface Salinity &  $ S_{t}$& 33.8   & psu\\
-Initial Bottom Salinity &  $ S_{b}$&  34.7  & psu\\
-Maximum Ocean depth &  $H_{ocean} $ & 720 & m \\
-Relaxation Time of Sponge Layer &  $T_{sponge}$ & 0.1  & days\\
-%Background Frictional Velocity Below Ice &  $u^{*}_{bg}$ & 0.0  & 104 \\
-%Drag Coefficient Below Ice&  c_{d} & $0.0025$  & (non dim)\\
-%Class 9 &  $3.9\times 10^{11}$ & 1659 & 104 \\
-Time Step for Static Shelf Experiment & $dt_{Static}$ &  1000  & s\\
-Time Step for Iceberg Calving Experiment & $dt_{Calving}$ &  10  & s\\
-%Class 1 &  $8.8\times 10^{7}$ & 60  & 0.0026 & 40 & 2000 \\
-%Class 2 &  $4.1\times 10^{8}$ & 100 & 0.0072 & 67 & 200\\
-%Class 3 &  $3.3\times 10^{9}$ & 200  & 0.029 &133 & 50 \\
-%Class 4 &  $1.8\times 10^{10}$& 350 &  0.12 &175  & 20 \\
-%Class 5 &  $3.8\times 10^{10}$ & 500  & 0.18 &250 & 10\\
-%Class 6 &  $7.5\times 10^{10}$ & 700   & 0.35 &250 & 5\\
-%Class 7 &  $1.2\times 10^{11}$ & 900  & 0.56 &250  & 2 \\
-%Class 8 &  $2.2\times 10^{11}$ & 1200  & 1.0&250 & 1 \\
-%Class 9 &  $3.9\times 10^{11}$ & 1600 & 1.8&250 & 1  \\
-%Class 10 & $7.4\times 10^{11}$ &  2200 & 3.5 &250  &1\\
-\hline
-\end{tabular}
-%\caption{Description of the iceberg calving classes used in the model.
-{\it Mass}, {\it Length}, {\it Area} and {\it Th} refer to the iceberg mass, length, area, and thickness at the time of calving.
-{\it Scaling} is the number of icebergs represented by one Lagrangian point particle.
-The iceberg mass and thickness for each class are the same as those reported in \citet{Gladstone2001}.
-The iceberg area and length for each class is calculated from the iceberg mass and thickness by assuming that the icebergs are cuboids with a length to width ratio of 1.5, using an iceberg density $\rho_{i}=850$kg/$\textrm{m}^{3}$.}
-% Note that the areas of the iceberg classes (calculated from the iceberg lengths and masses given in \citep{Gladstone2001}) are not monotonically increasing.
-\label{table:parameters2}
-\end{center}
-\end{table}
-
-\clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_spread_area.png}
-%\caption{ {Need to update this Figure. Also, I should try using orientation with the Bonds.}}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:}
-%\end{figure}
-
-% \clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_salt_layers.png}
-%\caption{ {}}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:}
-%\end{figure}
-
-%\clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_u_layers.png}
-%\caption{ {Need to update this Figure. }}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:}
-%\end{figure}
-
-%\clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_v_layers.png}
-%\caption{ {Need to update this Figure. }}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%                       Supplementary Figures                   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-\section{Supplementary Figures}
-\clearpage
-
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S\arabic{figure}}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_salt_layers.png}
-\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model salinity fields.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Salt_comparison}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_melt.png}
-\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian Ice shelf model melt fields.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Melt_comparison}
-\end{figure}
- \clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_vo_uo_sst.png}
-%\caption{ {Results of the static ice shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) meridional velocity, (b) zonal velocity and (c) ocean temperature in the top layer of the simulation (at the surface or directly below the ice shelf).}}
-%\end{center}
-%\label{fig:static_solo}
-%\end{figure} 
- %\clearpage
-
- \begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp_layers}
-\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-%FIgure created by \end{center}
-\end{center}
-%\label{fig:Calving_fixed_side}
-\end{figure}
-  \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp}
-\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Calving_fixed_top}
-\end{figure}
- \clearpage
-
- \section{Layer versions}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp_layers}
-\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-%FIgure created by \end{center}
-\end{center}
-%\label{fig:Calving_fixed_side}
-\end{figure}
-  \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp}
-\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Calving_fixed_top}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_temp_temp_v.png}
-\caption{ {Layered: Results of the static ice-shelf experiment using the LIISM model.
-Panels show snapshots of cross sections of the (a) temperature field after 1 time step, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity after 5 years.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:static_solo_temp_temp_v}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Layer: Results of the static ice-shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
-\caption{ {Layer: Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model barotropic stream function}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Bt_comparison}
-\end{figure}
- \clearpage
+ \end{article}
 

### 2017-02-08 Icebergs_only.tex
Editing iceberg only version

@@
 The numerical bonds hold the ice elements together and allow a collection elements to move as a unit.
-By manually breaking these bonds, we can simulate iceberg calving, allowing us to study the ocean response to giant iceberg detaching from an ice shelf or the fracturing of a large iceberg into smaller pieces.
+By manually breaking these bonds, we can simulate iceberg calving, allowing us to study the ocean response to giant iceberg detaching from an ice shelf (e.g.: Figure \ref{fig:Spread_area} and \ref{fig:SST_Collapse}) or the fracturing of a large iceberg into smaller pieces.
 
 The discrete element model (DEM) developed in this study is referred to at the Lagrangian Tabular Iceberg Model (LTAM). 
+%The LTAM model is coupled to the MOM6 numerical ocean model \citep{Hallberg2013}. 
 Section 2 gives a description of many of the key aspects of the LTAM.
@@
  \section{Summary}
-In study above we have presented a novel method that can be used to representing tabular icebergs in numerical ocean models.
+In study above we have presented a novel method that can be used to represent tabular icebergs in numerical ocean models.
 In this framework, tabular icebergs (or ice shelves) are constructed out of Lagrangian particles which are held together by numerical bonds.
@@
 \begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
+\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse}} and \ref{fig:Velocity_section_Collapse}.}
+\end{center}
+\label{fig:Spread_area}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp.png}
+\caption{ {Snapshots of the sea surface temperature in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+Regions with ice area fraction = 1 area plotted in white.}}
+\end{center}
+\label{fig:SST_Collapse}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Regular_towards_coast}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse}} and \ref{fig:Velocity_section_Collapse}.}
-\end{center}
-\label{fig:Spread_area}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
@@
 \label{fig:Temperature_section_Collapse}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp.png}
-\caption{ {Snapshots of the sea surface temperature in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-Regions with ice area fraction = 1 area plotted in white.}}
-\end{center}
-\label{fig:SST_Collapse}
 \end{figure}

### 2017-02-14 Icebergs_only.tex
More changes to iceberg only version

@@
 The calving of giant icebergs from the Antarctic ice shelves accounts for approximately half of Antarctic ice-shelf decay.
-After calving these tabular icebergs drift across large distances, altering regional ocean circulation, bottom water formation and local rates biological primary productivity.
-Freshwater fluxes from sub-marine melting can affect large-scale sea-ice distributions, which feedback onto the greater climate system.
+After calving these tabular icebergs drift across large distances, altering regional ocean circulation, bottom-water formation, sea-ice production and rates biological primary productivity in the icebergs' vicinity.
 However, despite their importance, the current generation of numerical models is unable to represent giant tabular icebergs a physically realistic way.
-In this study we develop novel method to model giant tabular icebergs. Tabular icebergs are constructed out of Lagrangian elements which are bonded together by numerical bonds. 
-These numerical bonds hold the ice element together and allow the individual elements to move as a unit.
-By breaking these bonds, we can simulate the  ocean response to giant iceberg detaching away from an ice shelf (also constructed from Lagrangian elements) or the fracturing of a large iceberg into smaller pieces.
-This paper provides a description and demonstration of the Lagrangian tabular-iceberg model and discusses a number of the technical elements involved its development.
-%We demonstrate the capabilities of the model by modeling a tabular iceberg breaking away an idealized ice shelf.
+In this study we develop novel framework to model giant tabular icebergs submerged in the ocean.
+In this framework, tabular icebergs are constructed out of Lagrangian elements that drift in the ocean, and are held together by numerical bonds.
+By breaking these bonds, a tabular iceberg can be made to split into smaller pieces, or to break away from an ice shelf (also constructed from Lagrangian elements).
+This paper provides a description of the Lagrangian tabular-iceberg model and discusses a number of the technical elements involved its development. 
+We demonstrate the capabilities of the model by modeling a tabular iceberg drifting away an idealized ice shelf.
 \end{abstract}
@@
 Observational estimates suggest that over the past 30 years approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
-After calving, icebergs slowly drift away from their mother glaciers, often becoming stuck in sea ice, or become grounded along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}.
+Iceberg sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while the far less numerous giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}.
+
+After calving, icebergs slowly drift away from their mother glaciers, often becoming stuck in sea ice, or grounding along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}.
 Giant tabular icebergs extend deep into the water column, and have to potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
-Iceberg sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while the far less numerous giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}.
-
-Freshwater fluxes from iceberg melt impact ocean hydrography, influencing sea-ice production and bottom-water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
+The freshwater flux from iceberg melt impacts ocean hydrography around the iceberg, influencing sea-ice production and bottom-water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
 The long distances traveled by giant icebergs before melting means that their meltwater impact is often felt hundreds of kilometers away from their calving origins \citep{Stern2016}.
-Melt water injection (and the accompanying upwelling) from icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}.
+Meltwater injection (and the accompanying upwelling) from icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}.
 The increased productivity associated with free-floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.
+
 %either increasing it by providing nutrients to the surface ocean, or decreasing by changing sea ice conditions
@@
 In recent years, there has been an increased interest in iceberg drift and decay.
-This surge of interest has been driven by (i) the need to understand polar freshwater cycles in order to create realistic climate forecasts and sea level projections \citep{Silva2006, Shepherd2007, Rignot2013}, (ii) the increased use of high-latitudes iceberg-filled waters for shipping lanes and offshore hydrocarbon exploration \citep{Pizzolato2014, Unger2014, Henderson2016}.
+This surge of interest has been driven by (i) the need to understand polar freshwater cycles in order to create realistic climate forecasts and sea level projections \citep{Silva2006, Shepherd2007, Rignot2013}, (ii) the increased use of high-latitudes iceberg-filled waters for shipping lanes and offshore hydrocarbon exploration in the Arctic \citep{Pizzolato2014, Unger2014, Henderson2016}.
 The increased interest in icebergs has led to the development of numerical models of iceberg drift and decay \citep{Mountain1980, Bigg1997, Gladstone2001, Kubat2005}, some of which have been included in global General Circulation Models \citep{Martin2010, Marsh2015}.
-These iceberg models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
-Since icebergs are treated as point particles, the iceberg models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such iceberg models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
-These models are not suitable for modeling larger tabular icebergs (or smaller icebergs at fine scales), where the size and structure of the iceberg may be an important feature in determining their drift and decay \citep{Stern2016}.
-They also are not suitable for studying the local effects that icebergs have on the surrounding ocean.
-For this reason, tabular icebergs (L $>$ 5km) are currently not represented in the iceberg models used in climate models, even though observations suggest that tabular icebergs account for  the vast majority of the total Southern Hemisphere icebergs mass \citep{Tournadre2016}.
-Similarly, operational iceberg models are often inadequate for projecting iceberg drift at fine scales \citep{Turnbull2015}.
+These iceberg drift models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
+Since icebergs are treated as point particles, iceberg drift models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such these models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
+
+Point-particle iceberg drift models are less suitable for modeling larger tabular icebergs, where the size and structure of the iceberg may be an important feature in determining their drift and decay \citep{Stern2016}.
+They also are not suitable for studying the local effects that icebergs have on the surrounding ocean, or the small scale processes that influence iceberg melt and decay \citep{Wagner2014, Stern2015}.
+For this reason, tabular icebergs (L $>$ 5km) are currently not represented in the iceberg drift models used in climate models, even though observations suggest that tabular icebergs account for  the vast majority of the total Southern Hemisphere iceberg mass \citep{Tournadre2016}.
+%Similarly, operational iceberg models are often inadequate for projecting iceberg drift at fine scales \citep{Turnbull2015}.
 
 The goal of this study is to develop a new iceberg model where tabular icebergs are explicitly resolved in the ocean.
-In this model, icebergs are no longer treated as point particles that feel the ocean at one point, but rather the icebergs have structure, depress the ocean surface, and can feel the ocean across multiple ocean grid cells.
+In this model, icebergs are no longer treated as point particles that interact with the ocean at a single location, but rather icebergs are given structure, so that they interact with the ocean across multiple ocean grid cells and depress the ocean surface over a wide area.
 To do this, we create tabular icebergs out of many Lagrangian elements which are `bonded' together by numerical bonds.
@@
 Section 2 gives a description of many of the key aspects of the LTAM.
-Since this model is a new approach to modeling iceberg, we present many of the technical elements involved in constructing the model.
-In Section 3 and 4, we demonstrate the capabilities of the model by simulating a tabular iceberg detaching from an idealized ice shelf.
+Since this model is a new approach to modeling icebergs, we present many of the technical elements involved in constructing the model.
+In section 3 and 4, we demonstrate the capabilities of the model by simulating a tabular iceberg detaching from an idealized ice shelf.
 
@@
 The LTAM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
-Each element represents a mass of ice which is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time.
+Each element represents a mass of ice that is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time.
 The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element.
@@
 The elements also interact with one another and can be bonded together to form larger structures.
-The angular momentum of the elements is not model explicitly, instead rotational motion of larger structures emerge as a consequence of bond orientation.
+The angular momentum of the elements is not modeled explicitly; instead rotational motion of larger structures emerge as a consequence of bond orientation.
 In different contexts, the LTAM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
@@
 The elements drift in the ocean, forced by atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force and a force due to the sea surface slope.
-When these ice elements move alone (without interactions with other elements), they can be thought of as representing individual (or clusters of) small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).
+When these ice elements move alone (without interactions with other elements), they can be thought of as representing individual (or clusters of) small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997} and \citet{Gladstone2001}).
 
@@
 \end{equation}
-where $\vec{r}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, and $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
+where $\vec{r}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
 We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F}_{IA})_{ij}=-(\vec{F}_{IA})_{ji}$).
@@
 In this example we see that modeling large structures using small elements bonded together, allows us to achieve large-scale structure and rotational motion, without having to include an equation for the angular momentum of the elements (as discussed in \citet{Jakobsen2001}).
-Animations of these simulations can be found in the supplementary materials.
+Animations of these uncoupled simulations can be found in the supplementary materials.
 
@@
 Larger ice structures are constructed by bonding together smaller elements.
+
+Finally, we note that since the tabular iceberg are explicitly resolved in the ocean, it is sufficient for each element to interact with ocean mixed layer (i.e.
+there is no need to manually embed the iceberg into the ocean by integrating ocean fields over the iceberg thickness, as in \citet{Merino2016}).
 
@@
 Since the calculation of the interactive forces is one of the most computationally expensive part of the algorithm, the Verlet scheme leads to a significant increase in the speed of the model.
-We note that the Verlet scheme used in the LTAM contains a small modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
+We note that the Verlet scheme used in the LTAM contains a modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
 The details of this time stepping schemed are outline in Appendix B.
@@
 The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we now have the tools to model giant tabular icebergs submerged in the ocean.
-We demonstrate this capability by performing a simulation of a tabular iceberg drifting away from an idealized ice shelf.
-This simulation is performed using the LTAM model coupled to the MOM6 ocean model \citep{Hallberg2013}.
+We demonstrate this capability by simulating a tabular iceberg drifting away from an idealized ice shelf.
+%This simulation is performed using the LTAM model coupled to the MOM6 ocean model \citep{Hallberg2013}. 
 %This section describes the experimental setup of these numerical experiments. The results are shown in Section 4.
@@
 The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference.
-The configuration is the same as that of the Ocean0 setup in the MISOMIP, with three changes made:
-\begin{enumerate}
-\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
-\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
-\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$).
+The configuration is the same as that of the Ocean0 setup in the MISOMIP, with minor changes to the ice-shelf geometry (see Appendix D for details).
+% (see supplementary materials for details).
+%
+%with three changes made:
+%\begin{enumerate}
+%\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
+%\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
+%\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$).
 This was achieved by using the average of the left and right flanks of the ice-shelf thickness.
-\end{enumerate}
-These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.
+%\end{enumerate}
+%These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.
 
@@
 The idealized ice shelf is constructed out of Lagrangian ice elements.
-Ice elements are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
+Ice elements are hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
 The sides of the gridded hexagons are initialized with length $S=0.98$ km.
-Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
+%Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
 Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
-The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
-
-Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
+The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the `mass-spreading' interpolation procedure discussed in Section 2.3.
+The pre-interpolation ice draft (treating elements as point masses) contains large grid artifacts (Figures \ref{fig:ISOMIP_mass_and_topog}c).
+These grid artifacts are much reduced after the mass-spreading interpolation is applied (Figure \ref{fig:ISOMIP_mass_and_topog}b).
+
+%Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
 Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
 When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice-shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
-The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
+These grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
 
@@
 The LTAM model is coupled to the MOM6 ocean model.
-The ocean model is run using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
+The ocean model is run using a vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
 In particular, model layers bend underneath the ice shelf as they would in a sigma-coordinate model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
@@
 %(select results are shown in the supplementary material).
+
 Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
-The simulation is initially at rest, with horizontally uniform initial ocean temperature and salinity profiles that vary linearly between specified surface and bottom values.
-The initial surface temperature and salinity are  $T_{t}=-1.9^{\circ}$C and $S_{t}=33.8$ psu, respectively.
-The initial temperature and salinity at the depth $H_{ocean}$ are $T_{b}=1.0^{\circ}$C and $S_{b}=34.7$ psu.
+The simulation is initially at rest, with horizontally uniform initial ocean temperature and salinity profiles which vary linearly between specified surface and bottom values: $T_{top}=-1.9^{\circ}$C, $T_{bottom}=1.0^{\circ}$C, $S_{top}=33.8$ psu, $S_{bottom}=34.7$.
 The maximum ocean depth is $H_{ocean}=720$ m.
@@
 The model is spun up for 5 years with all ice elements being held stationary.
-After spinup, a giant tabular iceberg is 'broken off' from the ice shelf, and allowed to drift into the open ocean.
+After spinup, a giant tabular iceberg is `broken off' from the ice shelf, and allowed to drift into the open ocean.
 This is achieved by allowing all ice elements initially within a 14.4 km radius of the center of the ice front to move freely while the other ice elements continue to be held stationary.
@@
 
-A wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice-shelf cavity.
+After the spinup period, a wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice-shelf cavity.
 Perturbation experiments were performed using other wind stress values.
@@
 
-During spinup, injection of positive buoyancy due to melting at the base of the ice shelf drives a circulation within the domain (not shown).
-The circulation compares well with an identical experiment run using an Eularian ice shelf model \citep{Goldberg2012}  (a detailed comparison of the Lagrangian and Eularian ice shelf models is presented in a separate study, and is not shown here).
-
-After spinup, the numerical bonds are severed, and the tabular iceberg and smaller ice fragments calve away from the ice shelf and begin to move (see animations in the supplementary materials).
-The tabular iceberg drifts to the northward east, driven by the wind and steered by the Coriolis force (Figure \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
-After the iceberg has moved away from the ice shelf, we observed a warming of the surface waters nearby ice front and iceberg edge (Figure \ref{fig:SST_Collapse}).
-This surface warming is caused by an upwelling of the warmer waters from beneath the ice shelf and iceberg.
-As the icebergs drifts away from the ice front, these warmer waters remain at the surface, mapping of the wake of the iceberg  (Figure \ref{fig:SST_Collapse}).
-The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color in the wake of tabular iceberg in the Southern Ocean \citep{Duprat2016}, suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface.
+During spinup, the injection of buoyant meltwater at the base of the ice shelf drives a circulation within the domain (not shown).
+The circulation compares well with an identical static ice-shelf experiment run using an Eularian ice shelf model \citep{Goldberg2012}  (a detailed comparison of the Lagrangian and Eularian ice shelf models is presented in a separate study, and is not shown here).
+
+Once spinup is complete, numerical bonds are severed and the icebergs begin to move away from the ice shelf (see animations in the supplementary materials).
+The semi-circular tabular iceberg moves as a cohesive unit due to the presence of the numerical bonds, while the smaller ice fragments quickly disperse (Figure \ref{fig:Spread_area}).
+The tabular iceberg drifts towards the northward east, driven by the wind and steered by the Coriolis force.
+A warming of the surface waters is observed around the tabular iceberg, with the largest warming occurring at the ice-shelf front and along the tabular iceberg's rounded edge (Figure \ref{fig:SST_Collapse}).
+This surface warming is caused by upwelling of the warmer waters from beneath the ice shelf and iceberg.
+As the icebergs drifts away from the ice shelf, these warmer waters remain at the surface, mapping of the wake of the iceberg  (Figure \ref{fig:SST_Collapse}).
+The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color in the wake of tabular iceberg in the Southern Ocean \citep{Duprat2016}, suggesting that the increased productivity around icebergs may be driven by upwelling water delivering nutrients to the surface.
 
@@
 The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg (Figure \ref{fig:Collapse_solo_melt}).
-Large melt rates are observed at the newly calved ice-shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving has created steep ice cliffs.
+The largest melt rates are observed at the newly calved ice-shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving has created steep ice cliffs.
 These sharp ice fronts allow for large ocean currents (Figure \ref{fig:Collapse_solo_melt}c), which drive the elevated melt rates.
-These elevated melt rates act to smooth out the ice front over time, making the ice cliff less steep.
+The elevated melt rates act to smooth out the ice front over time, making the ice cliff less steep.
 While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
@@
 As mentioned above, the direction (and speed) of the iceberg drift is largely determined by the wind speed and direction.
-Perturbation experiments using different wind stresses showed that for sufficiently large winds, the iceberg drifts to the north east when the zonal component of the wind stresses is positive, and to the north west when the zonal component of the wind stress is negative.
-For a purely zonal wind stress with $\tau_{x} \leq 0.01 \frac{\textrm{N}}{\textrm{m}^{2}}$, the iceberg does not move away from the ice shelf.
+Perturbation experiments using different wind stresses show that for sufficiently large winds, the tabular iceberg drifts to the north east when the zonal component of the wind stresses is positive, and to the north west when the zonal component of the wind stress is negative (not shown).
+For a purely zonal wind stress with $|\tau_{x}| \leq 0.01 \frac{\textrm{N}}{\textrm{m}^{2}}$, the iceberg does not move away from the ice shelf.
 When the wind is purely offshore ($\tau_{x} = 0.0 \frac{\textrm{N}}{\textrm{m}^{2}}$), a meridional wind stress $\tau_{y} \geq 0.05 \frac{\textrm{N}}{\textrm{m}^{2}}$ is needed to move the tabular iceberg away from the ice shelf.
@@
  \section{Summary}
-In study above we have presented a novel method that can be used to represent tabular icebergs in numerical ocean models.
-In this framework, tabular icebergs (or ice shelves) are constructed out of Lagrangian particles which are held together by numerical bonds.
-In this way icebergs are not treated as point particles (as in previous iceberg models), but rather are explicitly resolved in the ocean.
-This allows the icebergs to apply pressure to the ocean surface over a wide area (larger than a grid cell), and affect circulation patterns in a way that is more physically realistic.
-
-A demonstration of the tabular iceberg model was performed using an idealized semi-circular iceberg drifting away from an idealized ice shelf.
-The results showed that explicitly resolving the iceberg in the ocean allowed for a complex interaction between the tabular iceberg and the surrounding ocean.
-In our setup, the tabular iceberg is driven way from the ice shelf by ocean currents, wind stress, and the Coriolis force.
+In this study we present a novel framework for representing tabular icebergs in numerical ocean models.
+In this framework, giant tabular icebergs are constructed from collections of Lagrangian elements that are held together by numerical bonds.
+Constructing tabular icebergs out of many independent elements allows the icebergs to interact with the ocean across a wide area (larger than a grid cell), and behave as if they had a finite size and structure.
+This is in contrast to previous representations of icebergs in numerical models \citep{Jongma2009, Martin2010, Marsh2015} that represent icebergs as point particles.
+Explicitly resolving tabular icebergs in the ocean allows the icebergs to interact with the ocean in a more realistic way, and allows us to study the effect that tabular icebergs have on the ocean circulation.
+Including numerical bonds between elements allows for the possibility of breaking bonds to simulation iceberg calving and fracture.
+
+The capabilities of the tabular iceberg model was demonstrated by modeling a tabular iceberg drifting away from an idealized ice shelf (also constructed using Lagrangian elements).
+The results show that explicitly resolving the iceberg in the ocean allowed for a complex interaction between the tabular iceberg and the surrounding ocean.
+In our setup, the tabular iceberg is driven away from the ice shelf by ocean currents, wind stress, and the Coriolis force.
 As the iceberg moves through the water, it disturbs the ocean surface, driving barotropic ocean currents.
-The motion of the iceberg and melt beneath the iceberg also drive upwelling along the sides of the iceberg, which entrains ambient water and causes a warming of the surface ocean in the wake of the iceberg.
+The motion of the iceberg and melt beneath the iceberg drive upwelling along the sides of the iceberg, which entrains ambient water and causes a warming of the surface ocean in the wake of the iceberg.
 The changing ocean conditions feed back onto the iceberg, affecting its motion and melt rates.
@@
 Simulations without using numerical bonds showed that these bonds are essential for allowing the iceberg to move as a unit.
-We also saw that by breaking these numerical bonds we can simulate iceberg fracture, which is important process which rapidly increases the rate of iceberg decay.
-
-The model presented here is potentially a step towards including tabular icebergs in global general climate models (GCM's).
-However, before this can be done, there are a number of other outstanding questions to be resolved.
-Firstly, it is currently unclear how and when one would introduce tabular icebergs into climate simulations, especially if the GCM does not use an active ice shelf from which the tabular icebergs can calve.
-For simulations with ice shelves, a calving law would be needed to decide when to release the tabular iceberg into the ocean.
+We also demonstrate that by breaking these numerical bonds we can simulate iceberg fracture, which is important process which rapidly increases the rate of iceberg decay.
+
+To our knowledge, the model presented in this study is the first model to explicitly resolve drifting tabular icebergs in an ocean model.
+As such, a natural extension of this work is to try to include tabular icebergs into a general circulation model (GCM) used for climate projections.
+However, before this can be done, there are a number of issues that need to be resolved:
+firstly, the question of how and when to introduce tabular icebergs into the ocean needs to be addressed.
+For GCM's with active ice shelves, a calving law is needed to decide when to release the tabular iceberg into the ocean.
 The question of what calving law to use is a topic of ongoing research \citep{Benn2007, Alley2008, Levermann2012, Bassis2013} and is still unresolved.
-One potential way bypass this problem would be to run hindcast simulations using historically observed calving events.
-Another question is how and when to break the bonds within the freely floating icebergs to simulation iceberg breakup.
+One potential way to temporarily bypass this problem would be to run hindcast simulations using historically observed calving events.
+A related issue is the question of how and when to break the bonds within the freely floating icebergs to simulation iceberg breakup.
 Without a rule for iceberg breakup, the tabular icebergs would likely drift to unrealistically low latitudes.
-There are also a number of outstanding questions involving the interaction between tabular icebergs and sea ice, ocean biogeochemistry and iceberg grounding.
-None-the-less, the technical framework described in this article is potentially a using step towards including tabular icebergs in global general climate models (GCM's).
+Finally, further work is needed to understand (and model) the interactions between tabular icebergs and sea ice, and to parametrize the effects of iceberg grounding, as these interactions play a large role in dictating the trajectories of tabular icebergs.
+None-the-less, the technical framework described in this article is potentially a using step towards including tabular icebergs in global GCM's, and hence a step towards making more accurate projections of future sea level.
 
@@
 A useful tool in this process is that each element is assigned a unique number so that elements are easily identified.
+
+\section{Appendix D}
+The experiment configuration used in this study is the same as that of the Ocean0 setup in the MISOMIP, with the following three changes made:
+\begin{enumerate}
+\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
+\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
+\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$).
+This was achieved by using the average of the left and right flanks of the ice-shelf thickness.
+\end{enumerate}
+These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.
 
@@
 %
+\bibitem[Merino et al (2016)]{Merino2016}
+Merino, N., Le Sommer, J., Durand, G., Jourdain, N.
+C., Madec, G., Mathiot, P., and Tournadre, J.
+(2016), Antarctic icebergs melt over the Southern Ocean: climatology and impact on sea ice.
+{\it Ocean Modelling}, 104, 99-110.
+
 \bibitem[Nicholls (1996)]{Nicholls1996}
@@
 Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38–39
+
+\bibitem[Wagner et al (2014)]{Wagner2014}
+Wagner, T.
+J., Wadhams, P., Bates, R., Elosegui, P., Stern, A., Vella, D., E.
+P.
+Abrahamsen, A.
+Crawford, and Nicholls, K.
+W.
+(2014), The “footloose” mechanism: Iceberg decay from hydrostatic stresses.
+{\it Geophys.
+Res.
+Let.}, 41(15), 5522-5529.
 
@@
 \begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
+\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LIISM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The position of the transects is shown by the dashed line in Figure \ref{fig:Spread_area}c.}}
+\end{center}
+\label{fig:Velocity_section_Collapse}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
@@
 \label{fig:Temperature_section_Collapse}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The position of the transects is shown by the dashed line in Figure \ref{fig:Spread_area}c.}}
-\end{center}
-\label{fig:Velocity_section_Collapse}
 \end{figure}

### 2017-02-16 Icebergs_only.tex
More changes to iceberg only version

@@
 \label{F_interaction_i}
-(F_{IA})_{i}= \Sigma_{j \neq i} (F_{IA})_{ij},
-\end{equation}
-where $(F_{IA})_{ij}$ is the force on element $i$ by element $j$.
+(\vec{F}_{IA})_{i}= \Sigma_{j \neq i} (\vec{F}_{IA})_{ij},
+\end{equation}
+where $(\vec{F}_{IA})_{ij}$ is the force on element $i$ by element $j$.
 Both bonded and repulsive interactions are modeled using elastic stresses with frictional damping.
@@
 To aid in notation, we define a bond matrix $B_{ij}$ such that $B_{ij}=1$ if elements i and j are bonded together and  $B_{ij}=0$ otherwise.
-Using this notation, the interactive force $(\vec{F_{IA}})_{ij}$ on an element i by an element j is given by
+Using this notation, the interactive force $(\vec{F}_{IA})_{ij}$ on an element i by an element j is given by
 \begin{equation}
 \label{F_interactione}
-(\vec{F_{IA}})_{ij}= \left\{%
+(\vec{F}_{IA})_{ij}= \left\{%
   \begin{array}{ll}
-   (\vec{F_{e}})_{ij} + (\vec{F_{d}})_{ij}
+   (\vec{F}_{e})_{ij} + (\vec{F}_{d})_{ij}
     & \mbox{if $d_{ij} \leq L_{ij} $ }\\
  %     & \mbox{if $|x_{i} -x_{j}| \leq \frac{1}{2}(D_{i}+D_{j}) $ }\\
-    (\vec{F_{e}})_{ij} + (\vec{F_{d}})_{ij}
+    (\vec{F}_{e})_{ij} + (\vec{F}_{d})_{ij}
  %     & \mbox{if $|x_{i} -x_{j}| > \frac{1}{2}(D_{i}+D_{j}) \textrm{ and } B_{ij}=1 $ }\\
@@
 \label{F_elastic}
-(\vec{F_{e}})_{ij}= -\kappa_{e}  \bigg( d_{i,j}-L_{i,j} \bigg) T_{i,j} \vec{r},
-\end{equation}
-where $\vec{r}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
+(\vec{F_{e}})_{ij}= -\kappa_{e}  \bigg( d_{i,j}-L_{i,j} \bigg) T_{i,j} \vec{r}_{ij},
+\end{equation}
+where $\vec{r}_{ij}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
 We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F}_{IA})_{ij}=-(\vec{F}_{IA})_{ji}$).
 %This is in contrast to some other DEM models in the literature (e.g. \citet{Li2014}). 
-The minimum thickness is preferred to the average thickness, since this means that the for two bonded elements a fixed distance apart, acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero.
+The minimum thickness is preferred to the average thickness, since this means that for two bonded elements a fixed distance apart, the acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero.
 %
@@
 The frictional damping force has components that damp both the relative radial velocity and relative transverse velocities of the two elements.
-If $\vec{r}^{\perp}$ is the direction vector perpendicular to $\vec{r}$, and $P_{\vec{r}}$ and $P_{\vec{r^{\perp}}}$ are the projection matrices that project onto $\vec{r}$ and $\vec{r}^{\perp}$ respectively, then the frictional damping force is given by
+If $\vec{r}_{ij}^{\perp}$ is the direction vector perpendicular to $\vec{r}_{ij}$, and $P_{\vec{r}_{ij}}$ and $P_{\vec{r}_{ij}^{\perp}}$ are the projection matrices that project onto $\vec{r}_{ij}$ and $\vec{r}_{ij}^{\perp}$ respectively, then the frictional damping force is given by
 \begin{equation}
@@
 %(F_{d})_{ij}=   -C_{r}|(u_{i} -u_{j}) \cdot \vec{r}   | \vec{r}  - C_{t}|(u_{i} -u_{j})\cdot  \vec{r}^{\perp} | \vec{r}^{\perp})
-(\vec{F_{d}})_{ij}=   \Bigg (-c_{r} P_{\vec{r}}  - c_{t} P_{\vec{r}^{\perp}} \Bigg ) \cdot (\vec{u_{i}} -\vec{u_{j}} ) 
+(\vec{F_{d}})_{ij}=   \Bigg (-c_{r} P_{\vec{r}_{ij}}  - c_{t} P_{\vec{r}_{ij}^{\perp}} \Bigg ) \cdot (\vec{u_{i}} -\vec{u_{j}} ) 
 \end{equation}
@@
 The coupling from the ocean model to the LTAM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LTAM model, to be used in the momentum and thermodynamic equations of the ice elements.
-Within the LTAM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme.
-The LTAM model is not sensitive to the chosen interpolation scheme.
+Since tabular icebergs are explicitly resolved in the ocean, it is sufficient for each element to interact with ocean mixed layer only (i.e.: there is no need to manually embed icebergs into the ocean by integrating ocean fields over the icebergs' thickness, as suggested in \citet{Merino2016}).
+Within the LTAM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme. The LTAM model is not sensitive to the chosen interpolation scheme.
 
@@
 
-Finally, we note that since the tabular iceberg are explicitly resolved in the ocean, it is sufficient for each element to interact with ocean mixed layer (i.e.
-there is no need to manually embed the iceberg into the ocean by integrating ocean fields over the iceberg thickness, as in \citet{Merino2016}).
-
 \subsection{Thermodynamics}
@@
 respectively.
-In this way, elements with no bonds, melt like point particle icebergs, elements at the center of large structures melt like ice shelves, and elements at the sides of large structures have a combination of iceberg side and basal melt, and ice-shelf melt.
+In this way, elements with no bonds, melt like point-particle icebergs, elements at the center of large structures melt like ice shelves, and elements at the sides of large structures have a combination of iceberg side and basal melt, and ice-shelf melt.
 
@@
 The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference.
-The configuration is the same as that of the Ocean0 setup in the MISOMIP, with minor changes to the ice-shelf geometry (see Appendix D for details).
+The configuration is the same as that of the Ocean0 setup in the MISOMIP, with a few minor changes to the ice-shelf geometry (see Appendix D for details).
 % (see supplementary materials for details).
@@
 \subsection{Ocean model setup}
-The LTAM model is coupled to the MOM6 ocean model.
+The LTAM model is coupled to the MOM6 ocean model \citep{Hallberg2013}.
 The ocean model is run using a vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
 In particular, model layers bend underneath the ice shelf as they would in a sigma-coordinate model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
-The coordinate system was achieve using ALE regridding-remapping scheme \citep{White2009}.
+The coordinate system was achieved using ALE regridding-remapping scheme \citep{White2009}.
 The model uses a horizontal resolution of 2km, and 72 vertical layers.
@@
 
-After the spinup period, a wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice-shelf cavity.
+After the spinup period, a wind stress $\vec{\tau} = <\tau_{x},\tau_{y}> = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice-shelf cavity.
 Perturbation experiments were performed using other wind stress values.
@@
 
-During spinup, the injection of buoyant meltwater at the base of the ice shelf drives a circulation within the domain (not shown).
+During spinup, the injection of buoyant meltwater at the base of the ice shelf drives a clockwise circulation within the domain (not shown).
 The circulation compares well with an identical static ice-shelf experiment run using an Eularian ice shelf model \citep{Goldberg2012}  (a detailed comparison of the Lagrangian and Eularian ice shelf models is presented in a separate study, and is not shown here).
 
-Once spinup is complete, numerical bonds are severed and the icebergs begin to move away from the ice shelf (see animations in the supplementary materials).
+Once spinup is complete, the elements near the ice-shelf front are allowed to move freely, and the icebergs begin to drift away from the ice shelf (see animations in the supplementary materials).
 The semi-circular tabular iceberg moves as a cohesive unit due to the presence of the numerical bonds, while the smaller ice fragments quickly disperse (Figure \ref{fig:Spread_area}).
 The tabular iceberg drifts towards the northward east, driven by the wind and steered by the Coriolis force.
+
 A warming of the surface waters is observed around the tabular iceberg, with the largest warming occurring at the ice-shelf front and along the tabular iceberg's rounded edge (Figure \ref{fig:SST_Collapse}).
@@
 As mentioned above, the direction (and speed) of the iceberg drift is largely determined by the wind speed and direction.
-Perturbation experiments using different wind stresses show that for sufficiently large winds, the tabular iceberg drifts to the north east when the zonal component of the wind stresses is positive, and to the north west when the zonal component of the wind stress is negative (not shown).
+Perturbation experiments using different wind stresses show that for sufficiently large winds, the tabular iceberg drifts to the north east when $\tau_{x} >0$, and to the north west when $\tau_{x} <0$ (not shown).
 For a purely zonal wind stress with $|\tau_{x}| \leq 0.01 \frac{\textrm{N}}{\textrm{m}^{2}}$, the iceberg does not move away from the ice shelf.
@@
 In this case, the model behavior is more similar to an ice-shelf disintegration and does not create a cohesive tabular iceberg.
+By breaking some (but not all) numerical bonds, we can simulate the fracturing of tabular icebergs, allowing tabular icebergs to break into smaller pieces (Figure ???).
+The breaking of a tabular iceberg increases decay rate of the iceberg by increasing the surface area of ice exposed to the ocean.
+Splitting the tabular iceberg into smaller fragments also allows the fragments of the iceberg to move more rapidly, and be more strongly influenced by the wind.
 
@@
 
-The capabilities of the tabular iceberg model was demonstrated by modeling a tabular iceberg drifting away from an idealized ice shelf (also constructed using Lagrangian elements).
+The capabilities of the tabular iceberg model were demonstrated by modeling a tabular iceberg drifting away from an idealized ice shelf (also constructed using Lagrangian elements).
 The results show that explicitly resolving the iceberg in the ocean allowed for a complex interaction between the tabular iceberg and the surrounding ocean.
@@
 Simulations without using numerical bonds showed that these bonds are essential for allowing the iceberg to move as a unit.
-We also demonstrate that by breaking these numerical bonds we can simulate iceberg fracture, which is important process which rapidly increases the rate of iceberg decay.
+We also demonstrate that by breaking these numerical bonds we can simulate iceberg fracture, which is important process that increases the rate of iceberg decay.
 
 To our knowledge, the model presented in this study is the first model to explicitly resolve drifting tabular icebergs in an ocean model.
-As such, a natural extension of this work is to try to include tabular icebergs into a general circulation model (GCM) used for climate projections.
+A natural extension of this work is to try to include tabular icebergs into a general circulation model (GCM) used for climate projections.
 However, before this can be done, there are a number of issues that need to be resolved:
@@
 The element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$, where $\rho$ is the ice element density.
+$T_{si}$ is the sea ice thickness.
 
@@
 To do this, we modify the traditional verlet algorithm to include both an implicit and explicit acceleration, $a=a^{exp} +a^{imp}$.
-The explicit acceleration, $a^{exp}$ includes all forcing terms which depend only on the previous time step, while the implicit acceleration, $a^{imp}$  includes forcing terms which depend on the current time step (in particular the drag and Coriolis forces).
+The explicit acceleration, $a^{exp}$ includes all forcing terms which depend only on the previous time step and the current position, while the implicit acceleration, $a^{imp}$ includes forcing terms which depend on the velocity at the current time step (in particular the drag and Coriolis forces).
 
@@
 1) $ x_{n+1} = x_{n} + u_{n} \Delta t  + \frac{1}{2} \Delta t^{2} \Bigg(a^{exp}_{n} + a^{imp}_{n} \Bigg) $.\\
-2) Calculate $a^{exp}_{n+1}$, which is a function of $x_{n+1}$, and other quantities measured at time $t_{n}$. \\
+2) Calculate $a^{exp}_{n+1}$\\
+% (which is a function of $x_{n+1}$, and other quantities measured at time $t_{n}$). \\
 3) Calculate $a^{imp}_{n+1}$ and $u_{n+1} = u_{n} + \frac{\Delta t}{2} \Bigg(a^{exp}_{n} + a^{exp}_{n+1} \Bigg) +  (\Delta t) a^{imp}_{n+1}$\\
+%  (which is a function of $u_{n+1}$, $x_{n+1}$, and other quantities measured at time $t_{n}$)
 This scheme reduces to the traditional velocity verlet when $a^{imp}$ is set to zero.
 Note that $a^{exp}_{n+1} = a^{exp}_{n+1}(x_{n+1}, t_{n})$ is an explicit function of  $x_{n+1}$ and other quantities evaluated at time $t_{n}$, while $a^{imp}_{n+1}=a^{imp}_{n+1}(u_{n+1}, x_{n+1}, t_{n})$ additionally depends on $u_{n+1}$, and needs to be solved implicitly.
-For this reason, in step 3 $a^{imp}_{n+1}$ and $u_{n+1}$ need to be solved simultaneously, as described in the next subsection.
+For this reason in step three, $a^{imp}_{n+1}$ and $u_{n+1}$ need to be solved simultaneously, as described in the next subsection.
 
@@
  \subsection{Solving for the velocity implicitly}
-Since this modified scheme contains some forcing terms which are handled implicitly, steps 2 and 3 need to be solved together.
+Since this modified scheme contains some forcing terms which are handled implicitly, $a^{imp}_{n+1}$ and $u_{n+1}$ need to be calculated simultaniously.
 We demonstrate how this is done, using a simplified one-dimensional version of equation (1), neglecting the atmospheric drag, sea ice drag and Coriolis force, so that the only implicitly treated term is the ocean drag.
-In this demonstration, we use a superscript to denote the ocean drag force, $F^{o}$ and ocean velocity, $u^{o}$ to avoid confusion with the subscripts indicating time step.
-We also define an explicit force $F^{exp}$, which accounts for all forces not proportional the element velocity.
+In this demonstration, we use a superscript to denote the ocean drag force, $F^{o}$, and ocean velocity, $u^{o}$, to avoid confusion with the subscripts indicating time step.
+We also define an explicit force, $F^{exp}$, which accounts for all forces not proportional the element velocity.
 With these simplifications, the implicit and explicit accelerations are
@@
  \begin{equation}
- u^{*}_{n} =  u_{n}  + \frac{1}{2} (\Delta t) a_{n}. 
+ u^{*}_{n} =  u_{n}  + \frac{1}{2} (\Delta t) a^{exp}_{n}. 
  \end{equation}
@@
 \section{Appendix D}
-The experiment configuration used in this study is the same as that of the Ocean0 setup in the MISOMIP, with the following three changes made:
+The experiment configuration used to initialize the calving tabular iceberg simulation (in this study) is the same as that of the Ocean0 setup in the MISOMIP, with the following three changes made:
 \begin{enumerate}
@@
 \clearpage
-
-\section{Possibly add}
-\subsection{Orientation}
-Possibly add a section where we spread mass using the orientation of the icebergs.
 
@@
 Res.
-Lett.}, 42, 459–465.
+Lett.}, 42, 459Ð465.
 
@@
 Nicholls.
-(2001), Iceberg trajectory modeling and meltwater injection in the Southern Ocean (1978–2012).
+(2001), Iceberg trajectory modeling and meltwater injection in the Southern Ocean (1978Ð2012).
 {\it J.
@@
 
-\bibitem[Grosfeld and Sandhäger (2004)]{Grosfeld2004}
-Grosfeld, K., and H. Sandhäger, (2004). The evolution of a coupled ice shelf–ocean system under different climate states. {\it Global and Planetary Change}, 42(1), 107-132.
+\bibitem[Grosfeld and SandhŠger (2004)]{Grosfeld2004}
+Grosfeld, K., and H. SandhŠger, (2004). The evolution of a coupled ice shelfÐocean system under different climate states. {\it Global and Planetary Change}, 42(1), 107-132.
 
@@
 Goosse, and H.
-Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104–113.
+Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104Ð113.
 
 \bibitem[Kubat et al (2005)]{Kubat2005}
-Kubat I., M. Sayed, S. Savage, T. Carrieres (2005), An operational model of iceberg drift {\it Int. J. Off. Polar Eng.}, 15 (2), 125–131
+Kubat I., M. Sayed, S. Savage, T. Carrieres (2005), An operational model of iceberg drift {\it Int. J. Off. Polar Eng.}, 15 (2), 125Ð131
 
@@
 Coward, and J.L.
-Sommer (2015), NEMO–ICB (v1.
+Sommer (2015), NEMOÐICB (v1.
 0): interactive icebergs in the NEMO ocean model globally configured at eddy-permitting resolution.
@@
 Shaw, and M.
-Vernet (2007), Free-drifting icebergs: Hotspots of chemical and biological enrichment in the Weddell Sea, {\it Science}, 317, 478–482.
+Vernet (2007), Free-drifting icebergs: Hotspots of chemical and biological enrichment in the Weddell Sea, {\it Science}, 317, 478Ð482.
 
@@
 \bibitem[Tournadre et al (2016)]{Tournadre2016}
-Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. Rémy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.
+Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. RŽmy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.
 
@@
 \bibitem[Vernet et al (2012)]{Vernet2012}
-Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38–39
+Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38Ð39
 
@@
 W.
-(2014), The “footloose” mechanism: Iceberg decay from hydrostatic stresses.
+(2014), The ÒfootlooseÓ mechanism: Iceberg decay from hydrostatic stresses.
 {\it Geophys.
@@
 Adcroft, and R.
-Hallberg (2009), High-order regridding–remapping schemes for continuous isopycnal and generalized coordinates in ocean models.
+Hallberg (2009), High-order regriddingÐremapping schemes for continuous isopycnal and generalized coordinates in ocean models.
 {\it J.
@@
 
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ |c c c c| }
+\hline
+Parameter & Symbol & Value &  Unit \\
+\hline
+Domain Length &  $L_{x}$ & 80  & km \\
+Domain Width &  $L_{y}$ & 480  & km \\
+Horizontal Resolution &  $\Delta x$ & 2  & km \\
+Number of vertical layers &  $N_{l}$ & 72  & non-dim\\
+Horizontal Viscosity &  $\nu_{H}$ & 6.0 & $\frac{m^{2}}{s}$ \\
+Diapycnal Viscosity &  $\nu_{V} $ & $10^{-3}$ & $\frac{m^{2}}{s}$ \\
+Horizontal Diffusivity & $ \epsilon_{H}$ & 1.0 & $ \frac{m^{2}}{s}$ \\
+Diapycnal Diffusivity &  $\epsilon_{V} $ & $5 \times 10^{-5}$ & $\frac{m^{2}}{s}$ \\
+Initial Surface Temperature &  $ T_{t}$& -1.9   & $ ^{o} C$\\
+Initial Bottom Temperature &  $ T_{b}$&  1.0  & $ ^{o} C$\\
+Initial Surface Salinity &  $ S_{t}$& 33.8   & psu\\
+Initial Bottom Salinity &  $ S_{b}$&  34.7  & psu\\
+Maximum Ocean depth &  $H_{ocean} $ & 720 & m \\
+Relaxation Time of Sponge Layer &  $T_{sponge}$ & 0.1  & days\\
+%Background Frictional Velocity Below Ice &  $u^{*}_{bg}$ & 0.0  & 104 \\
+%Drag Coefficient Below Ice&  c_{d} & $0.0025$  & (non dim)\\
+%Class 9 &  $3.9\times 10^{11}$ & 1659 & 104 \\
+Time Step for Static Shelf Experiment & $dt_{Static}$ &  1000  & s\\
+Time Step for Iceberg Calving Experiment & $dt_{Calving}$ &  10  & s\\
+%Class 1 &  $8.8\times 10^{7}$ & 60  & 0.0026 & 40 & 2000 \\
+%Class 2 &  $4.1\times 10^{8}$ & 100 & 0.0072 & 67 & 200\\
+%Class 3 &  $3.3\times 10^{9}$ & 200  & 0.029 &133 & 50 \\
+%Class 4 &  $1.8\times 10^{10}$& 350 &  0.12 &175  & 20 \\
+%Class 5 &  $3.8\times 10^{10}$ & 500  & 0.18 &250 & 10\\
+%Class 6 &  $7.5\times 10^{10}$ & 700   & 0.35 &250 & 5\\
+%Class 7 &  $1.2\times 10^{11}$ & 900  & 0.56 &250  & 2 \\
+%Class 8 &  $2.2\times 10^{11}$ & 1200  & 1.0&250 & 1 \\
+%Class 9 &  $3.9\times 10^{11}$ & 1600 & 1.8&250 & 1  \\
+%Class 10 & $7.4\times 10^{11}$ &  2200 & 3.5 &250  &1\\
+\hline
+\end{tabular}
+%\caption{Description of the iceberg calving classes used in the model.
+{\it Mass}, {\it Length}, {\it Area} and {\it Th} refer to the iceberg mass, length, area, and thickness at the time of calving.
+{\it Scaling} is the number of icebergs represented by one Lagrangian point particle.
+The iceberg mass and thickness for each class are the same as those reported in \citet{Gladstone2001}.
+The iceberg area and length for each class is calculated from the iceberg mass and thickness by assuming that the icebergs are cuboids with a length to width ratio of 1.5, using an iceberg density $\rho_{i}=850$kg/$\textrm{m}^{3}$.}
+% Note that the areas of the iceberg classes (calculated from the iceberg lengths and masses given in \citep{Gladstone2001}) are not monotonically increasing.
+\label{table:parameters2}
+\end{center}
+\end{table}
+
+\clearpage
+
 \begin{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment.
+\caption{ {Snapshots of the fraction of ice cover in the LTAM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse}} and \ref{fig:Velocity_section_Collapse}.}
+The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Velocity_section_Collapse} and \ref{fig:Temperature_section_Collapse}}.}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp.png}
-\caption{ {Snapshots of the sea surface temperature in the LIISM tabular iceberg calving experiment.
+\caption{ {Snapshots of the sea surface temperature in the LTAM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Regular_towards_coast}
-\caption{ {Results of an ice-only LIISM simulation with no bonds between ice elements.
+\caption{ {Results of an ice-only LTAM simulation with no bonds between ice elements.
 Ice elements are initialized throughout the domain, as shown in panel (a).
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Tabular_and_regular_towards_coast_manual}
-\caption{ {Results of an ice-only LIISM simulation using bonds between elements.
+\caption{ {Results of an ice-only LTAM simulation using bonds between elements.
 Ice elements are initialized throughout the domain, as shown in panel (a).
@@
 Adjacent elements are bonded together.
-The centers of bonded elements are plotted in pink.
-The element bonds form equilateral triangles which give the larger structure rigidity.
-The black circles shows to the interactive length scales used in element interactions.
-(b) Intersection of a hexagonal element and an ocean grid.
+The element bonds (plotted in pink) form equilateral triangles which give the larger structure rigidity.
+The black circles show the circular element shape used in element interactions, and are inscribed inside the hexagonal shape used for mass-spreading.
+(b) Intersection of a hexagonal element and the ocean grid.
 The colors indicate the fraction of the hexagon that lies in each grid cell.
-These fractions are used as weights to spread LIISM properties to the ocean grid (see text for more details).}}
+These fractions are used as weights to spread LTAM properties to the ocean grid (see text for more details).}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_spread_mass_mass.png}
-\caption{ {(a) Ocean bottom topography in MISOMIP configuration.
-(b) ice-shelf draft used in static shelf experiment.
-The ice draft is calculated from the ice mass in an ocean grid cell, which is found by spreading ice mass across ocean cells accounting for the size of each element (as explained in Section 2.3).
-(c) Same as in panel (b), except that the interpolation does not account for iceberg size, and instead treats elements as point masses.}}
+\caption{ {(a) Ocean bottom topography and (b) ice-shelf draft used to initialized the tabular iceberg calving simulation.
+The ice draft is calculated from the total mass in an ocean grid cell after the mass-spreading interpolation has been applied (as explained in Section 2.3).
+(c) Initial ice draft that would be calculated if the mass-spreading interpolation were not used (i.e.: elements treated as point masses).}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LIISM tabular iceberg calving experiment.
+\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LTAM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LIISM tabular iceberg calving experiment.
+\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LTAM tabular iceberg calving experiment.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
  \clearpage
+
  \end{article}
+ \clearpage 
+\section{Extra Figure:}
+ \clearpage 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
+\caption{ {Melt rate 30 days after calving for simulations using melt rates derived using (a) three equation model, (b) icebergs drift parametrization, (c) a mixture between the two (as described in Section 2.5.}}
+\end{center}
+\label{fig:threemelt}
+\end{figure}
+ \clearpage
 

### 2017-02-16 Icebergs_only.tex
More changes to iceberg only version

@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
-\caption{ {Melt rate 30 days after calving for simulations using melt rates derived using (a) three equation model, (b) icebergs drift parametrization, (c) a mixture between the two (as described in Section 2.5.}}
+\caption{ {Melt rate 30 days after calving for simulations using melt rates derived using (a) three equation model, (b) icebergs drift parametrization, (c) a mixture between the two (as described in Section 2.5.)}}
 \end{center}

### 2017-02-24 Lagrangian_MISOMIP.tex
More changes to the Lagrangian MISOMIP paper

--- 2017-01-27 Tech1.tex
@@
 %\titlerunninghead{Effects of iceberg calving size}
-\titlerunninghead{THE EFFECTS OF ICEBERG CALVING SIZE}
+\titlerunninghead{Lagrangian Ice-Shelf Cavity Modeling }
 
@@
 
-\authoraddr{G. Marquez, Geophysical Fluid Dynamics Laboratory, Princeton University}
+\authoraddr{G. Marques, Geophysical Fluid Dynamics Laboratory, Princeton University}
 
@@
 %\title{The effect of calving-size distribution on sea-ice formation around Antarctica}
-\title{Modeling ice-shelf cavities and calving tabular icebergs}
+\title{Modeling ice-shelf cavities using Lagrangian elements}
 %\title{The effects of iceberg calving-size distribution in a global climate model}
@@
  \authors{A.A. Stern,\altaffilmark{1} , A. Adcroft\altaffilmark{1}
-   and O. Sergienko \altaffilmark{1} , G. Marquez\altaffilmark{1}, R. Hallberg\altaffilmark{1}}
+   and O. Sergienko \altaffilmark{1} , G. Marques\altaffilmark{1}, R. Hallberg\altaffilmark{1}}
 
@@
 \begin{abstract}
-The calving of giant icebergs is an important process in the Antarctic freshwater cycle.
-Iceberg calving can significantly alter the geometry of an ice-shelf cavity, potentially affecting the circulation within the cavity.
-Giant icebergs which break away can drift across large distance, altering regional ocean circulation, sea ice distributions and bottom water formation.
-However, despite its importance, the current generation of numerical models is unable to represent this process in a physically realistic way.
-In this study we develop a model of an ice-shelf cavity using a Lagrangian ice shelf.
-The ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
+%ceberg calving is an important feature of the Antarctic environment. In where giant pieces of the ice shelf break away from the shelf to form giant tabular icebergs and drift into the open ocean.
+
+Iceberg calving is an important feature of the Antarctic environment, and accounts for approximately half of Antarctic ice-shelf decay. 
+However, despite its importance, the current generation of ocean models are unable to represent iceberg calving in a physically realistic way.
+This is because current models of ice-shelf cavities represent the ice shelf on an static Eularian grid, which does not lend itself to modeling drifting icebergs. 
+In this study we develop a new ice-shelf cavity model where the ice shelf is represented on a `Lagrangian grid'.
+In this model, the ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
 This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-The model developed in the manuscript is referred to as the Lagrangian Iceberg/Ice Shelf Model (LIISM).
-This paper provides a description of the LIISM model and discusses a number of the technical elements involved in building a Lagrangian ice shelf.
-To test the model, the LIISM is used to model an idealized ice-shelf cavity which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-Results from static ice-shelf experiments compare well to results using a more traditional Eularian ice-shelf models.
-The novel capabilities of the  LIISM are demonstrated by modeling a tabular iceberg breaking away from the idealized ice shelf.
-
+We test the model by simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). 
+We then compare the results to a second simulation that uses an Eularian ice shelf with an otherwise identical configuration.
+Results show that the Lagrangian and Eularian models are almost indistinguishable.
+% For example, differences in the models are two orders of magnitude smaller than the differences observed when changing the ocean model coordinate system. 
+The similarly between the Eularian and Lagrangian models provides a proof of concept for the Lagrangian model, and means that we can confidently use this model to extend the capabilities of the Eularian model.% The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
+
+% and freshwater fluxes from icebergs affect regional ocean circulation, sea ice distributions and bottom water formation around Antarctica
 \end{abstract}
@@
 \section{Introduction}
-%\subsection{Key points for writing introduction}
-%
-%1) Physical processes that affect the ocean circulation around Antarctica (involving ice shelf cavities /tabular icebergs). 
-%
-%2) Why is it important that we are about to model these regions correctly, and tabular icebergs?
-%
-%3) What are the significant efforts that have been made thus far towards correctly modeling ice shelf cavities / Antarctic fresh water fluxes.
-%
-%4) What is missing - and what we intend to add
-%
-%5) Similar things which have been done in the past (if there are any)
-%
-%6) Short summary and paper description.
-%
-%\subsection{Introduction}
 Floating ice shelves cover vast regions of the Antarctic polar oceans.
@@
 Beneath the ice shelves, both the bottom topography and the ice-shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}.
-The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean within the ice shelves cavities a unique character.
-
-In addition to suppressing the depth of ocean surface, the ice shelves also melt (and break), thus providing a freshwater flux into the ice-shelf cavities. 
-%Perhaps remove this line....:
-This melting and breaking of Antarctic ice shelves is a key component in the Antarctic meltwater system.
-%, and affect the ocean hydrography and biology both inside and outside of the ice shelf cavities. %Some elements of this Antarctic meltwater system are discussed in the following paragraphs. 
-%
-Within the ice-shelf cavities, the input of buoyant meltwater into the ocean creates rising density plumes, which are guided along the ice-shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
-The strength of the circulation within the cavity feeds back onto the ice-shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice-shelf melt \citep{Lewis1986, Jacobs2011}.
-
-The Antarctic ice shelves are also characterized by large infrequent calving events where massive pieces of the ice shelves break off, to create giant tabular icebergs.
-Observational estimates suggest that approximately half of Antarctic ice-shelf decay is due to iceberg calving, while the other half occurs through ice-shelf melting \citep{Depoorter2013, Rignot2013}.
-Calving icebergs' sizes appear to fit a power law distribution, with the majority of icebergs being small (L$<$ 1 km), while giant tabular icebergs (L $>$ 5km) account for more than 90$\%$ of the icebergs mass \citep{Tournadre2016}.
-After calving, icebergs slowly drift away from their mother glaciers, often becoming stuck in sea ice, or become grounded along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}.
-Giant tabular icebergs also extend deep into the water column, and have to potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
-
-Melt water from both ice-shelf melt and iceberg melt impact the ocean hydrography outside of the ice-shelf cavities, influencing sea ice production and bottom water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
-The long distances traveled by giant icebergs before melting means that their meltwater impact is often felt hundreds of kilometers away from their calving origins \citep{Stern2016}.
-Melt water injection (and the accompanying upwelling) from ice shelves and icebergs can also influence biological productivity by providing nutrients to the surface ocean or changing sea ice conditions \citep{Arrigo2002, Vernet2012, Biddle2015}.
-The increased productivity associated with free-floating tabular icebergs has been linked with local increases in ocean carbon uptake, potentially large enough to be a significant fraction of the Southern Ocean carbon sequestration \citep{Smith2007}.
-%either increasing it by providing nutrients to the surface ocean, or decreasing by changing sea ice conditions
-
-In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic meltwater system described in the previous paragraphs.
-This increased interest has led to accelerated efforts to accurately model Antarctic ice-shelf cavities \citep{Asay-Davis2016}.
+The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean in this region a unique character.
+
+Satellite observations suggest that ice-shelf decay occurs via two main processes: melting and breaking \citep{Depoorter2013, Rignot2013}.
+Each of these is responsible for approximately half of the ice-shelf decay, and each influences the surrounding ocean (and ice-shelf geometry) in a distinct way.
+Melting at the base of ice shelves causes freshwater fluxes into the ice-shelf cavity.
+The input of buoyant meltwater creates rising density plumes, which are guided along the ice-shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
+Over time, melting at the ice-shelf base can erode the ice shelf, gradually altering the ice-shelf geometry.
+%The strength of the circulation within the cavity feeds back onto the ice-shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice-shelf melt \citep{Lewis1986, Jacobs2011}.
+In contrast, ice-shelf breaking causes sudden changes to the ice-shelf geometry, and releases giant icebergs into the ocean.
+After calving, these tabular icebergs can travel large distances and impact ocean hydrography \citep{Martin2010, Stern2015}, sea-ice formation \citep{Robinson2012, Stern2016} and ocean biology \citep{Smith2007, Vernet2012, Biddle2015} many miles away.
+
+In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic mass balance, and hence, on modeling Antarctic sub-ice-shelf cavities \citep{Asay-Davis2016}.
+% This increased interest has led to accelerated efforts to accurately model Antarctic ice-shelf cavities \citep{Asay-Davis2016}.
 Modeling the ocean beneath the ice shelves presents a unique set of challenges, since (i) the presence of ice shelves provides a rigid upper boundary for the ocean model which is not encountered elsewhere in the ocean, and (ii) melting and breaking ice shelves imply a changing ocean boundary conditions which present numerous numerical difficulties.
 
-The earliest models of ocean ice-shelf cavities were developed using a static ice shelves with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
+The earliest models of ocean ice-shelf cavities were developed using static ice shelves with a fixed shape \citep{Hellmer1989, Determan1994, Grosfeld1997, Holland2001, Losch2008}.
 In these models, ice-shelf melting was represented through salinity and temperature fluxes, while the ice-shelf geometry remained unchanged.
@@
 More recently, dynamic ice-shelf models have been coupled the ocean cavity, allowing the study of grounding line migration, which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
-As far as we know, all models of ice-shelf cavities to date have neglected ice-shelf breaking and iceberg detachment.
-
-In parallel to these efforts to develop ice-shelf cavity models, a number of iceberg drift models have been developed, and have been included in some global General Circulation Models \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
-These iceberg drift models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
-Since icebergs are treated as point particles, the iceberg drift models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such iceberg drift models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
-These models are not suitable for modeling larger tabular icebergs, which feel the ocean over many grid cells, depress the ocean surface and change circulation patterns \citep{Stern2016}.
-They also not suitable for studying  the local effects that icebergs have on the surrounding ocean.
-For this reason, tabular icebergs (L $>$ 5km) are currently not represented in the iceberg drift models used in climate models, even though observations suggest that tabular icebergs account for  the vast majority of the total Southern Hemisphere icebergs mass \citep{Tournadre2016}.
-
-The ice-shelf cavity models and iceberg drift models described above have been developed separately from one another, and have not been designed to be used together in a physically consistent way.
-As such, it has not been possible to model the calving of tabular icebergs away from an ice shelf, which is an important part of the Antarctic climate system.
-The goal of this study is to develop a model which combines features of the ice-shelf cavity models and the iceberg drift models, to create an ice-shelf cavity model that is able to calve tabular icebergs.
-To do this, we create an ice-shelf model out of Lagrangian elements which are `bonded' together by numerical bonds.
-In this framework, icebergs do not get created when a calving event takes place (as in iceberg drift models), but rather the icebergs `break away' from an existing ice shelf, thus changing the geometry of the ice-shelf cavity.
-Modeling iceberg calving in a physically consistent way allows us to study the ocean response to iceberg detachment.
-%(see Figures \ref{fig:Calving_fixed_side} and Figures \ref{fig:Calving_fixed_top}, for example).  
-Also, by allowing icebergs protrude deep into the water column we can study the ocean dynamics around individual tabular icebergs (which was not possible in iceberg drift models).
-
-In all simulation in this study, the shape of the calving iceberg is prescribed.
-The question of how to correctly prescribe a calving law is undoubtably a very important question, which has rightfully received much attention in recent years \citep{Benn2007, Alley2008, Levermann2012}.
-\citet{Bassis2013}, for example, used a discrete element model (DEM) model to study the generation and propagation of cracks within an ice shelf (not coupled to an ocean model).
-In this study, we bypass the question of how to correctly calve icebergs or break bonds.
-Instead we focus on developing a framework to model the ocean response to ice-shelf breaking and the presence of tabular icebergs.
-This framework of representing ice shelves using a Lagrangian grid might be a step towards including giant tabular icebergs in climate models.
-Including ice fracture into this model will be a later step.
-
-The model developed in this study is referred to at the Lagrangian Iceberg/Ice Shelf Model (LIISM).
-Section 2 gives a description of many of the key aspects of the LIISM.
-Since this model is a new approach to modeling ice-shelf cavities, we present many of the technical elements involved in constructing the model.
-Those readers who are more interested in the model capabilities, should skip directly to the numerical experiments presented in the later sections.
-In Section 3 and 4, the LIISM model is used to simulate the circulation beneath an idealized ice shelf.
-The LIISM model results are validated by comparing them to an existing Eularian ice-shelf model.
-We then we move beyond the capabilities of the existing ice-shelf model by allowing a piece of the ice shelf to break away, becoming a tabular icebergs, and consider the ocean response to this calving event.
-
-%A prerequisite of a complete model of an ice shelf cavity with a calving ice shelf is an understanding of the physical processes involved in iceberg calving.
-The importance of this problem for projecting sea level has meant that the search for a ``calving law" has received much attention in recent years.
-However, even with a theory of ice shelf breaking, there are still significant technical barriers preventing us from modeling icebergs calving away from ice shelves in a dynamically consistent way.
-In this paper, we d
-
-%This work bears some similarity to [Basis et al], who used a DEM model to model the generation and propagation of cracks within an ice shelf.
-The present study is distinct from [Basis et al] in that (i) we  focus on the ocean's response to iceberg calving and thus our DEM model is coupled to a fully dynamic ocean model, (ii) the element in our DEM model are of scale > 1 km, while those in Basis were much smaller (1 meter), since we focus on the large scale oceanography, rather than the small scale fracture mechanics.
-Finally, we do not model the breaking in iceberg bonds and ice dynamics.
-However, including bonds between ice elements in our model means that modeling ice shelf breaking is a natural extension to this work.
-
-%This same constraint is present in previous iceberg models, and has meant that those models have only been able to represent smaller icebergs (e.g.
-icebergs with area less than $3.5km^{2}$ in \citet{Gladstone2001, Martin2010}).
-However, as mentioned above, satellite observations of iceberg size show that more than 80(?) percent of Southern Hemispheric icebergs mass is stored in icebergs with areas greater than $3.5km^{2}$  \citep{Tournadre2016}, which motivates the including of larger icebergs in climate models.
-
-\section{Model description}
-%, which can be used to model small icebergs, tabular icebergs, sea ice and ice shelf cavities
-%In this section we describe many key elements of the LIISM.  
-The LIISM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
-Each element represents a mass of ice which is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time.
-The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element.
-The elements are forced by oceanic and atmospheric forces, which are provided by the user, or are determined by coupling the LIISM to an ocean/atmosphere model.
-The elements also interact with one another and can be bonded together to form larger structures.
-In different contexts, the LIISM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
-%In this latter case, the LIISM model can be categorized as a discrete element model (DEM). 
-% in the sense that large structures are constructed from smaller independent Lagrangian elements.
-
-The LIISM model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}.
-When run with the correct set of runtime flags, the model runs as a traditional iceberg drift model.
-%
-%In this section, we discuss the equations of motion governing the element movement and the thermodynamic equations governing the decay of the elements. The also discuss the interactive forces
-
-\subsection{Equations of motion}
-The elements drift in the ocean, forced by atmosphere, ocean and sea-ice drag forces, as well as the Coriolis force and a force due to the sea surface slope.
-When these ice elements move alone (without interactions with other elements), they can be thought of as representing of small icebergs, and follow the same equations described in the iceberg drift model of \citet{Martin2010} (based on the equations outlined in \citet{Bigg1997, Gladstone2001}).
-
-In addition to the environmental forces, the elements in the LIISM model experience interactive forces due to the presence of other elements.
-Two types of interactive forces are included between elements.
-The first force is repulsive force which is applied to elements to prevent them from moving too close to one another.
-This repulsive force prevents icebergs from piling up on top of one another.
-The second interactive force is a force due to numerical `bonds', and is only applied if two elements are `bonded' together.
-When two elements are bonded, each element feels an attractive force that prevents the elements from moving too far apart from one another.
-The interactive forces between two bonded elements are defined such that in the absence of other forces the elements come to rest adjacent to one another, with no overlap of the iceberg areas.
-
-The momentum equation for each element is given by 
-\begin{equation}
-\label{Iceberg_mom_eq}
-M \frac{D \vec{u}}{Dt}=\vec{F}_{A} + \vec{F}_{W}+ \vec{F}_{R}+\vec{F}_{C} +\vec{F}_{SS}+\vec{F}_{SI}+\vec{F}_{IA} ,
-\end{equation}
-where $\frac{D}{Dt}$ is the total (Lagrangian) derivative, $M$ is the mass of the element, $\vec{u}$ is the velocity of the element, and the terms on the right hand side give the forces on the element due to air drag $(\vec{F}_{A})$, water drag $(\vec{F}_{W})$, sea ice drag $(\vec{F}_{SI})$, Coriolis force $(\vec{F}_{C})$, wave radiation force $(\vec{F}_{R})$, sea surface slope $(\vec{F}_{SS})$, and interactions with other elements ($\vec{F}_{IA}$).
-The environmental forces are the same as those presented in \citet{Martin2010}, and are provided for completeness in Appendix A.
-The details of the interactive forces are provided in below.
-
-\subsection{Interactive Forces}
-The interactive force on an element is calculated by adding together the interactions with all other elements, such that the interactive force on element $i$, $(\vec{F}_{IA})_{i}$ is given by:
-\begin{equation}
-\label{F_interaction_i}
-(F_{IA})_{i}= \Sigma_{j \neq i} (F_{IA})_{ij},
-\end{equation}
-where $(F_{IA})_{ij}$ is the force on element $i$ by element $j$.
-Both bonded and repulsive interactions are modeled using elastic stresses with frictional damping.
-The elastic component of the force is a function of the distance between the two elements, while the  frictional damping force depends on the relative velocity of the two elements.
-
-To describe the forces between two elements, we begin by introducing some notation.  Let $\vec{x_{i}}$, $\vec{x_{j}}$ be the positions of elements i and j. The distance between elements i and j is
-\begin{equation}
-\label{distance}
-d_{ij}= | \vec{x_{i}} - \vec{x_{j}}|.
-\end{equation}
-We then define the interaction diameter of an element by 
-\begin{equation}
-\label{Diameter}
-D_{i}=2 \sqrt{\frac{A_{i}}{\pi}},
-\end{equation}
-where $A_{i}$ is the planar surface area of element i. Using this, we define the critical interactive length scale, 
-\begin{equation}
-L_{ij}=\frac{D_{i} + D_{j}}{2},
-\label{eq:Interaction_crit}
-\end{equation}
-which governs interactions between elements i and j. 
-Repulsive forces are only applied when $d_{i,j} \textless L_{i,j}$, while bonded forces are only applied when the when $d_{i,j} \textgreater L_{i,j}$ and a bond exists between element i and j.
-Bond and repulsive forces are designed to such that in the absence of other forces, bonded particles will settle in an equilibrium position where elements are separated by the critical interaction length scale $L_{i,j}$.
-% (see schematic in Figure \ref{fig:Interactive_forces}).
-
-To aid in notation, we define a bond matrix $B_{ij}$ such that $B_{ij}=1$ if elements i and j are bonded together and  $B_{ij}=0$ otherwise.
-Using this notation, the interactive force $(\vec{F_{IA}})_{ij}$ on an element i by an element j is given by
-\begin{equation}
-\label{F_interactione}
-(\vec{F_{IA}})_{ij}= \left\{%
-  \begin{array}{ll}
-   (\vec{F_{e}})_{ij} + (\vec{F_{d}})_{ij}
-    & \mbox{if $d_{ij} \leq L_{ij} $ }\\
- %     & \mbox{if $|x_{i} -x_{j}| \leq \frac{1}{2}(D_{i}+D_{j}) $ }\\
-    (\vec{F_{e}})_{ij} + (\vec{F_{d}})_{ij}
- %     & \mbox{if $|x_{i} -x_{j}| > \frac{1}{2}(D_{i}+D_{j}) \textrm{ and } B_{ij}=1 $ }\\
-       & \mbox{if $d_{ij} >  L_{ij}  \textrm{ and } B_{ij}=1 $ }\\
-      0
- %     & \mbox{if $|x_{i} -x_{j}| > \frac{1}{2}(D_{i}+D_{j}) \textrm{ and } B_{ij}=0 $ }.\\
-      & \mbox{if $d_{ij} > L_{ij} \textrm{ and } B_{ij}=0 $ }.\\
-  \end{array}
-\right.
-\end{equation}
-$(\vec{F_{e}})_{ij}$ and $(\vec{F_{d}})_{ij}$ are the elastic and frictional damping components of the interactive force between elements i and j.
-The elastic force $(\vec{F_{e}})_{ij}$ between elements is given by
-\begin{equation}
-\label{F_elastic}
-(\vec{F_{e}})_{ij}= -\kappa_{e}  \bigg( d_{i,j}-L_{i,j} \bigg) T_{i,j} \vec{r},
-\end{equation}
-where $\vec{r}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, and $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
-We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F}_{IA})_{ij}=-(\vec{F}_{IA})_{ji}$).
-%This is in contrast to some other DEM models in the literature (e.g. \citet{Li2014}). 
-The minimum thickness is preferred to the average thickness, since this means that the for two bonded elements a fixed distance apart, acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero.
-%
-%Since ice elements are able to melt entirely, the repulsive forces between elements need to be carefully defined so that they are stable even for very small elements with mass approaching zero.
-We define the elastic repulsive force $(F_{r})_{ij}$ between elements i and j as
-%\begin{equation}
-%\label{F_elastic}
-%(F_{r})_{ij}= -\kappa_{r} A_{o}(i,j) T_{i,j}\vec{r},
-%\end{equation}
-%where $A_{o}(i,j)$ is the overlap area of the two circles centered at $\vec{x_{i}}$ and $\vec{x_{j}}$, with diameter $D_{i}$ and $D_{j}$ (see Figure \ref{fig:Interactive_forces}), respectively, and $\kappa_{r}$ is the repulsive spring constant.
-We choose $(F_{r})_{ij}$ to be proportional to the overlap area between the interactive circles surrounding each element so that the acceleration due to this repulsive force is bounded, even as the element mass approaches zero.
-This consideration is not needed for the bonded force, since element bonds will be broken when elements are smaller than a threshold size.
-%[Should we use a bonded force given by  $(F_{b})_{ij}= -\kappa_{b}  \bigg( d_{i,j}-L_{i,j}) \bigg)^{2} T_{i,j} \vec{r}$ rather? Come back to this.]
-
-The frictional damping force has components that damp both the relative radial velocity and relative transverse velocities of the two elements.
-If $\vec{r}^{\perp}$ is the direction vector perpendicular to $\vec{r}$, and $P_{\vec{r}}$ and $P_{\vec{r^{\perp}}}$ are the projection matrices that project onto $\vec{r}$ and $\vec{r}^{\perp}$ respectively, then the frictional damping force is given by
-\begin{equation}
-\label{F_damping} 
-%(F_{d})_{ij}=   -C_{r}|(u_{i} -u_{j}) \cdot \vec{r}   | \vec{r}  - C_{t}|(u_{i} -u_{j})\cdot  \vec{r}^{\perp} | \vec{r}^{\perp})
-(\vec{F_{d}})_{ij}=   \Bigg (-c_{r} P_{\vec{r}}  - c_{t} P_{\vec{r}^{\perp}} \Bigg ) \cdot (\vec{u_{i}} -\vec{u_{j}} ) 
-\end{equation}
-Here $c_{r}$ and $c_{t}$ are the radial and transverse drag coefficients.
-For the simulation below, we set $c_{r}=2\sqrt{\kappa_{e} }$ and  $c_{t}=\frac{1}{4}c_{r}$ so that the radial elastic force is critically damped, and the transverse damping is sub critical.
-The damping forces are implemented using an implicit time stepping scheme, to avoid stability issues for very small elements (details found in Appendix B).
-
-The effectiveness of the repulsive forces can be seen in Figure \ref{fig:Regular_Uncoupled_sim}, which shows an uncoupled (ice only) simulation where ice elements drift westward into a bay, and eventually come to rest with minimal overlap between elements.
-The effectiveness of the numerical bonds is demonstrated in Figure \ref{fig:Uncoupled_sim}, where tabular icebergs (constructed from many ice elements bonded together) and individual icebergs (unbonded elements) drift together towards a convex coast line.
-When the tabular icebergs arrive at the coast, they bump into the coastline and begin to rotate, influencing the paths of the other icebergs.
-In this example we see that modeling large structures using small elements bonded together, allows us to achieve large-scale structure and rotational motion, without having to include an equation for the angular momentum of the elements (as discussed in \citet{Jakobsen2001}).
-Animations of these simulations can be found in the supplementary materials.
-
-\subsection{Element geometry and packing}
-Elements are packed differently depending on the shape of the elements.
-For all simulations in this study, we use elements whose surface areas are equally-sized regular hexagons.
-In order to pack these elements together, the hexagonal elements are initially arranged in a staggered lattice, with each element bonded to the adjacent elements (see Figure  \ref{fig:Hex_intersections}a).
-In this arrangement, each element (away from the edges) is bonded to six other elements.
-The bonds between elements form a pattern of equilateral triangles, which give the larger structure rigidity.
-
-Some experiments were also performed using rectangular elements, arranged in a regular (non-staggered) lattice.
-In this case, each element forms four bonds with adjacent elements.
-However, the resultant structures were found to be much less rigid and tended to collapse when sufficient forces was applied.
-For this reason, hexagonal elements were preferred.
-
-\subsection{Ocean-ice and ice-ocean coupling}
-The LIISM model is coupled to the ocean model via a two-way synchronous coupling, meaning that ocean model fields are passed to the LIISM model and the LIISM model fields are passed back to the ocean model at every time step.
-Passing fields between the two models involves interpolating fields between the Eulerian grid of the ocean model and the `Lagrangian grid' of the LIISM model (i.e.: onto the ice elements).
-
-The coupling from the ocean model to the LIISM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LIISM model, to be used in the momentum and thermodynamic equations of the ice elements.
-Within the LIISM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme.
-The LIISM model is not sensitive to the chosen interpolation scheme.
-
-%More care needs to be taken when passing fields back from the LIISM model to the ocean model. 
-The coupling in the other direction, from the LIISM model to the ocean model, is more complex.
-The LIISM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean by applying a no-slip boundary condition and frictional velocity beneath the ice.
-Fields from the LIISM model are interpolated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model.
-Since the LIISM model applies large pressures to the ocean surface, the ocean model is sensitive to the interpolation scheme used to map the LIISM fields to the ocean grid.
-Sudden jumps to the ocean surface pressure can trigger tsunamis within the ocean model, making the ocean model become unstable.
-
-The interpolation of the LIISM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LIISM model (see Section 2.3).
-Fields are `spread' to the ocean model grid by exactly calculating what fraction of an element's surface area lies in a particular grid box, and dividing the field in proportion to this fraction.
-%While the position of a particular element might be inside one ocean grid cell, the implied shape of the element will often intersect other ocean grid cells. 
-For example, consider a hexagonal element in the LIISM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
-In this situation, the mass of the element is divided between these four ocean cells in proportion to the overlap area between the hexagonal element and the grid cell (this fraction is shown by the colors in \ref{fig:Hex_intersections}b).
-An advantage of this approach is that there are no jumps in pressure as an element moves from one grid cell to another.
-
-The numerical calculation of the intersection between hexagons and the ocean grid is simplified by dividing the hexagon into 6 equilateral triangles.
-This method allows for the intersection to be found even when the hexagon is not aligned with the grid.
-%The LIISM model can be run using hexagonal or rectangular elements.
-
-The field-spreading scheme is coded with the restriction that an element's area can only intersect a maximum of four ocean grid cells at a time.
-A consequence of this is that this sets a limit on the maximum size of elements that can be represented using this model, i.e.: the longest horizontal dimension of an ice element must be smaller than the ocean grid spacing.
-Larger ice structures are constructed by bonding together smaller elements.
-
-\subsection{Thermodynamics}
-The ice elements decay according to a number of melt parameterizations.
-As the ice elements melt, their mass decreases, and the appropriate salt, mass and heat fluxes are passed to the ocean.
-In this section we described the melt parametrization for bonded, unbonded and partially bonded elements.
-
-As mentioned above, ice elements which do not interact with other elements are modeled identically to the point particle icebergs described in \citet{Martin2010}.
-These elements melt according to three semi-empirical parametrization for melt commonly used in previous iceberg studies \citep{Gladstone2001,Martin2010}.
-Three types of iceberg melting are used: basal melt, $M_{b}$, melt due to wave erosion, $M_{e}$ and melt due to buoyant convection, $M_{v}$.
-$M_{e}$ and $M_{v}$ are applied to the sides of the ice element, while $M_{b}$ is applied at the ice element base.
-The details of $M_{b}$.
-$M_{v}$ and $M_{e}$ are given in Appendix A.
-
-When multiple elements are bonded together to form larger structures, it is no long appropriate to use the parameterizations for melt developed for individual point-particle icebergs.
-An element which is completely surrounded by other elements, is meant to represent a piece of ice in the middle of a large structure, and hence will not experience a melt at its sides due to wave erosion or buoyant convection.
-Also, the iceberg basal melt rate, $M_{b}$ described above is based on boundary layer theory of flow past a finite plate, and is only appropriate for basal surfaces where the distance from the leading edge is sufficiently small \citep{Eckert1950, Weeks1973}.
-For an element in the interior of large structures, the distance from the edge of the structure is large, and so using $M_{b}$ for the basal melt is not appropriate.
-Instead, the basal melt, $M_{s}$ is determined using the three equation model for basal melt, which is a typical melting parametrization beneath used beneath ice shelves \citep{Holland1999}.% (see Appendix A).
-
-When using both individual elements and bonded elements in the same simulation, we determine which melt rate parameterizations to use based on the amount of bonds that each element has.
-An element which is in the center of a large structure will form the maximum number of bonds, while unbonded elements form zero bonds.
-If maximum number of bonds that an element can form (given the shape of the element) is $N_{max}$, and the number bonds that an element has is $N_{b}$, then the side melt and bottom melt for that element are given by
-\begin{equation}
-M_{side}=\frac{(N_{max}-N_{b})}{N_{max}}  (M_{v} +M_{e})
-\end{equation}
-and
-\begin{equation}
-M_{bottom}=\frac{(N_{max}-N_{b})}{N_{max}}M_{b} +\frac{N_{b}}{N_{max}}M_{s}
-\end{equation}
-respectively.
-In this way, elements with no bonds, melt like point particle icebergs, elements at the center of large structures melt like ice shelves, and elements at the sides of large structures have a combination of iceberg side and basal melt, and ice-shelf melt.
-
-\subsection{Algorithms and computational efficiency}
-Including interactions between elements leads to an increase in the computational complexity of the model.
-In this subsection we comment on some of the algorithmic procedures that have been used to increase the computational efficiency.
-Readers who are not interested in this more technical side of the model should skip this section.
-\subsubsection{Time stepping}
-The ice elements in the LIISM model are advected using a semi-implicit velocity Verlet time-stepping scheme.
-The velocity verlet time stepping scheme is commonly used in DEM models in video games because it is computational efficient and has desirable stability properties \citep{Jakobsen2001}.
-This time stepping scheme was preferred to the Runge-Kutta  4, which was used in the iceberg model of \citet{Martin2010} since, the Verlet time stepping only requires one calculation of the interactive forces per time step (while the Runge-Kutta scheme requires the interactive forces to be calculated four times).
-Since the calculation of the interactive forces is one of the most computationally expensive part of the algorithm, the Verlet scheme leads to a significant increase in the speed of the model.
-We note that the Verlet scheme used in the LIISM contains a small modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
-The details of this time stepping schemed are outline in Appendix B.
-\subsubsection{Interactions and Bonds}
-At every time step, we calculate the force on each element due to interactions with every other element.
-In principle, this involves order $n^{2}$ operations (for n elements).
-However, since each element only has repulsive interactions with elements that are less than one ocean grid cell away, and each element only has bonded interactions with a small number of other elements, we are able to reduce the complexity of the system.
-
-The complexity reduction is achieved by storing the element data in an efficient way that prevents having to search through all element pairs to check if they are close to one another or are bonded with one another.
-The data storage system works as follows: pointers to the memory structures containing each element are stored in linked list data structures, which allow elements to be added and removed from the lists easily without restructuring the entire list.
-Instead of using one list for all the elements on a processor, we use a separate linked list for each ocean grid cell.
-When an element moves between ocean grid cells, it is removed from its original list and added to the list corresponding to its new ocean grid cell.
-Since the area of elements has to be smaller than the area of an ocean grid cell, the critical interaction length scale (equation \ref{eq:Interaction_crit}) is less than the length of a grid cell.
-This means that elements only experience repulsive forces with elements in the same ocean grid cell, or in one of the 8 adjacent cells.
-Limiting the possible repulsive interactions to elements in these 9 linked lists substantially reduces the computational time needed to calculate the total interactive force.
-
-Bonded interactions are handled slightly differently.
-Each bond is assigned a piece of memory.
-Each ice element contains a linked list of each of its bonds (typically up to six bonds per element).
-At each time step, the code traverses the lists of bonded elements, and adds a bonded force corresponding to these bond.
-The bonded force is only applied if $\vec{r}_{i,j} > L_{ij}$, to avoid double counting an interaction.
-Having a list of bonds stored with each element reduces the computational complexity of bonded interactions from order $n^{2}$ to order n.
-Handling bonded attractive forces separately to the repulsive and non-bonded forces means that we do not need to check whether two elements are bonded, which further increases the computational efficiency.
-
-\subsubsection{Parallelization and halos}
-The LIISM model runs on multiple processors in parallel.
-When elements move from an ocean cell on one processor to an ocean cell on a second processor, the memory has to be passed from one processor the next, added and removed to the appropriate lists and the memory has to be allocated and deallocated correctly.
-Element interactions across the edge of processors are handled using computational halos.
-A computational halo is a copy of the edge of a one processor which is appended to the edge of a second processor, so that the first processor can `see' the second processor during a time step.
-Before a time step, elements at the edges of each processor are copied onto the halos of adjacent processors so that they can be used in calculating the interactive forces.
-After each time step, these halos and removed, and the process is repeated.
-These halo updates are one of the most computationally expensive parts of the LIISM model.
-
-Keeping track of pairs of bonded elements that move across a processor edge requires a lot of book keeping since bonds have to be severed and reconnected.
-Details of how the bonds are broken and reconnected across processor boundaries are provided in Appendix~C.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \section{Experiment Setup}
-%The introduction of Lagrangian elements, numerical bond and appropriate interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice shelf cavities which undergo large calving events, and create giant tabular icebergs.
-
-%We demonstrate this capability in an experimental setup using an idealized ice shelf. For these experiments the LIISM model is coupled to the MOM6 ocean model.
-% This section contains a description of the experimental setup and numerical experiments performed. The results of these simulations are presented in Section 4.
-
- %In the examples below, the LIISM model is firstly used in uncoupled mode to model the movement of freely drifting icebergs.
-Secondly, the coupled LIISM with static ice elements is used to model an idealized ice shelf cavity.
-Finally, the fully-coupled LIISM is used to model a tabular iceberg which calves off of this ice shelf.
-
-%\subsection{Uncoupled simulation}
-%We begin by demonstrating the LIISM model uncoupled to the ocean.
-For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide.
-Land points are arranged in a semi-circle, in the west of the domain, as shown by the black dots in Figure \ref{fig:Uncoupled_sim}.
-Three hundred ice elements are initialized with diameters uniformly sampled from the interval [0 40km], and positioned randomly at positions with $x \leq 300$km.
-These ice elements can be thought to represent interacting sea ice flows or icebergs.
-Three `tabular icebergs' are initialized by arranging ice elements in a staggered lattices with adjacent elements bonded together, as described in Section 2.4.
-The three tabular icebergs contain 25, 16 and 4 elements, respectively.
-Each of the elements that make up the tabular icebergs has a diameter of 40km.
-All elements have an initial thickness of 10m.
-%
-%The simulation is forced by an imposed westward ocean current of u=0.1m/s.
-Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
-The initial setup is shown in Figure \ref{fig:Uncoupled_sim}a.
-
-%\subsection{Coupled Ocean-Ice simulations}
-%\subsection{Description of idealized ice shelf cavity}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+As far as we know, all models of ice-shelf cavities to date have omitted ice-shelf breaking and iceberg detachment.
+This is because (i) there is much uncertainty of the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on a static Eularian grids, which do not lend themselves to modeling drifting icebergs.
+In contrast, existing {\it iceberg} models represent icebergs as Lagrangian particles, since this is a convenient way to model discrete objects traveling over large distances \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
+To date there has been no real effort to synthesize these two approaches (i.e.: to combine ice shelf and iceberg models).
+
+In this study we develop a new ice-shelf cavity model where the ice shelf is represented on a `Lagrangian grid'.
+In this model, the ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
+This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
+Figures \ref{fig:Spread_area} and \ref{fig:Temperature_section_Collapse}, which show a tabular iceberg drifting away an idealized ice shelf, demonstrate the enhanced capabilities of this Lagrangian model (see \citet{Stern2017} for more details).
+
+%This iceberg drifting simulation is described in a separate study \citep{Stern2017}.
+%Here, we instead focus comparing the Lagrangian model to existing Eularian model in a static ice shelf configuration. 
+However, before analyzing the improved capabilities of the Lagrangian ice-shelf model, it is necessary to thoroughly test and benchmark the Lagrangian model in a more familiar configuration. 
+To do this we compare the Lagrangian ice-shelf-cavity model to existing Eularian model in a static ice-shelf configuration. 
+For this comparison, we use the model configuration developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). 
+The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, and (ii) to prove that the Lagrangian model can replicate the behavior of an Eularian ice-shelf model when modeling static ice shelves.
+%In particular, we aim to show that for a static ice shelf, Lagrangian ice shelf model gives the same results as an Eularian model in the same configuration (using the same ocean model). 
+Demonstrating this is a prerequisite for moving beyond the capabilities of the Eularian model, and increases our confidence in more complex simulations involving calving icebergs. 
+%An analysis of an ice shelf cavity with a tabular iceberg drifting away from the from the ice shelf is provided in a separate study \citep{Stern2017}.
+
+%Results from this static ice shelf experiment are compared to results using an existing Eularian ice shelf coupled to the same ocean model.
+The strong agreement between these two models implies that the Lagrangian ice shelf has been implemented correctly.
+This is a good starting point for moving beyond the capabilities of the Eularian model.
+The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
+
+\section{Lagrangian model description}
+This section provides a brief description of the Lagrangian Tabular Iceberg Model (LTAM), which is used to construct the Lagrangian ice shelf used in this study.
+A detailed description of the LTAM, including many of the technical details involved in constructing the model, can be found in \citet{Stern2017}.
+
+\subsection{Lagrangian grid}
+The LTAM is a discrete element model (DEM) in that the objects of the model are Lagrangian elements.
+Each Lagrangian element represents a mass of ice which is floating in the ocean.
+The elements each have their own position, velocity, mass, and a set of dimensions, which can evolve in time.
+Each element moves according to its own momentum equation which is solved in the (Lagrangian) reference frame of the element.
+The elements are forced by oceanic, sea ice and atmospheric drag forces, as well as a force due to sea surface height gradients and the Coriolis force.
+As the elements drift, they decay according to melt parametrization.
+The elements can also be `bonded' together by numerical bonds, which hold the elements together and allow many elements to move together as a unit.
+By bonding many ice elements together, the LTAM model is able to form larger structures, such as tabular icebergs or (non-dynamic) ice shelves.
+
+When constructing ice shelves using the LTAM model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
+In this Lagrangian grid, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
+This is in contrast to the more traditional approach of modeling ice shelves on an Eularian grid, where the grid is fixed in time.
+The major advantage of modeling ice shelves using a Lagrangian grid is that the grid is not static, which means that we can simulate pieces of ice breaking away from the ice shelf to form icebergs that drift in the open ocean (Figures \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
+One consequence of using Lagrangian elements for the ice-shelf grid is all variables need to be interpolated from the `Lagrangian grid' onto the Eularian ocean grid in order to be passed to the ocean model.
+The details of this interpolation are discussed below.
+
+\subsection{Interaction with the ocean}
+Since the LTAM model uses a Lagrangian grid, all of the ice shelf information is stored with the elements.
+At every time step, this information has to be interpolated from the Lagrangian grid to (Eularian) ocean grid, so that it can be passed to the ocean model.
+The interpolation from the Lagrangian grid to the Eularian ocean grid is done by assuming that the elements have surface areas that are shaped as regular hexagons.
+Element's properties are `spread' from the Lagrangian grid to the Eularian grid by exactly calculating fraction of an elements surface area that is contained in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
+
+Five fields are `spread' from the Lagrangian to Eularian grids at each time step: mass, surface area, temperature flux, salinity flux and mass flux.
+Once these five fields are in hand, the LTAM mode interacts with the ocean model in exactly the same way the Eularian model does.
+As in Eularian ice-shelf models, these fields are passed to the ocean model and are used to:
+(i) apply a pressure to the ocean surface, 
+(ii) alter the upper-ocean boundary condition to reflect that the ocean is covered by ice,
+and (iii) apply salt, temperature and mass fluxes associated with ice-shelf melting and freezing.
+
+The ocean is sensitive to small changes to the ocean surface pressure, which can trigger barotropic ocean waves.
+This means that accurately interpolating fields from the Lagrangian to Eularian grids is the key to making the Lagrangian ice-shelf model behave like the Eularian ice-shelf model for using static ice-shelf simulations.
+Ocean mixed layer properties are passed from ocean model to the LTAM model, and are interpolated onto the elements using a bilinear interpolation.
+The model is less sensitive to the details of this interpolation.
+%In the next section we use an idealized setup to demonstrate that this is done correctly in the LTAM model.
+
+%Elements are initially arranged in regular staggered lattice so that the they are perfectly packed together
+%For example, consider a hexagonal element which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b). In this situation,r.
 
  \section{Experiment Setup}
-The introduction of Lagrangian elements, numerical bonds and interpolation schemes between the Eularian and Lagrangian grids (discussed in Section 2) means that we are now able to model ice-shelf cavities which undergo large calving events.
-We demonstrate this capability by performing numerical experiments with the LIISM model coupled to the MOM6 ocean model \citep{Hallberg2013}.
-%This section describes the experimental setup of these numerical experiments. The results are shown in Section 4.
-
-\subsection{MISOMIP configuration}
-In order for our (pre-calving) simulations to be easily comparable to previous models of ice-shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
-%For this experiment, we use the ice-shelf geometry, ocean topography and various parameters used in the Marine Ice Ocean Modeling Intercomparion project (MISOMIP) [reference]. 
+% the proof of concept for
+The LTAM model is used to simulate the flow within an idealized ice-shelf cavity.
+The simulations are repeated using an Eularian ice shelf with an identical configuration.
+The details of the experimental setup for both the Lagrangian and Eularian models are presented here.
+
+\subsection{Domain configuration}
+In order for our simulations to be easily comparable to previous models of ice-shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP) \citep{Asay-Davis2016}.
 The MISOMIP configuration was developed as a standardized configuration to allow for a comparison between various ocean-ice coupled models.
-The configuration consists of an idealized ice shelf in a rectangular domain.
-The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650km.
+The configuration consists of an idealized ice shelf in a rectangular domain $L_{x}=80$km long and $L_{y}=480$km wide.
+The ice shelf is grounded on the southern side of the domain with the ice-shelf front at y=650km.
 The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference.
@@
 
-The LIISM model is coupled to the MOM6 ocean model. 
-The ocean model is run in using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
-In particular, model layers bend underneath the ice shelf as they would in a sigma model, but collapse to zero thickness when they intersect with bottom topography, as they would in a z-level model.
-The coordinate system was achieve using ALE regridding-remapping scheme \citep{White2009}.
-The model used a horizontal resolution of 2km, and 72 vertical layers.
-All simulation were repeated using the ocean model is run layered mode (results were similar and are not presented here).
-%(select results are shown in the supplementary material). 
-Ocean parameters are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
-The simulation is initially at rest, with horizontally uniform initial ocean temperature  (Figure \ref{fig:static_solo_temp_temp_v}a) and salinity profiles that vary linearly between specified surface and bottom values.
-The initial surface temperature and salinity are  $T_{t}=-1.9^{\circ}$C and $S_{t}=33.8$ psu, respectively.
-The initial temperature and salinity at the depth $H_{ocean}$ are $T_{b}=1.0^{\circ}$C and $S_{b}=34.7$ psu.
+\subsection{Ocean Model}
+The Lagrangian and Eularian ice shelves are coupled to the MOM6 ocean model \citep{Hallberg2013}. 
+The ocean model is run in using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate, achieved using ALE regridding-remapping scheme \citep{White2009}.
+In this vertical coordinate, model layers bend underneath surface topography (i.e.: the ice shelf), as they would in a sigma coordinate model, and intersect the bottom topography, as they would in a z-coordinate model.
+The model has 72 vertical layers and has a horizontal resolution of $\Delta x= 2$ km.
+The numerical simulations were all repeated using an isopycnal coordinate (without ALE regrinding-remapping).
+The results were qualitatively similar to the ALE results.
+All results presented below are from the ALE simulations, unless specified otherwise.
+
+Ocean parameters are shown in Table 1 and are specified in the MISOMIP configuration \citep{Asay-Davis2016}.
+The simulation is initialized from rest, with horizontally uniform initial ocean temperature and salinity profiles which vary linearly between specified surface and bottom values: $T_{top}=-1.9^{\circ}$C, $T_{bottom}=1.0^{\circ}$C, $S_{top}=33.8$ psu, $S_{bottom}=34.7$.
 The maximum ocean depth is $H_{ocean}=720$ m.
 A sponge layer is used on the northern boundary, which relaxes back to the initial temperature and salinity with a relaxation time scale of $T_{sponge}=0.1$ days.
-Melting is set to zero for ocean cells where the ocean column thickness is less than 10m to avoid using more energy to melt ice than is present in the water column.
-
-%\textbf{Initializing Lagrangian elements:}\\
-\subsection{Initializing Lagrangian elements:}
-Ice elements in the LIISM model are set to be hexagonal and are arranged in a regular staggered lattice (as discussed in Section 2.3).
-The sides of the gridded hexagons are initialized with length $S=0.98$ km.
-Recall that the element size must be smaller than the ocean grid spacing (i.e.: $2S<\Delta x$ = 2 km).
+Melting is set to zero for ocean cells where the ocean column thickness is less than 10m.
+
+\subsection{Lagrangian ice-shelf simulations:}
+%\subsection{Lagrangian and Eularian ice shelf simulations:}
+The Lagrangian ice shelf is created using 10882 Lagrangian hexagonal elements with sides of length $S=0.98$ km .
+The positions of the hexagonal elements are initialized by packing them together in a space-filling staggered lattice.
 Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
-The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.3.
-
-Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
+The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.2.
+
+%Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
 Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
@@
 The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
-
-\subsection{Numerical experiment}
-\begin{enumerate}
-\item
-\textbf{Static ice-shelf experiment:}\\
-%\subsection{Static ice shelf experiment}
-In the first experiment, we use a static ice shelf where the velocity of all ice elements is set to zero.
-In this experiment, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as in the Ocean0 experiement in the MISOMIP \citep{Asay-Davis2016}).
-In this setup, ice-shelf melting generates a temperature and salinity flux into the ocean, but does not change the thickness of the ice shelf.
+%
+\subsection{Eularian ice-shelf simulations:}
+The Eularian ice-shelf simulation is performed using an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, which is an optional module of the the MOM6 ocean model.
+The ice shelf is initialized on the same grid as the ocean model with a horizontal resolution of $\Delta x = 2$ km.
+The ice-shelf thickness field is using the same ice-shelf draft used for the Lagrangian model (Figure \ref{fig:ISOMIP_mass_and_topog}b).
+
+%\subsection{Eularian ice shelf simulation:}
+\subsection{ice-shelf motion and decay}
+The melt rates in both the Lagrangian and Eularian ice-shelf simulations are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}.
+In both experiments the ice shelf is held stationary.
+In the Eularian code, this is achieved by setting the ice-shelf velocity to zero, while in Lagrangian ice shelf, the element velocities are set to zero.
+In both simulations, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
+In this setup, ice-shelves melting generate temperature and salinity fluxes into the ocean, but do not change the thickness of the ice shelf / ice elements.
 This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
-
-Results of the static ice-shelf experiment using the LISSM model are compared to the results from an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, run in an identical configuration (using the ice draft from Figure \ref{fig:ISOMIP_mass_and_topog}b).
-Results from the static ice-shelf experiment are analyzed after 5 years of model spinup.
-
-%Another set of experiments were performed using a static ice shelf which decays as it melts. The results over a 5 year period were fairly similar to the non-decaying shelf, and are not shown.
-
-% \subsection{Decaying ice shelf experiment}
-%In the second experiment, the LIISM ice shelf is allowed to decay as the ice melts.
-This setup provides a more challenging test of the ocean-ice coupling, as the ocean responds to a moving lateral boundary.
-For this experiment, we increase the temperature of initial temperature profile and the sponge layer by 4 degrees, to make the ice shelf decay more rapidly.
-
-\item
- \textbf{Tabular iceberg calving:}\\
-% \subsection{Tabular iceberg calving}
-Next, we preform a numerical experiment which demonstrates capabilities of the LIISM model that can not be performed by traditional Eularian ice-shelf models.
-In this experiments we break off a large piece of the ice shelf and allow it to drift into the ocean as a tabular iceberg.
-
-All ice elements initially within a 14.4 km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held are stationary.
-Ice elements less than 12 km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
-A ring of elements whose distance, $d$, from the ice front center obeys $12 \textrm{ km} \leq   d \leq14.4 \textrm{ km}$, are allowed to move freely, but have all their bonds removed.
-Elements in this half annulus represent fragments of the ice shelf which calve into small pieces during a large calving event.
-Breaking the bonds of these surrounding elements allows the tabular iceberg to move away from the ice-shelf cavity more easily.
-
-A wind stress $\vec{\tau} = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to drive the tabular iceberg away from the ice-shelf cavity.
-Perturbation experiments were performed using other wind stress values.
-
-The tabular iceberg calving experiment is initialized using the ocean state from the static ice-shelf experiment after 5 years of simulation time.
-In tabular iceberg calving experiment, the ice shelf and icebergs are allowed to decay as they melt. 
-\end{enumerate}
-
-%\begin{enumerate}
-%\item
-%\textbf{Tabular iceberg with fixed velocity}:\\
-%In this simulation, the velocity of the non-stationary elements is fixed to u=0m/s, v=0.01m/s.
-This simulation allows us to study the response of the ocean to disturbance caused by a tabular iceberg moving through the water (with an fixed velocity).
-This simulation is not fully coupled since the velocity of the elements is prescribed.
-%\item
-%\textbf{Tabular iceberg with bonded elements}:\\
- %All non-stationary ice elements are bonded together by the numerical bonds.
-This experiments is fully-coupled in that the ice elements are driven the ocean, and the pressure exerted by the ice elements drives ocean flow.
-In order to make the iceberg drift away from the ice shelf, we imposed a zonal wind stress of $\tau_{x}$ = 0.1 $\frac{N}{m^{2}}$.
-.
-%\item
-%\textbf{Tabular iceberg with unbonded elements}:\\
-%This simulation is identical to the bonded elements simulation, except that all the numerical bonds are broken, so that the elements are free to move away from one another.
-%\end{enumerate}
-
-%\section{Results}
-%\subsection{Uncoupled simulation}
-%Figure \ref{fig:Uncoupled_sim} shows the results of the uncoupled simulation described in subsection 3.1.
-The figure shows snapshots of the positions of ice elements at after t=0, 300, 600 and 900 days.
-During the simulation, the ice elements drift westward with the prescribed ocean current until the reach the land boundary on the western side of the domain.
-Once the elements reach the western coastline, the elements become trapped against the coast and can not move further.
-When new elements approach the elements at the coast, they interact with the elements already at the coast, and are repulsed.
-The elements eventually settle in an equilibrium position where there is minimal overlap between elements.
-%
-%The tabular icebergs also drift westward towards the coast.
-The elements within the tabular icebergs which arrive first at the coastline  bump up against the coastline (or elements already at the coast).
-This interaction causes the tabular icebergs to rotate, and change directions.
-The tabular icebergs continue to drift and interact with other elements until they too settle into an equilibrium position and come to rest.
-The rotation of the tabular icebergs confirms the this solid body rotation can me modeled using elements and bonds, without having to include an equation for the angular momentum of the elements (as discussed in \citet{Jakobsen2001}).
-%
-%Comparing the northern and southern halves of the simulation shows how large tabular icebergs can interfere with the trajectories and movement of smaller icebergs (or sea ice flows).
-These types of interactions will likely play an important role in ice choked fjords [reference] and Antarctic coastal regions [reference].
+The models are spun up for 5 years, and results are considered after the spinup period.
 
 \section{Results}
-
-%\subsection{Mass spreading}
-%When the model is run, the average ice draft in an ocean grid cell, is calculated from the total mass of ice elements in that grid cell by assuming that the ice elements are in hydrostatic balance.
-The total mass is found by summing up over all ice elements located in that grid cell, while allowing elements to spread their mass across neighboring grid cells (as discussed in Section 2.3).
-Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft of the ice shelf above the ice shelf cavity in the coupled static ice shelf simulation using this interpolation method, while Figure \ref{fig:ISOMIP_mass_and_topog}c shows the draft which is calculated without spreading an elements mass across neighboring cells (i.e.: treating elements as point masses).
-When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
-The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
-In simulations without mass spreading, irregularities in ice draft cause irregularities in the ocean surface pressure, which cause spurious motion in the ocean (not shown).
-This is much reduced or absent when mass spreading is used.
-
-%\subsection{Coupled simulation}
-\subsection{Static ice-shelf experiment}
-The LIISM results from the static ice-shelf experiment fit well within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
+\subsection{Results from the Lagrangian ice-shelf simulation}
+The results from the Lagrangian ice-shelf simulation fit within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
 The initial water temperatures inside the domain are warmer than the in-situ freezing point, and cause melting at the ice-shelf base.
@@
 As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_temp_v}b).
-This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water which provides the thermal energy required for continuous ice-shelf melt.
+This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water, which provides the thermal energy required for continuous ice-shelf melt.
 
@@
 These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front.\\
-\\
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front.
+
 %\subsubsection{Comparison with Eularian ice shelf model}
-\textbf{Comparison of LIISM and Eularian ice-shelf model}\\
-The LIISM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
-To get a quantitative comparison, we compare the LIISM results to a simulation using an Eulerian ice-shelf model with an identical configuration.
-The results show that two simulations have very similar circulations (Figures \ref{fig:Bt_comparison}), melt rates and temperature/salinity profiles (see supplementary materials).
-The differences between the barotropic stream functions of the two simulations (for example) are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems [double check that this is correct].
+\subsection{Comparison of Lagrangian and Eularian ice-shelf models}
+The LTAM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
+To get a quantitative comparison, we compare the Lagrangian ice-shelf model results to a simulation using an Eulerian ice-shelf model with an identical configuration.
+The results show that two simulations are almost indistinguishable.
+This is the case both for simulations using the ALE-hybrid vertical coordinate system and the isopycnal vertical coordinate.
+The Lagrangian and Eularian models are have very similar circulations (Figures \ref{fig:Bt_comparison}), melt rates (Figures \ref{fig:Melt_comparison}) temperature/salinity profiles (Figures \ref{fig:Salt_comparison}).
+The differences between the barotropic stream functions of the two simulations(for example), are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems (Figures \ref{fig:Bt_comparison} and \ref{fig:layer_Bt_comparison}).
 
 The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
-Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes based on the three equation model, and (iii) alter the upper ocean boundary condition below the ice shelf.
-The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LIISM model, and that the LIISM is able to model sub-ice-shelf cavities as well as the Eularian model does.
+Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes to the ocean, and (iii) alter the upper ocean boundary condition below the ice shelf.
+The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LTAM model, and that the LTAM is able to model sub-ice-shelf cavities as well as the Eularian model does.
 This is a good starting point for moving beyond the capabilities of the Eularian model.
 
-%Figures \ref{fig:Melt_comparison} show the time-averaged melt rates of both the Lagrangian and Eulerian ice shelf models, averaged over the first 5 years of the simulation.
-The melt rates of the Eulerian and Lagrangian models are very similar with slight difference showing up at the grounding line and ice front (Figure \ref{fig:Melt_comparison}).
-The slight difference at the grounding line are a result of the fact that elements in the LIISM model are smaller than a grid cell in length.
-This means that ice element near the grounding line may be ungrounded in the LIISM model, while the grid cell is considered grounded in the Eularian model.
-At the ice front, the Eularian model has a straight ice front, while the LIISM model has a staggered ice front, which is a result of the staggered hexagonal packing.
-
-%The small changes in melt at the grounding line and ice front drive slight changes to the circulation beneath the ice shelf, which in turn lead to small difference in the temperature and salinity profiles over time.
-This is seen by comparing the time-averaged ocean salinity profiles for the Lagrangian and Eularian ice shelves (Figure \ref{fig:Salt_comparison} ) and also  by comparing the the time-averaged barotropic stream function of the two simulations (see Figures \ref{fig:Bt_comparison}) and in the supplementary material).
-
-%\subsection{Decaying ice shelf experiment}
-%In the decaying ice shelf experiment, the ice shelf is allowed to decay as it melts.
-As the ice shelf melts, it decays and the pressure on the top layer of the ocean model decreases (Figure \ref{fig:Decaying_shelf}).
-The ice shelf decays most rapidly near to the grounding line.
-Grounding line migration due to melt does not take place since melting is set to zero where the ocean thickness is less that 10m.
-
-%As the ice shelf melts, there is a mass flux into the ocean.
-The integrated sea surface height north of the ice shelf does not change during the course of the simulation, since the extra mass flux into the ocean, is exactly offset by a decrease mass of the ice shelf, as expected.
-
-\subsection{Tabular iceberg calving experiment}
-The tabular iceberg calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf (see animations of  in the supplementary materials).
-After the numerical bonds are severed, the tabular iceberg and smaller ice fragments calve away from the ice shelf and begin to move.
-The tabular iceberg drifts to the northward east, driven by the wind and steered by the Coriolis force (Figure \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
-After the iceberg has moved away from the ice shelf, we observed a warming of the surface waters nearby ice front and iceberg edge (Figure \ref{fig:SST_Collapse}).
-This surface warming is caused by an upwelling of the warmer waters from beneath the ice shelf and iceberg.
-As the icebergs drifts away from the ice front, these warmer waters remain at the surface, mapping of the wake of the iceberg  (Figure \ref{fig:SST_Collapse}).
-The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color in the wake of tabular iceberg in the Southern Ocean \citep{Duprat2016}, suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface.
-
-The motion of the tabular iceberg disturbs the ocean surface, which drives ocean velocities through out the water column (Figure \ref{fig:Velocity_section_Collapse}).
-The elevated velocities around the tabular iceberg lead to increased vertical mixing in the vicinity of the iceberg, which alters the stratification of the water column (Figure \ref{fig:Temperature_section_Collapse}), heating the upper ocean.
-The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg (Figure \ref{fig:Collapse_solo_melt}).
-Large melt rates are observed at the newly calved ice-shelf front and on the rounded side of the iceberg (Figure \ref{fig:Collapse_solo_melt}a), where the iceberg calving has created steep ice cliffs.
-These sharp ice fronts allow for large ocean currents (Figure \ref{fig:Collapse_solo_melt}c), which drive the elevated melt rates.
-These elevated melt rates act to smooth out the ice front over time, making the ice cliff less steep.
-While this is likely a real phenomena that could be observed in nature, we should be wary of the modeled velocities at the ice cliffs, since large changes in ice-shelf thicknesses are often associated with numerical pressure gradient errors which can drive spurious motion.
-
-As mentioned above, the direction (and speed) of the iceberg drift is largely determined by the wind speed and direction.
-Perturbation experiments using different wind stresses showed that for sufficiently large winds, the iceberg drifts to the north east when the zonal component of the wind stresses is positive, and to the north west when the zonal component of the wind stress is negative.
-For a purely zonal wind stress with $\tau_{x} \leq 0.01 \frac{\textrm{N}}{\textrm{m}^{2}}$, the iceberg does not move away from the ice shelf.
-When the wind is purely offshore ($\tau_{x} = 0.0 \frac{\textrm{N}}{\textrm{m}^{2}}$), a meridional wind stress $\tau_{y} \geq 0.05 \frac{\textrm{N}}{\textrm{m}^{2}}$ is needed to move the tabular iceberg away from the ice shelf.
-While this result is partly an artifact of the artificial shape of the calving iceberg, it is also consistent with \citet{Bassis2013} who noted that calving is a two step process consisting of (i) ice-shelf breaking and (ii) iceberg detachment.
-The results here suggest that strong (cross-shore) winds may be required to drive large tabular icebergs away from their mother glaciers.
-
-Finally, we note that the numerical bonds in the LIISM model are needed in order to allow the tabular iceberg to retain its shape.
-Comparing the iceberg calving simulation with an identical simulation where all numerical bonds have been removed, shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
-In this case, the model behavior is more similar to an ice-shelf disintegration and does not create a cohesive tabular iceberg.
-
-%\subsubsection{Tabular iceberg with fixed velocity}
-%\textbf{Tabular iceberg with fixed velocity}\\
-%The fixed iceberg velocity calving experiment demonstrates that the model is able to simulate a tabular iceberg being calved from an ice shelf.
-After the iceberg calves, it moves northwards away from the ice shelf with a prescribed velocity.
-After the iceberg has calved away from the ice shelf, we observed a warming of the surface waters near the near the ice front and iceberg edge.
-This surface warming is caused by an upwelling of the warmer waters from beneath the ice shelf and iceberg.
-As the icebergs drifts away from the ice front, these warmer waters remain in the wake of the iceberg (Figures \ref{fig:Calving_fixed_top}).
-The signature of upwelling water in the wake of a drifting tabular iceberg bears some similarity to satellite observations of streaks of increased ocean color near to tabular iceberg in the Southern Ocean [reference],  suggesting that the increased productivity around iceberg may be driven by upwelling water delivering nutrients to the surface.
-The motion of the iceberg also drives barotropic velocities through out the water column, which disturb the initial stratification of the water column (Figures \ref{fig:Calving_fixed_side}).
-
-%\subsubsection{Fully coupled tabular iceberg}
-%\textbf{Fully coupled tabular iceberg}\\
-%The necessity of bonds between ice elements is demonstrated by comparing two simulations where an iceberg calves, and is allowed to evolve freely with the flow.
-In the Bonded simulation, the elements in the calved iceberg are bonded together, while in the Unbonded simulation the all bonds between elements in the tabular iceberg are broken.
-
-%The motions of elements in the tabular iceberg in these two simulations are rather different. 
-%In the Bonded simulation, the ice element in the tabular iceberg remain close to one another, and the tabular iceberg retains its shape (Figure \ref{fig:Bond_vs_No_bond}a,c).
-The elements are forced by the melt-water-driven current at the ice front, which moves towards the north-west (see Figure \ref{fig:static_solo} in the supplementary material).
-This current, together with the Coriolis force, cause the iceberg to rotate before moving away from the ice shelf (Figure \ref{fig:Bond_vs_No_bond}a).
-
-%In the Unbonded simulation, the ice elements in tabular iceberg are not constrained to move together.
-Instead, the elements spread out and drift towards the north-west for the same reason discussed above.
-Since the ice elements are not closely, packed together, they apply a smaller pressure to the ocean surface, spread over a larger area (Figure \ref{fig:Bond_vs_No_bond}c).
-The type of behavior could be relevant in simulating ice shelf disintegrations, rather than tabular iceberg calving.
-
- \section{Discussion}
-In order to accurately project future sea level, it is likely that we will need to develop fully-coupled global general climate models (GCM's) with dynamic ice-shelf cavities which are able to melt, break and interact with the ocean in physically realistic ways.
-In the sections above, we have seen that constructing ice shelves out of Lagrangian elements is a potentially useful method for introducing breakable ice shelves and tabular icebergs into climate models.
-In this section we briefly discuss a few of the things which still need to be done in order to introduce this technology into next generation GCM's.
-
-One element which is missing from the LIISM ice shelf is that the ice shelf is not dynamic.
+\section{Conclusion}
+%In order to accurately project future sea level, it is likely that we will need to develop fully-coupled global general climate models (GCM's) with dynamic ice-shelf cavities which are able to melt, break and interact with the ocean in physically realistic ways.
+This will require us to create models of ice shelf cavities with capabilities that can not currently be simulated by the current generation of ice shelf models.
+
+This study presents a new Lagrangian framework for modeling sub-ice-shelf cavities.
+In this framework, the ice shelf is constructed out of many Lagrangian elements, which are bonded together by numerical bonds.
+The collection of Lagrangian elements can be thought of as being a Lagrangian grid, which stores the ice-shelf properties.
+Unlike Eularian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
+This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:Spread_area} and \ref{fig:Temperature_section_Collapse}).
+This capability is currently not possible using more traditional Eularian models \citep{Stern2017}.
+%
+%A consequence of using a Lagrangian ice shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eularian ocean grid in order to be passed to the ocean model.
+This is done by exactly calculation the fraction of each ice element that lies in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
+
+The present study focuses on using the Lagrangian ice shelf to model static ice shelves.
+The model is demonstrated by modeling the circulation beneath a (static) idealized ice shelf, which was developed as part of the MISOMIP inter-comparison project.
+The results from the Lagrangian ice-shelf model fit within our paradigm of understanding for circulation within ice-shelf cavities: buoyant meltwater that enters the ice-shelf cavity drives freshwater plumes at the ice-shelf base, which drives the circulation within the cavity.
+The circulation, melt rates and ocean hydrography achieved using the Lagrangian ice shelf compare well with other simulations in the MISOMIP experiments.
+
+A direct comparison comparison between one Lagrangian and Eularian ice-shelf models showed that the results are extremely similar, and differences between the Lagrangian and Eularian ice shelves models (resulting from interpolation errors) are much smaller than the differences observed when changing the ocean vertical coordinate system (for example).
+Achieving similarity between when using a Lagrangian and Eularian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
+
+%\subsection{Future developments}
+%Having created a Lagrangian ice shelf which can be used to model ice shelf cavities, a natural next step to try to introduce this technology into a general circulation model (GCM).
+However, before this can be done, a number of challenges need to be overcome.
+% 
+%One element which is missing from the LTAM ice shelf is that the ice shelf is not dynamic.
 Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice-shelf geometry to change over time.
@@
 A challenge will be to develop models with similar ice dynamics in a Lagrangian framework.
-This can perhaps be achieved using smooth particle hydrodynamics (SPH) methods, which allow partial differential equations to be solved on a Lagrangian gird \citep{Liu2010, Pan2013}.
+This can perhaps be achieved using smooth particle hydrodynamics (SPH) methods, which allow partial differential equations to be solved on a Lagrangian grid \citep{Liu2010, Pan2013}.
 However, it is presently unclear how one would evolve the numerical bonds over time, so the bonds could still be used to hold the ice shelf and tabular icebergs together.
 This may involve performing a regridding of the ice element or a regridding of the numerical bonds after severa time steps, or perhaps allowing the numerical bonds to break and form in a dynamic way.
-
-The other major innovation which will need to be introduced is a method for breaking numerical bonds.
+%
+%The other major innovation which will need to be introduced is a method for breaking numerical bonds.
 This is essentially equivalent to determining an ice-shelf calving law, and is a famously difficult problem.
@@
 The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eularian ice-shelf studies \citep{Pralong2005, Borstad2012}.
-
-In addition to these two problems, more work needs to be done to determine the interaction between tabular icebergs and sea ice, as the presence of sea ice can arrest the motion of tabular icebergs and the presence of icebergs likely affects sea ice formation and dynamics.
+%
+%In addition to these two problems, more work needs to be done to determine the interaction between tabular icebergs and sea ice, as the presence of sea ice can arrest the motion of tabular icebergs and the presence of icebergs likely affects sea ice formation and dynamics.
 A possible path towards this is to model sea ice using a Lagrangian grid \citep{Hopkins1996, Li2014}, and to treat sea ice - iceberg interactions in the same way that iceberg - iceberg interactions are treated in this study.
-A number of preliminary experiments have been run using the LIISM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
+A number of preliminary experiments have been run using the LTAM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
 % Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
 These will need to be considered in order to model the primary productivity around tabular icebergs.
-
-Finally, there are a number of other open questions associated with introducing giant tabular icebergs into climate models: (i) how to correctly link tabular icebergs' melt water fluxes to ocean biology, (ii) how to deal with giant calving events in small ensemble simulations where one calving event can skew the ensemble statistics, (iii) how to introduce tabular icebergs into models which do not use a fully dynamic ice sheet, and (iv) how to model the breakup and fracture of freely-floating tabular icebergs.
+%
+%Finally, there are a number of other open questions associated with introducing giant tabular icebergs into climate models: (i) how to correctly link tabular icebergs' melt water fluxes to ocean biology, (ii) how to deal with giant calving events in small ensemble simulations where one calving event can skew the ensemble statistics, (iii) how to introduce tabular icebergs into models which do not use a fully dynamic ice sheet, and (iv) how to model the breakup and fracture of freely-floating tabular icebergs.
 These and other questions will need to be answered in order to achieve physically realistic tabular icebergs and ice shelves in GCM's.
@@
 % in order to represent large breakable ice shelves and icebergs
-
-%How do we grow icebergs?
-
-\section{Appendix A}
-\subsection{Environmental forces on ice elements}
-The non-interactive forces on an ice element are as described in \citep{Martin2010}, and are repeated here for completeness. 
-The forces on an element due to air (a), ocean (o) and sea ice (si) drag are given by
-\begin{equation}
-(\vec{F}_{a}) = \rho_{a} (0.5 c_{a,v} W F + c_{a,h} L W) | \vec{u}_{a} - \vec{u}|(\vec{u}_{a} - \vec{u}),
-\end{equation}
-\begin{equation}
-(\vec{F}_{o}) = \rho_{o} (0.5 c_{o,v} W (D-T_{si})F + c_{o,h} L W) | \vec{u}_{o} - \vec{u}|(\vec{u}_{o} - \vec{u}),
-\label{eq:ocean_drag_eq}
-\end{equation}
-\begin{equation}
-(\vec{F}_{si}) = \rho_{si} (0.5 c_{si,v} W T_{si}F + c_{si,h} L W) | \vec{u}_{si} - \vec{u}|(\vec{u}_{si} - \vec{u}).
-\end{equation}
-Here $\rho_{a}$, $\rho_{o}$, $\rho_{si}$, are the density of air, ocean and sea ice, respectively.
-$c_{a,v}$, $c_{o,v}$ and $c_{si,v}$ are the vertical drag coefficients with air, ocean and sea ice, while $c_{a,h}$, $c_{o,h}$ and $c_{si,h}$ are the respective horizontal drag coefficients.
-$\vec{u}_{a}$, $\vec{u}_{o}$, $\vec{u}_{si}$, are the velocities air, ocean and sea ice, respectively.
-L, W, T, F and D are the length, width, thickness, freeboard and draft of the ice element.
-The element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$, where $\rho$ is the ice element density.
-
-The  wave radiation force $(\vec{F}_{R})$ is given by
-\begin{equation}
-\vec{F}_{R} = \frac{1}{2}\rho_{o} c_{r} g a \textrm{ min}(a,F)  \textrm{ } 2\frac{WL}{W+L} \frac{\vec{v}_{a}}{|\vec{v}_{a} |}
-\end{equation}
-where g is the acceleration due to gravity, a is the wave amplitude empirically related to the wind speed by  $a=0.010125|\vec{v}_{a} -  \vec{v}_{o}| $, and $c_{wd}$ is the wave drag coefficient defined as
-\begin{equation}
-c_{wd}=0.06 \textrm{ min} \Bigg( \textrm{ max} \Bigg[0,\frac{L-L_{c}}{L_{t}-L_{c} } \Bigg]  , 1    \Bigg), 
-\end{equation}
-where $L_{w}=0.32|\vec{v}_{a} -  \vec{v}_{o}|^{2}$ is an empirical wave length, $L_{c}=0.125 L_{w}$ is the cutoff length, and  $L_{t}=0.25 L_{w}$ is the upper limit.
-
-The pressure gradient force is approximated as a force due to sea surface slope and given by
-\begin{equation}
-\vec{F}_{SS} = -M g \vec{\nabla} \eta
-   \end{equation}
-where $\eta$ is the sea surface height.
-
-\subsection{Melt rate parametrization}
-As discussed in Section 2.5, unbounded ice elements in the LIISM model decay according to parameterizations for iceberg decay typically used in iceberg drift models \citep{Martin2010}, while ice elements within larger ice structures have only a basal melt given by the three equation model \citep{Holland1999} .
-
-For unbonded ice elements, the element thickness decays due to basal melt at a rate $M_{b}$, while the length and width of the elements decay as a result of melt due to wave erosion, $M_{e}$, and melt due to buoyant convection, $M_{v}$.
-Following \citet{Martin2010}, the basal melt rate, wave erosion melt rate, and buoyant convection melt rate are parameterized by
-\begin{equation}
-M_{b} = 0.58 | \vec{v} - \vec{v}_{0}|^{0.8} \frac{\tilde{T}_{0} - \tilde{T}}{L^{0.2}}
-\end{equation}
-\begin{equation}
-M_{e} = \frac{1}{12} S_{s} \Bigg(  1 + \cos{[\pi A_{i}^{3}]}  \Bigg) \Bigg( \tilde{T}_{0} +2 \Bigg ),
-\end{equation}
-\begin{equation}
-M_{v} =  \Bigg(7.62 \times 10^{-3}  \Bigg )   \tilde{T}_{0} + \Bigg( 1.29 \times 10^{-3} \Bigg)\tilde{T}_{0}^{2}.
-\end{equation}
-$\tilde{T}$ is the effective iceberg temperature and is set to $\tilde{T}=4^{\circ}$C, $\tilde{T}_{0}$ is the temperature at the top of the ocean,  $A_{i}$ is the sea ice area fraction, and $S_{s}$ is the sea state, which is given by the Beaufort scale
-\begin{equation}
-S_{s} =  \frac{2}{3}  | \vec{u}_{a} - \vec{u}_{o} |^{\frac{1}{2}}  +\frac{1}{10}   | \vec{u}_{a} -\vec{u}_{o} |
-\end{equation}
-All three melt rates are in units of meters per day.
-
-For elements inside larger structures, the melt due to wave erosion  and melt due to buoyant convection are set to zero, and the basal melt, $M_{s}$ is given by the standard three equation model \citep{Holland1999}.
-%\begin{equation}
-%M_{s} =\frac{ 1}{L_{ice} \rho_{ice} }    \rho_{o} c_{po}\gamma_{T}  \Bigg(  T_{o} -T_{f}(S_{o},p_{o})  \Bigg)
-%\end{equation}
-%where $T_{o}$, $S_{o}$, $p_{o}$ are the ocean mixed layer temperature, salinity and pressure.
-$T_{f}(S_{ml}, p_{ml})$ is the salinity and pressure dependent freezing point of sea water at salinity $S_{o}$ and pressure $p_{o}$.
-$\gamma_{T}$ is the turbulent transfer coefficient given by
-%\begin{equation}
-%\gamma_{T}=\frac{1}{\Gamma_{Turb} +\Gamma^{T}_{Molec}}
-%\end{equation}
-
-\section{Appendix B}
-\subsection{Modified Verlet Algorithm}
-The LIISM model uses a version velocity verlet time-stepping algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
-The traditional velocity verlet algorithm is commonly used in molecular dynamics, as it is simple to implement, second order accurate and computationally efficient \citep{Swope1982, Omelyan2002}.
-Here we modify the tradition scheme to allow for the drag forces to be modeled implicitly, which prevents large accelerations for element's whose mass approaches zero. 
-To do this, we modify the traditional verlet algorithm to include both an implicit and explicit acceleration, $a(t)=a_{exp}(t)+a_{imp}(t)$.
-The explicit acceleration, $a_{exp}(t)$ includes all forcing terms which depend only on the previous time step, while the implicit acceleration, $a_{imp}(t)$  includes forcing terms which depend on the current time step (in particular the drag and Coriolis forces).
-
-%1) $ x(t_{n+1}) = x(t_{n}) + u(t_{n}) \Delta t  + \frac{1}{2} \Delta t^{2} a(t_{n}) $.\\
-%2) Calculate $a(t_{n+1})$\\
-%3) $u(t_{n+1}) = u(t_{n}) + \frac{\Delta t}{2} \Bigg(a(t_{n}) + a(t_{n+1}) \Bigg)$\\
-%Note that in step 2, $a(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other quantites evaluated at time $t_{n}$.
-
-Using a time step of $\Delta t$ and the notation $t_{n+1}= t_{n} + (\Delta t)$, the modified velocity verlet scheme can be written as:\\
-1) $ x(t_{n+1}) = x(t_{n}) + u(t_{n}) \Delta t  + \frac{1}{2} \Delta t^{2} \Bigg(a_{exp}(t_{n}) + a_{imp}(t_{n} )\Bigg) $.\\
-2) Calculate $a_{exp}(t_{n+1})$ and  $a_{imp}(t_{n+1})$\\
-3) $u(t_{n+1}) = u(t_{n}) + \frac{\Delta t}{2} \Bigg(a_{exp}(t_{n}) + a_{exp}(t_{n+1}) \Bigg) +  (\Delta t) a_{imp}(t_{n+1})$\\
-This scheme reduces to the traditional velocity verlet when $a_{imp}$ is set to zero.
-Note that at step 2, $a_{exp}(t_{n+1})$ is an explicit function of  $x(t_{n+1})$ and other quantities evaluated at time $t_{n}$, while $a_{imp}(t_{n+1})$ additionally depends on $u(t_{n+1})$, and needs to be solved implicitly).
-For this reason, steps 2 and 3 need to be solved simultaneously, as described in the next subsection.
-
- In equation (1), the forces due to ocean drag, atmospheric drag and sea ice drag are treated implicitly.
-The force due to sea surface slope and wave radiation are treated explicitly.
-The Coriolis term is handled using Crank-Nicolson scheme so that half of the effect is implicit and half is explicit.
-The elastic part of the interactive forces is treated explicitly, while the interactive damping is handled semi-implicitly in that the drag force on element A by element B depends on the velocities of elements A and B evaluated at time $t_{n+1}$ and $t_{n}$, respectively.
-
- %A full description of how the scheme is implemented is provided below.
-
- \subsection{Solving for the velocity implicitly}
-Since this modified scheme contains some forcing terms which are handled implicitly, steps 2 and 3 need to be solved together.
-We demonstrate how this is done, using a simplified one-dimensional version of equation (1), neglecting the atmospheric drag, sea ice drag and Coriolis force, so that the only implicitly treated term is the ocean drag.
-We also define an explicit force $F_{exp}$, which accounts for all forces not proportional the element velocity.
-With these simplifications, the implicit and explicit accelerations are
- \begin{equation}
-a_{exp} =\frac{1}{M} ( \vec{F}_{exp} )
-\end{equation}
- \begin{equation}
-a_{imp} =\frac{1}{M} (F_{o})
-\end{equation}
-The ocean drag force at time $t_{n+1}$ is modeled (mostly) implicitly as 
-\begin{equation}
-\label{eq:Drag}
-F_{W}(t_{n+1}) = \tilde{c}_{o} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) -u(t_{n+1}) ),
-\end{equation}
-where $\tilde{c}_{o}$ is the effective drag coefficient, accounting for the dimensions of the ice element (see equation \ref{eq:ocean_drag_eq}).
-
-%The consequences of the drag not being fully implicit are discussed below. 
-Step 3 of the modified velocity verlet scheme can be rewritten by introducing an intermediate velocity $u^{*}$, which only depends on the velocity and acceleration at time $t_{n}$,
- \begin{equation}
- u^{*}(t_{n}) =  u(t_{n})  + \frac{1}{2} (\Delta t) a(t_{n}). 
- \end{equation}
-Using this, the updated velocity (Step 3) can be written 
- %\begin{equation}
- %x(t_{n+1}) = x(t_{n}) + v^{*}(t_{n}) \Delta t 
- % \end{equation}
- \begin{equation}
-u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2} a_{exp}(t_{n+1})+  (\Delta t) a_{imp}(t_{n+1}).
- \end{equation}
-
-Including the forcing terms into this equations gives
- \begin{equation}
-u(t_{n+1}) = u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}     \Bigg(  c_{w} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) -u(t_{n+1}) )   \Bigg)
- \end{equation}
-Solving for $u(t_{n+1})$ in terms of quantities which only depend on the previous time step gives
- \begin{equation}
-u(t_{n+1}) = \frac{u^{*}(t_{n}) + \frac{\Delta t}{2M} ( F_{exp} (t_{n+1})) +   \frac{\Delta t}{M}    \Bigg(  c_{w} |u_{o}(t_{n}) -u(t_{n}) | (u_{o}(t_{n}) )   \Bigg)}{  \Bigg( 1+  \frac{\Delta t}{M}       c_{w} |u_{o}(t_{n}) -u(t_{n}) |    \Bigg)}
- \end{equation}
-Once the $u(t_{n+1})$  has been found, it can be used to calculated the explicit and implicit accelerations, which are required for the next time step.
-
-Finally, we note that the the drag term (equation \ref{eq:Drag}) is not entirely implicit, since the element velocity inside the absolute value is evaluated at time $t_{n}$, rather than at time $t_{n+1}$.
-This is done so that we can solve for the updated velocity analytically.
-One consequence of this is that it gives rise to a small oscillation in the element velocity.
-This oscillation is addressed by using a predictive corrective scheme: once you have solved for a first guess of the velocity at time $t_{n+1}$, this estimate of the velocity is used to update the estimate of the drag force (i.e.: inside the absolute value signs).
-Using the updated drag, you can now repeat the process described above to find an improved estimate of the velocity.
-We found that two iterations were sufficient to remove the unwanted oscillation.
-
-The procedure described in this section is easily extended to include more forcing terms and two dimensions (where it involves inverting a $2 \times 2$ matrix).
-
-\section{Appendix C}
-\textbf{Connecting bonds across processor boundaries}\\
-Since the LIISM model can be parallelized across multiple processors, it often happens that two elements on different processes are bonded together.
-Keeping track of numerical bonds across processor boundaries requires a lot of book keeping.
-In this section we describe the how LIISM model avoids segmentation faults by severing and reconnecting bonds at the edge of a processor during halo updates.
-
-%When a bonded element moves off the edge of a processor, the bond needs to be broken (to avoid segmentation faults).
-Before the next time step, the code performs a `halo update', and a copy of the element is written to the halo of the original processor.
-After this, the bond which was broken at the previous time step, needs to be reconnected.
-This processes of severing and reconnecting bonds requires a lot of bookkeeping, some of which are described below.
-
-The basics of the bond bookkeeping work as follows:
-consider an element A and an element B that are bonded together.
-Each element has a copy of the bond (a piece of memory which describes the bond between the two elements), which is stored with the element.
-Let A-B be the bond stored by element A, and B-A be the bond stored by element B.
-Bond A-B contains a pointer which points to element B and bond B-A contains a pointer which points to element A.
-
-Consider a situation where element A and B are originally on Processor 1, and then element B moves to Processor 2.
-When this occurs, the memory assigned to element B on processor 1 is removed, and is allocated on Processor 2.
-This means that the pointer to element B in bond A-B (stored in element A on Processor 1) is no longer assigned.
-Similarly, the pointer to element A in bond B-A (stored in element B on Processor 2) is no longer assigned.
-Before the next time step, a halo update occurs, so that the there is a copy of element A in the halo of Processor 2 and a copy of element B in the halo of Processor 1.
-After the halo update, the bonds A-B and B-A have to be reconnected on both Processor 1 and 2.
-To aid in reconnecting the bonds, a copy of the grid cell number of element B is stored in the bond A-B and a copy of the grid cell number of element A is stored in the bond B-A.
-We refer to this as the `most recent address'.
-Before a bond is moved from one processor to another, the `most recent address' is updated, so that the bond can be reconnected later.
-To reconnect bond A-B on Processor 1 (for example), we find the most recent address of element B, and search through the list of elements in the grid cell corresponding to the most recent address of element B until element B is found.
-The pointer to element B in bond A-B is reassigned and the bond is said to be connected.
-
-Once all bonds are reconnected, a bond quality control is done where we loop through all bonds and check that they are working properly.
-To check that a bond is working properly is a four step process.
-For example, consider the bond A-B stored in element A on Processor 1.
-To check the quality of this bond, we use the following four steps:
-\begin{enumerate}
-\item Check that the pointer to element B is assigned on bond A-B (stored on element A).
-\item Check that the corresponding bond B-A exists on element B.
-\item Check that a pointer to element A exists in this bond B-A.
-\item Check that the element A which is being pointed to is the same element A where you started.
-\end{enumerate}
-All four of these tests must pass in order to make sure that the memory is correctly assigned.
-A useful tool in this process is that each element is assigned a unique number so that elements are easily identified.
-
-\clearpage
-
-\section{Possibly add}
-\subsection{Orientation}
-Possibly add a section where we spread mass using the orientation of the icebergs.
 
@@
 
+\bibitem[Stern et al (2017)]{Stern2017}
+Stern, A. A., A. Adcroft, O. Sergienko, G. Marques, R. Hallberg (2017), Modeling tabular icebergs coupled to an ocean model. {\it Ocean Modeling}
+
 \bibitem[Swope et al (1982)]{Swope1982}
@@
  \end{article} 
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Diagrams/Interactive forces.pdf}
-%\caption{ {Schematic of interactive forces}}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:Interactive_forces}
-%\end{figure}
- %\clearpage
+\section{New Figure ideas:}
+1) Combine Figure 1 and Figure 2 into a new figure (so that this paper uses different figures to the tabular iceberg paper)\\
+\\
+2) Figure showing the layout of hexagons, which is different to the tabular iceberg paper - perhaps have hexagons directly over ice shelf draft?\\
+\\
+3) Combine the barotropic stream function figure for layered into one figure.
+
+\section{Things to think about:}
+1) The dynamics of the ice elements are not related to ice shelf dynamics. This needs to be explained somehow/somewhere.\\
+
+ \clearpage
 
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Regular_towards_coast}
-\caption{ {Results of an ice-only LIISM simulation with no bonds between ice elements.
-Ice elements are initialized throughout the domain, as shown in panel (a).
-The elements are forced by an imposed westward ocean current of u=0.1m/s (no ocean model is used).
-Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
-The figure shows snapshots of ice element positions at time (a) t=0, (b) 200, (c) 400, (d) 600 days.
-The size of the dots shows the surface area (and interaction diameter) of each ice element.
-Land points are shown by black circles.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
+\caption{ {Snapshots of the fraction of ice cover in the LTAM tabular iceberg calving simulation.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The dashed line in panel (c) shows the location of the vertical transects shown in Figure \ref{fig:Temperature_section_Collapse}}.}
 \end{center}
-%FIgure created by \end{center}
-\label{fig:Regular_Uncoupled_sim}
+\label{fig:Spread_area}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Tabular_and_regular_towards_coast_manual}
-\caption{ {Results of an ice-only LIISM simulation using bonds between elements.
-Ice elements are initialized throughout the domain, as shown in panel (a).
-Three tabular icebergs are included, with 25, 16 and 4 elements respectively.
-The elements are forced by an imposed westward ocean current of u=0.1m/s (no ocean model is used).
-Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
-The figure shows snapshots of ice element positions at time (a) t=0, (b) 300, (c) 600, (d) 900 days.
-The size of the dots shows the surface area (and interaction diameter) of each ice element.
-Bonds between ice elements are plotted in magenta.
-Land points are shown by black circles.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
+\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LTAM tabular iceberg calving experiment.
+Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
+The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:Spread_area}c.}}
 \end{center}
-%FIgure created by \end{center}
-\label{fig:Uncoupled_sim}
-\end{figure}
- \clearpage
-
-%We begin by demonstrating the LIISM model uncoupled to the ocean.
-For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide.
-Land points are arranged in a semi-circle, in the west of the domain, as shown by the black dots in Figure \ref{fig:Uncoupled_sim}.
-Three hundred ice elements are initialized with diameters uniformly sampled from the interval [0 40km], and positioned randomly at positions with $x \leq 300$km.
-These ice elements can be thought to represent interacting sea ice flows or icebergs.
-Three `tabular icebergs' are initialized by arranging ice elements in a staggered lattices with adjacent elements bonded together, as described in Section 2.4.
-The three tabular icebergs contain 25, 16 and 4 elements, respectively.
-Each of the elements that make up the tabular icebergs has a diameter of 40km.
-All elements have an initial thickness of 10m.
-%
-%The simulation is forced by an imposed westward ocean current of u=0.1m/s.
-Forces due to sea surface slope, atmospheric drag, Coriolis and sea ice drag are set to zero.
-The initial setup is shown in Figure \ref{fig:Uncoupled_sim}a.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
-\caption{ {(a) Hexagonal elements are initialized in a staggered lattice as shown.
-Adjacent elements are bonded together.
-The centers of bonded elements are plotted in pink.
-The element bonds form equilateral triangles which give the larger structure rigidity.
-The black circles shows to the interactive length scales used in element interactions.
-(b) Intersection of a hexagonal element and an ocean grid.
-The colors indicate the fraction of the hexagon that lies in each grid cell.
-These fractions are used as weights to spread LIISM properties to the ocean grid (see text for more details).}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:Hex_intersections}
+\label{fig:Temperature_section_Collapse}
 \end{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_spread_mass_mass.png}
-\caption{ {(a) Ocean bottom topography in MISOMIP configuration.
-(b) ice-shelf draft used in static shelf experiment.
-The ice draft is calculated from the ice mass in an ocean grid cell, which is found by spreading ice mass across ocean cells accounting for the size of each element (as explained in Section 2.3).
-(c) Same as in panel (b), except that the interpolation does not account for iceberg size, and instead treats elements as point masses.}}
+\caption{ {(a) Ocean bottom topography and (b) ice-shelf draft used to initialized the tabular iceberg calving simulation.
+The ice draft is calculated from the total mass in an ocean grid cell after the mass-spreading interpolation has been applied (as explained in Section 2.2).
+(c) Initial ice draft that would be calculated if the mass-spreading interpolation were not used (i.e.: elements treated as point masses).}}
 \end{center}
-%FIgure created by \end{center}
 \label{fig:ISOMIP_mass_and_topog}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:static_solo_temp_temp_v}
@@
 \end{center}
-%FIgure created by \end{center}
 \label{fig:static_solo_melt}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse}} and \ref{fig:Velocity_section_Collapse}.}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_melt.png}
+\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian Ice shelf model melt fields.}}
 \end{center}
-%FIgure created by \end{center}
-\label{fig:Spread_area}
+\label{fig:Melt_comparison}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The position of the vertical transects is shown by the dashed lines in Figure \ref{ig:Spread_area}c.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_salt_layers.png}
+\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model salinity fields.}}
 \end{center}
-%FIgure created by \end{center}
-\label{fig:Temperature_section_Collapse}
+\label{fig:Salt_comparison}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp.png}
-\caption{ {Snapshots of the sea surface temperature in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-Regions with ice area fraction = 1 area plotted in white.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
+\caption{ {Layer: Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model barotropic stream function}}
 \end{center}
-%FIgure created by \end{center}
-\label{fig:SST_Collapse}
+\label{fig:layer_Bt_comparison}
 \end{figure}
  \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LIISM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The position of the transects is shown by the dashed line in Figure \ref{fig:Spread_area}c.}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:Velocity_section_Collapse}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg_calved.png}
-\caption{ {Results of the tabular iceberg calving simulation 30 days after the iceberg calves.
-The three panels show snapshots of the (a) melt rate, (b) top-of-ocean temperature and (c) $u^{*}$ at the base of the ice shelf.
-Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:Collapse_solo_melt}
-\end{figure}
- \clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/melting_shelf_temp_layers.png}
-%\caption{ {Temperature section at $y=\frac{L_{y}}{2}$ for the decaying ice shelf simulation (using the LIISM ice shelf) at time (a) t=0, (b) t=100(?), (c) t=200 days.
-As the ice shelf melts, it decays and the pressure at the ocean surface decreases.
-}}
-%\end{center}
-%FIgure created by \end{center}
-%\label{fig:Decaying_shelf}
-%\end{figure}
-
-%\clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_temp_layers.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/drift_bond_salt_layers.png}
-\caption{ {Results from the tabular iceberg calving experiment with and without iceberg bonds.
-The top row shows the fractional ice cover for the simulations (a) with and (b) without numerical bonds.
-The bottom row shows the corresponding vertical temperature section at $x=58 $km for the simulation (c) with and (d) without bonds.
-The location of the vertical transects in panels (c) and (d) are shown by the dashed lines in panels (a) and (b), respectively.
-All snapshots are taken at time t = 30 days.
-The simulations uses wind stress $\vec{\tau}=< 0.0, 0.05 >.$}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:Bond_vs_No_bond}
-\end{figure}
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_salt_layers.png}
-\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model salinity fields.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Salt_comparison}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_melt.png}
-\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian Ice shelf model melt fields.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Melt_comparison}
-\end{figure}
- \clearpage
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_vo_uo_sst.png}
-%\caption{ {Results of the static ice shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) meridional velocity, (b) zonal velocity and (c) ocean temperature in the top layer of the simulation (at the surface or directly below the ice shelf).}}
-%\end{center}
-%\label{fig:static_solo}
-%\end{figure} 
- %\clearpage
-
- \begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp_layers}
-\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-%FIgure created by \end{center}
-\end{center}
-%\label{fig:Calving_fixed_side}
-\end{figure}
-  \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_after_melt_fixed_01_temp}
-\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Calving_fixed_top}
-\end{figure}
- \clearpage
-
- \section{Layer versions}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp_layers}
-\caption{ {Layer: Temperature section at $y=\frac{L_{y}}{2}$ for the tabular iceberg calving with fixed velocity simulation (using the LIISM ice shelf) at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-%FIgure created by \end{center}
-\end{center}
-%\label{fig:Calving_fixed_side}
-\end{figure}
-  \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_after_melt_fixed_01_temp}
-\caption{ {Layer: Sea surface temperature for the tabular iceberg calving with fixed velocity simulation at time (a) t=15, (b) t=30, and (c) t=60 days.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Calving_fixed_top}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_temp_temp_v.png}
-\caption{ {Layered: Results of the static ice-shelf experiment using the LIISM model.
-Panels show snapshots of cross sections of the (a) temperature field after 1 time step, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity after 5 years.}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:static_solo_temp_temp_v}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Layer: Results of the static ice-shelf experiment using the LIISM model.
-The three panels show 5 year time average of the (a) melt rate, (b) ocean surface temperature and (c) $u^{*}$  in the top layer of the simulation (at the surface or directly below the ice shelf).}}
-\end{center}
-%FIgure created by \end{center}
-\label{fig:}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
-\caption{ {Layer: Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model barotropic stream function}}
-\end{center}
-%FIgure created by \end{center}
-%\label{fig:Bt_comparison}
-\end{figure}
- \clearpage
-
  \end{document}

### 2017-02-24 Icebergs_only.tex
Addressed some of Alistairs paper concerns. Not all done yet

@@
 The calving of giant icebergs from the Antarctic ice shelves accounts for approximately half of Antarctic ice-shelf decay.
-After calving these tabular icebergs drift across large distances, altering regional ocean circulation, bottom-water formation, sea-ice production and rates biological primary productivity in the icebergs' vicinity.
-However, despite their importance, the current generation of numerical models is unable to represent giant tabular icebergs a physically realistic way.
-In this study we develop novel framework to model giant tabular icebergs submerged in the ocean.
+After calving, these tabular icebergs drift across large distances, altering regional ocean circulation, bottom-water formation, sea-ice production and biological primary productivity in the icebergs' vicinity.
+However, despite their importance, the current generation of numerical models is unable to represent giant tabular icebergs in a physically realistic way.
+In this study we develop a novel framework to model giant tabular icebergs submerged in the ocean.
 In this framework, tabular icebergs are constructed out of Lagrangian elements that drift in the ocean, and are held together by numerical bonds.
-By breaking these bonds, a tabular iceberg can be made to split into smaller pieces, or to break away from an ice shelf (also constructed from Lagrangian elements).
-This paper provides a description of the Lagrangian tabular-iceberg model and discusses a number of the technical elements involved its development. 
+By breaking these bonds, a tabular iceberg can be made to split into smaller pieces, or to break away from an ice shelf.
+We describe the Lagrangian tabular-iceberg model and discuss a number of the technical elements involved in its development. 
 We demonstrate the capabilities of the model by modeling a tabular iceberg drifting away an idealized ice shelf.
@@
 
-After calving, icebergs slowly drift away from their mother glaciers, often becoming stuck in sea ice, or grounding along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}.
-Giant tabular icebergs extend deep into the water column, and have to potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
+After calving, icebergs slowly drift away from their source glaciers, often becoming stuck in sea ice, or grounding along the Antarctic coast \citep{Lichey2001, Dowdeswell2007}.
+Giant tabular icebergs extend deep into the water column, and have the potential to disrupt ocean circulation patterns for months or even years after calving \citep{Robinson2012, Stern2015}.
 The freshwater flux from iceberg melt impacts ocean hydrography around the iceberg, influencing sea-ice production and bottom-water formation \citep{Arrigo2002, Robinson2012, Nicholls2009}.
@@
 In recent years, there has been an increased interest in iceberg drift and decay.
-This surge of interest has been driven by (i) the need to understand polar freshwater cycles in order to create realistic climate forecasts and sea level projections \citep{Silva2006, Shepherd2007, Rignot2013}, (ii) the increased use of high-latitudes iceberg-filled waters for shipping lanes and offshore hydrocarbon exploration in the Arctic \citep{Pizzolato2014, Unger2014, Henderson2016}.
+This surge of interest has been driven by (i) the need to understand polar freshwater cycles in order to create realistic climate forecasts and sea level projections \citep{Silva2006, Shepherd2007, Rignot2013}; and (ii) the increased use of high-latitudes iceberg-filled waters for shipping lanes and offshore hydrocarbon exploration in the Arctic \citep{Pizzolato2014, Unger2014, Henderson2016}.
 The increased interest in icebergs has led to the development of numerical models of iceberg drift and decay \citep{Mountain1980, Bigg1997, Gladstone2001, Kubat2005}, some of which have been included in global General Circulation Models \citep{Martin2010, Marsh2015}.
 These iceberg drift models treat icebergs as Lagrangian point particles, which are advected by the flow, and melt according to certain parameterizations for icebergs melt.
-Since icebergs are treated as point particles, iceberg drift models are mostly suitable for modeling smaller icebergs drifting across large distances, and as such these models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
+Since icebergs are treated as point particles, iceberg drift models are mostly suitable for modeling icebergs smaller than an ocean grid cell.
+Consequently, these models have mostly been used to represent icebergs smaller than 3.5km on a global scale \citep{Jongma2009, Martin2010, Marsh2015}.
 
@@
 
-The goal of this study is to develop a new iceberg model where tabular icebergs are explicitly resolved in the ocean.
+The goal of this study is to develop a new iceberg model where tabular icebergs are explicitly resolved.
 In this model, icebergs are no longer treated as point particles that interact with the ocean at a single location, but rather icebergs are given structure, so that they interact with the ocean across multiple ocean grid cells and depress the ocean surface over a wide area.
-To do this, we create tabular icebergs out of many Lagrangian elements which are `bonded' together by numerical bonds.
-The numerical bonds hold the ice elements together and allow a collection elements to move as a unit.
+To do this, we create tabular icebergs out of many Lagrangian elements with finite extent which are `bonded' together by numerical bonds.
+The numerical bonds hold the ice elements together and allow a collection of elements to move as a unit.
 By manually breaking these bonds, we can simulate iceberg calving, allowing us to study the ocean response to giant iceberg detaching from an ice shelf (e.g.: Figure \ref{fig:Spread_area} and \ref{fig:SST_Collapse}) or the fracturing of a large iceberg into smaller pieces.
 
-The discrete element model (DEM) developed in this study is referred to at the Lagrangian Tabular Iceberg Model (LTAM). 
-%The LTAM model is coupled to the MOM6 numerical ocean model \citep{Hallberg2013}. 
-Section 2 gives a description of many of the key aspects of the LTAM.
+The discrete element model (DEM) developed in this study is referred to at the Lagrangian Tabular Iceberg Model (LTIM). 
+%The LTIM model is coupled to the MOM6 numerical ocean model \citep{Hallberg2013}. 
+Section 2 gives a description of many of the key aspects of the LTIM.
 Since this model is a new approach to modeling icebergs, we present many of the technical elements involved in constructing the model.
@@
 %, which can be used to model small icebergs, tabular icebergs, sea ice and ice shelf cavities
-%In this section we describe many key elements of the LTAM.  
-The LTAM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
+%In this section we describe many key elements of the LTIM.  
+The LTIM is a Lagrangian particle-based model (or DEM model) in that the objects of the model are Lagrangian elements.
 Each element represents a mass of ice that is floating in the ocean, and has a position, velocity, mass, and a set of dimensions, which can evolve in time.
 The motion of each element is determined by a momentum equation which is solved in the (Lagrangian) reference frame of the element.
-The elements are forced by oceanic and atmospheric forces, which are provided by the user, or are determined by coupling the LTAM to an ocean/atmosphere model.
+The elements are forced by oceanic and atmospheric forces, which are provided by the user, or are determined by coupling the LTIM to an ocean/atmosphere model.
 The elements also interact with one another and can be bonded together to form larger structures.
-The angular momentum of the elements is not modeled explicitly; instead rotational motion of larger structures emerge as a consequence of bond orientation.
-In different contexts, the LTAM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
-%In this latter case, the LTAM model can be categorized as a discrete element model (DEM). 
+The angular momentum of the elements is not modeled explicitly; instead rotational motion of larger structures emerge as a consequence of bond orientation and collective motion.
+In different contexts, the LTIM elements can be thought to represent individual icebergs, sea ice flows, or, when the elements are bonded together, they can represent larger structures such as tabular icebergs or ice shelves.
+%In this latter case, the LTIM model can be categorized as a discrete element model (DEM). 
 % in the sense that large structures are constructed from smaller independent Lagrangian elements.
 
-The LTAM model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}.
+The LTIM model is developed on the code base of an existing iceberg drift model \citep{Martin2010, Stern2016}.
 When run with the correct set of runtime flags, the model runs as a traditional iceberg drift model.
@@
 
-In addition to the environmental forces, the elements in the LTAM model experience interactive forces due to the presence of other elements.
+In addition to the environmental forces, the elements in the LTIM model experience interactive forces due to the presence of other elements.
 Two types of interactive forces are included between elements.
-The first force is repulsive force which is applied to elements to prevent them from moving too close to one another.
+The first force is a repulsive force which is applied to elements to prevent them from moving too close to one another.
 This repulsive force prevents icebergs from piling up on top of one another.
-The second interactive force is a force due to numerical `bonds', and is only applied if two elements are `bonded' together.
+The second interactive force is a force due to numerical `bonds', and is only applied if two elements are labelled as `bonded'.
 When two elements are bonded, each element feels an attractive force that prevents the elements from moving too far apart from one another.
@@
 where $\vec{r}_{ij}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between the position of element i and j, $\kappa_{e}$ is the spring constant, and $T_{i,j}$ is the minimum of the thickness of elements i, j.
-We choose $(\vec{F_{b}})_{ij}$ proportional to $T_{i,j}$ (the minimum thickness of elements i and j) so the formulation of interactive forces has the desired property that it obeys Newton's 3rd Law (i.e.: $(\vec{F}_{IA})_{ij}=-(\vec{F}_{IA})_{ji}$).
+The interactive forces obey Newton's 3rd Law (i.e.: $(\vec{F}_{IA})_{ij}=-(\vec{F}_{IA})_{ji}$).
 %This is in contrast to some other DEM models in the literature (e.g. \citet{Li2014}). 
-The minimum thickness is preferred to the average thickness, since this means that for two bonded elements a fixed distance apart, the acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero.
+The minimum thickness, $T_{i,j}$, is preferred to the average thickness, since this means that for two bonded elements a fixed distance apart, the acceleration due to elastic forces is bounded, even when the thickness of one of the elements approaches zero.
 %
@@
 
-\subsection{Element geometry and packing}
+\subsection{Initializing element geometry and packing}
 For purposes of packing, we assume that elements have surface areas which are shaped as equally-sized regular hexagons (note that the elements are assumed to be circular for proposes of interactions, but are assumed to be hexagonal for packing purposes).
@@
 \subsection{Ocean-ice and ice-ocean coupling}
-The LTAM model is coupled to the ocean model via a two-way synchronous coupling, meaning that ocean model fields are passed to the LTAM model and the LTAM model fields are passed back to the ocean model at every time step.
-Passing fields between the two models involves interpolating fields between the Eulerian grid of the ocean model and the `Lagrangian grid' of the LTAM model (i.e.: onto the ice elements).
-
-The coupling from the ocean model to the LTAM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LTAM model, to be used in the momentum and thermodynamic equations of the ice elements.
+The LTIM model is coupled to the ocean model via a two-way synchronous coupling, meaning that ocean model fields are passed to the LTIM model and the LTIM model fields are passed back to the ocean model at every time step.
+Passing fields between the two models involves interpolating fields between the Eulerian grid of the ocean model and aggregating the `Lagrangian grid' of the LTIM model (i.e.: onto the ice elements).
+
+The coupling from the ocean model to the LTIM model is straight forward: at every time step, the ocean mixed layer temperature, salinity, velocity and sea-ice concentration are passed from the ocean model to the LTIM model, to be used in the momentum and thermodynamic equations of the ice elements.
 Since tabular icebergs are explicitly resolved in the ocean, it is sufficient for each element to interact with ocean mixed layer only (i.e.: there is no need to manually embed icebergs into the ocean by integrating ocean fields over the icebergs' thickness, as suggested in \citet{Merino2016}).
-Within the LTAM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme. The LTAM model is not sensitive to the chosen interpolation scheme.
-
-%More care needs to be taken when passing fields back from the LTAM model to the ocean model. 
-The coupling in the other direction, from the LTAM model to the ocean model, is more complex.
-The LTAM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) applying a heat, salinity and mass flux to the ocean, associated with ice melting, and (iii) affecting the upper ocean by applying a no-slip boundary condition and frictional velocity beneath the ice.
-Fields from the LTAM model are interpolated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model.
-Since the LTAM model applies large pressures to the ocean surface, the ocean model is sensitive to the interpolation scheme used to map the LTAM fields to the ocean grid.
-Sudden jumps to the ocean surface pressure can trigger tsunamis within the ocean model, making the ocean model become unstable.
-
-The interpolation of the LTAM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LTAM model (see Section 2.3).
+Within the LTIM model, the ocean model fields are interpolated onto the Lagrangian grid using a bilinear interpolation scheme. The LTIM model is not sensitive to the chosen interpolation scheme.
+
+%More care needs to be taken when passing fields back from the LTIM model to the ocean model. 
+The coupling from the LTIM to ocean model is more complex.
+The LTIM model influences the ocean by: (i) applying a pressure to the ocean surface, (ii) imposing heat, salinity and mass fluxes on the ocean, associated with ice melting, and (iii) affecting the upper ocean by applying a no-slip boundary condition and frictional velocity beneath the ice.
+Fields from the LTIM model are aggregated from the Lagrangian grid to the Eulerian ocean grid before they are passed to the ocean model.
+Since LTIM applies large pressures to the ocean surface, the ocean model is sensitive to the interpolation scheme used to map the LTIM fields to the ocean grid.
+Sudden jumps to the ocean surface pressure can trigger tsunamis within the ocean model, making the ocean model unrealistic.
+
+The aggregation of the LTIM fields onto the ocean grid is done in a way that is consistent with the shape of the elements in the LTIM model (see Section 2.3).
 Fields are `spread' to the ocean model grid by exactly calculating what fraction of an element's surface area lies in a particular grid box, and dividing the field in proportion to this fraction.
 %While the position of a particular element might be inside one ocean grid cell, the implied shape of the element will often intersect other ocean grid cells. 
-For example, consider a hexagonal element in the LTAM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
+For example, consider a hexagonal element in the LTIM model, which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b).
 In this situation, the mass of the element is divided between these four ocean cells in proportion to the overlap area between the hexagonal element and the grid cell (this fraction is shown by the colors in \ref{fig:Hex_intersections}b).
@@
 This method allows for the intersection to be found even when the hexagon is not aligned with the grid.
-%The LTAM model can be run using hexagonal or rectangular elements.
+%The LTIM model can be run using hexagonal or rectangular elements.
 
@@
 At every time step, we calculate the force on each element due to interactions with every other element.
-In principle, this involves order $n^{2}$ operations (for n elements).
+In principle, this involves order $N^{2}$ operations (for N elements).
 However, since each element only has repulsive interactions with elements that are less than one ocean grid cell away, and each element only has bonded interactions with a small number of other elements, we are able to reduce the complexity of the system.
@@
 The bonded force is only applied if $d_{i,j} > L_{ij}$, to avoid double counting an interaction.
-Having a list of bonds stored with each element reduces the computational complexity of bonded interactions from order $n^{2}$ to order n.
+Having a list of bonds stored with each element reduces the computational complexity of bonded interactions from order $N^{2}$ to order N.
 Handling bonded attractive forces separately to the repulsive and non-bonded forces means that we do not need to check whether two elements are bonded, which further increases the computational efficiency.
@@
 \subsubsection{Parallelization and halos}
-The LTAM model runs on multiple processors in parallel.
+The LTIM model runs on multiple processors in parallel (and the same grid as the ocean decomposition).
 When elements move from an ocean cell on one processor to an ocean cell on a second processor, the memory has to be passed from one processor the next, added and removed to the appropriate lists and the memory has to be allocated and deallocated correctly.
@@
 A computational halo is a copy of the edge of a one processor which is appended to the edge of a second processor, so that the first processor can `see' the second processor during a time step.
-Before a time step, elements at the edges of each processor are copied onto the halos of adjacent processors so that they can be used in calculating the interactive forces.
+Before each time step, elements at the edges of each processor are copied onto the halos of adjacent processors so that they can be used in calculating the interactive forces.
 After each time step, these halos and removed, and the process is repeated.
-These halo updates are one of the most computationally expensive parts of the LTAM model.
+These halo updates are one of the most computationally expensive parts of the LTIM model.
 
@@
 \subsubsection{Time stepping}
-The ice elements in the LTAM model are advected using a semi-implicit velocity Verlet time-stepping scheme.
-The velocity verlet time stepping scheme is commonly used in DEM models in video games because it is computational efficient and has desirable stability properties \citep{Jakobsen2001}.
-This time stepping scheme was preferred to the Runge-Kutta  4, which was used in the iceberg model of \citet{Martin2010} since, the Verlet time stepping only requires one calculation of the interactive forces per time step (while the Runge-Kutta scheme requires the interactive forces to be calculated four times).
+The ice elements in the LTIM model are advected using a semi-implicit velocity Verlet time-stepping scheme.
+The velocity Verlet time stepping scheme is commonly used in DEM models in video games because it is computational efficient and has desirable stability properties \citep{Jakobsen2001}.
+This time stepping scheme was preferred to the Runge-Kutta  4, which was used in the iceberg model of \citet{Martin2010} since the Verlet time stepping only requires a calculation of the interactive forces once per time step (while the Runge-Kutta scheme requires the interactive forces to be calculated four times).
 Since the calculation of the interactive forces is one of the most computationally expensive part of the algorithm, the Verlet scheme leads to a significant increase in the speed of the model.
-We note that the Verlet scheme used in the LTAM contains a modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
+We note that the Verlet scheme used in the LTIM contains a modification of the original (fully explicit) velocity Verlet time stepping scheme in that damping terms are treated implicitly (which increases the numerical stability).
 The details of this time stepping schemed are outline in Appendix B.
@@
 
-%We demonstrate this capability in an experimental setup using an idealized ice shelf. For these experiments the LTAM model is coupled to the MOM6 ocean model.
+%We demonstrate this capability in an experimental setup using an idealized ice shelf. For these experiments the LTIM model is coupled to the MOM6 ocean model.
 % This section contains a description of the experimental setup and numerical experiments performed. The results of these simulations are presented in Section 4.
 
- %In the examples below, the LTAM model is firstly used in uncoupled mode to model the movement of freely drifting icebergs.
-Secondly, the coupled LTAM with static ice elements is used to model an idealized ice shelf cavity.
-Finally, the fully-coupled LTAM is used to model a tabular iceberg which calves off of this ice shelf.
+ %In the examples below, the LTIM model is firstly used in uncoupled mode to model the movement of freely drifting icebergs.
+Secondly, the coupled LTIM with static ice elements is used to model an idealized ice shelf cavity.
+Finally, the fully-coupled LTIM is used to model a tabular iceberg which calves off of this ice shelf.
 
 %\subsection{Uncoupled simulation}
-%We begin by demonstrating the LTAM model uncoupled to the ocean.
+%We begin by demonstrating the LTIM model uncoupled to the ocean.
 For this experiment, we use a rectangular domain, $L_{x}=1000$ km long and $L_{y}=500$ km wide.
@@
 We demonstrate this capability by simulating a tabular iceberg drifting away from an idealized ice shelf.
-%This simulation is performed using the LTAM model coupled to the MOM6 ocean model \citep{Hallberg2013}. 
+%This simulation is performed using the LTIM model coupled to the MOM6 ocean model \citep{Hallberg2013}. 
 %This section describes the experimental setup of these numerical experiments. The results are shown in Section 4.
@@
 \subsection{Ocean model setup}
-The LTAM model is coupled to the MOM6 ocean model \citep{Hallberg2013}.
+The LTIM model is coupled to the MOM6 ocean model \citep{Hallberg2013}.
 The ocean model is run using a vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate.
@@
 The model uses a horizontal resolution of 2km, and 72 vertical layers.
-All simulation were repeated using the ocean model run layered mode (results were similar and are not presented here).
+All simulations were repeated using the ocean model configured in isopycnal mode (results were similar and are not presented here).
 %(select results are shown in the supplementary material).
@@
 The melt rates of the Eulerian and Lagrangian models are very similar with slight difference showing up at the grounding line and ice front (Figure \ref{fig:Melt_comparison}).
-The slight difference at the grounding line are a result of the fact that elements in the LTAM model are smaller than a grid cell in length.
-This means that ice element near the grounding line may be ungrounded in the LTAM model, while the grid cell is considered grounded in the Eularian model.
-At the ice front, the Eularian model has a straight ice front, while the LTAM model has a staggered ice front, which is a result of the staggered hexagonal packing.
+The slight difference at the grounding line are a result of the fact that elements in the LTIM model are smaller than a grid cell in length.
+This means that ice element near the grounding line may be ungrounded in the LTIM model, while the grid cell is considered grounded in the Eularian model.
+At the ice front, the Eularian model has a straight ice front, while the LTIM model has a staggered ice front, which is a result of the staggered hexagonal packing.
 
@@
 The motion of the tabular iceberg disturbs the ocean surface, which drives ocean velocities through out the water column (Figure \ref{fig:Velocity_section_Collapse}).
-The elevated velocities around the tabular iceberg lead to increased vertical mixing in the vicinity of the iceberg, which alters the stratification of the water column (Figure \ref{fig:Temperature_section_Collapse}), heating the upper ocean.
+The elevated shears around the tabular iceberg lead to increased vertical mixing in the vicinity of the iceberg, which alters the stratification of the water column (Figure \ref{fig:Temperature_section_Collapse}), heating the upper ocean.
 The increased ocean velocities and increased surface temperatures cause elevated melt rates at the base of the ice shelf and iceberg (Figure \ref{fig:Collapse_solo_melt}).
@@
 
-Finally, we note that the numerical bonds in the LTAM model are needed in order to allow the tabular iceberg to retain its shape.
+Finally, we note that the numerical bonds in the LTIM model are needed in order to allow the tabular iceberg to retain its shape.
 Comparing the iceberg calving simulation with an identical simulation where all numerical bonds have been removed, shows that in the absence of the bonds, the ice elements quickly disperse (Figure \ref{fig:Bond_vs_No_bond}).
@@
 
-To our knowledge, the model presented in this study is the first model to explicitly resolve drifting tabular icebergs in an ocean model.
+To our knowledge, the model presented in this study is the first model to explicitly resolve drifting tabular icebergs in an ocean model that can be used for climate.
 A natural extension of this work is to try to include tabular icebergs into a general circulation model (GCM) used for climate projections.
@@
 \subsection{Melt rate parametrization}
-As discussed in Section 2.5, unbounded ice elements in the LTAM model decay according to parameterizations for iceberg decay typically used in iceberg drift models \citep{Martin2010}, while ice elements within larger ice structures have only a basal melt given by the three equation model \citep{Holland1999} .
+As discussed in Section 2.5, unbounded ice elements in the LTIM model decay according to parameterizations for iceberg decay typically used in iceberg drift models \citep{Martin2010}, while ice elements within larger ice structures have only a basal melt given by the three equation model \citep{Holland1999} .
 
@@
 \subsection{Modified Verlet Algorithm}
-The LTAM model uses a version velocity verlet time-stepping algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
-The traditional velocity verlet algorithm is commonly used in molecular dynamics, as it is simple to implement, second order accurate and computationally efficient \citep{Swope1982, Omelyan2002}.
-Here we modify the tradition scheme to allow for the drag forces to be modeled implicitly, which prevents large accelerations for element's whose mass approaches zero. 
-To do this, we modify the traditional verlet algorithm to include both an implicit and explicit acceleration, $a=a^{exp} +a^{imp}$.
+The LTIM model uses a version velocity Verlet time-stepping algorithm, which has been modified to allow part of the forcing to be calculated implicitly.
+The traditional velocity Verlet algorithm is commonly used in molecular dynamics, as it is simple to implement, second order accurate and computationally efficient \citep{Swope1982, Omelyan2002}.
+Here we modify the traditional scheme to allow for the drag forces to be modeled implicitly, which prevents large accelerations for element's whose mass approaches zero. 
+To do this, we include both an implicit and explicit acceleration, $a=a^{exp} +a^{imp}$.
 The explicit acceleration, $a^{exp}$ includes all forcing terms which depend only on the previous time step and the current position, while the implicit acceleration, $a^{imp}$ includes forcing terms which depend on the velocity at the current time step (in particular the drag and Coriolis forces).
@@
 
-Using a time step of $\Delta t$, and subscripts to denote the time step (so that $t_{n+1}= t_{n} + \Delta t$), the modified velocity verlet scheme can be written as:\\
+Using a time step of $\Delta t$, and subscripts to denote the time step (so that $t_{n+1}= t_{n} + \Delta t$), the modified velocity Verlet scheme can be written as:\\
 1) $ x_{n+1} = x_{n} + u_{n} \Delta t  + \frac{1}{2} \Delta t^{2} \Bigg(a^{exp}_{n} + a^{imp}_{n} \Bigg) $.\\
@@
 %  (which is a function of $u_{n+1}$, $x_{n+1}$, and other quantities measured at time $t_{n}$)
-This scheme reduces to the traditional velocity verlet when $a^{imp}$ is set to zero.
+This scheme reduces to the traditional velocity Verlet when $a^{imp}$ is set to zero.
 Note that $a^{exp}_{n+1} = a^{exp}_{n+1}(x_{n+1}, t_{n})$ is an explicit function of  $x_{n+1}$ and other quantities evaluated at time $t_{n}$, while $a^{imp}_{n+1}=a^{imp}_{n+1}(u_{n+1}, x_{n+1}, t_{n})$ additionally depends on $u_{n+1}$, and needs to be solved implicitly.
@@
 %The consequences of the drag not being fully implicit are discussed below. 
-Step 3 of the modified velocity verlet scheme can be rewritten by introducing an intermediate velocity $u^{*}$, which only depends on the velocity and acceleration at time $t_{n}$,
+Step 3 of the modified velocity Verlet scheme can be rewritten by introducing an intermediate velocity $u^{*}$, which only depends on the velocity and acceleration at time $t_{n}$,
  \begin{equation}
@@
  \end{equation}
-Once the $u_{n+1}$  has been found, it can be used to calculated the explicit and implicit accelerations, which are required for the next time step.
+Once the $u_{n+1}$  has been found, it can be used to calculate the explicit and implicit accelerations, which are required for the next time step.
 
@@
 This is done so that we can solve for the updated velocity analytically.
-One consequence of this is that it gives rise to a small oscillation in the element velocity.
-This oscillation is addressed by using a predictive corrective scheme: once you have solved for a first guess of the velocity at time $t_{n+1}$, this estimate of the velocity is used to update the estimate of the drag force (i.e.: inside the absolute value signs).
-Using the updated drag, you can now repeat the process described above to find an improved estimate of the velocity.
+One consequence of this is that it can give rise to a small oscillation in the element velocity.
+This oscillation is addressed by using a predictive corrective scheme: after solving for a first guess of the velocity at time $t_{n+1}$, this estimate of the velocity is used to update the estimate of the drag force (i.e.: inside the absolute value signs).
+This updated drag, can now be used to repeat the process described above to find an improved estimate of the velocity.
 We found that two iterations were sufficient to remove the unwanted oscillation.
@@
 \textbf{Connecting bonds across processor boundaries}\\
-Since the LTAM model can be parallelized across multiple processors, it often happens that two elements on different processes are bonded together.
+Since the LTIM model is parallelized across multiple processors, it often happens that two elements on different processes are bonded together.
 Keeping track of numerical bonds across processor boundaries requires a lot of book keeping.
-In this section we describe the how LTAM model avoids segmentation faults by severing and reconnecting bonds at the edge of a processor during halo updates.
+In this section we describe the how LTIM model handles bonds across processor boundaries.
 
@@
 \bibitem[Losch (2008)]{Losch2008}
-Losch, M. (2008). Modeling ice shelf cavities in az coordinate ocean general circulation model. {\it J. of Geophys. Res.: Oceans}, 113(C8).
+Losch, M. (2008). Modeling ice shelf cavities in a z coordinate ocean general circulation model. {\it J. of Geophys. Res.: Oceans}, 113(C8).
 
@@
 \bibitem[Stern et al (2016)]{Stern2016}
-Stern, A. A., A. Adcroft, and O. Sergienko (2016), The effects of Antarctic iceberg calving?size distribution in a global climate model. {\it J. of Geophys. Res.: Oceans}, 121(8), 5773-5788.
+Stern, A. A., A. Adcroft, and O. Sergienko (2016), The effects of Antarctic iceberg calving size distribution in a global climate model. {\it J. of Geophys. Res.: Oceans}, 121(8), 5773-5788.
 
@@
 \bibitem[Unger (2014)]{Unger2014}
-Unger, J. D., 2014. Regulating the Arctic Gold Rush:  Recommended Regulatory Reforms to Protect Alaska's ArcticEnvironment from Offshore Oil Drilling Pollution . {\it Alaska L. Rev}, 31
+Unger, J. D., 2014. Regulating the Arctic Gold Rush:  Recommended Regulatory Reforms to Protect Alaska's Arctic Environment from Offshore Oil Drilling Pollution . {\it Alaska L. Rev}, 31
 
@@
 Adcroft, and R.
-Hallberg (2009), High-order regriddingÐremapping schemes for continuous isopycnal and generalized coordinates in ocean models.
+Hallberg (2009), High-order regridding-remapping schemes for continuous isopycnal and generalized coordinates in ocean models.
 {\it J.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LTAM tabular iceberg calving simulation.
+\caption{ {Snapshots of the fraction of ice cover in the LTIM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp.png}
-\caption{ {Snapshots of the sea surface temperature in the LTAM tabular iceberg calving simulation.
+\caption{ {Snapshots of the sea surface temperature in the LTIM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Regular_towards_coast}
-\caption{ {Results of an ice-only LTAM simulation with no bonds between ice elements.
+\caption{ {Results of an ice-only LTIM simulation with no bonds between ice elements.
 Ice elements are initialized throughout the domain, as shown in panel (a).
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Tabular_and_regular_towards_coast_manual}
-\caption{ {Results of an ice-only LTAM simulation using bonds between elements.
+\caption{ {Results of an ice-only LTIM simulation using bonds between elements.
 Ice elements are initialized throughout the domain, as shown in panel (a).
@@
 The colors indicate the fraction of the hexagon that lies in each grid cell.
-These fractions are used as weights to spread LTAM properties to the ocean grid (see text for more details).}}
+These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details).}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_v_layers_x10.png}
-\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LTAM tabular iceberg calving simulation.
+\caption{ {Snapshots of vertical sections of meridional velocity at $x=58 $km in the LTIM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LTAM tabular iceberg calving experiment.
+\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LTIM tabular iceberg calving experiment.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 All snapshots are taken at time t = 30 days.
-The simulations uses wind stress $\vec{\tau}=< 0.0, 0.05 >.$}}
+The simulations use wind stress $\vec{\tau}=< 0.0, 0.05 >.$}}
 \end{center}

### 2017-03-10 Icebergs_only.tex
Updating James article. Updating the uncoupled matlab scripts so that elements ahve tails. THere are also updates to the Lagrangian_MISOMIP text. These are older, and I must have forgotton to add them.

@@
 \begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/PIIB_with_hexagons.png}
+\caption{Schematic showing how Lagrangian elements are used when modeling tabular icebergs.
+Lagrangian elements (blue dots) are initialized in a staggered lattice covering the surface area of the iceberg.
+For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (grey hexagons).
+For purposed of element interactions, the ice elements are assumed to be circular (black circles).
+Elements are initially bonded to adjacent elements using numerical bonds (dashed white lines).
+These numerical bonds form equilateral triangles which give the shape rigidity.
+The inset panel shows a schematic of the intersection of a hexagonal element and the ocean grid.
+The colors indicate the fraction of the hexagon that lies in each grid cell.
+These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details) The background photo in the larger schematic is an areal photograph of iceberg PIIB (Area= 42 $\textrm{km}^{2}$) taken in Baffin Bay in 2012.
+The red ship can be identified on the bottom of the photo for scale.
+}
+\end{center}
+\label{fig:Spread_area}
+\end{figure}
+ \clearpage
+
+(a) Hexagonal elements are initialized in a staggered lattice as shown.
+Adjacent elements are bonded together.
+The element bonds (plotted in pink) form equilateral triangles which give the larger structure rigidity.
+The black circles show the circular element shape used in element interactions, and are inscribed inside the hexagonal shape used for mass-spreading.
+(b) Intersection of a hexagonal element and the ocean grid.
+The colors indicate the fraction of the hexagon that lies in each grid cell.
+These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details).
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
@@
 \end{center}
-\label{fig:Spread_area}
+\label{fig:Hex_intersections}
 \end{figure}
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
-\caption{ {(a) Hexagonal elements are initialized in a staggered lattice as shown.
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
+%\caption{ {(a) Hexagonal elements are initialized in a staggered lattice as shown.
 Adjacent elements are bonded together.
@@
 These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details).}}
-\end{center}
-\label{fig:Hex_intersections}
-\end{figure}
- \clearpage
+%\end{center}
+%\label{fig:Hex_intersections}
+%\end{figure}
+ %\clearpage
 

### 2017-03-10 regular_towards_coast.m

@@ -41,7 +41,7 @@ cd(path_name)
 % filename='Two_particle_spring';
 % filename='Two_particle_Jacobi';
 % filename='Big_and_small_bergs_curved_coast_again';
- filename='New_test_curved_coast';
+filename='New_test_curved_coast';
 % filename='New_test_curved_coast_up_pia';
 %filename='New_test_curved_coast_up_pia_and_q_ia';
 %filename='From_saved_test';
@@ -60,6 +60,7 @@ plot_the_bonds=1;
 plot_land_each_time=0;
 plot_L_eff=1;
 make_a_movie=0;
+plot_tails=1;
 
 %Defining the grid
 Lx=500*1000;%100*1000; %Length of the domain
@@ -146,19 +147,19 @@ for time_count=time_ind_list;
     set(gca,'fontsize',fontsize)
     text(500,505,letter_list(plot_count,:),'fontsize',fontsize)
     
-        %Plotting the land
-        hold on
-        for i=1:Nx
-            for j=1:Ny
-                if Land(i,j)==1
-                    count=count+1;
-                    %hline10(i,j)=plot(x(i)/1000,y(j)/1000,'k*');
-                    mult=5;
-                    hline11(i,j)=fill((x(i)/1000)+(((mult*dx/2)/1000).*cos(circ_ind)),(y(j)/1000)+(((mult*dx/2)/1000).*sin(circ_ind)),'k');
-                    %hline11(i,j)=plot((x(i)/1000)+(((dx/2)/1000).*cos(circ_ind)),(y(j)/1000)+(((dx/2)/1000).*sin(circ_ind)),'k','linewidth',4);
-                end
+    %Plotting the land
+    hold on
+    for i=1:Nx
+        for j=1:Ny
+            if Land(i,j)==1
+                count=count+1;
+                %hline10(i,j)=plot(x(i)/1000,y(j)/1000,'k*');
+                mult=5;
+                hline11(i,j)=fill((x(i)/1000)+(((mult*dx/2)/1000).*cos(circ_ind)),(y(j)/1000)+(((mult*dx/2)/1000).*sin(circ_ind)),'k');
+                %hline11(i,j)=plot((x(i)/1000)+(((dx/2)/1000).*cos(circ_ind)),(y(j)/1000)+(((dx/2)/1000).*sin(circ_ind)),'k','linewidth',4);
             end
         end
+    end
     
     
     if plot_the_area==1
@@ -184,42 +185,60 @@ for time_count=time_ind_list;
         
[…]

### 2017-03-17 Scripts_for_paper_figures/Fig_Collapse_solo_melt.sh
Updating Figure scripts to improve Figures

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -broken_shelf=True -save_figure=True  
+./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -ylim_min=240. -ylim_max=440.0 -broken_shelf=True -use_Mixed_Melt=True -save_figure=True  

### 2017-03-17 Scripts_for_paper_figures/Fig_Drift_berg.sh

@@ -1,0 +1,2 @@
+cd ../
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -save_figure=True

### 2017-03-17 Scripts_for_paper_figures/Fig_SST_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.2  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=12 -save_figure=True

### 2017-03-17 Scripts_for_paper_figures/Fig_Splitting_berg.sh

@@ -1,0 +1,2 @@
+cd ../
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -save_figure=True

### 2017-03-17 Scripts_for_paper_figures/Fig_Temperature_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.3 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=10 -colorbar_units='(deg C)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.3 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(deg C)' -use_Mixed_Melt=True -save_figure=True

### 2017-03-17 Scripts_for_paper_figures/Fig_Velocity_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=10 -colorbar_units='(m/s)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(m/s)' -use_Mixed_Melt=True -save_figure=True

### 2017-03-17 Scripts_for_paper_figures/Fig_spread_area_snapshots.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=icebergs_month.nc -plot_horizontal_field=True -use_ALE=True -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=Blues -field=spread_area -vmin=0.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=False -dir_slice_num=1 -colorbar_units='(non dim)' -save_figure=True
+./snapshots.py -extension=icebergs_month.nc -plot_horizontal_field=True -use_ALE=True -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=Blues -field=spread_area -vmin=0.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=False -dir_slice_num=1 -colorbar_units='(non dim)' -use_Mixed_Melt=True -save_figure=True

### 2017-03-22 static_shelf_comparison.py
Adding changes to static ice shelf comparison

@@ -55,6 +55,21 @@ def mask_grounded_ice(data,depth,base):
 
    return data
 
+def mask_ice(data,ice_base):
+   """
+   Mask regions where the ice shelf is above ocean Works with 2D or 3D arrays.
+   This is not coded so well, a bit of a hack.
+   """
+   mask=np.zeros([data.shape[1],data.shape[2]])+1.
+   mask[np.where(ice_base>0)]=np.nan
+   if len(data.shape) == 2: # 2D array
+	   data[k,:,:]=data[:,:]*mask[:,:]
+   if len(data.shape) == 3: # 3D array
+	   for k in range(data.shape[0]):
+		   data[k,:,:]=data[k,:,:]*mask[:,:]
+   
+   return data
+
 def mask_ocean(data,area):
    """
    Mask open ocean. Works with 2D or 3D arrays.
@@ -248,7 +263,7 @@ def plot_data_field(data,x,y,vmin=None,vmax=None,flipped=False,colorbar=True,cma
 		tmp=y ; y=x ; x=tmp
 		x=transpose_matrix(x)
 		y=transpose_matrix(y)
-		y=-y+(np.max(y))
+		#y=-y+(np.max(y))
 		(xlabel , ylabel) = switch_x_and_y(xlabel , ylabel)
 	
 	print 'Starting to plot...'	
@@ -278,6 +293,9 @@ def plot_data_field(data,x,y,vmin=None,vmax=None,flipped=False,colorbar=True,cma
 	plt.ylabel(ylabel)
 	#plt.grid(True)
 	plt.title(title)
+
+	if flipped is True:
+		plt.gca().invert_yaxis()
 
 	if return_handle is True:
 		return datamap

### 2017-03-22 Lagrangian_MISOMIP.tex

@@
 \section{Lagrangian model description}
-This section provides a brief description of the Lagrangian Tabular Iceberg Model (LTAM), which is used to construct the Lagrangian ice shelf used in this study.
-A detailed description of the LTAM, including many of the technical details involved in constructing the model, can be found in \citet{Stern2017}.
+This section provides a brief description of the Lagrangian Bonded Ice shelf Model (LBIM), which is used to construct the Lagrangian ice shelf used in this study.
+A detailed description of the LBIM, including many of the technical details involved in constructing the model, can be found in \citet{Stern2017}.
 
 \subsection{Lagrangian grid}
-The LTAM is a discrete element model (DEM) in that the objects of the model are Lagrangian elements.
+The LBIM is a discrete element model (DEM) in that the objects of the model are Lagrangian elements.
 Each Lagrangian element represents a mass of ice which is floating in the ocean.
@@
 The elements can also be `bonded' together by numerical bonds, which hold the elements together and allow many elements to move together as a unit.
-By bonding many ice elements together, the LTAM model is able to form larger structures, such as tabular icebergs or (non-dynamic) ice shelves.
-
-When constructing ice shelves using the LTAM model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
+By bonding many ice elements together, the LBIM model is able to form larger structures, such as tabular icebergs or (non-dynamic) ice shelves.
+
+When constructing ice shelves using the LBIM model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
 In this Lagrangian grid, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
@@
 \subsection{Interaction with the ocean}
-Since the LTAM model uses a Lagrangian grid, all of the ice shelf information is stored with the elements.
+Since the LBIM model uses a Lagrangian grid, all of the ice shelf information is stored with the elements.
 At every time step, this information has to be interpolated from the Lagrangian grid to (Eularian) ocean grid, so that it can be passed to the ocean model.
@@
 Five fields are `spread' from the Lagrangian to Eularian grids at each time step: mass, surface area, temperature flux, salinity flux and mass flux.
-Once these five fields are in hand, the LTAM mode interacts with the ocean model in exactly the same way the Eularian model does.
+Once these five fields are in hand, the LBIM mode interacts with the ocean model in exactly the same way the Eularian model does.
 As in Eularian ice-shelf models, these fields are passed to the ocean model and are used to:
@@
 This means that accurately interpolating fields from the Lagrangian to Eularian grids is the key to making the Lagrangian ice-shelf model behave like the Eularian ice-shelf model for using static ice-shelf simulations.
-Ocean mixed layer properties are passed from ocean model to the LTAM model, and are interpolated onto the elements using a bilinear interpolation.
+Ocean mixed layer properties are passed from ocean model to the LBIM model, and are interpolated onto the elements using a bilinear interpolation.
 The model is less sensitive to the details of this interpolation.
-%In the next section we use an idealized setup to demonstrate that this is done correctly in the LTAM model.
+%In the next section we use an idealized setup to demonstrate that this is done correctly in the LBIM model.
 
@@
 % the proof of concept for
-The LTAM model is used to simulate the flow within an idealized ice-shelf cavity.
+The LBIM model is used to simulate the flow within an idealized ice-shelf cavity.
 The simulations are repeated using an Eularian ice shelf with an identical configuration.
@@
 \subsection{Comparison of Lagrangian and Eularian ice-shelf models}
-The LTAM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
+The LBIM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
 To get a quantitative comparison, we compare the Lagrangian ice-shelf model results to a simulation using an Eulerian ice-shelf model with an identical configuration.
@@
 Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes to the ocean, and (iii) alter the upper ocean boundary condition below the ice shelf.
-The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LTAM model, and that the LTAM is able to model sub-ice-shelf cavities as well as the Eularian model does.
+The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LBIM model, and that the LBIM is able to model sub-ice-shelf cavities as well as the Eularian model does.
 This is a good starting point for moving beyond the capabilities of the Eularian model.
@@
 % 
-%One element which is missing from the LTAM ice shelf is that the ice shelf is not dynamic.
+%One element which is missing from the LBIM ice shelf is that the ice shelf is not dynamic.
 Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice-shelf geometry to change over time.
@@
 A possible path towards this is to model sea ice using a Lagrangian grid \citep{Hopkins1996, Li2014}, and to treat sea ice - iceberg interactions in the same way that iceberg - iceberg interactions are treated in this study.
-A number of preliminary experiments have been run using the LTAM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
+A number of preliminary experiments have been run using the LBIM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
 % Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LTAM tabular iceberg calving simulation.
+\caption{ {Snapshots of the fraction of ice cover in the LBIM tabular iceberg calving simulation.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LTAM tabular iceberg calving experiment.
+\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LBIM tabular iceberg calving experiment.
 Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.

### 2017-03-22 Tech1.tex

@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
+\caption{ {Comparison on melt rates using (a) three equation model, (b) iceberg melt parametrization, and (c) mixed melting.}}
+\end{center}
+%FIgure created by \end{center}
+%\label{fig:Bt_comparison}
+\end{figure}
+ \clearpage
+
  \end{document}

### 2017-03-22 snapshots.py
Figure script updates

@@ -51,9 +51,13 @@ def parseCommandLine():
 	#General flags
 	parser.add_argument('-rotated', type='bool', default=True,
 		                        help=''' Rotates the figures so that latitude runs in the vertical (involves switching x and y. ''')
+	
 	parser.add_argument('-use_ALE', type='bool', default=True,
 		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
-	use_ALE=True
+	
+	parser.add_argument('-use_Mixed_Melt', type='bool', default=False,
+		                        help=''' When true, figure plots using Mixed_melt_data ''')
+	
 	parser.add_argument('-use_days_title', type='bool', default=False,
 		                        help=''' When true, the day number is used as a title for the figures. ''')
 	#What to plot?
@@ -112,8 +116,18 @@ def parseCommandLine():
 	parser.add_argument('-xmax', type=float, default=960.0,
 		                        help='''Minimum x used for plotting (only applies to vertical sectins for now)''')
 
+	parser.add_argument('-ylim_min', type=float, default=240.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+
+	parser.add_argument('-ylim_max', type=float, default=440.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+
 	parser.add_argument('-dir_slice_num', type=int, default=1,
 		                        help='''The index of the transect used (in the direction not plotted''')
+	
+	parser.add_argument('-dashed_num', type=int, default=1,
+		                        help='''The index where the dashed line is plotted''')
+
 
 	parser.add_argument('-colorbar_units', type=str, default='',
 		                        help='''The units for the colorbar''')
@@ -136,6 +150,7 @@ def main(args):
 	rotated=args.rotated
 	use_ALE=args.use_ALE
 	use_days_title=args.use_days_title
+	use_Mixed_Melt=args.use_Mixed_Melt
 
 	#What to plot?
[…]

### 2017-03-22 static_shelf_comparison.py

@@ -114,18 +114,18 @@ def mask_grounded_ice(data,depth,base):
 
    return data
 
-def mask_ocean(data,area):
+def mask_ocean(data,area,tol=0.0):
    """
    Mask open ocean. Works with 2D or 3D arrays.
    """
    if len(data.shape) == 2: # 2D array
-     data = np.ma.masked_where(area==0.0,data)
+     data = np.ma.masked_where(area<=tol,data)
      #data[np.where(area<0.5)]=np.nan
 
    else: # 3D array
      NZ,NY,NX = data.shape
      area=np.resize(area,(NZ,NY,NX))
-     data = np.ma.masked_where(area==0,data)
+     data = np.ma.masked_where(area<=tol,data)
 
    return  data
 

### 2017-03-22 static_shelf_solo.py

@@ -57,6 +57,9 @@ def parseCommandLine():
 	parser.add_argument('-broken_shelf', type='bool', default=False,
 		                        help=''' When true, figure plots data after ice shelf breakoff ''')
 	
+	parser.add_argument('-use_Mixed_Melt', type='bool', default=False,
+		                        help=''' When true, figure plots using Mixed_melt_data ''')
+	
 	parser.add_argument('-three_fields_flag', type=str, default='plot_melt_sst_ustar_berg',
 		                        help='''String determines which set three fields to plot. Options are plot_vel_vel_sst, plot_depth_spread_mass_mass
 					plot_melt_sst_ustar_berg.  Other values will plot the 1 field given in the script''')
@@ -107,6 +110,11 @@ def parseCommandLine():
 	#parser.add_argument('-dir_slice_num', type=int, default=1,
 	#	                        help='''The index of the transect used (in the direction not plotted''')
 
+	parser.add_argument('-ylim_min', type=float, default=0.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+
+	parser.add_argument('-ylim_max', type=float, default=480.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
 
 
 
@@ -139,6 +147,7 @@ def main(args):
 	broken_path=''
 	if broken_shelf is True:
 		Folder_name= 'After_melt_Collapse_diag_Strong_Wind/' 
+		Folder_name= 'After_melt_Collapse_diag_Strong_Wind/' 
 		broken_path='_calved'
 	Berg_path=Path+'Bergs/' + Folder_name
 
@@ -147,11 +156,19 @@ def main(args):
 	ice_geometry_filename=Shelf_path+'/MOM_Shelf_IC.nc'
 	ISOMIP_IC_filename=Shelf_path+'ISOMIP_IC.nc'
 	
+
+	#Using Mixed_melt_flag
+	use_mixed_melt_flag=''
+	if args.use_Mixed_Melt is True:
+		use_mixed_melt_flag='Mixed_Melt_'
+		Folder_name= 'Mixed_Melt_' +Folder_name
+
 	#Using ALE ice shelf
 	use_ALE_flag=''
 	if use_ALE is True:
[…]

### 2017-03-22 three_melt_rates.py

@@ -20,13 +20,44 @@ from static_shelf_comparison import *
 ##########################################################  Main Program   #########################################################################
 ####################################################################################################################################################
 
-def main():
-	parser = argparse.ArgumentParser()
-	args = parser.parse_args()
+def parseCommandLine():
+        """
+        Parse the command line positional and optional arguments.
+        This is the highest level procedure invoked from the very end of the script.
+        """
+
+        parser = argparse.ArgumentParser(description=
+        '''
+        Plot snapshots of either surface or vertical sections, for Tech paper.
+        ''',
+        epilog='Written by Alon Stern, Dec. 2016.')
+	
+	#Adding an extra boolian type argument
+        parser.register('type','bool',str2bool) # add type keyword to registries
+
+
+
+	#Adding arguments:
+
+	#Saving figure
+	parser.add_argument('-save_figure', type='bool', default=False,
+		                        help=''' When true, the figure produced by the script is saved''')
+	
+	#Plotting flags
+	parser.add_argument('-ylim_min', type=float, default=240.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+
+	parser.add_argument('-ylim_max', type=float, default=440.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+	
+	optCmdLineArgs = parser.parse_args()
+	return optCmdLineArgs
+
+def main(args):
 
 
 	#Plotting flags
-	save_figure=True
+	save_figure=args.save_figure
 
 	#General flags
 	rotated=True
@@ -46,8 +77,8 @@ def main():
 	path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/'
 	extension='00060101.icebergs_month.nc'
 	IceShelfMelt_file = path +  'ALE_z_After_melt_Collapse_diag_Strong_Wind/' +extension
[…]

### 2017-03-22 Two_panel_schematic.py
Lots of the files

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+import matplotlib.pyplot as plt
+#import matplotlib
+import numpy
+#%matplotlib inline
+import matplotlib.image as mpimg
+
+
+
+##########################################################  Main Program   #########################################################################
+####################################################################################################################################################
+
+
+
+
+
+if __name__ == '__main__':
+	
+	#Read in image 1
+	im_hexaberg = mpimg.imread('Figures/hexaberg.png')
+	
+	#Read in the photo
+	im_schematic = mpimg.imread('Figures/schematic_berg.png')
+	
+	plt.figure(figsize=(12,8));	
+	#ax=plt.subplot(1,2,1)
+	ax = plt.gcf().add_axes([0.02,0.1,.6,.6]);
+	ax.imshow(im_schematic); plt.axis('off')
+	ax.text(1,1,'(a)', ha='right', va='bottom',transform=ax.transAxes,fontsize=15)
+	#ax=plt.subplot(1,2,2)
+	ax = plt.gcf().add_axes([0.5,0.15,.5,.5]);
+	ax.imshow(im_hexaberg); plt.axis('off')
+	ax.text(1,1,'(b)', ha='right', va='bottom',transform=ax.transAxes,fontsize=15)
+		
+	#plt.gca().annotate('Ocean mesh', xy=(x+.05,y-0.05), xytext=(x+0.1,y-0.5),
+	#			   arrowprops=dict(arrowstyle='->', connectionstyle='arc3,rad=.2'))
+
+	plt.savefig('Figures/Two_panel_schematic_berg.png',dpi=300,bbox_inches='tight');
+	
+	#Schematic()
+	plt.show()
+	print 'Script complete'
+
+	#sys.exit(main())
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2017-03-22 hexagon_xy.m

@@ -1,0 +1,37 @@
+function hexagon_xy(x0,y0,H,color_str,linewidth)
+
+
+berg_count=1;
+hold on
+%plot(x0,y0,'o','linewidth',2 )
+%plot(x0+(H.*cos(circ_ind)),y0+(H.*sin(circ_ind)),'k','linewidth',2 )
+
+circ_ind=[0:0.1:2*pi];
+S=(2/sqrt(3))*H;   %side of hexigon
+
+if color_str=='grey'
+    color_str=[0.4,0.4,0.4];
+end
+%elseif color_str=='light_grey'
+%    color_str=[0.9,0.9,0.9];
+%end
+
+
+%line 1
+plot([x0+S x0+H/sqrt(3)],[y0 y0+H],'Color',color_str,'linewidth',linewidth)
+%line 2
+plot([x0+H/sqrt(3) x0+H/sqrt(3)-S],[y0+H y0+H],'Color',color_str,'linewidth',linewidth)
+%line 3
+plot([x0+H/sqrt(3)-S x0-S],[y0+H y0],'Color',color_str,'linewidth',linewidth)
+%line 4
+plot([x0-S x0+H/sqrt(3)-S],[y0 y0-H],'Color',color_str,'linewidth',linewidth)
+%line 5
+plot([x0+H/sqrt(3)-S x0+H/sqrt(3)],[y0-H y0-H],'Color',color_str,'linewidth',linewidth)
+%line 6
+plot([x0+H/sqrt(3) x0+S],[y0-H y0],'Color',color_str,'linewidth',linewidth)
+
+
+
+
+
+

### 2017-03-29 snapshots.py
Moving figure lables to the left

@@ -316,7 +316,8 @@ def main(args):
 			datamap=plot_data_field(data1,x,y,vmin,vmax,flipped,colorbar=False,cmap=cmap,title=title,xlabel='x (km)',ylabel='',ylim_min=ylim_min,\
 					ylim_max=ylim_max,colorbar_units=args.colorbar_units,return_handle=True)  
 
-			text(1,1,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+			#text(1,1,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+			text(0.1,1,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 			if n==0:
 				plt.ylabel('y (km)',fontsize=20)
 			if n>0:

### 2017-03-29 static_shelf_solo.py

@@ -305,7 +305,7 @@ def main(args):
 					xlabel='x (km)',ylabel='',return_handle=True, colorbar_units=colorbar_unit_list[k],colorbar_shrink=0.5,ylim_min=ylim_min, ylim_max=ylim_max)	
 			if k==0:
 				plt.ylabel('y (km)')
-			text(1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+			text(0.1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 			#plt.ylim([550., 750])
 			if k>0:
 				ax.set_yticks([])
@@ -436,7 +436,7 @@ def main(args):
 			if k==2:
 				plt.xlabel('y (km)',fontsize=20)
 			plt.ylabel('Depth (m)',fontsize=20)
-			text(1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+			text(0.1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 		
 		#For plotting purposes
 		field=field+'_'+ vertical_coordinate

### 2017-03-29 three_melt_rates.py

@@ -140,7 +140,7 @@ def main(args):
 					xlabel='x (km)',ylabel='', ylim_min=ylo,ylim_max=yhi, return_handle=True)	
 					#title=Title_list[k],xlabel='x (km)',ylabel='', ylim_min=ylo,ylim_max=yhi, return_handle=True)	
 			#plt.plot(xvec,grounding_line, linewidth=3.0,color='black')
-			text(1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+			text(0.1,1,letter_labels[k], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 
 			if k==0:
 				plt.ylabel('y (km)',fontsize=20)

### 2017-03-29 Two_panel_schematic.py
moving labels left

@@ -26,11 +26,11 @@ if __name__ == '__main__':
 	#ax=plt.subplot(1,2,1)
 	ax = plt.gcf().add_axes([0.02,0.1,.6,.6]);
 	ax.imshow(im_schematic); plt.axis('off')
-	ax.text(1,1,'(a)', ha='right', va='bottom',transform=ax.transAxes,fontsize=15)
+	ax.text(.12,0.97,'(a)', ha='right', va='bottom',transform=ax.transAxes,fontsize=15)
 	#ax=plt.subplot(1,2,2)
 	ax = plt.gcf().add_axes([0.5,0.15,.5,.5]);
 	ax.imshow(im_hexaberg); plt.axis('off')
-	ax.text(1,1,'(b)', ha='right', va='bottom',transform=ax.transAxes,fontsize=15)
+	ax.text(.12,0.97,'(b)', ha='right', va='bottom',transform=ax.transAxes,fontsize=15)
 		
 	#plt.gca().annotate('Ocean mesh', xy=(x+.05,y-0.05), xytext=(x+0.1,y-0.5),
 	#			   arrowprops=dict(arrowstyle='->', connectionstyle='arc3,rad=.2'))

### 2017-03-29 regular_towards_coast.m

@@ -116,6 +116,7 @@ figure;
 colormap(blue_white)
 
 letter_list=['(a)';'(b)';'(c)';'(d)'];
+letter_list=[' ';' ';' ';' '];
 hold on
 count=0;
 plot_count=0;

### 2017-03-29 snapshots.py
More updates

@@ -316,7 +316,6 @@ def main(args):
 			datamap=plot_data_field(data1,x,y,vmin,vmax,flipped,colorbar=False,cmap=cmap,title=title,xlabel='x (km)',ylabel='',ylim_min=ylim_min,\
 					ylim_max=ylim_max,colorbar_units=args.colorbar_units,return_handle=True)  
 
-			#text(1,1,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 			text(0.1,1,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 			if n==0:
 				plt.ylabel('y (km)',fontsize=20)
@@ -403,7 +402,7 @@ def main(args):
 			#CS = contourf(y1, z1[, data1_tmp,levels=levels1, hatches=[' '], fill=False,cmap='Greys',norm=cNorm2 )
 			#print data1
 			
-			text(1,1,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+			text(0.075,1.0,letter_labels[n], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
 			if n==2:
 				plt.xlabel('y (km)',fontsize=20)
 			if n<2:

### 2017-05-10 Scripts_for_ice_shelf_paper/Fig_static_solo_melt.sh
Adding a directory for Figures from Lagrangian ice shelf paper

@@ -1,0 +1,2 @@
+cd ../
+./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=110.0 -ylim_max=370.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 

### 2017-05-10 Scripts_for_ice_shelf_paper/Fig_static_solo_melt.sh
Small figure update

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=110.0 -ylim_max=370.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 
+./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=100.0 -ylim_max=380.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 

### 2017-05-10 Scripts_for_paper_figures/Fig_static_solo_melt.sh

@@ -1,2 +1,0 @@
-cd ../
-./static_shelf_solo.py -plot_horizontal_field=True -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 

### 2017-05-10 Scripts_for_ice_shelf_paper/Fig_static_solo_melt.sh
Added lables to BT_comparison Figure

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=100.0 -ylim_max=380.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 
+./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=100.0 -ylim_max=380.0 -melt_vmax=6.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 

### 2017-05-10 Scripts_for_paper_figures/Fig_BT_comparison.sh

@@ -1,2 +1,0 @@
-cd ../
-./static_shelf_comparison.py -fields_to_compare=plot_bt_stream_comparison -save_figure=True 

### 2017-05-10 static_shelf_comparison.py

@@ -565,7 +565,8 @@ def main(args):
 	Berg_ocean_file=Berg_path+'00010101.ocean_month.nc'
 	Berg_iceberg_file=Berg_path+'00010101.icebergs_month.nc'
 
-
+	#Other
+	letter_labels=np.array(['(a)','(b)','(c)','(d)','(e)'])
 
 	#Load static fields
 	(depth, shelf_area, ice_base, x,y, xvec, yvec)=load_static_variables(ocean_geometry_filename,ice_geometry_filename,ISOMIP_IC_filename,rotated)	
@@ -616,21 +617,26 @@ def main(args):
 
 		data1=calculate_barotropic_streamfunction(Shelf_ocean_file,depth,ice_base,time_slice='mean',time_slice_num=-1,rotated=rotated)
 		data2=calculate_barotropic_streamfunction(Berg_ocean_file,depth,ice_base,time_slice='mean',time_slice_num=-1,rotated=rotated)
-		plt.subplot(1,3,1)
+		ax=plt.subplot(1,3,1)
 		plot_data_field(data2,x,y,vmin,vmax,flipped,colorbar=True,cmap=cmap,title='Lagrangian',\
 				xlabel='x (km)',ylabel='y (km)',colorbar_shrink=0.5,colorbar_units='(Sv)')	
                 plt.plot(xvec,grounding_line, linewidth=3.0,color='black')
                 plt.plot(xvec,ice_front, linewidth=3.0,color='black')
-		plt.subplot(1,3,2)
+		text(0.1,1,letter_labels[0], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+		
+		ax=plt.subplot(1,3,2)
 		plot_data_field(data1,x,y,vmin,vmax,flipped,colorbar=True,cmap=cmap,title='Eularian',\
 				xlabel='x (km)',ylabel='',colorbar_shrink=0.5,colorbar_units='(Sv)')	
                 plt.plot(xvec,grounding_line, linewidth=3.0,color='black')
                 plt.plot(xvec,ice_front, linewidth=3.0,color='black')
-		plt.subplot(1,3,3)
+		text(0.1,1,letter_labels[1], ha='right', va='bottom',transform=ax.transAxes,fontsize=20)
+		
+		ax=plt.subplot(1,3,3)
 		plot_data_field(data1-data2,x,y,-vmax, vmax, flipped,colorbar=True,cmap='bwr',title='Difference',\
[…]

### 2017-05-10 static_shelf_solo.py

@@ -117,6 +117,9 @@ def parseCommandLine():
 		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
 
 
+	parser.add_argument('-melt_vmax', type=float, default=10.0,
+		                        help='''Maximum melt rate used for plotting colorbar (only applies to melt, temp, ustar figure)''')
+
 
         optCmdLineArgs = parser.parse_args()
         return optCmdLineArgs
@@ -246,7 +249,7 @@ def main(args):
 			vmax_list=np.array([3.0, -0.5, 0.001])
 			if use_ALE is True:
 				vmin_list=np.array([0.0, -1.9, 0.0])
-				vmax_list=np.array([10.0, -0.5, 0.005])
+				vmax_list=np.array([args.melt_vmax, -0.5, 0.005])
 			cmap_list=np.array(['jet', 'jet', 'jet'])
 			mask_grounded=np.array([True,True, True])
 			#mask_open_ocean=np.array([True,False, True])

### 2017-05-10 Scripts_for_ice_shelf_paper/Fig_static_solo_melt.sh
More figure updates

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=100.0 -ylim_max=380.0 -melt_vmax=6.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 
+./static_shelf_solo.py -plot_horizontal_field=True -ylim_min=100.0 -ylim_max=380.0 -melt_vmax=7.0  -three_fields_flag=plot_melt_sst_ustar_berg -time_slice=mean -save_figure=True 

### 2017-05-10 static_shelf_comparison.py

@@ -57,6 +57,14 @@ def parseCommandLine():
 	parser.add_argument('-only_shelf_ALE', type='bool', default=False,
 		                        help=''' When true, Figures compares Shelf ALE and Layer (must be used with use_ALE=True ''')
 
+
+	parser.add_argument('-ylim_min', type=float, default=0.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+
+	parser.add_argument('-ylim_max', type=float, default=480.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
+
+
 	optCmdLineArgs = parser.parse_args()
 	return optCmdLineArgs
 
@@ -579,6 +587,10 @@ def main(args):
 	#fig = plt.figure(facecolor='black')
 	ax = fig.add_subplot(111,axisbg='gray')
 
+	#Scale
+	ylim_min=args.ylim_min
+	ylim_max=args.ylim_max
+
 	######################################################################################################################
 	################################  Plotting melt comparison  ##########################################################
 	######################################################################################################################
@@ -586,22 +598,48 @@ def main(args):
 	if fields_to_compare=='plot_melt_comparison':
 		vmin=0.0  ; vmax=3.0  ; vdiff=3.0
 		if use_ALE is True:
-			vmin=0.0  ; vmax=8.0  ; vdiff=8.0
+			vmin=0.0  ; vmax=7.0  ; vdiff=8.0
 		flipped=False
 		field='melt'
 
 		data1=load_and_compress_data(Shelf_ocean_file,field='melt',time_slice='mean',time_slice_num=-1,rotated=rotated)
 		data2=load_and_compress_data(Berg_iceberg_file,field='melt_m_per_year',time_slice='mean',time_slice_num=-1,rotated=rotated) #field name is difference since it comes from a diff file.
 
+		#Masking out ocean and grounded ice
+		mask_open_ocean=True
+		if mask_open_ocean == True:
+			mask_ocean_using_bergs=True
[…]

### 2017-05-22 Lagrangian_MISOMIP.tex
Updated version of Ice shelf paper, plus more Figures

--- 2017-02-24 Lagrangian_MISOMIP.tex
@@
 
-Iceberg calving is an important feature of the Antarctic environment, and accounts for approximately half of Antarctic ice-shelf decay. 
-However, despite its importance, the current generation of ocean models are unable to represent iceberg calving in a physically realistic way.
-This is because current models of ice-shelf cavities represent the ice shelf on an static Eularian grid, which does not lend itself to modeling drifting icebergs. 
-In this study we develop a new ice-shelf cavity model where the ice shelf is represented on a `Lagrangian grid'.
-In this model, the ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
+The calving of large tabular icebergs away from Antarctic ice shelves is an important feature of the Antarctic environment, and accounts for approximately half of Antarctic ice-shelf decay. 
+However, despite its importance, the current generation of ice-ocean models is unable to represent ice-shelf calving in a physically realistic way.
+One reason for this is that current ice-shelf models are mostly built on static Eularian grids, and were not designed to easily allow pieces of the ice shelf to break off and become icebergs. 
+In this study we develop a new ice-shelf cavity model where the ice shelf is constructed out of Lagrangian elements that are bonded together by numerical bonds.
 This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-We test the model by simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). 
-We then compare the results to a second simulation that uses an Eularian ice shelf with an otherwise identical configuration.
+We test newly developed Lagrangian ice -shelf model by simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
+The Lagrangian model results are compared to a second simulation that uses an Eularian ice shelf with an otherwise identical configuration.
 Results show that the Lagrangian and Eularian models are almost indistinguishable.
 % For example, differences in the models are two orders of magnitude smaller than the differences observed when changing the ocean model coordinate system. 
-The similarly between the Eularian and Lagrangian models provides a proof of concept for the Lagrangian model, and means that we can confidently use this model to extend the capabilities of the Eularian model.% The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
+The similarly between the Eularian and Lagrangian models in a static ice-shelf configuration provides a proof of concept for the Lagrangian model, and means that we can confidently use Lagrangian ice-shelf models to extend the capabilities of the Eularian models.% The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
 
@@
 \textbf{Key Points:}\\
-
-% \end{article} must follow the references section, before the figures
+\begin{itemize}
+\item A novel modeling framework is developed to model breakable ice shelves and ice-shelf cavities using Lagrangian elements, held together by numerical bonds.
+\item The ocean circulation beneath a (static) Lagrangian ice shelf is almost indistinguishable from the circulation beneath an Eularian ice-shelf model run in an identical configuration. 
+\item The similarity between the models provides a proof of concept for the Lagrangian model, allowing the Lagrangian model to be used simulations involving tabular iceberg calving. 
+\end{itemize}
+
 %  and tables.
@@
 Beneath the ice shelves, both the bottom topography and the ice-shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}.
-The topographic constraint imposed by the ice shelf at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean in this region a unique character.
+The topographic constraint imposed by the ice shelves at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean in the region a unique character.
 
@@
 As far as we know, all models of ice-shelf cavities to date have omitted ice-shelf breaking and iceberg detachment.
-This is because (i) there is much uncertainty of the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on a static Eularian grids, which do not lend themselves to modeling drifting icebergs.
+This is because (i) there is much uncertainty of the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on static Eularian grids, which do not lend themselves to modeling iceberg detachment and drift.
 In contrast, existing {\it iceberg} models represent icebergs as Lagrangian particles, since this is a convenient way to model discrete objects traveling over large distances \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
@@
 In this study we develop a new ice-shelf cavity model where the ice shelf is represented on a `Lagrangian grid'.
-In this model, the ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds.
+In this model, the ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds (see schematic Figures \ref{fig:Schematic}).
 This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-Figures \ref{fig:Spread_area} and \ref{fig:Temperature_section_Collapse}, which show a tabular iceberg drifting away an idealized ice shelf, demonstrate the enhanced capabilities of this Lagrangian model (see \citet{Stern2017} for more details).
+An example of this enhanced capability of the Lagrangian model is demonstrated in Figures \ref{fig:Iceberg_calving}, which shows a tabular iceberg drifting away an idealized ice shelf (see \citet{Stern2017} for more details).
 
@@
 For this comparison, we use the model configuration developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). 
-The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, and (ii) to prove that the Lagrangian model can replicate the behavior of an Eularian ice-shelf model when modeling static ice shelves.
-%In particular, we aim to show that for a static ice shelf, Lagrangian ice shelf model gives the same results as an Eularian model in the same configuration (using the same ocean model). 
-Demonstrating this is a prerequisite for moving beyond the capabilities of the Eularian model, and increases our confidence in more complex simulations involving calving icebergs. 
-%An analysis of an ice shelf cavity with a tabular iceberg drifting away from the from the ice shelf is provided in a separate study \citep{Stern2017}.
+The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, and (ii) to prove that the Lagrangian model can replicate the behavior of an Eularian ice-shelf model when modeling ocean cavities beneath static ice shelves.
+%In particular, we aim to show that for a static ice shelf, Lagrangian ice-shelf model gives the same results as an Eularian model in the same configuration (using the same ocean model). 
+Demonstrating that the Lagrangian model compares well to more traditional Eularian models is a prerequisite for using the Lagrangian model to move beyond the capabilities of the Eularian model, and increases our confidence in more complex Lagrangian simulations involving calving icebergs.
+%An analysis of an ice-shelf cavity with a tabular iceberg drifting away from the from the ice shelf is provided in a separate study \citep{Stern2017}.
 
@@
 \section{Lagrangian model description}
-This section provides a brief description of the Lagrangian Tabular Iceberg Model (LTAM), which is used to construct the Lagrangian ice shelf used in this study.
-A detailed description of the LTAM, including many of the technical details involved in constructing the model, can be found in \citet{Stern2017}.
-
-\subsection{Lagrangian grid}
-The LTAM is a discrete element model (DEM) in that the objects of the model are Lagrangian elements.
-Each Lagrangian element represents a mass of ice which is floating in the ocean.
+The Kinematic Iceberg Dynamics (KID) model is Lagrangian model that has been developed in order to simulate ice-shelf cavities with breakable ice shelves.
+The model represents ice shelves using Lagrangian elements joined together by numerical bonds.
+By breaking these bonds, the model is able to simulate ice-shelf calving and iceberg breakup.
+
+The goal of this study is to show that this Lagrangian ice-shelf model can replicate the results of an Eularian ice-shelf model when used in a static ice-shelf configuration (with all the elements being held stationary).
+Although the ice elements do not move in the static ice-shelf experiment, this configuration is a relevant test for the Lagrangian model, as it tests the interpolation and aggregation between Eularian and Lagrangian grids, and also test the coupling between the ocean and ice-shelf models.
+Benchmarking the Lagrangian ice-shelf model to an existing Eularian model in a static ice-shelf configuration is a prerequisite for using the Lagrangian model in more complex experimental setups with moving elements.
+
+In this section we briefly describe the fully dynamic Lagrangian ice-shelf model.
+We then focus on element packing and interpolation between the Eularian and Lagrangian grids, which are the parts of the model which are relevant to static ice simulations.
+A complete description of the KID model, including details of the momentum budget and element interactions can be found in \citet{Stern2017}.
+
+\subsection{Kinematic Iceberg Dynamics model}
+The KID model is a Lagrangian particle-based model, in that the objects of the model are Lagrangian elements.
+Each Lagrangian element represents a column of ice that is floating in the ocean.
 The elements each have their own position, velocity, mass, and a set of dimensions, which can evolve in time.
 Each element moves according to its own momentum equation which is solved in the (Lagrangian) reference frame of the element.
-The elements are forced by oceanic, sea ice and atmospheric drag forces, as well as a force due to sea surface height gradients and the Coriolis force.
-As the elements drift, they decay according to melt parametrization.
-The elements can also be `bonded' together by numerical bonds, which hold the elements together and allow many elements to move together as a unit.
-By bonding many ice elements together, the LTAM model is able to form larger structures, such as tabular icebergs or (non-dynamic) ice shelves.
-
-When constructing ice shelves using the LTAM model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
-In this Lagrangian grid, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
+The elements are forced by oceanic, sea ice and atmospheric drag forces, as well as a forces due to sea surface height gradients, and the Coriolis force \citep{Bigg1997, Gladstone2001, Martin2010, Stern2017}.
+The elements also interact with other elements and can be `bonded' together by numerical bonds, which hold the elements together and allow many elements to move together as a unit.
+By bonding many ice elements together, the model is able to form larger structures, such as tabular icebergs or ice shelves (see schematic Figures \ref{fig:Schematic}).
+% The interactive forces between elements aggregate to give the larger structures an effective rheology.
+
+The Lagrangian elements melt when they are exposed to above-freezing ocean mixed-layer temperatures.
+The melt rates of the elements are prescribed using parametrizations developed for iceberg and ice-shelf decay \citep{Bigg1997, Holland1999, Gladstone2001, Martin2010}.
+As the elements melt, heat, salt and mass fluxes are passed to the ocean to simulate freshwater injection to the ocean surface.
+% In this study we focus on comparing the model to a Eularian model, so the melt rate of elements is determined using the three equation model for basal melt, which is a typical melting parametrization used beneath ice shelves \citep{Holland1999}.
+
+\subsection{Initializing element geometry and packing}
+The elements in the Lagrangian model are assumed to have surface areas which are shaped as equally-sized regular hexagons.
+We initialize the Lagrangian model by positioning the elements in a staggered lattice, so that the elements fit together and perfectly tile the ice-shelf surface (Figures \ref{fig:Schematic}b).
+Hexagonal elements are used so that when adjacent pairs of elements are bonded together, the network of bonds form equilateral triangles, which gives rigidity to the larger structure \citep{Stern2017}.
+
+\subsection{Interpolation and aggregation onto the Lagrangian grid}
+When constructing ice shelves using the Lagrangian model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
+In this framework the nodes of the Lagrangian grid (elements) can move at every time step, altering the shape of the ice shelf.
 This is in contrast to the more traditional approach of modeling ice shelves on an Eularian grid, where the grid is fixed in time.
-The major advantage of modeling ice shelves using a Lagrangian grid is that the grid is not static, which means that we can simulate pieces of ice breaking away from the ice shelf to form icebergs that drift in the open ocean (Figures \ref{fig:Spread_area}, \ref{fig:Temperature_section_Collapse}).
-One consequence of using Lagrangian elements for the ice-shelf grid is all variables need to be interpolated from the `Lagrangian grid' onto the Eularian ocean grid in order to be passed to the ocean model.
-The details of this interpolation are discussed below.
-
-\subsection{Interaction with the ocean}
-Since the LTAM model uses a Lagrangian grid, all of the ice shelf information is stored with the elements.
-At every time step, this information has to be interpolated from the Lagrangian grid to (Eularian) ocean grid, so that it can be passed to the ocean model.
-The interpolation from the Lagrangian grid to the Eularian ocean grid is done by assuming that the elements have surface areas that are shaped as regular hexagons.
-Element's properties are `spread' from the Lagrangian grid to the Eularian grid by exactly calculating fraction of an elements surface area that is contained in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
-
-Five fields are `spread' from the Lagrangian to Eularian grids at each time step: mass, surface area, temperature flux, salinity flux and mass flux.
-Once these five fields are in hand, the LTAM mode interacts with the ocean model in exactly the same way the Eularian model does.
-As in Eularian ice-shelf models, these fields are passed to the ocean model and are used to:
-(i) apply a pressure to the ocean surface, 
-(ii) alter the upper-ocean boundary condition to reflect that the ocean is covered by ice,
-and (iii) apply salt, temperature and mass fluxes associated with ice-shelf melting and freezing.
-
-The ocean is sensitive to small changes to the ocean surface pressure, which can trigger barotropic ocean waves.
-This means that accurately interpolating fields from the Lagrangian to Eularian grids is the key to making the Lagrangian ice-shelf model behave like the Eularian ice-shelf model for using static ice-shelf simulations.
-Ocean mixed layer properties are passed from ocean model to the LTAM model, and are interpolated onto the elements using a bilinear interpolation.
-The model is less sensitive to the details of this interpolation.
-%In the next section we use an idealized setup to demonstrate that this is done correctly in the LTAM model.
-
-%Elements are initially arranged in regular staggered lattice so that the they are perfectly packed together
-%For example, consider a hexagonal element which is positioned such that it intersects four ocean grid cells (Figure \ref{fig:Hex_intersections}b). In this situation,r.
+Using a Lagrangian grid is a convenient framework for modeling breakable ice shelves since it allows pieces of the ice-shelf grid to break away from the ice shelf and become part of the iceberg grid \citep{Stern2017}.
+
+In the experiments presented in this study, the ice-shelf model is coupled to an ocean model, which is runs on a static Eularian grid.
+At every time step, ice-shelf fields are passed from the ice-shelf model to the ocean model and from the ocean model to the ice-shelf model.
+Four ocean (mixed layer) fields are passed from the ocean model to the ice-shelf model: temperature, salinity and zonal and meridional velocities.
+These fields are interpolated onto the Lagrangian grid (i.e.: onto the elements in the ice-shelf model) using a bilinear interpolation scheme.
+
+At the end of a ice-shelf model time step, ice-shelf fields are aggregated from the elements back onto the Eularian ocean grid, and are then passed from the ice-shelf model to the ocean model.
+The aggregation from the Lagrangian grid to the Eularian ocean grid is done in a way which is consistent with the shape of the elements.
+For the purposes of aggregation, we assume that the elements have surface areas that are shaped as regular hexagons.
+Element's properties are aggregated from the Lagrangian grid to the Eularian grid by exactly calculating fraction of an elements surface area that is contained in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
+
+\subsection{Lagrangian vs Eularian ice-shelf model}
+In the next section, simulations using the Lagrangian ice-shelf model are compared to simulations using an Eularian ice-shelf model with an an identical configuration.
+While the internal framework and grids of the Eularian and Lagrangian ice-shelf models are quite different, both models are coupled to the ocean model using the same coupling structure.
+Five fields are passed from the ice-shelf models to ocean model: mass, surface area, temperature flux, salinity flux and mass flux.
+The Eularian model uses the same grid as the ocean model, while in the Lagrangian model these fields are aggregated onto the ocean model grid before being passed through the coupler.
+Once in the ocean model, these fields and are used to: (i) apply a pressure to the ocean surface, (ii) alter the upper-ocean boundary condition to reflect that the ocean is covered by ice, and (iii) apply salt, temperature and mass fluxes associated with ice-shelf melting and freezing.
+
+Since the coupling with the ocean model is handled in the same way for both the Eularian and Lagrangian models and both models are coupled to the same ocean model, any differences between the two models in the static ice-shelf configuration (using the same melt rate parametrization) are likely due to the interpolation/aggregation between the ice and ocean grids.
+By accurately aggregating fields from the Lagrangian grid to Eularian ocean grids, we can make the Lagrangian ice-shelf model behave like the Eularian ice-shelf model in static ice-shelf simulations.
+%Apart from the step of aggregating between the Lagrangian and Eularian grids, the interaction between the Lagrangian ice-shelf model and ocean model is exactly the same as the interaction between an Eularian ice-shelf model and an ocean model.
 
@@
 % the proof of concept for
-The LTAM model is used to simulate the flow within an idealized ice-shelf cavity.
+The KID model is used to simulate the flow within an idealized ice-shelf cavity.
 The simulations are repeated using an Eularian ice shelf with an identical configuration.
@@
 The ice shelf is grounded on the southern side of the domain with the ice-shelf front at y=650km.
-The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference.
+The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}.
 The configuration is the same as that of the Ocean0 setup in the MISOMIP, with three changes made:
@@
 The numerical simulations were all repeated using an isopycnal coordinate (without ALE regrinding-remapping).
-The results were qualitatively similar to the ALE results.
-All results presented below are from the ALE simulations, unless specified otherwise.
-
-Ocean parameters are shown in Table 1 and are specified in the MISOMIP configuration \citep{Asay-Davis2016}.
+The results were qualitatively similar to the ALE results, and are therefore not presented here.
+% All results presented below are from the ALE simulations, unless specified otherwise.
+
+The ocean parameters used in the simulations are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
 The simulation is initialized from rest, with horizontally uniform initial ocean temperature and salinity profiles which vary linearly between specified surface and bottom values: $T_{top}=-1.9^{\circ}$C, $T_{bottom}=1.0^{\circ}$C, $S_{top}=33.8$ psu, $S_{bottom}=34.7$.
 The maximum ocean depth is $H_{ocean}=720$ m.
-A sponge layer is used on the northern boundary, which relaxes back to the initial temperature and salinity with a relaxation time scale of $T_{sponge}=0.1$ days.
+A sponge layer is used on the northern boundary, which relaxes back to the initial temperature and salinity with a relaxation time scale of $T_{sponge}=0.1$ days over a distance of 10 km.
 Melting is set to zero for ocean cells where the ocean column thickness is less than 10m.
@@
 Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
-The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the 'mass-spreading' interpolation procedure discussed in Section 2.2.
+The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the aggregation procedure discussed in Section 2.3.
 
@@
 The ice shelf is initialized on the same grid as the ocean model with a horizontal resolution of $\Delta x = 2$ km.
-The ice-shelf thickness field is using the same ice-shelf draft used for the Lagrangian model (Figure \ref{fig:ISOMIP_mass_and_topog}b).
+The ice-shelf thickness field is initialized using the same ice-shelf draft used for the Lagrangian model (Figure \ref{fig:ISOMIP_mass_and_topog}).
 
 %\subsection{Eularian ice shelf simulation:}
-\subsection{ice-shelf motion and decay}
+\subsection{Ice-shelf decay}
 The melt rates in both the Lagrangian and Eularian ice-shelf simulations are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}.
@@
 In both simulations, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
-In this setup, ice-shelves melting generate temperature and salinity fluxes into the ocean, but do not change the thickness of the ice shelf / ice elements.
+In this setup, ice-shelf melting generates temperature and salinity fluxes into the ocean, but does not change the thickness of the ice shelf / ice elements.
 This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
-The models are spun up for 5 years, and results are considered after the spinup period.
+%The simulation is run for 5 years, and results are considered after the spinup period.
 
@@
 The results from the Lagrangian ice-shelf simulation fit within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
-The initial water temperatures inside the domain are warmer than the in-situ freezing point, and cause melting at the ice-shelf base.
-The melt water entering the domain is more buoyant than the water around it, and rises  along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_temp_v}b, c).
-As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_temp_v}b).
+The ocean temperatures inside the domain are warmer than the in-situ freezing point (Figure \ref{fig:static_solo_temp_v_v}a), and cause melting at the ice-shelf base (Figure  \ref{fig:static_solo_melt}c).
+The meltwater entering the domain is more buoyant than the water around it, and rises along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_v_v}).
+%As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_v_v}a).
 This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water, which provides the thermal energy required for continuous ice-shelf melt.
@@
 These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front.
-
-%\subsubsection{Comparison with Eularian ice shelf model}
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front (Figure  \ref{fig:static_solo_melt}c).
+
+%\subsubsection{Comparison with Eularian ice-shelf model}
 \subsection{Comparison of Lagrangian and Eularian ice-shelf models}
-The LTAM results from the static ice-shelf experiment are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration.
+The Lagrangian ice-shelf model results are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration (see Section 3.4).
 To get a quantitative comparison, we compare the Lagrangian ice-shelf model results to a simulation using an Eulerian ice-shelf model with an identical configuration.
 The results show that two simulations are almost indistinguishable.
-This is the case both for simulations using the ALE-hybrid vertical coordinate system and the isopycnal vertical coordinate.
-The Lagrangian and Eularian models are have very similar circulations (Figures \ref{fig:Bt_comparison}), melt rates (Figures \ref{fig:Melt_comparison}) temperature/salinity profiles (Figures \ref{fig:Salt_comparison}).
-The differences between the barotropic stream functions of the two simulations(for example), are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems (Figures \ref{fig:Bt_comparison} and \ref{fig:layer_Bt_comparison}).
-
-The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
+This is demonstrated, for example, in Figures \ref{fig:Bt_comparison}, which shows the time-averaged barotropic stream function of the Lagrangian (Figures \ref{fig:Bt_comparison}a) and Eularian (Figures \ref{fig:Bt_comparison}b) simulations, and the difference between the two (Figures \ref{fig:Bt_comparison}c).
+%For scale, we note that the differences between the barotropic stream functions in the two simulations, are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems described in Section 3.2 (not shown).
+The difference between the Lagrangian and Eularian barotropic stream functions are two orders of magnitude smaller than typical differences observed between simulations using different models in the MISOMIP \citep{Asay-Davis2016}.
+The similarity of the Lagrangian and Eularian simulations are also reflected in the fact that the simulations have very similar ice-shelf melt rates and ocean temperature/salinity profiles (shown in Figures \ref{fig:Melt_comparison} and Figures \ref{fig:Salt_comparison} in the supplementary materials).
+
+%This is the case both for simulations using the ALE-hybrid vertical coordinate system and the isopycnal vertical coordinate (not shown).
+
+%The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
 Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes to the ocean, and (iii) alter the upper ocean boundary condition below the ice shelf.
-The agreement between the Eularian and Lagrangian simulations is a confirmation that these three tasks are being done correctly within the LTAM model, and that the LTAM is able to model sub-ice-shelf cavities as well as the Eularian model does.
+The agreement between the Eularian and Lagrangian simulations is a confirmation that the Lagrangian model is able to simulate sub-ice-shelf cavities as well as the Eularian model does.
 This is a good starting point for moving beyond the capabilities of the Eularian model.
@@
 %In order to accurately project future sea level, it is likely that we will need to develop fully-coupled global general climate models (GCM's) with dynamic ice-shelf cavities which are able to melt, break and interact with the ocean in physically realistic ways.
-This will require us to create models of ice shelf cavities with capabilities that can not currently be simulated by the current generation of ice shelf models.
+This will require us to create models of ice shelf cavities with capabilities that can not currently be simulated by the current generation of ice-shelf models.
 
@@
 Unlike Eularian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
-This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:Spread_area} and \ref{fig:Temperature_section_Collapse}).
+This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:Iceberg_calving}).
 This capability is currently not possible using more traditional Eularian models \citep{Stern2017}.
 %
-%A consequence of using a Lagrangian ice shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eularian ocean grid in order to be passed to the ocean model.
+%A consequence of using a Lagrangian ice-shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eularian ocean grid in order to be passed to the ocean model.
 This is done by exactly calculation the fraction of each ice element that lies in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
@@
 
-A direct comparison comparison between one Lagrangian and Eularian ice-shelf models showed that the results are extremely similar, and differences between the Lagrangian and Eularian ice shelves models (resulting from interpolation errors) are much smaller than the differences observed when changing the ocean vertical coordinate system (for example).
-Achieving similarity between when using a Lagrangian and Eularian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
+A direct comparison comparison between the Lagrangian and a Eularian ice-shelf model coupled to the same ocean model shows that the results are extremely similar.
+Differences between the Lagrangian and Eularian ice shelves models (resulting from interpolation errors) are much smaller than the differences observed when changing the ocean vertical coordinate system (for example).
+Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eularian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
 
@@
 % 
-%One element which is missing from the LTAM ice shelf is that the ice shelf is not dynamic.
+%One element which is missing from the KID ice shelf is that the ice shelf is not dynamic.
 Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice-shelf geometry to change over time.
@@
 A possible path towards this is to model sea ice using a Lagrangian grid \citep{Hopkins1996, Li2014}, and to treat sea ice - iceberg interactions in the same way that iceberg - iceberg interactions are treated in this study.
-A number of preliminary experiments have been run using the LTAM model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
+A number of preliminary experiments have been run using the KID model with some ice element representing collections of sea ice flows, and have yielded interesting results (to be presented elsewhere).
 % Finally, there are a number of open questions about how to correctly link tabular icebergs to ocean biology by allowing for icebergs to have nutrient concentration (especially iron).
@@
 Goosse, and H.
-Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104–113.
+Renssen (2009), The effect of dynamic-thermodynamic icebergs on the Southern Ocean climate in a three-dimensional model, {\it Ocean Modell.}, 26, 104Ð113.
 
@@
 \bibitem[Tournadre et al (2016)]{Tournadre2016}
-Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. Rémy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.
+Tournadre, J., N. Bouhier, F. Girard-Ardhuin, and F. RŽmy (2016), Antarctic icebergs distributions 1992-2014. {\it J. Geophys Res: Oceans}.
 
 \bibitem[Vernet et al (2012)]{Vernet2012}
-Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38–39
+Vernet, M., et al. (2012), Islands of ice: Influence of free-drifting Antarctic icebergs on pelagic marine ecosystems, {Oceanography}, 25(3), 38Ð39
 
@@
  \end{article}
-\section{New Figure ideas:}
-1) Combine Figure 1 and Figure 2 into a new figure (so that this paper uses different figures to the tabular iceberg paper)\\
-\\
-2) Figure showing the layout of hexagons, which is different to the tabular iceberg paper - perhaps have hexagons directly over ice shelf draft?\\
-\\
-3) Combine the barotropic stream function figure for layered into one figure.
-
-\section{Things to think about:}
-1) The dynamics of the ice elements are not related to ice shelf dynamics. This needs to be explained somehow/somewhere.\\
-
- \clearpage
 
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
-\caption{ {Snapshots of the fraction of ice cover in the LTAM tabular iceberg calving simulation.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The dashed line in panel (c) shows the location of the vertical transects shown in Figure \ref{fig:Temperature_section_Collapse}}.}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Two_panel_schematic_shelf.png}
+\caption{ {Schematic showing how ice shelves and tabular icebergs are constructed using Lagrangian elements. 
+(a) Schematic of multiple ice elements that are joined together by numerical bonds (magenta lines) to form larger structures such as ice shelves and tabular icebergs.
+These numerical elements have finite extent and are able to interact with the ocean across multiple grid cells, and can interact with other elements.
+(b) Areal photograph of an ice shelf and tabular iceberg with elements superimposed over it to illustrate how the Lagrangian elements can be used to model ice shelves and tabular icebergs.
+In this schematic the ice elements (purple dots) are initialized in a staggered lattice covering the surface area of the iceberg.
+For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (red hexagons).
+For purposed of element interactions, the ice elements are assumed to be circular (black circles).
+Elements are initially bonded to adjacent elements using numerical bonds (magenta lines).
+These numerical bonds form equilateral triangles which give the shape rigidity.
+An ocean grid has been included (dashed cyan lines).
+%The background photo in the larger schematic is an areal photograph of iceberg PIIB (Area= 42 $\textrm{km}^{2}$) taken in Baffin Bay in 2012.
+The red ship can be identified on the bottom of the photo for scale.
+%Schematic showing how Lagrangian elements are used when modeling tabular icebergs.
+Lagrangian elements (blue dots) are initialized in a staggered lattice covering the surface area of the iceberg.
+For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (grey hexagons).
+For purposed of element interactions, the ice elements are assumed to be circular (black circles).
+Elements are initially bonded to adjacent elements using numerical bonds (dashed white lines).
+These numerical bonds form equilateral triangles which give the shape rigidity.
+%The inset panel shows a schematic of the intersection of a hexagonal element and the ocean grid.
+The colors indicate the fraction of the hexagon that lies in each grid cell.
+These fractions are used as weights to spread iceberg model properties to the ocean grid (see text for more details).
+}}
 \end{center}
-\label{fig:Spread_area}
+\label{fig:Schematic}
 \end{figure}
  \clearpage
-
+-
 \begin{figure}
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_temp_layers_x10.png}
-\caption{ {Snapshots of vertical sections of ocean temperature at $x=58 $km in the LTAM tabular iceberg calving experiment.
-Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving.
-The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:Spread_area}c.}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
+\caption{ {Snapshots of a simulation where a Lagrangian ice-shelf calves a tabular iceberg viewed (a) from above and (b) from the side.
+The snapshots is taken 30 days after calving.
+Panel (a) shows the sea surface temperature.
+Grid cells with ice mass $>10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.
+Panel (b) shows a vertical sections of ocean temperature at $x$=54~km.
+The position of the vertical section is shown by the dashed line in panel (a).
+The solid line in panel (a) shows the position of the grounding line.}}
 \end{center}
-\label{fig:Temperature_section_Collapse}
+\label{fig:Iceberg_calving}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_spread_mass_mass.png}
-\caption{ {(a) Ocean bottom topography and (b) ice-shelf draft used to initialized the tabular iceberg calving simulation.
-The ice draft is calculated from the total mass in an ocean grid cell after the mass-spreading interpolation has been applied (as explained in Section 2.2).
-(c) Initial ice draft that would be calculated if the mass-spreading interpolation were not used (i.e.: elements treated as point masses).}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Lagrangian_shelf_domain.png}
+\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eularian static ice-shelf simulations}}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_temp_v.png}
-\caption{ {Results of the static ice-shelf experiment using the LIISM model coupled to MOM6.
-Panels show cross sections of the (a) initial temperature field, (b) temperature anomaly after 5-years (relative the the initial field), and (c) meridional velocity near the ice-shelf base after 5 years of simulation.
-The region shown in panel (c) is indicated by the black box on panel (b),}}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
+\caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model.
+Panels show cross sections of the (a) ocean temperature anomaly relative the the initial temperature, and (b) the meridional ocean velocity.
+Panel (c) again shows the meridional ocean velocity, and is zoomed into the region near the ice-shelf base (the zoomed-in region is indicated with a black box (b)).}}
 \end{center}
-\label{fig:static_solo_temp_temp_v}
+\label{fig:static_solo_temp_v_v}
 \end{figure} 
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Results of the static ice-shelf experiment using the LIISM model coupled to MOM6.
-The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
+\caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6.
+The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean temperature and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
 Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
@@
 \label{fig:Bt_comparison}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_melt.png}
-\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian Ice shelf model melt fields.}}
-\end{center}
-\label{fig:Melt_comparison}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_salt_layers.png}
-\caption{ {Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model salinity fields.}}
-\end{center}
-\label{fig:Salt_comparison}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/static_shelf_comparison_barotropic_sf.png}
-\caption{ {Layer: Comparison of Eulerian ice-shelf model and Lagrangian ice-shelf model barotropic stream function}}
-\end{center}
-\label{fig:layer_Bt_comparison}
 \end{figure}
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_spread_area.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_Iceberg_calving.png}
 %\caption{ {Need to update this Figure. Also, I should try using orientation with the Bonds.}}
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_melt.png}
+\caption{ {Time-averaged melt rates in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration.
+Panel (c) shows the difference between panels (a) and (b).
+The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
+\end{center}
+\label{fig:Melt_comparison}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\caption{ {Time-averaged vertical sections of salility in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration at at $x$=54~km.
+Panel (c) shows the difference between panels (a) and (b).
+The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
+\end{center}
+\label{fig:Salt_comparison}
+\end{figure}
+ \clearpage
+
  \end{document}

### 2017-06-13 static_shelf_comparison.py
New Comparison files

@@ -49,6 +49,12 @@ def parseCommandLine():
 	parser.add_argument('-fields_to_compare', type=str, default='plot_bt_stream_comparison',
 		                        help=''' This flag determine whether to plot horizontal, vertical, or special case for barotropic stream function
 					(should remove this later). Options are plot_bt_stream_comparison, plot_melt_comparison, plot_cross_section   ''')
+	
+	parser.add_argument('-field', type=str, default='melt',
+		                        help=''' Which field is plotted when horizontal comparison is used   ''')
+	
+	parser.add_argument('-file_type', type=str, default='ice',
+		                        help=''' Which file the data is loaded from when horizontal comparison is used   ''')
 
 	#Which file type to use
 	parser.add_argument('-use_title_on_figure', type='bool', default=False,
@@ -64,7 +70,31 @@ def parseCommandLine():
 	parser.add_argument('-ylim_max', type=float, default=480.0,
 		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
 
+	parser.add_argument('-vmin', type=float, default=0.0,
+		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
 
+	parser.add_argument('-vmax', type=float, default=7.0,
+		                        help='''Max value used in colorbar for plotting (only applies to horizontal sections)''')
+	
+	parser.add_argument('-vdiff', type=float, default=8.0,
+		                        help='''Anomaly value used in colorbar for plotting (only applies to horizontal sections)''')
+	
+	parser.add_argument('-time_slice', type=str, default=' ',
+		                        help='''Decides which time slice to use (mean, all...  ''')
+	
+	parser.add_argument('-time_slice_num', type=int, default=-1,
+		                        help='''Decides which time slice to use (mean, all...  ''')
+	
+	parser.add_argument('-direction', type=str, default='xy',
+		                        help='''Decides which direction to  use  ''')
+	
+	parser.add_argument('-dir_slice', type=str, default=' ',
+		                        help='''Decides which direction slice to  use  ''')
+	
[…]

### 2017-06-13 testing_static_script.sh

@@ -1,0 +1,20 @@
+#Meridional Velocity
+#./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=VO -vmin=-0.1 -vmax=0.1 -vdiff=0.02 -time_slice=mean -time_slice_num=-1 -save_figure=True
+
+#Zonal Velocity, UO
+#./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=UO -vmin=-0.1 -vmax=0.1 -vdiff=0.02 -time_slice=mean -time_slice_num=-1 -use_ALE=True -save_figure=True
+
+#Sea Surface Temp
+#./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=SST -vmin=-2 -vmax=0 -vdiff=0.3 -time_slice=mean -time_slice_num=-1 -save_figure=True
+
+#Sea Surface Salinity
+#./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=SSS -vmin=33.6 -vmax=34.2 -vdiff=0.3 -time_slice=mean -time_slice_num=-1 -save_figure=True
+
+#Sea Surface Salinity
+#./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=SSS -vmin=33.6 -vmax=34.2 -vdiff=0.3 -time_slice=mean -time_slice_num=-1 -save_figure=True
+
+#Rho mixed layer
+#./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=Rml -vmin=1026.8 -vmax=1027.6 -vdiff=0.1 -time_slice=mean -time_slice_num=-1 -file_type=prog -save_figure=True
+
+#Mixed layer depth
+./static_shelf_comparison.py -fields_to_compare=horizontal_comparison -field=e -vmin=0 -vmax=1 -vdiff=0.5 -time_slice=mean -time_slice_num=-1 -file_type=prog -save_figure=True

### 2017-06-13 submission1/Submission2_prep/Response_to_reviews.tex
Working on JAMES revisions and Lagrangian paper

\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amscd}
\usepackage{fancyheadings}
\usepackage[usenames,dvipsnames]{color}
\usepackage{float}
\usepackage[margin=2.5cm]{geometry}

\usepackage{color}

\definecolor{light-gray}{gray}{0.75}
\definecolor{dark-gray}{gray}{0.35}

\floatstyle{boxed}
\restylefloat{figure}
\color{black}
\usepackage{lineno}
\color{black}

%\linenumbers

\begin{document}
Dear Editor,\\
\\
\\
Below are point-by-point responses covering the reviewers' individual comments. A copy of the manuscript has also been included with changes and additions recorded in red. \\
\\
Sincerely,\\
Alon Stern, on behalf of the co-authors.
\clearpage
\textbf{Reviewer 1 Evaluations:}\\
Recommendation: Return to author for minor revisions\\
Significant (Required): Yes, the science is at the forefront of the discipline.\\
Supported (Required): Yes\\
Referencing (Required): Yes\\
Quality (Required): The organization of the manuscript and presentation of the data and results need some improvement.\\
Data (Required): No\\
Accurate Key Points (Required): Yes\\
\\
Reviewer 1 (Formal Review for Authors (shown to authors)):\\
\\
The article presents a novel and very exciting new methodology to include tabular icebergs into general circulation models. The new approach uses numerical bonds to group single icebergs/ice elements with finite extent together to form tabular icebergs with complex shapes, where previously levitating point-particle icebergs with typically zero area coverage have been used. The article is an original and exciting contribution in the ongoing discussion about the inclusion of giant tabular icebergs into ocean and climate models, and therefore -in my opinion- very suitable for publication inÊJAMES.Ê\\
\\
\textcolor{red}{}\\
\\
The authors describe the model and the technical details very well, and there are only some points that should be worked out in more detail (see specific comments below). This concerns (a) details about the surface areas where the melt rates and various forces are acting on when proceeding from rectangular point-particle icebergs to (bonded) hexagonal ice elements. In contrast to the thermodynamics/melting parameterization, it is also less clear how (b) the dynamics of inner ice elements is handled, and whether these could be subject to erroneous form drags despite being actually "shielded" by means of the outer elements. Finally, (c) when exactly do the interactive forces enter the computation? Are the ice elements first allowed to drift independently, and then the velocity/position is corrected for via $F_{ia}$ (or $a_{ia}$) afterwards? This could all be suitably added to the appendix; it is important information for other model centers that apply point-particle iceberg models and which could desire to also extend their existing models with interactive bonding forces.\\
\\
\textcolor{red}{}\\
\\
As a comment, despite some obvious issues when using point-particle methods for the modeling of large tabular icebergs, there have been previous successful attempts to model tabular icebergs with the existing technology (after some modifications), and this could be mentioned in your review-like introduction as well (see specific comment below). Those studies are, i.a., Lichey and Hellmer (2001), Hunke and Comeau (2011), and Rackow et al. (2017), which are already cited in the manuscript except for Hunke and Comeau (2011).Ê
The point-particle method has been modified in the above studies in order to improve the drift representation of tabular icebergs, e.g., by (i) including sea ice-iceberg interaction, leading to increased drift speeds when icebergs are "captured" in sea ice, and (ii) by modifications to the sea surface slope force $F_{ss}$ in order to account for the vast horizontal extent of tabular icebergs, and (iii) by manually embedding icebergs into the ocean vertically, as was also done in Merino et al. (2016) (cited in l. 255).
\\
\textcolor{red}{A paragraph has been added to the introduction at line 81 which reviews some of the attempts to move beyond levitating point particle icebergs using the existing technology.} \textcolor{blue}{[Lichey and Hellmer (2001) is not discussed in details since the suggested parametrization is not related directly to the size and structure of tabular icebergs. It is cited as a paper that has modeled tabular icebergs using existing technology.]}\\
\\
Your proposed model framework is a very original idea and is able to produce impressive iceberg-iceberg and iceberg-coastline interactions, but the added value of resolving realistic collisions and ocean-embedded icebergs in a climate context is not immediately clear, and so it is a little too early to entirely deny the applicability of the simpler point-particle model to the tabular iceberg case. At some point, it would be great to see a comparison of the new methodology with the "old" one and to show the possible superiority of the new approach in a systematic manner.\\
\\
\textcolor{red}{}\\
\\
Overall, the study presents fabulous work and, I think, the fact that icebergs are finally non-levitating should be strongly emphasized, also in the abstract, because it is a real milestone as you rightly mention in lines 467-469. I recommend the paper for publication in JAMES subject to minor revisions.\\
\\
\textcolor{red}{We would like to thank the reviewer for the very favorable review of our work. We agree that the fact that icebergs are non-levitating in our new iceberg framework is an important feature which was underemphasized. We have added the word `submerged' to the paper title, and edited the abstract, introduction and conclusion to further emphasize this point.\\
\\
Line 18 in abstract has been edited and now reads: ``In this framework, tabular icebergs are represented by non-levitating Lagrangian elements that drift are submerged in the ocean.'' \\
\\
A brief discussion of levitating and non-levitating icebergs models has been added to the new paragraph in the introduction at line 81. The development of a iceberg model where icebergs are submerged in the flow (and not levitating) has been added as one of the goals of the study at line 103.\\
\\
A few words have been added to the first paragraph of the conclusion to emphasize that the iceberg models allows icebergs to be non-levitating.}\\
\\
----
Some general clarifications would further improve the paper:\\
\\
\textcolor{red}{}\\
\\
- When initializing your idealized ice shelf, the ice elements will have decreasing thickness towards the ice shelf front, correct? If the ice elements behave like icebergs in point-particle models, that would also imply different freeboards. Do you somehow enforce a level ice shelf surface? Do you generally enforce a level surface for bonded ice elements, i.e. tabular icebergs?\\
\\
\textcolor{red}{All of the ice elements are assumed to be floating in the ocean (in isostatic equilibrium), so that the mass of a column of ice is equal to the mass of water it displaces.  This means that ``the element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$'' (see line 610). Since the ice shelf is thickest at the grounding line, and gets much thinner toward the ice front, this implies that the the elevation of the ice surface decrease towards the ice front (as the reviewer correctly points out).\\
\\
The following lines have been added at line 410 to clarify: ``The initial ice thicknesses of the elements are calculated from the ice mass by assuming that the ice has a constant density, $\rho$. The draft and freeboard are related to the ice thickness by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$, where $\rho$ and $\rho_{o}$ are the density of ice and seawater respectively."} \textcolor{blue}{[Perhaps we should not add these lines to the text since they already appear in the text in the appendix? ]}\\
\\
- In the case of tabular icebergs, your bonded ice elements are ice columns that are potentially close to the limit for iceberg capsizing. Do you turn off the capsizing parameterization for bonded ice elements? Would the ice elements capsize immediately after bond breakup?\\
\\
\textcolor{red}{1) Iceberg rolling is turned off bonded icebergs. 2) All icebergs are initialized with D>??? and W=?. This means that W/D > 0.92 stability requirement. (hopefully).}\\
\\
- Have you already followed a tabular iceberg until it was completely melted? What about capsizing of a laterally strongly eroded former tabular iceberg that still consists of several bonded ice elements, is this even possible?Ê\\
\\
\textcolor{red}{}\\
\\
- From your experience, will the timestep limitation due to the interactive forces be too prohibitive for long climate model runs? What is the computational overhead when using the new framework compared to the original point-particle model code?\\
\\

----
Specific comments:\\
\\
l. 14: comma after "sea ice formation"\\
\\
\textcolor{red}{Comma has been added}\\
\\
l. 16: "the current generation of ocean circulation models do not represent" -> "the current generation of ocean circulation models usually does not represent"\\
\\
\textcolor{red}{The word `usually' has been added.}\\
\\
l. 22: I think the comma after "its breakup" should be dropped\\
\\
\textcolor{red}{Comma has been removed}\\
\\
l. 60-64: It is fair to say that these models have been mostly used for icebergs smaller than 3.5 km on a global scale, but there are also studies applying the point-particle models to tabular Antarctic icebergs (see above comment). I suggest to extend your short overview by also discussing those simpler models in order to put the new framework into a broader context.\\
\\
\textcolor{red}{A paragraph has been added to the introduction at line 81 which reviews some of the attempts to move model tabular icebergs using the existing technology.} \\
\\
l. 72-74: As far as I understand, iceberg breakup and calving is still an unresolved issue even when using bonded ice elements? The technical capability to cut an iceberg into pieces is certainly there, but the "when" and "how" is still unresolved (which bonds should be removed and why/when?). One could argue that dynamic iceberg lists in simple point-particle models already provide a similar technical capability, because an iceberg that is destined to break into pieces could simply be removed from that list and be replaced by a set of smaller child icebergs. I have the impression that not much is gained using the new methodology with regard to the exact timing/modeling of iceberg calving and break up. Maybe you can clarify the sentence and what you mean by "representation of iceberg breakup and calving".\\
\\
\textcolor{red}{We agree with the reviewer that the issue of iceberg breakup and calving is still unresolved and there is still much to be understood about the physic that govern these processes.  We do however believe the the present work provides a framework which allows iceberg calving (away from a submerged ice shelf) to be modeled more easily. Firstly, is not clear how the calving of icebergs away from a submerged ice shelf could be represented using levitating icebergs (since removing mass from the ice shelf would trigger artificial tsunamis). If icebergs are non-levitating then it becomes important that the size of the iceberg matches the size of the piece of ice calving away from the ice shelf. 
Calving icebergs can have many different structures and shapes. It is not clear how this could be represented using rectangular, circular icebergs or point particle icebergs.
Representing icebergs and ice shelves using ice elements submerged in the ocean means therefore puts fewer restrictions on possible calving laws. Similarly with icebergs breakup, it is unclear how one would represent an iceberg breaking up into two pieces with distinct shapes by introducing child icebergs to replace the parent. This could be achieve by keeping track of icebergs shape, but this is a non-trivial exercise.\\

Lines 72-74 have been removed, and have been replaced with a very brief discussing of how levitating point particle icebergs are largely incompatible
with submerged ice shelf models.}\\
\\
l. 84: "should run sufficiently quickly" $->$ "should run sufficiently quick" (or fast)ÊÊ\\
\\
\textcolor{red}{Changed to "should run sufficiently fast"}\\
\\
l. 139-143: What happens to bonded ice elements? The body forces $F_{ss}$ and $F_{c}$ acting on an ice element are clearly not affected by the number of neighboring ice elements, but I suspect you would treat the other forces acting on the inner ice elements differently, probably similar to the modifications for the melting paramerizations in Section 2.5 (eq. 9 and 10)?\\
This is because inner ice elements should be subject to atmospheric and oceanic skin (surface and bottom) drags only, and the form drags would only act on outer ice elements; ice elements with less than 6 neighbors could partially feel form and skin drags. Similarly, wave radiation and sea ice drag should only act on the outer elements, correct? It wasn't clear to me how this is handled, also after reading appendix A. Moreover, which areas are the forces acting on in extension to the Martin and Adcroft (2010) case? Are they formulated based on the apothem $A_{p}$?\\
\\
\textcolor{red}{}\\
\\
l. 174: Later, you are mostly using "$d_{i,j}$" with comma instead of "$d_{ij}$". Similarly, $L_{ij}$ in l. 178 should be changed consistently.\\
\\
\textcolor{red}{The comma between i and j has been removed throughout the text for consistency.}\\
\\
l. 186: The force formulation in the first two rows of equation 6 is identical, so what about combining it into a single case using if (...) OR if (... and ...) ?\\
\\
\textcolor{red}{}\\
\\
l. 191-194: I was worried that bonds between ice elements of very different size and mass could result in strange behaviour, if you choose your timestep too large, and strong oscillations around the center of mass. After some thought, I think this is a very clever way to deal with the fact that tabular icebergs (bonded ice elements) will not melt homogeneously, but instead will erode very quickly along the outer sides, leading to high accelerations of the (smaller and lighter) ice elements along the iceberg boundary compared to the slower melting inner ice elements. If noteworthy, maybe you can elaborate a bit more about your experiences leading to that adjustment.\\
\\
\textcolor{red}{}\\
\\
l. 200: add vector arrow to $r_{ij}$\\
\\
\textcolor{red}{}\\
\\
l. 202: "is used reduce", change to "is used to reduce"\\
\\
l. 213: Is it possible to briefly derive the stability condition?Ê\\
\\
\textcolor{red}{}\\
\\
l. 221-225: Very impressive! Why does it rotate exactly? Is it because the first element hitting the coast is stopped (how is this handled?), and due to the bonds the other elements are forced onto a circular path? By the way, are the coastal points also some kind of "stationary ice elements" in your simulation, or how would this be handled in global simulations? Would you need to prescribe repulsive forces along the coasts?\\
\\
\textcolor{red}{}\\
\\
l. 236: "is the length the apothems" -> "is the length of the apothems"\\
\\
\textcolor{red}{}\\
\\
l. 246, 248, 387, 407, 439, ... : Please change "Eularian" to "Eulerian" throughout the text, there are many occasions where it is misspelled.\\
\\
\textcolor{red}{}\\
\\
l. 250: delete ":"\\
\\
\textcolor{red}{}\\
\\
l. 254/255: Similarly to the vertical embedding, there is no need to manually embed tabular icebergs -horizontally- into the ocean by averaging $F_{ss}$ over a larger area, as suggested in above comment (ii), because in your framework the sea surface slope force $F_{ss}$ is conveniently evaluated in different locations (for every ice element separately).\\
\\
\textcolor{red}{}\\
\\
l. 260: "(iii) imposing heat, salt, and mass fluxes on the ocean, associated with ice melting" Which salinity do you assume for the iceberg meltwater?\\
\\
\textcolor{red}{}\\
\\
l. 277: "[...] This method allows for the intersection to be found even when the hexagon is not aligned with the grid." Is your implementation particularly efficient so that it could be worth sharing it here?\\
\\
\textcolor{red}{}\\
\\
l. 282: comma after "i.e." instead of ":"\\
\\
\textcolor{red}{}\\
\\
l. 287: "described" -> "describe"\\
\\
\textcolor{red}{}\\
\\
l. 295: "The details of $M_{b}$, $M_{v}$, and $M_{e}$ are given in Appendix A." What is "W" for an ice element? Do you assume hexagons or circles? Is it 2*$A_{p}$?
Moreover, what is the area that, for example, the wave erosion $M_{e}$ is acting on (for rectangular point-particle icebergs this is usually assumed to be 2 side walls, I think; what is it for hexagons, 3 side walls?) It might prove to be very useful to list the surface areas the different forces and melt rates are acting on in the new framework, where you proceeded from point-particle icebergs to (hexagonal) ice elements.\\
You could list it either here or in the appendix.\\
\\
\textcolor{red}{}\\
\\
l. 302 and 306: delete the comma before "$M_{b}$" and "$M_{s}$"\\
\\
\textcolor{red}{}\\
\\
l. 308: "... which is a typical melting parameterization used beneath ice shelves [Holland and Jenkins, 1999]." One could mention that the 3-equation model for ice shelf melting has been previously applied for the estimation of tabular iceberg melting, e.g. in Silva et al. [2006] and Rackow et al. [2017]. When proceeding to larger iceberg structures this is a natural extension of the model's original range of application.\\
\\
\textcolor{red}{}\\
\\
l. 309-318: This is a clever way to account for the different melting along the boundary elements and inner elements (eq. 9 and 10). Since you do the weighting for the melt rates, the bottom and side areas where the bottom and side melt rates are acting on is unchanged compared to MA2010, correct?\\
\\
\textcolor{red}{}\\
\\
l. 347: "in a following way" -> "in the following way"\\
\\
\textcolor{red}{}\\
\\
l. 348/349: "up to six bonds per element" Do you support more bonds, for example along the ice shelf front where you added smaller elements to fill the gaps (l.403/404)?\\
\\
\textcolor{red}{}\\
\\
l. 360/361: "from one processor the next ..." -> "from one processor to the next, added to and removed from the appropriate lists, and the"\\
\\
\textcolor{red}{}\\
\\
l. 363: "a one" -> either "a" or "one"\\
\\
\textcolor{red}{}\\
\\
l. 389: "in an idealized setting"\\
\\
\textcolor{red}{}\\
\\
l. 400, l. 434, l. 441: delete ":" in section heading\\
\\
\textcolor{red}{}\\
\\
l. 405: "preprocessing inversion" What is that supposed to mean?\\
\\
\textcolor{red}{}\\
\\
l. 418: "using the ALE regridding-remapping scheme"\\
\\
\textcolor{red}{}\\
\\
l. 468: "modeling" -> "model"\\
\\
\textcolor{red}{}\\
\\
l. 495: "tabular icebergs"\\
\\
\textcolor{red}{}\\
\\
l. 515: "As the iceberg drifts"\\
\\
\textcolor{red}{}\\
\\
l. 532: "phenomenon"\\
\\
\textcolor{red}{}\\
\\
l. 540/541: Surprisingly, this is in contrast to the findings in Silva et al. [2006], where the authors show that the point-particle iceberg-melt parameterization leads to "on average, half the amount of melting compared to the Holland and Jenkins [1999] model." What could be the reason for this?\\
\\
l. 570: "at the edge"\\
\\
\textcolor{red}{}\\
\\
l. 572: "showed" -> "show"\\
\\
\textcolor{red}{}\\
\\
l. 574: "which is an important process"\\
\\
\textcolor{red}{}\\
\\
l. 580: "the question of how and when to introduce tabular icebergs into the ocean needs to be addressed." You could nicely refer to your earlier Stern et al. [2016] paper, where this question is explicitly raised. The question was also echoed and discussed in the Rackow et al. study.\\
\\
\textcolor{red}{}\\
\\
----
Comments on the appendix:\\
\\
l. 602: "the velocities of air,"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 604 "freeboard,"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 621: "as a result of wave erosion" (delete melt due to)\\
\\
\textcolor{red}{Corrected}\\
\\
l. 623 "wave erosion 'melt' rate", l. 631 "the 'melt' due to wave erosion"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 641: " which prevents large accelerations for elements whose mass"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 659: "using the Crank-Nicolson scheme"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 671: "for all forces not proportional to the element velocity"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 682, eq. 27: "Solving for $u(t_{n+1})$ in terms of quantities which only depend on the previous time step gives"Ê\\
One could remind the reader here that -although the notation includes "n+1"- $F^exp_{(n+1)}$ is an explicit function of $x_{(n+1)}$ and other quantities evaluated at $t_{n}$, so those are all known properties at this point.\\
\\
\textcolor{red}{}\\
\\
l. 691: "This updated drag can now"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 700: "In this section we describe how the"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 725: "when the following four tests pass"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 724-731: I suspect this only needs to be done once for debugging purposes until everything works, correct? Why do you provide this debugging information here?Ê\\
\\
\textcolor{red}{}\\
\\
l. 918: There is an error in the citation for the 'footloose' mechanism.\\
\\
\textcolor{red}{Corrected}\\
\\
----
Comments on the figures:\\
\\
Figure 1: In the left plot (a), please correct "Interacting bergs".\\
\\
\textcolor{red}{Corrected}\\
\\
l. 928 "Previous iceberg models"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 931: "can be joined together"\\
\\
\textcolor{red}{Corrected}\\
\\
l. 934: "For purposes of mass", l. 935 "For purposes of element"\\
\\
\textcolor{red}{Corrected}\\
\\
Maybe it is possible to include an arrow pointing to the red ship?\\
\\
\textcolor{red}{}\\
\\
Figure 4 and 5: ", as shown in the top left panel"\\
\\
\textcolor{red}{Corrected}\\
\\
Figure 6: "For purposes of mass aggregation", "For purposes of element interactions"\\
\\
\textcolor{red}{Corrected}\\
\\
Figure 13: Please base the caption on the better explanation and wording in the main text, lines 537-540.\\
\\
\textcolor{red}{}\\
\\
----\\
AGU Data Policy:\\
\\
I was not able to access the model code using the link provided in the Acknowledgements, so please link to the model code explicitly. I was able to access the setup scripts for the experiments through the provided link, however.\\
\\
\textcolor{red}{}\\
\\
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Reviewer 2 Evaluations:}\\
Recommendation: Return to author for minor revisions\\
Significant (Required): Yes, the paper is a significant contribution and worthy of prompt publication.\\
Supported (Required): Yes\\
Referencing (Required): Yes\\
Quality (Required): Yes, it is well-written, logically organized, and the figures and tables are appropriate.\\
Data (Required): Yes\\
Accurate Key Points (Required): Yes\\
\\

Review for 'Modeling tabular icebergs coupled to an ocean model'\\
A. Stern, A. Adcroft, O. Sergienko, G. Marques\\
submitted to Journal of Advances in Modeling Earth Systems.\\
Summary\\
This is a strong paper demonstrating a number of technical advancements in iceberg modeling, with an aim towards modeling giant tabular icebergs in a GCM. Icebergs are modeled as Lagrangian elements that are embedded into the ocean model, occupying space in the ocean grid and distributing fluxes associated with icebergs proportionally across multiple ocean grid cells based on occupied area. This is an improvement over typical Lagrangian point particle iceberg models, and a particularly needed improvement as grid resolutions are becoming finer, to the point where treating icebergs as existing in a single ocean grid cell may not be appropriate.\\
\\
Giant icebergs are modeled by numerically bonding a number of smaller ice elements, another novel development. This has the advantage of allowing the ocean state across multiple grid cells to influence the iceberg's drift and decay. This also provides a framework for modeling iceberg post-calving breakup events, which is an important decay mechanism not taken into account in most iceberg models. There is also an opposite repulsive force that is in place to prevent ice elements from piling atop each other, and is more computationally efficient than calculating a collision force, as would be done in a discrete element model.\\
\\
Overall I think this is a strong paper well suited for the Journal of Advances in Modeling Earth Systems. I have two comments that I think could be addressed or clarified, and a few small suggestions and edits.\\
\\
\textcolor{red}{We would like to thank the reviewer for taking the time to review this manuscript, and for the favorable review. We have responded to your comments individually
below}\\
\\
Comments\\
- Section 2.4 Ocean-ice coupling: It's clear the icebergs are embedded in the ocean model, but does this extend to the sea ice model? Since the ice elements can take up a considerable portion of a grid cell, what happens when iceberg area plus sea ice area exceeds the grid cell area?\\
\\
\textcolor{red}{The interactions between icebergs and sea ice is an important topic that has not yet included in the tabular iceberg model.  For this reason, the simulations presented in this study did not contain sea ice. We are currently working on improving the tabular iceberg model so that it interacts with sea ice in a more realistic way, and so that the surface area of icebergs and sea ice in a grid cell is always smaller than the grid cell area.
The final paragraph of the conclusion reminds readers that more work is needed to model iceberg sea ice interactions. This line reads: "Further work is also needed to understand (and model) the interactions between tabular icebergs and sea ice..."}\\
\\
- Section 4.3 Ocean response: There seems to be competing effects at play that I believe deserves more discussion here: i) enhanced freshwater/cooling due to iceberg melt in the upper ocean that increases stratification, reduces vertical mixing, thus preventing warmer waters from reaching the surface (as described by the authors in JGR:Oceans 2016). ii) The observed/described effect here of elevated shears around the iceberg that lead to increased vertical mixing and upwelling of warmer waters to the surface. Is the observed ocean warming/upwelling response due to the icebergs being embedded in the ocean model, causing enhanced shearing? Are the fluxes from the iceberg model sent to the ocean at the surface, not at depth? Is effect i) simply not applicable in this modeling setup?\\
\\
\textcolor{red}{}\\
\\
Minor Edits:\\
- Section 2.2: subscript notation convention is not consistent ($L_{ij}$ vs. $L_{i,j}$, $d_{ij}$ vs. $d_{i,j}$).\\
\\
\textcolor{red}{The comma between i and j has been removed everywhere for consistency.}\\
\\
- Section 2.4, Lines 246, 248. Eulerian spelling.\\
\\
\textcolor{red}{Spelling has been corrected}\\
\\
- Section 6.1: The forcing terms for the momentum equation are calculated using ice element length and width - are these also calculated assuming circular elements or tabular with some fixed aspect ratio?\\
\\
\textcolor{red}{The forcing terms in the momentum equation are taken directly from Martin and Adcroft 2010. In these forcing terms, the element is assumed to be a cuboid. A line has been added to Section 6.1 which reads: "For these non-interactive forces, the elements are assumed to be cuboids with time-evolving lengths, widths and thicknesses."}\\
\\
- Section 6.2: Please provide an expression for the basal melt term $M_{s}$.\\
\\
\textcolor{red}{}\\
\\
- Figure 8c: it would be nice to be able to see more clearly the upwelling around the iceberg as you can see in Figure 2c surface plot, with perhaps a a zoom/inset around the iceberg with a different colorscale.\\

\end{document}

### 2017-06-13 Lagrangian_MISOMIP.tex
Working on JAMES revisions and Lagrangian paper

@@
 
-The calving of large tabular icebergs away from Antarctic ice shelves is an important feature of the Antarctic environment, and accounts for approximately half of Antarctic ice-shelf decay. 
-However, despite its importance, the current generation of ice-ocean models is unable to represent ice-shelf calving in a physically realistic way.
-One reason for this is that current ice-shelf models are mostly built on static Eularian grids, and were not designed to easily allow pieces of the ice shelf to break off and become icebergs. 
+The current generation of ice-ocean models is unable to represent ice-shelf calving in a physically realistic way despite its controlling role of the mass balance and extent of Antarctic ice shelves.
+This is primarily due to static Eulerian approach of the current ice-shelf/sub-ice-shelf cavity models that does not allow separation and modification of computational domains that would represent breaking of pieces of an ice shelf that would become freely floating icebergs.
 In this study we develop a new ice-shelf cavity model where the ice shelf is constructed out of Lagrangian elements that are bonded together by numerical bonds.
 This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-We test newly developed Lagrangian ice -shelf model by simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-The Lagrangian model results are compared to a second simulation that uses an Eularian ice shelf with an otherwise identical configuration.
+We test this Lagrangian ice -shelf model by simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
+The Lagrangian model results are compared to results of an Eularian model simulations with identical configuration.
 Results show that the Lagrangian and Eularian models are almost indistinguishable.
 % For example, differences in the models are two orders of magnitude smaller than the differences observed when changing the ocean model coordinate system. 
-The similarly between the Eularian and Lagrangian models in a static ice-shelf configuration provides a proof of concept for the Lagrangian model, and means that we can confidently use Lagrangian ice-shelf models to extend the capabilities of the Eularian models.% The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
+The similarly between the Eularian and Lagrangian models in a static ice-shelf configuration provides a proof of concept for the Lagrangian model, and means that we can confidently use Lagrangian ice-shelf models to extend the capabilities of ice-shelf-cavity models.% The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
 
@@
 \section{Introduction}
-Floating ice shelves cover vast regions of the Antarctic polar oceans.
-These massive platforms of ice extend deep into the water column, applying large pressures to surface of the ocean, which is often hundreds of meters below global sea level.
-Beneath the ice shelves, both the bottom topography and the ice-shelf geometry play a role in steering ocean currents \citep{Nicholls1996, Jenkins2010,  Stern2014}.
-The topographic constraint imposed by the ice shelves at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities, and gives the ocean in the region a unique character.
-
-Satellite observations suggest that ice-shelf decay occurs via two main processes: melting and breaking \citep{Depoorter2013, Rignot2013}.
+%\sout{Floating ice shelves cover vast regions of the Antarctic polar oceans.
+These massive platforms of ice extend deep into the water column, depressing the surface of the liquid ocean, often to hundreds of meters below global-mean sea level.
+Beneath the ice shelves, both the bottom topography and the ice-shelf geometry play a role in steering ocean currents [Nicholls1996, Jenkins2010,  Stern2014].
+The topographic constraint imposed by the ice shelves at the ocean's upper boundary significantly affects the circulation within the ice-shelf cavities.}
+%
+Satellite observations show that ice-shelf decay occurs via two main processes: melting and breaking \citep{Depoorter2013, Rignot2013}.
 Each of these is responsible for approximately half of the ice-shelf decay, and each influences the surrounding ocean (and ice-shelf geometry) in a distinct way.
-Melting at the base of ice shelves causes freshwater fluxes into the ice-shelf cavity.
+Melting at the base of ice shelves causes fluxes freshwater into the ice-shelf cavity.
 The input of buoyant meltwater creates rising density plumes, which are guided along the ice-shelf base, and help drive ocean circulation beneath the ice shelves \citep{MacAyeal1984,  Holland2006}.
 Over time, melting at the ice-shelf base can erode the ice shelf, gradually altering the ice-shelf geometry.
-%The strength of the circulation within the cavity feeds back onto the ice-shelf melt rates, by removing cold water from the cavity, and drawing in warmer waters from the open ocean, thus providing the constant supply of thermal energy needed for continuous ice-shelf melt \citep{Lewis1986, Jacobs2011}.
-In contrast, ice-shelf breaking causes sudden changes to the ice-shelf geometry, and releases giant icebergs into the ocean.
+In contrast, iceberg calving causes sudden changes to the ice-shelf geometry, and releases giant icebergs into the ocean.
 After calving, these tabular icebergs can travel large distances and impact ocean hydrography \citep{Martin2010, Stern2015}, sea-ice formation \citep{Robinson2012, Stern2016} and ocean biology \citep{Smith2007, Vernet2012, Biddle2015} many miles away.
 
-In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic mass balance, and hence, on modeling Antarctic sub-ice-shelf cavities \citep{Asay-Davis2016}.
-% This increased interest has led to accelerated efforts to accurately model Antarctic ice-shelf cavities \citep{Asay-Davis2016}.
-Modeling the ocean beneath the ice shelves presents a unique set of challenges, since (i) the presence of ice shelves provides a rigid upper boundary for the ocean model which is not encountered elsewhere in the ocean, and (ii) melting and breaking ice shelves imply a changing ocean boundary conditions which present numerous numerical difficulties.
+%\sout{In recent years society's need for improved projections of future sea level has lead to an increased focus on the Antarctic mass balance, and hence, on modeling Antarctic sub-ice-shelf cavities [Asay-Davis2016]}
+Modeling the ocean beneath the ice shelves presents a unique set of challenges, since (i) the presence of ice shelves provides a quasi-rigid upper boundary for the ocean model which is not encountered elsewhere in the ocean, and (ii) melting and breaking ice shelves imply changing ocean boundary conditions which present numerous numerical difficulties.
 
@@
 Later models of ice-shelf cavities allowed the ice-shelf geometry to evolve as the ice shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}.
-More recently, dynamic ice-shelf models have been coupled the ocean cavity, allowing the study of grounding line migration, which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
-
-As far as we know, all models of ice-shelf cavities to date have omitted ice-shelf breaking and iceberg detachment.
-This is because (i) there is much uncertainty of the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on static Eularian grids, which do not lend themselves to modeling iceberg detachment and drift.
+More recently, dynamic ice-shelf models have been coupled to the ocean cavity, allowing the study of grounding line migration which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006, Seroussi2017}.
+
+All models of ice-shelf cavities to date have omitted ice-shelf breaking and iceberg detachment.
+This is because (i) there is much uncertainty about the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on static Eularian grids, which do not lend themselves to modeling iceberg detachment and drift.
 In contrast, existing {\it iceberg} models represent icebergs as Lagrangian particles, since this is a convenient way to model discrete objects traveling over large distances \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
@@
 
-In this study we develop a new ice-shelf cavity model where the ice shelf is represented on a `Lagrangian grid'.
+In this study we develop a new ice-shelf cavity model where the ice shelf is simulated with Lagrangian elements \citep{Stern2017}.
 In this model, the ice shelf is constructed out of Lagrangian elements which are bonded together by numerical bonds (see schematic Figures \ref{fig:Schematic}).
 This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-An example of this enhanced capability of the Lagrangian model is demonstrated in Figures \ref{fig:Iceberg_calving}, which shows a tabular iceberg drifting away an idealized ice shelf (see \citet{Stern2017} for more details).
+An example of this enhanced capability of the Lagrangian model is demonstrated in Figures \ref{fig:Iceberg_calving}, which shows a tabular iceberg drifting away from an idealized ice shelf (see \citet{Stern2017} for more details).
 
@@
 %Here, we instead focus comparing the Lagrangian model to existing Eularian model in a static ice shelf configuration. 
-However, before analyzing the improved capabilities of the Lagrangian ice-shelf model, it is necessary to thoroughly test and benchmark the Lagrangian model in a more familiar configuration. 
+However, before analyzing the improved capabilities of the Lagrangian ice-shelf model, it is necessary to thoroughly test and benchmark the Lagrangian ice-shelf model in a more familiar configuration.
 To do this we compare the Lagrangian ice-shelf-cavity model to existing Eularian model in a static ice-shelf configuration. 
@@
 \section{Lagrangian model description}
-The Kinematic Iceberg Dynamics (KID) model is Lagrangian model that has been developed in order to simulate ice-shelf cavities with breakable ice shelves.
+The Kinematic Iceberg Dynamics (KID) model is a Lagrangian model that has been developed in order to simulate ice-shelf cavities with breakable ice shelves.
 The model represents ice shelves using Lagrangian elements joined together by numerical bonds.
@@
 
-The goal of this study is to show that this Lagrangian ice-shelf model can replicate the results of an Eularian ice-shelf model when used in a static ice-shelf configuration (with all the elements being held stationary).
-Although the ice elements do not move in the static ice-shelf experiment, this configuration is a relevant test for the Lagrangian model, as it tests the interpolation and aggregation between Eularian and Lagrangian grids, and also test the coupling between the ocean and ice-shelf models.
-Benchmarking the Lagrangian ice-shelf model to an existing Eularian model in a static ice-shelf configuration is a prerequisite for using the Lagrangian model in more complex experimental setups with moving elements.
-
-In this section we briefly describe the fully dynamic Lagrangian ice-shelf model.
+%\sout{The goal of this study is to show that this Lagrangian ice-shelf model can replicate the results of an Eularian ice-shelf model when used in a static ice-shelf configuration (with all the elements being held stationary).
+}
+Although the ice elements do not move in the static ice-shelf experiment presented in this paper, this configuration is a relevant test for the Lagrangian model, as it tests the interpolation and aggregation between Eularian and Lagrangian grids, and also tests the coupling between the ocean and ice-shelf models.
+
+In this section we describe the fully dynamic Lagrangian ice-shelf model.
 We then focus on element packing and interpolation between the Eularian and Lagrangian grids, which are the parts of the model which are relevant to static ice simulations.
@@
 Each Lagrangian element represents a column of ice that is floating in the ocean.
-The elements each have their own position, velocity, mass, and a set of dimensions, which can evolve in time.
-Each element moves according to its own momentum equation which is solved in the (Lagrangian) reference frame of the element.
-The elements are forced by oceanic, sea ice and atmospheric drag forces, as well as a forces due to sea surface height gradients, and the Coriolis force \citep{Bigg1997, Gladstone2001, Martin2010, Stern2017}.
-The elements also interact with other elements and can be `bonded' together by numerical bonds, which hold the elements together and allow many elements to move together as a unit.
-By bonding many ice elements together, the model is able to form larger structures, such as tabular icebergs or ice shelves (see schematic Figures \ref{fig:Schematic}).
+The elements have their own position, velocity, mass, and a set of dimensions, which can evolve in time.
+Each element moves according to its own momentum balance which is computed in the (Lagrangian) reference frame of the element.
+The elements experience oceanic, sea ice and atmospheric drag forces, as well as a forces due to sea surface height gradients, and the Coriolis force \citep{Bigg1997, Gladstone2001, Martin2010, Stern2017}.
+The elements also interact with other elements and can be `bonded' together by numerical bonds, which allow many elements to move together as a unit.
+By bonding many ice elements together, the model is able to form larger structures, such as tabular icebergs or ice shelves (Figures \ref{fig:Schematic}).
 % The interactive forces between elements aggregate to give the larger structures an effective rheology.
 
-The Lagrangian elements melt when they are exposed to above-freezing ocean mixed-layer temperatures.
+The thickness and extent of the Lagrangian elements change due to melting when they are exposed to above-freezing ocean mixed-layer temperatures.
 The melt rates of the elements are prescribed using parametrizations developed for iceberg and ice-shelf decay \citep{Bigg1997, Holland1999, Gladstone2001, Martin2010}.
-As the elements melt, heat, salt and mass fluxes are passed to the ocean to simulate freshwater injection to the ocean surface.
+The corresponding heat, salt and mass fluxes are passed to the ocean to simulate freshwater injection to the ocean surface.
 % In this study we focus on comparing the model to a Eularian model, so the melt rate of elements is determined using the three equation model for basal melt, which is a typical melting parametrization used beneath ice shelves \citep{Holland1999}.
@@
 \subsection{Initializing element geometry and packing}
-The elements in the Lagrangian model are assumed to have surface areas which are shaped as equally-sized regular hexagons.
-We initialize the Lagrangian model by positioning the elements in a staggered lattice, so that the elements fit together and perfectly tile the ice-shelf surface (Figures \ref{fig:Schematic}b).
+The elements in the Lagrangian model are shaped as equally-sized regular hexagons.
+We initialize the Lagrangian model by positioning the elements in a staggered lattice of equally-size hexagons, so that the elements fit together and perfectly tile the ice-shelf surface (Figures \ref{fig:Schematic}b).
 Hexagonal elements are used so that when adjacent pairs of elements are bonded together, the network of bonds form equilateral triangles, which gives rigidity to the larger structure \citep{Stern2017}.
+\textcolor{red}{???
+Maybe add some comments about accuracy of continuity of fields like pressure etc on the discrete elements???}
 
@@
 Four ocean (mixed layer) fields are passed from the ocean model to the ice-shelf model: temperature, salinity and zonal and meridional velocities.
-These fields are interpolated onto the Lagrangian grid (i.e.: onto the elements in the ice-shelf model) using a bilinear interpolation scheme.
+These fields are interpolated onto the Lagrangian elements using a bilinear interpolation scheme.
 
@@
 For the purposes of aggregation, we assume that the elements have surface areas that are shaped as regular hexagons.
-Element's properties are aggregated from the Lagrangian grid to the Eularian grid by exactly calculating fraction of an elements surface area that is contained in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
+Element's properties are aggregated from the Lagrangian grid to the Eularian grid by exactly calculating the fraction of an element that is intersects each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
+\textcolor{red}{???
+This part is a bit hard to follow, it needs more explanation.
+Don't know whether a schematic could help.
+???}
 
@@
 The Eularian model uses the same grid as the ocean model, while in the Lagrangian model these fields are aggregated onto the ocean model grid before being passed through the coupler.
-Once in the ocean model, these fields and are used to: (i) apply a pressure to the ocean surface, (ii) alter the upper-ocean boundary condition to reflect that the ocean is covered by ice, and (iii) apply salt, temperature and mass fluxes associated with ice-shelf melting and freezing.
+Once in the ocean model, these fields and are used to: (i) apply a pressure to the ocean surface, \textcolor{red}{???
+This condition is specific to MOM6.
+Some explanations are required either about MOM6 specifics or how this could be handled in general.
+What if an ocean would be z-coordinate, what would be an equivalent of this condition???}(ii) alter the upper-ocean boundary condition to reflect that the ocean is covered by ice, \textcolor{red}{another ambiguous statement} and (iii) apply salt, temperature and mass fluxes associated with ice-shelf melting and freezing.
 
 Since the coupling with the ocean model is handled in the same way for both the Eularian and Lagrangian models and both models are coupled to the same ocean model, any differences between the two models in the static ice-shelf configuration (using the same melt rate parametrization) are likely due to the interpolation/aggregation between the ice and ocean grids.
-By accurately aggregating fields from the Lagrangian grid to Eularian ocean grids, we can make the Lagrangian ice-shelf model behave like the Eularian ice-shelf model in static ice-shelf simulations.
+By accurately aggregating fields from the Lagrangian grid to Eularian ocean grids, we aim to make the Lagrangian ice-shelf model behave like the Eularian ice-shelf model in static ice-shelf simulations.
 %Apart from the step of aggregating between the Lagrangian and Eularian grids, the interaction between the Lagrangian ice-shelf model and ocean model is exactly the same as the interaction between an Eularian ice-shelf model and an ocean model.
@@
 % the proof of concept for
-The KID model is used to simulate the flow within an idealized ice-shelf cavity.
+%\sout{The KID model is used to represent the ice shelf in an idealized ice-shelf cavity MOM6 ocean flow.
 The simulations are repeated using an Eularian ice shelf with an identical configuration.
-The details of the experimental setup for both the Lagrangian and Eularian models are presented here.
-
+The details of the experimental setup for both the Lagrangian and Eularian models are presented here.}
+%
 \subsection{Domain configuration}
 In order for our simulations to be easily comparable to previous models of ice-shelf cavities, we use an experimental setup based on the configuration created for the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP) \citep{Asay-Davis2016}.
-The MISOMIP configuration was developed as a standardized configuration to allow for a comparison between various ocean-ice coupled models.
 The configuration consists of an idealized ice shelf in a rectangular domain $L_{x}=80$km long and $L_{y}=480$km wide.
@@
 The Lagrangian and Eularian ice shelves are coupled to the MOM6 ocean model \citep{Hallberg2013}. 
-The ocean model is run in using vertical coordinate system which is a hybrid between a sigma-level and a z-level coordinate, achieved using ALE regridding-remapping scheme \citep{White2009}.
+The ocean model is run using a hybrid vertical coordinate system which blends a sigma-level and a z-level coordinate \citep{Stern2017}, implemented using the ALE method \citep{White2009}.
 In this vertical coordinate, model layers bend underneath surface topography (i.e.: the ice shelf), as they would in a sigma coordinate model, and intersect the bottom topography, as they would in a z-coordinate model.
@@
 The numerical simulations were all repeated using an isopycnal coordinate (without ALE regrinding-remapping).
-The results were qualitatively similar to the ALE results, and are therefore not presented here.
+The results were qualitatively similar to the hybrid-coordinate results, and are therefore not presented here.
 % All results presented below are from the ALE simulations, unless specified otherwise.
@@
 The ocean parameters used in the simulations are as specified in the MISOMIP configuration \citep{Asay-Davis2016}, and are shown in Table 1.
-The simulation is initialized from rest, with horizontally uniform initial ocean temperature and salinity profiles which vary linearly between specified surface and bottom values: $T_{top}=-1.9^{\circ}$C, $T_{bottom}=1.0^{\circ}$C, $S_{top}=33.8$ psu, $S_{bottom}=34.7$.
+The simulation is initialized from rest, with horizontally uniform initial ocean temperature and salinity profiles which vary linearly between specified open-ocean surface and bottom values: $T_{top}=-1.9^{\circ}$C, $T_{bottom}=1.0^{\circ}$C, $S_{top}=33.8$ psu, $S_{bottom}=34.7$.
 The maximum ocean depth is $H_{ocean}=720$ m.
@@
 %\subsection{Eularian ice shelf simulation:}
-\subsection{Ice-shelf decay}
+\subsection{Sub-ice-shelf melting}
 The melt rates in both the Lagrangian and Eularian ice-shelf simulations are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}.
@@
 In the Eularian code, this is achieved by setting the ice-shelf velocity to zero, while in Lagrangian ice shelf, the element velocities are set to zero.
-In both simulations, the ice shelf is thermodynamically active and is able to `melt' but has a constant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
+In both simulations, the ice shelf is thermodynamically active and is able to `melt' but has a time-invariant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
 In this setup, ice-shelf melting generates temperature and salinity fluxes into the ocean, but does not change the thickness of the ice shelf / ice elements.
@@
 
+\textcolor{red}{???
+This section is a bit thin.
+Perhaps it'd be worth looking at more fields and also discuss to under which circumstances differences between the KID and Eularian models can be larger and start affecting simulations and the results ???}
+
 \section{Conclusion}
@@
 In this framework, the ice shelf is constructed out of many Lagrangian elements, which are bonded together by numerical bonds.
-The collection of Lagrangian elements can be thought of as being a Lagrangian grid, which stores the ice-shelf properties.
+The collection of Lagrangian elements store the ice-shelf properties.
 Unlike Eularian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
@@
 
-The present study focuses on using the Lagrangian ice shelf to model static ice shelves.
-The model is demonstrated by modeling the circulation beneath a (static) idealized ice shelf, which was developed as part of the MISOMIP inter-comparison project.
+The framework capabilities are demonstrated by modeling the circulation beneath a (static) idealized ice shelf, which was developed as part of the MISOMIP inter-comparison project.
 The results from the Lagrangian ice-shelf model fit within our paradigm of understanding for circulation within ice-shelf cavities: buoyant meltwater that enters the ice-shelf cavity drives freshwater plumes at the ice-shelf base, which drives the circulation within the cavity.
@@
 
-A direct comparison comparison between the Lagrangian and a Eularian ice-shelf model coupled to the same ocean model shows that the results are extremely similar.
+A direct comparison \sout{comparison} between the Lagrangian and a Eularian ice-shelf model coupled to the same ocean model shows that the results are extremely similar.
 Differences between the Lagrangian and Eularian ice shelves models (resulting from interpolation errors) are much smaller than the differences observed when changing the ocean vertical coordinate system (for example).
@@
 
-\bibitem[Holland and Jenkins (1999)]{Holland1999}
+\bibitem[Holland and Jenkins(1999)]{Holland1999}
 Holland, D. M., and A. Jenkins (1999), Modeling thermodynamic ice-ocean interactions at the base of an ice shelf. {J. of Phys. Oceanogr.} 29.8, 1787-1800.
@@
 Pralong, A., and M. Funk (2005), Dynamic damage model of crevasse opening and application to glacier calving, {\it J. Geophys. Res.}, 110, B01309.
+
+\bibitem[Seroussi et al (2017)]{Seroussi2017}
+Seroussi H., Y.
+Nakayama, E.Y.
+Larour, D.
+Menemenlis, M.
+Morlighem, E.
+Rignot, and A.
+Khazendar (2017), Continued retreat of Thwaites Glacier, West Antarctica, controlled by bed topography and ocean circulation, {\it Geophys.
+Res.
+Lett.}, 44
 

### 2017-06-13 Schematic_bergs.py

@@ -37,7 +37,7 @@ def Schematic():
 		    draw_polygon(x+dr*numpy.random.rand(),y+dr*numpy.random.rand(),
 				 0.05+0.1*numpy.random.rand(),nsegs=20,ls='r')
 		plt.gca().annotate('(ii) Finite extent bergs', xy=(x+1.5,y+1.5), xytext=(x+.5,y+2.1))
-		plt.gca().annotate('Interactiing bergs', xy=(x+1.3,y+.8), xytext=(x+.5,y+.3),
+		plt.gca().annotate('Interacting bergs', xy=(x+1.3,y+.8), xytext=(x+.5,y+.3),
 				   arrowprops=dict(arrowstyle='->', connectionstyle='arc3,rad=.2'))
 		# A tabular berg
 		hx,hy=[1.5,0,1,2,0.5,1.5,2.5,-1,0,1,2,-.5,.5,1.5,0],[-1,0,0,0,1,1,1,2,2,2,2,3,3,3,4]

### 2017-06-30 submission1/Submission2_prep/Response_to_reviews.tex
Revisions draft 1

@@
 The new approach uses numerical bonds to group single icebergs/ice elements with finite extent together to form tabular icebergs with complex shapes, where previously levitating point-particle icebergs with typically zero area coverage have been used.
-The article is an original and exciting contribution in the ongoing discussion about the inclusion of giant tabular icebergs into ocean and climate models, and therefore -in my opinion- very suitable for publication inÊJAMES.Ê\\
+The article is an original and exciting contribution in the ongoing discussion about the inclusion of giant tabular icebergs into ocean and climate models, and therefore -in my opinion- very suitable for publication in JAMES.Ê\\
 \\
-\textcolor{red}{}\\
+\textcolor{red}{We would like to thank the reviewer for taking the time to carefully review our manuscript and for the favorable review.
+The reviewer's comments are addressed on a point by point basis below.}\\
 \\
 The authors describe the model and the technical details very well, and there are only some points that should be worked out in more detail (see specific comments below).
-This concerns (a) details about the surface areas where the melt rates and various forces are acting on when proceeding from rectangular point-particle icebergs to (bonded) hexagonal ice elements.
-In contrast to the thermodynamics/melting parameterization, it is also less clear how (b) the dynamics of inner ice elements is handled, and whether these could be subject to erroneous form drags despite being actually "shielded" by means of the outer elements.
+This concerns (a) details about the surface areas where the melt rates and various forces are acting on when proceeding from rectangular point-particle icebergs to (bonded) hexagonal ice elements.\\
+\\
+\textcolor{red}{For the purposes of non-interactive forces and applying melt rates, the elements are treated as cuboids, as in Martin and Adcroft (2010) and most other point-particle iceberg models.
+We chose to treat the icebergs as cuboids so that when no bonds were used, the forces and melt rates were completely unchanged from the Martin and Adcroft (2010).
+While assuming a different shape iceberg for the purposes of applying mass to the ocean and applying forces and melt rates introduces an a small error, this error is small compared to the uncertainty in the drag coefficients, melt rate parametrizations and other uncertainties built into a iceberg model.
+A few lines have been added to the start of Section 6.1 and of Section 6.2 to make it clear exactly which surfaces the forces and melt rates are applied to.}\\
+\\
+In contrast to the thermodynamics/melting parameterization, it is also less clear how (b) the dynamics of inner ice elements is handled, and whether these could be subject to erroneous form drags despite being actually "shielded" by means of the outer elements.\\
+\\
+\textcolor{red}{We agree with the reviewer that the side drag acting on the interior elements should be treated in a similar way to how the interior melting is handled.
+This was not done correctly in the original version of the manuscript, and has now been corrected.
+We have added a description of this to Appendix A and have added a few further sentences to the end of Section 2.5 to direct the reader to Appendix A.
+A  variable $\epsilon = 1- \frac{N_{b}}{N_{max}}$ representing the fraction of an elements perimeter surrounded by ocean has been introduced to ease the notation.
+Equation 9 and 10 have be rewritten in terms of this new variable.
+The modification to the drag law does not make a qualitative difference to the results or figures.}\\
+\\
 Finally, (c) when exactly do the interactive forces enter the computation?
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The interactive forces are included in the momentum equation for each particle, as shown in equation (1).
+The interactive forces are added to the total force balance which is used to update the iceberg velocity.
+This velocity is in turn used to update the iceberg position.
+The numerical scheme used to update the iceberg position and velocity is outlined in in Appendix B.}\\
+%\textcolor{blue}{[I am not sure why this was unclear. Should I add more text to clarify further?]}\\
 \\
@@
 (2016) (cited in l.
-255).
+255).\\
 \\
-\textcolor{red}{A paragraph has been added to the introduction at line 81 which reviews some of the attempts to move beyond levitating point particle icebergs using the existing technology.} \textcolor{blue}{[Lichey and Hellmer (2001) is not discussed in details since the suggested parametrization is not related directly to the size and structure of tabular icebergs.
+\textcolor{red}{There have been a number of studies which have modified the point-particle iceberg model in order to better represent tabular icebergs.
+A paragraph has been added to the introduction which reviews some of the attempts to move beyond levitating point particle icebergs using the existing technology.} \\
+%\textcolor{blue}{[Lichey and Hellmer (2001) is not discussed in details since the suggested parametrization is not related directly to the size and structure of tabular icebergs.
 It is cited as a paper that has modeled tabular icebergs using existing technology.]}\\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{We agree with the reviewer that it is too early to conclude that (appropriately modified) point-particle iceberg models can not be used to represent tabular icebergs in GCM's.
+However, more work is needed to improve the current point-particle iceberg models so that they can be used to represent tabular icebergs.
+A brief discussion on this point has been added to the new introduction described above.
+A comparison between the resolved icebergs in our study and a modified point particle iceberg model would certainly be useful to help constrain both models.}\\
 \\
@@
 \\
-\textcolor{red}{We would like to thank the reviewer for the very favorable review of our work.
-We agree that the fact that icebergs are non-levitating in our new iceberg framework is an important feature which was underemphasized.
-We have added the word `submerged' to the paper title, and edited the abstract, introduction and conclusion to further emphasize this point.\\
-\\
-Line 18 in abstract has been edited and now reads: ``In this framework, tabular icebergs are represented by non-levitating Lagrangian elements that drift are submerged in the ocean.'' \\
-\\
-A brief discussion of levitating and non-levitating icebergs models has been added to the new paragraph in the introduction at line 81.
+\textcolor{red}{We agree that the fact that icebergs are non-levitating in our new iceberg framework is an important feature which was underemphasized.
+We have added the word `submerged' to the paper title, and edited the abstract, introduction and conclusion to further emphasize this point.}\\
+%\\
+%\textcolor{red}{Line 18 in abstract has been edited and now reads: ``In this framework, tabular icebergs are represented by non-levitating Lagrangian elements that drift are submerged in the ocean.'' \\
+%\\
+%A brief discussion of levitating and non-levitating icebergs models has been added to the new paragraph in the introduction at line 81.
 The development of a iceberg model where icebergs are submerged in the flow (and not levitating) has been added as one of the goals of the study at line 103.\\
-\\
-A few words have been added to the first paragraph of the conclusion to emphasize that the iceberg models allows icebergs to be non-levitating.}\\
+%\\
+%A few words have been added to the first paragraph of the conclusion to emphasize that the iceberg models allows icebergs to be non-levitating.}\\
 \\
@@
 Some general clarifications would further improve the paper:\\
-\\
-\textcolor{red}{}\\
 \\
@@
 \textcolor{red}{All of the ice elements are assumed to be floating in the ocean (in isostatic equilibrium), so that the mass of a column of ice is equal to the mass of water it displaces.
-This means that ``the element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$'' (see line 610).
-Since the ice shelf is thickest at the grounding line, and gets much thinner toward the ice front, this implies that the the elevation of the ice surface decrease towards the ice front (as the reviewer correctly points out).\\
-\\
-The following lines have been added at line 410 to clarify: ``The initial ice thicknesses of the elements are calculated from the ice mass by assuming that the ice has a constant density, $\rho$.
+This means that ``the element thickness is related to the draft and freeboard by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$'' (see Appendix A).
+Since the ice shelf is thickest at the grounding line, and gets much thinner toward the ice front, this implies that the the elevation of the ice surface decrease towards the ice front (as the reviewer correctly points out).
+We do not enforce a level surface for bonded ice elements.}\\
+%\\
+%\textcolor{red}{The following lines have been added at line 410 to clarify: ``The initial ice thicknesses of the elements are calculated from the ice mass by assuming that the ice has a constant density, $\rho$.
 The draft and freeboard are related to the ice thickness by $T=F+D$ and $D=\frac{\rho}{\rho_{o}} T$, where $\rho$ and $\rho_{o}$ are the density of ice and seawater respectively."} \textcolor{blue}{[Perhaps we should not add these lines to the text since they already appear in the text in the appendix?
@@
 \\
-\textcolor{red}{1) Iceberg rolling is turned off bonded icebergs. 2) All icebergs are initialized with D>??? and W=?. This means that W/D > 0.92 stability requirement. (hopefully).}\\
+\textcolor{red}{In the simulations in the first submission of the manuscript, iceberg capsizing was turned off.
+All of the ice elements in the calving iceberg were initialized to be stable and not close to the capsizing limit.
+Since the simulations are only run for a short period of time (60 days), iceberg melting does not does not bring the ice elements close to the capsizing limit.}
+%\\
+\textcolor{red}{However, we like with the reviewers suggestion of turning capsizing off for bonded elements only, and have implemented this change.
+The change does not make any qualitative difference to the simulation or figures but could improve for longer simulations.}
+\textcolor{red}{Details of the iceberg rolling scheme have been added to the end of Appendix A.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{We have not yet followed a tabular iceberg until it melted completely.
+This will be done in a future study.
+As mentioned above in our setup bonded elements are prohibited from capsizing.}\\
 \\
@@
 \\
-
+\textcolor{red}{The interactive forces were designed to run sufficiently quickly that they can be used in a climate model at a later stage.
+In the simulations presented in this study, the extra time needed to calculate bonded interactions is small compared to other parts of the iceberg code and very small compared to the time taken to run the ocean model.
+This is illustrated by the fact that the simulation where all bonds were removed took slightly longer than the bonded simulation.}\\
+\\
+\textcolor{red}{Embedding the elements in the ocean means that the coupling time step between the iceberg model and the ocean model has to be reduced to prevent the movement of the iceberg exciting artificial gravity waves in the ocean.
+This is true for simulations with and without iceberg bonds.
+An effort is currently underway to improve the coupling between the iceberg model and the ocean model to allow for a larger coupling time step (i.e.: splitting the iceberg dynamics into a fast part and a slow part with different coupling time steps).
+At this stage it is still too early to say whether our model will be able to be used for global simulations, however, it is being build with this intension.}\\
+\\
 ----
@@
 \\
-\textcolor{red}{Comma has been added}\\
+\textcolor{red}{A comma has been added}\\
 \\
-l. 16: "the current generation of ocean circulation models do not represent" -> "the current generation of ocean circulation models usually does not represent"\\
+l. 16: "the current generation of ocean circulation models do not represent" $- >$ "the current generation of ocean circulation models usually does not represent"\\
 \\
@@
 \\
-\textcolor{red}{Comma has been removed}\\
+\textcolor{red}{The comma has been removed}\\
 \\
@@
 \\
-\textcolor{red}{A paragraph has been added to the introduction at line 81 which reviews some of the attempts to move model tabular icebergs using the existing technology.} \\
+\textcolor{red}{A paragraph has been added to the introduction which reviews some of the attempts to model tabular icebergs using the existing technology.} \\
 \\
@@
 \textcolor{red}{We agree with the reviewer that the issue of iceberg breakup and calving is still unresolved and there is still much to be understood about the physic that govern these processes.
-We do however believe the the present work provides a framework which allows iceberg calving (away from a submerged ice shelf) to be modeled more easily.
-Firstly, is not clear how the calving of icebergs away from a submerged ice shelf could be represented using levitating icebergs (since removing mass from the ice shelf would trigger artificial tsunamis).
-If icebergs are non-levitating then it becomes important that the size of the iceberg matches the size of the piece of ice calving away from the ice shelf.
-Calving icebergs can have many different structures and shapes. It is not clear how this could be represented using rectangular, circular icebergs or point particle icebergs.
-Representing icebergs and ice shelves using ice elements submerged in the ocean means therefore puts fewer restrictions on possible calving laws.
-Similarly with icebergs breakup, it is unclear how one would represent an iceberg breaking up into two pieces with distinct shapes by introducing child icebergs to replace the parent.
-This could be achieve by keeping track of icebergs shape, but this is a non-trivial exercise.\\
-
-Lines 72-74 have been removed, and have been replaced with a very brief discussing of how levitating point particle icebergs are largely incompatible
-with submerged ice shelf models.}\\
+While do believe that the framework developed in this study could useful for testing out developed calving laws, it does not address the physics of ice fracture directly.
+Line 72-74 have been removed to avoid any confusion.
+A few sentences have been added to the start of Section 3.5 to clarify that we are not addressing the physics of calving in this study, but rather focusing on building a framework to represent tabular icebergs.}\\
+%
+%\textcolor{red}{Lines 72-74 have been removed, and have been replaced with a very brief discussing of how levitating point particle icebergs are largely incompatible with submerged ice shelf models.}\\
 \\
@@
 \\
-\textcolor{red}{Changed to "should run sufficiently fast"}\\
+\textcolor{red}{Changed to ``should run sufficiently fast"}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{We agree with the reviewer that the side drag (and wave radiation force) acting on the interior elements should be treated in a similar way to how the interior melting is handled.
+We have added a description of this to Appendix A and have added a few lines to the end of Section 2.5.
+A  variable $\epsilon = 1- \frac{N_{b}}{N_{max}}$ representing the fraction of an elements perimeter surrounded by ocean has been introduced to ease the notation.
+Equation 9 and 10 have be rewritten in terms of this new variable.
+The modification to the drag law does not make a qualitative difference to the results presented in the figures.
+To find the length and width of the elements in the drag forces we assume that the elements have cuboid shape as in Martin and Adcroft (2010), as discussed above.
+}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The equation has been rearranged as suggested.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Different melt rates at the sides and center of the iceberg were used to allow for the sides of the iceberg to erode faster than the center of the berg.
+A consequence of using this method is that large ice elements in the interior are often bonded to much smaller elements at the sides.
+As the reviewer correctly points out, using the minimum mass $M_{ij}$ in the calculation of the interactive forces avoids strong oscillations for large elements bonded to very small elements.
+We decided on using this method after attempting to use the average mass.
+In a two element test case, using the average mass led to very high accelerations when the mass of the smaller iceberg decreased to zero.
+We do not believe that details of this testing are particularly noteworthy or would be of interest to a general reader.}\\
+\\
+\textcolor{red}{While performing these tests, we also noted that the damping of the elastic interactive force perpendicular to the relative motion of the elements should be set to zero.
+This perpendicular damping has been removed (see equation 8).}\\
+%\\
+%, as done in Li et al [2014] (reference below)\textcolor{red}{Li, B., H.
+Li, Y.
+Liu, A.
+Wang and S.
+Ji (2014), A modified discrete element model for sea ice dynamics.
+Acta Oceanologica Sinica, 33(1), 56-63.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The vector arrow has been added.}\\
 \\
@@
 \\
+\textcolor{red}{The word `to' has been added}\\
+\\
 l. 213: Is it possible to briefly derive the stability condition?Ê\\
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The stability condition for a one dimensional linearly damped oscillator is derived by writing the second order system out as a matrix equation and analyzing under what conditions the modulus of the eigenvalues of the matrix are bounded by 1 (i.e.: the system is stable).
+For the newly-developed implicit velocity Verlet method time-stepping scheme, this last step was done numerically (while it can be solved analytically for the original Velocity Verlet method).
+The stability of the non-linearly damped oscillator follows from the stability of the linearly damped oscillator since the CFL criteria is independent of the magnitude of the drag coefficient.
+The methods involved in the stability analysis are quite standard, so we do not believe it merits being included in the manuscript.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The iceberg rotates due to the effect of the Coriolis force, and also due to the iceberg interacting with the side wall.
+The interactions of elements with the boundary are handled by manually moving the element back to the closest ocean point.
+The code handling interactions with the boundary was inherited from the underlying point-particle iceberg model codebase and has not been changed.
+It has therefore already been used in global simulations.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The word `of' has been added.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The spelling has been corrected.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Colon has been removed}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Good point. This explanation and the reference to Rackow et al (2017) has been added to the end of the sentence.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Iceberg meltwater is assumed to have zero salinity and is injected into the ocean boundary layer.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Finding the intersection between the triangle and the grid is a somewhat messy calculation involving a few special cases. We do not believe that it is worth sharing the details.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Comma has been added.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{This has been corrected}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{When applying the melt rates (and applying the drag forces) we assume that the elements are shaped as cuboids, as in Martin and Adcroft (2010) and most other point-particle iceberg models.
+We chose to treat the icebergs as cuboids so that when no bonds were used, the forces and melt rates were unchanged for the Martin and Adcroft (2010) version.
+While assuming a different shape iceberg for the purposes of applying mass to the ocean and applying forces and melt rates introduces an a small error, this error is small compared to the uncertainty in the drag coefficients and melt rate parametrization.
+A few lines have been added to the start of Section 6.1 and of Section 6.2 to make it clear exactly which surfaces the forces and melt rates are applied to, and to discuss the potential error introduced.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{Commas have been added}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{A reference to Silva et al. [2006] and Rackow et al. [2017] has been added to the description of the melt rate parametrization in Section 2.5.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{That is correct.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{This has been corrected.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The maximum number of bonds is an input parameter of the model.
+In our simulations a maximum of six bonds are used (when using hexagonal elements).
+More bonds can easily be added, but this increases the amount of memory stored with easy element (and passed between processors), and slows the model down the model.
+Smaller ice elements are only used to fill in gaps along the perimeter of the domain, and not at the ice front.
+These elements are held stationary, and are not bonded.
+A sentence has been added to Section 3.2 to clarify.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The colons have been removed.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The initial masses of the ice elements are calculated from the gridded ice thickness using bilinear interpolation. This has been corrected in the text.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The word `the' has been added.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{This sentence has been edited so that it is grammatically correct.}\\
 \\
@@
 \\
+\textcolor{red}{Figure 13 compares the Holland and Jenkins [1999] 3-equation-model melt rate with the Bigg et al [1997] melt rate.
+Here the Bigg et al [1997] includes contributions from the side erosion, basal melt rate and buoyant convection.
+In contrast, the Silva et al [2006] paper compare the 3 equation model melt rate to only the basal melt rate from Biggs et al [1997].
+Since the side erosion term dominates the melt rate contribution, our results do not contradict Silva et al [2006].
+A sentence has been added to Section 4.4 which clarifies this point}\\
+\\
 l. 570: "at the edge"\\
 \\
-\textcolor{red}{}\\
+\textcolor{red}{This has been corrected.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{A reference to Stern et al [2016] has been added.}\\
 \\
@@
 l. 682, eq. 27: "Solving for $u(t_{n+1})$ in terms of quantities which only depend on the previous time step gives"Ê\\
-One could remind the reader here that -although the notation includes "n+1"- $F^exp_{(n+1)}$ is an explicit function of $x_{(n+1)}$ and other quantities evaluated at $t_{n}$, so those are all known properties at this point.\\
+One could remind the reader here that -although the notation includes "n+1"- $F^{exp}_{(n+1)}$ is an explicit function of $x_{(n+1)}$ and other quantities evaluated at $t_{n}$, so those are all known properties at this point.\\
 \\
-\textcolor{red}{}\\
+\textcolor{red}{A sentence has been added to the text reminding the reader that $F^{exp}_{(n+1)}$ is already known.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{These lines have been removed.}\\
+%\textcolor{blue}{[Should I remove these lines? They could be helpful for someone trying to reproduce our results.]}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{We prefer not to add an arrow pointing to the ship, as the ship is not an important feature of the Figure.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The caption of Figure 13 has been reworded.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{The model source code is open source and can be found at $\textrm{https://github.com/NOAA-GFDL}$. This has been added to the acknowledgements.}\\
 \\
@@
 For this reason, the simulations presented in this study did not contain sea ice.
-We are currently working on improving the tabular iceberg model so that it interacts with sea ice in a more realistic way, and so that the surface area of icebergs and sea ice in a grid cell is always smaller than the grid cell area.
-The final paragraph of the conclusion reminds readers that more work is needed to model iceberg sea ice interactions.
+We are currently working on improving the tabular iceberg model so that it interacts with sea ice in a more realistic way.
+As the reviewer points out, an important constraint is that the combined surface area of icebergs and sea ice in a grid cell is always smaller than the grid cell area.}\\
+%The final paragraph of the conclusion reminds readers that more work is needed to model iceberg sea ice interactions.
 This line reads: "Further work is also needed to understand (and model) the interactions between tabular icebergs and sea ice..."}\\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{In our iceberg model, the iceberg is fully submerged in the water column so that the freshwater fluxes below the iceberg are injected more than 200 meters below sea level.
+The presence of the iceberg in the water column allows for upwelling to occur around the iceberg leading to a warming of the ocean surface.
+As the reviewer correctly points out, this result is in contrast to results observed using levitating point-particle icebergs models where freshwater fluxes applied to the ocean surface cause a cooling of the ocean surface.
+This is an important consideration since the warming/cooling around melting icebergs can drive changes in sea ice concentrations (as reported in Stern et al 2016).
+In the real-world ocean the sign of the ocean surface temperature response will likely depend on the ambient stratification around the iceberg and the amount of entrainment in the iceberg plume.
+More work is required to determine whether the presence of tabular icebergs in an ocean model will lead to a net warming or cooling of the Southern Ocean, and this is certainly an interesting topic for a future study.}\\
+\\
+\textcolor{red}{A paragraph has been added to the text to Section 4.3 discussing these competing effects/mechanisms, and the possible implications of using submerged icebergs on Southern Ocean sea ice concentrations.}\\
 \\
@@
 \\
-\textcolor{red}{The forcing terms in the momentum equation are taken directly from Martin and Adcroft 2010.
+\textcolor{red}{
+%The forcing terms in the momentum equation are taken directly from Martin and Adcroft 2010.
 In these forcing terms, the element is assumed to be a cuboid.
-A line has been added to Section 6.1 which reads: "For these non-interactive forces, the elements are assumed to be cuboids with time-evolving lengths, widths and thicknesses."}\\
+A line has been added to Section 6.1 which reads: "For these non-interactive forces, the elements are assumed to be cuboids with time-evolving lengths, widths and thicknesses."
+For the purposes of non-interactive forces and applying melt rates, the elements are treated as cuboids, as in Martin and Adcroft (2010) and most other point-particle iceberg models.
+We chose to treat the icebergs as cuboids so that when no bonds were used, the forces and melt rates were unchanged from the Martin and Adcroft (2010) model.
+While assuming a different shape iceberg for the purposes of applying mass to the ocean and applying forces / melt rates introduces an a small error, this error is small compared to the uncertainties in the drag coefficients and melt rate parametrizations.
+A few lines have been added to the start of Section 6.1 and of Section 6.2 to make it clear exactly which surfaces the forces and melt rates are applied to, and to discuss potential  errors introduced.}\\
 \\
@@
 \\
-\textcolor{red}{}\\
+\textcolor{red}{A description of $M_{s}$ has been added to the end of Appendix A.}\\
 \\
 - Figure 8c: it would be nice to be able to see more clearly the upwelling around the iceberg as you can see in Figure 2c surface plot, with perhaps a a zoom/inset around the iceberg with a different colorscale.\\
+\\
+\textcolor{red}{The main goal of this study is to present the modeling framework for modeling tabular icebergs.
+As such, we have chosen not to discuss the oceanography around the tabular in too much detail.
+We are planning a follow up paper which focusses specifically on the oceanography around calving tabular icebergs, We believe that your suggested figures fit better into the follow up study..}\\
+\\
 

### 2017-06-30 Schematic_bergs.py

@@ -68,7 +68,7 @@ def Schematic():
 if __name__ == '__main__':
 	Schematic()
 	plt.show()
-	print 'Script complete'
+	print('Script complete')
 	#sys.exit(main())
 
 

### 2017-07-08 Scripts_for_paper_figures/Fig_Drift_berg.sh
Updating scripts and Figures

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -use_Mixed_Melt=True -plot_second_colorbar=False -use_Revision=False -second_colorbar_units='(m)' -save_figure=True

### 2017-07-08 Scripts_for_paper_figures/Fig_SST_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=12 -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=12 -plot_second_colorbar=False -second_colorbar_units='(m)' -use_Revision=False -save_figure=True

### 2017-07-08 Scripts_for_paper_figures/Fig_Splitting_berg.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -use_Mixed_Melt=False -save_figure=True

### 2017-07-08 Scripts_for_paper_figures/Fig_Temperature_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.3 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(deg C)' -use_Mixed_Melt=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=True -vanom=0.5 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(deg C)' -use_Mixed_Melt=True -save_figure=True

### 2017-07-08 snapshots.py

@@ -55,6 +55,9 @@ def parseCommandLine():
 	parser.add_argument('-use_ALE', type='bool', default=True,
 		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
 	
+	parser.add_argument('-use_Revision', type='bool', default=True,
+		                        help='''When true, it uses the results of the Revision simulations (including new drag and rolling)    ''')
+	
 	parser.add_argument('-use_Mixed_Melt', type='bool', default=False,
 		                        help=''' When true, figure plots using Mixed_melt_data ''')
 	
@@ -131,6 +134,14 @@ def parseCommandLine():
 
 	parser.add_argument('-colorbar_units', type=str, default='',
 		                        help='''The units for the colorbar''')
+	
+	parser.add_argument('-second_colorbar_units', type=str, default='',
+		                        help='''The units for the colorbar''')
+	
+	parser.add_argument('-plot_second_colorbar', type='bool', default=False,
+		                        help=''' If true, then plots two colorbars ''')
+
+	
 
         optCmdLineArgs = parser.parse_args()
         return optCmdLineArgs
@@ -149,6 +160,7 @@ def main(args):
 	#General flags
 	rotated=args.rotated
 	use_ALE=args.use_ALE
+	use_Revision=args.use_Revision
 	use_days_title=args.use_days_title
 	use_Mixed_Melt=args.use_Mixed_Melt
 
@@ -162,8 +174,12 @@ def main(args):
 	berg_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/'
 	Geometry_path=berg_path+'Melt_on_high_melt_with_decay/'
 	ALE_flag=''
+	Revision_flag=''
 	if use_ALE is True:
 		ALE_flag='ALE_z_'
+		if use_Revision is True:
+			Revision_flag='Revision_'
+			berg_path=berg_path+Revision_flag
 		berg_path=berg_path+ALE_flag
 	Mixed_Melt_flag=''
 	if use_Mixed_Melt is True:
@@ -255,6 +271,7 @@ def main(args):
 	field=args.field
 	vmin=args.vmin
 	vmax=args.vmax
[…]

### 2017-07-08 static_shelf_comparison.py

@@ -45,6 +45,9 @@ def parseCommandLine():
 	parser.add_argument('-use_ALE', type='bool', default=True,
 		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
 	
+	parser.add_argument('-use_Revision', type='bool', default=True,
+		                        help='''When true, it uses the results of the Revision simulations (including new drag and rolling)    ''')
+	
 	#What to plot?
 	parser.add_argument('-fields_to_compare', type=str, default='plot_bt_stream_comparison',
 		                        help=''' This flag determine whether to plot horizontal, vertical, or special case for barotropic stream function
@@ -362,8 +365,10 @@ def calculate_barotropic_streamfunction(filename,depth,ice_base,time_slice=None,
 	
 def get_vertical_dimentions(filename, vertical_coordinate, time_slice, time_slice_num, direction ,dir_slice, dir_slice_num,rotated=False):
 	if vertical_coordinate=='z':
+		print 'The filename is ....', filename
 		with nc.Dataset(filename) as file:
-			z = file.variables['zt'][:]
+			#z = file.variables['zt'][:]
+			z = file.variables['z_l'][:]
 		return z
 	if vertical_coordinate=='layers':
 		z=load_and_compress_data(filename, 'e' , time_slice, time_slice_num, direction ,dir_slice, dir_slice_num,rotated=rotated)
@@ -600,6 +605,7 @@ def main(args):
 	#General flags
 	rotated=args.rotated
 	use_ALE=args.use_ALE
+	use_Revision=args.use_Revision
 
 	#What to plot?
 	fields_to_compare=args.fields_to_compare
@@ -622,10 +628,13 @@ def main(args):
 
 	#Using ALE ice shelf
 	use_ALE_flag=''
+	use_Revision_flag=''
 	if use_ALE is True:
-		
 		use_ALE_flag='ALE_z_'
 		Folder_name='ALE_z_' +Folder_name
+		if use_Revision is True:
+			use_Revision_flag='Revision_'
+			Folder_name='Revision_' +Folder_name
 		Shelf_path=Path+'Shelf/' + Folder_name
 		Berg_path=Path+'Bergs/' + Folder_name
 
@@ -852,7 +861,7 @@ def main(args):
 
 
 	if save_figure==True:
-		output_file='Figures/'+ use_ALE_flag +'static_shelf_comparison_' + field + '.png'
[…]

### 2017-07-08 static_shelf_solo.py

@@ -49,6 +49,9 @@ def parseCommandLine():
 	parser.add_argument('-use_ALE', type='bool', default=True,
 		                        help='''When true, it uses the results of the ALE simulations. When false, layed simulations are used.    ''')
 	
+	parser.add_argument('-use_Revision', type='bool', default=True,
+		                        help='''When true, it uses the results of the Revision simulations (including new drag and rolling)    ''')
+	
 	#What to plot?
 	parser.add_argument('-plot_horizontal_field', type='bool', default=True,
 		                        help='''    ''')
@@ -135,6 +138,7 @@ def main(args):
 	#General Flags
 	rotated=args.rotated
 	use_ALE=args.use_ALE
+	use_Revision=args.use_Revision
 	broken_shelf=args.broken_shelf
 
 	#What to plot?
@@ -168,9 +172,13 @@ def main(args):
 
 	#Using ALE ice shelf
 	use_ALE_flag=''
+	use_Revision_flag=''
 	if use_ALE is True:
 		use_ALE_flag='ALE_z_'
 		Folder_name='ALE_z_' +Folder_name
+		if use_Revision is True:
+			use_Revision_flag='Revision_'
+			Folder_name='Revision_' +Folder_name
 		
 		Shelf_path=Path+'Shelf/' + Folder_name
 		Berg_path=Path+'Bergs/' + Folder_name
@@ -462,7 +470,7 @@ def main(args):
 
 
 	if save_figure==True:
-		output_file='Figures/'+use_ALE_flag+'static_shelf_solo' + plot_flag +broken_path+ '.png'
+		output_file='Figures/'+use_Revision_flag +use_ALE_flag+'static_shelf_solo' + plot_flag +broken_path+ '.png'
 		plt.savefig(output_file,dpi=300,bbox_inches='tight')
 		print 'Saving ' ,output_file
 

### 2017-07-08 Scripts_for_paper_figures/Fig_SST_Collapse.sh
Updating scripts

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=12 -plot_second_colorbar=False -second_colorbar_units='(m)' -use_Revision=False -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=False -dashed_num=12 -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -save_figure=True

### 2017-07-08 static_shelf_comparison.py

@@ -455,8 +455,17 @@ def get_plot_axes_limits(x, y, xlim_min, xlim_max, ylim_min, ylim_max):
 		ylim_max=np.max(y)
 	return [xlim_min, xlim_max, ylim_min, ylim_max]
 
+def truncate_colormap(cmap, minval=0.0, maxval=1.0, n=100):
+	cmap = plt.get_cmap(cmap)
+	new_cmap = matplotlib.colors.LinearSegmentedColormap.from_list(
+        'trunc({n},{a:.2f},{b:.2f})'.format(n=cmap.name, a=minval, b=maxval),
+        cmap(np.linspace(minval, maxval, n)))
+	return new_cmap
+
 def plot_data_field(data,x,y,vmin=None,vmax=None,flipped=False,colorbar=True,cmap='jet',title='',xlabel='',ylabel='',return_handle=False,grounding_line=None, \
 		xlim_min=None, xlim_max=None, ylim_min=None,ylim_max=None,colorbar_units='',colorbar_shrink=1.0): 
+	if cmap=='Greys':
+		cmap = truncate_colormap(cmap, 0.0, 0.75)
 	if flipped is True:
 		data=transpose_matrix(data)
 		tmp=y ; y=x ; x=tmp

### 2017-07-09 Scripts_for_paper_figures/Fig_Collapse_solo_melt.sh
Updating figures for revision

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -ylim_min=240. -ylim_max=440.0 -broken_shelf=True -use_Mixed_Melt=True -save_figure=True  
+./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -ylim_min=240. -ylim_max=440.0 -broken_shelf=True -use_Mixed_Melt=True -use_Mixed_Melt=True  -use_Revision=True -save_figure=True  

### 2017-07-09 Scripts_for_paper_figures/Fig_Drift_berg.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -use_Mixed_Melt=True -plot_second_colorbar=False -use_Revision=False -second_colorbar_units='(m)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -use_Mixed_Melt=True -plot_second_colorbar=True -use_Revision=True -second_colorbar_units='(m)' -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_SST_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=False -dashed_num=12 -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=9 -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_Splitting_berg.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -use_Mixed_Melt=False -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -use_Mixed_Melt=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_Temperature_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=True -vanom=0.5 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(deg C)' -use_Mixed_Melt=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.5 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=9 -colorbar_units='(deg C)' -use_Mixed_Melt=True -use_Revision=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_Velocity_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(m/s)' -use_Mixed_Melt=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=9 -colorbar_units='(m/s)' -use_Mixed_Melt=True -use_Revision=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_three_melt_rates.sh

@@ -1,2 +1,2 @@
 cd ../
-./three_melt_rates.py  -ylim_min=240. -ylim_max=440.0  -save_figure=True  
+./three_melt_rates.py -use_Revision=True -time_ind=59 -ylim_min=240. -ylim_max=440.0  -save_figure=True  

### 2017-07-09 snapshots.py

@@ -373,7 +373,7 @@ def main(args):
 			direction='xz'
 			dist=xvec
 
-		for n in range(1):
+		for n in range(3):
 			#plot_anomaly=False
 			#vertical_coordinate='layers'  #'z'
 			#vertical_coordinate='z'
@@ -408,7 +408,7 @@ def main(args):
 				(y0 ,z0 ,data0) =interpolated_onto_vertical_grid(data0, elevation0, dist, vertical_coordinate)
 				data1=data1-data0
 				vmin=-vanom  ; vmax=vanom
-			print 'ZZZZZZZ', z1-z0	
+			#print 'ZZZZZZZ', z1-z0	
 
 			ax=plt.subplot(3,1,n+1)
 			if use_days_title is True:

### 2017-07-09 three_melt_rates.py

@@ -50,6 +50,12 @@ def parseCommandLine():
 	parser.add_argument('-ylim_max', type=float, default=440.0,
 		                        help='''Minimum y used for plotting (only applies to horizontal sections)''')
 	
+	parser.add_argument('-use_Revision', type='bool', default=True,
+		                        help='''When true, it uses the results of the Revision simulations (including new drag and rolling)    ''')
+	
+	parser.add_argument('-time_ind', type=int, default=40,
+		                        help='''Time index of snapshot 1  ''')
+	
 	optCmdLineArgs = parser.parse_args()
 	return optCmdLineArgs
 
@@ -74,11 +80,19 @@ def main(args):
 
 
 	#Defining path
+	use_Revision=args.use_Revision
+	Revision_flag=''
 	path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/'
 	extension='00060101.icebergs_month.nc'
-	IceShelfMelt_file = path +  'ALE_z_After_melt_Collapse_diag_Strong_Wind/' +extension
 	IcebergMelt_file = path + 'ALE_z_Berg_melt_After_melt_Collapse_diag_Strong_Wind/' + extension
+	if use_Revision is True:
+		Revision_flag='Revision_'
+		path=path+Revision_flag
+	IceShelfMelt_file = path +  'ALE_z_After_melt_Collapse_diag_Strong_Wind/' +extension
 	MixedMelt_file = path + 'ALE_z_Mixed_Melt_After_melt_Collapse_diag_Strong_Wind/' + extension
+	print IceShelfMelt_file
+	print IcebergMelt_file
+	print MixedMelt_file
 
 	#Geometry files
 	Shelf_path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Shelf/Melt_on_without_decay_with_spreading_trimmed_shelf/' 
@@ -104,7 +118,7 @@ def main(args):
 	if plot_horizontal_field is True:
 		cmap='jet'
 		time_slice=''
-		time_slice_num=40
+		time_slice_num=args.time_ind
 		flipped=False
 		#field='uo' ; vmin=-0.03  ; vmax=0.03 ; cmap='bwr'; time_slice='mean'
[…]

### 2017-07-09 Scripts_for_paper_figures/Fig_Collapse_solo_melt.sh
Updating figures

@@ -1,2 +1,2 @@
 cd ../
-./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -ylim_min=240. -ylim_max=440.0 -broken_shelf=True -use_Mixed_Melt=True -use_Mixed_Melt=True  -use_Revision=True -save_figure=True  
+./static_shelf_solo.py -three_fields_flag=plot_melt_sst_ustar_berg -ylim_min=240. -ylim_max=440.0 -broken_shelf=True -use_Mixed_Melt=True -use_Mixed_Melt=True  -use_Revision=True -time_slice_num=99 -save_figure=True  

### 2017-07-09 Scripts_for_paper_figures/Fig_Drift_berg.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -use_Mixed_Melt=True -plot_second_colorbar=True -use_Revision=True -second_colorbar_units='(m)' -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=79 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Drift' -use_Mixed_Melt=True -plot_second_colorbar=True -use_Revision=True -second_colorbar_units='(m)' -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_SST_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=9 -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=30 -time_ind3=99 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.4  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -use_Mixed_Melt=True -dashed_num=12 -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_Splitting_berg.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -use_Mixed_Melt=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=True -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=99 -cmap=jet -field=temp -vmin=-1.8 -vmax=-1.3  -use_days_title=False -mask_using_bergs=True -dir_slice_num=1 -colorbar_units='(deg C)' -simulation='Splitting' -plot_second_colorbar=True -second_colorbar_units='(m)' -use_Revision=True -use_Mixed_Melt=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_Temperature_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.5 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=9 -colorbar_units='(deg C)' -use_Mixed_Melt=True -use_Revision=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=99 -cmap=jet -field=temp -vmin=-2.0 -vmax=1.0  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.5 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(deg C)' -use_Mixed_Melt=True -use_Revision=True -save_figure=True

### 2017-07-09 Scripts_for_paper_figures/Fig_Velocity_section_Collapse.sh

@@ -1,2 +1,2 @@
 cd ../
-./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=59 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=9 -colorbar_units='(m/s)' -use_Mixed_Melt=True -use_Revision=True -save_figure=True
+./snapshots.py -extension=ocean_month.nc -plot_horizontal_field=False -use_ALE=True  -time_ind1=14 -time_ind2=29 -time_ind3=99 -cmap=jet -field=v -vmin=-0.1 -vmax=0.1  -use_days_title=False -mask_using_bergs=True -plot_anomaly=False -vanom=0.1 -vertical_coordinate=layers -xmin=130.0 -xmax=430.0 -dir_slice_num=12 -colorbar_units='(m/s)' -use_Mixed_Melt=True -use_Revision=True -save_figure=True

### 2017-07-09 three_melt_rates.py
Updating figures

@@ -84,10 +84,10 @@ def main(args):
 	Revision_flag=''
 	path='/lustre/f1/unswept/Alon.Stern/MOM6-examples_Alon/ice_ocean_SIS2/Tech_ISOMIP/Bergs/'
 	extension='00060101.icebergs_month.nc'
-	IcebergMelt_file = path + 'ALE_z_Berg_melt_After_melt_Collapse_diag_Strong_Wind/' + extension
 	if use_Revision is True:
 		Revision_flag='Revision_'
 		path=path+Revision_flag
+	IcebergMelt_file = path + 'ALE_z_Berg_melt_After_melt_Collapse_diag_Strong_Wind/' + extension
 	IceShelfMelt_file = path +  'ALE_z_After_melt_Collapse_diag_Strong_Wind/' +extension
 	MixedMelt_file = path + 'ALE_z_Mixed_Melt_After_melt_Collapse_diag_Strong_Wind/' + extension
 	print IceShelfMelt_file
@@ -141,10 +141,13 @@ def main(args):
 		for k in range(3):
 			ax=plt.subplot(1,3,k+1)
 			#Temporary line:
-			if k==1:
-				time_slice_num=40
-			else:
-				time_slice_num=args.time_ind
+			print k
+			#if k==1:
+			#	time_slice_num=40
+			#elif k==0:
+			#	time_slice_num=59
+			#else:
+			time_slice_num=args.time_ind
 			data=load_and_compress_data(filename_list[k],field=field,time_slice=time_slice,time_slice_num=time_slice_num,rotated=rotated)
 
 			mask_open_ocean = True

### 2017-11-06 Lagrangian_MISOMIP.tex
Draft so far

@@
 %ceberg calving is an important feature of the Antarctic environment. In where giant pieces of the ice shelf break away from the shelf to form giant tabular icebergs and drift into the open ocean. 
-
-The current generation of ice-ocean models is unable to represent ice-shelf calving in a physically realistic way despite its controlling role of the mass balance and extent of Antarctic ice shelves.
-This is primarily due to static Eulerian approach of the current ice-shelf/sub-ice-shelf cavity models that does not allow separation and modification of computational domains that would represent breaking of pieces of an ice shelf that would become freely floating icebergs.
-In this study we develop a new ice-shelf cavity model where the ice shelf is constructed out of Lagrangian elements that are bonded together by numerical bonds.
-This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-We test this Lagrangian ice -shelf model by simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-The Lagrangian model results are compared to results of an Eularian model simulations with identical configuration.
-Results show that the Lagrangian and Eularian models are almost indistinguishable.
+The current generation of ice-ocean models is unable to represent ice-shelf calving in a physically realistic way, despite the controlling role that calving plays in the setting mass balance and extent of Antarctic ice shelves.
+The infrequency of large calving events together with the difficulty of placing observational instruments around tabular icebergs means that little is known about how calving icebergs affect the ocean.
+%This is primarily due to the static Eulerian modeling framework employed by current ice-shelf/sub-ice-shelf cavity models.
+This approach does not allow separation and modification of computational domains, which would represent breaking of pieces of an ice shelf, that would become freely floating icebergs.
+In this study we present a novel model of an ice-shelf cavity below a breakable ice shelf constructed of Lagrangian elements.
+% In this Lagrangian ice shelf model, large pieces of the ice shelf can break away from the ice shelf and become tabular icebergs. 
+We validate the Lagrangian ice shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an Eulerian model simulations with identical configuration.
+%simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). 
+%The Lagrangian model results are compared to results of an Eulerian model simulations with identical configuration.
+%Results show that the Lagrangian and Eulerian models are almost indistinguishable, which  provides a proof of concept for the Lagrangian model.
 % For example, differences in the models are two orders of magnitude smaller than the differences observed when changing the ocean model coordinate system. 
-The similarly between the Eularian and Lagrangian models in a static ice-shelf configuration provides a proof of concept for the Lagrangian model, and means that we can confidently use Lagrangian ice-shelf models to extend the capabilities of ice-shelf-cavity models.% The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
+%The similarly between the Eulerian and Lagrangian models in a static ice-shelf configuration provides a proof of concept for the Lagrangian model, and means that we can confidently use Lagrangian ice-shelf models to extend the capabilities of ice-shelf-cavity models.
+The Lagrangian model is then used to simulate the ocean's response to a tabular iceberg calving away from the ice shelf.
+The results show a calving iceberg can lead to large changes in the surrounding ocean.
+Changes in circulation patterns and enhanced vertical mixing are observed at the ice front and around the iceberg following the calving event.
+The vertical mixing at the ice front warms the ocean surface and cools the water column at depth, allowing cooler waters to enter the ice shelf cavity, which in turn leads to reduced melt rates within the cavity.
+A Taylor column is observed below the iceberg, which moves with the iceberg as it drifts into the open ocean.
+As the tabular iceberg drifts further from the ice shelf, the circulation within the ice shelf cavity tends towards a new steady state, consistent with the new ice shelf geometry.
 
@@
 \item A novel modeling framework is developed to model breakable ice shelves and ice-shelf cavities using Lagrangian elements, held together by numerical bonds.
-\item The ocean circulation beneath a (static) Lagrangian ice shelf is almost indistinguishable from the circulation beneath an Eularian ice-shelf model run in an identical configuration. 
-\item The similarity between the models provides a proof of concept for the Lagrangian model, allowing the Lagrangian model to be used simulations involving tabular iceberg calving. 
+\item The ocean circulation beneath a (static) Lagrangian ice shelf is almost indistinguishable from the circulation beneath an Eulerian ice-shelf model run in an identical configuration, which  provides a proof of concept for the Lagrangian model.
+\item Enhanced ocean mixing occurs near the ice front after a large calving event, which warms the ocean surface and cools the water column at depth.
+The cool sub-surface anomalies enter the ice shelf cavity and cause reduced basal melt in the period following the calving event.
 \end{itemize}
@@
 All models of ice-shelf cavities to date have omitted ice-shelf breaking and iceberg detachment.
-This is because (i) there is much uncertainty about the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on static Eularian grids, which do not lend themselves to modeling iceberg detachment and drift.
+This is because (i) there is much uncertainty about the physics that govern ice-shelf breaking \citep{Benn2007, Alley2008, Levermann2012, Bassis2013}, and (ii) current models of ice-shelf cavities represent the ice shelves on static Eulerian grids, which do not lend themselves to modeling iceberg detachment and drift.
 In contrast, existing {\it iceberg} models represent icebergs as Lagrangian particles, since this is a convenient way to model discrete objects traveling over large distances \citep{Bigg1997, Gladstone2001, Martin2010, Marsh2015}.
@@
 This Lagrangian framework allows for large pieces of the ice shelf to break away and become tabular icebergs.
-An example of this enhanced capability of the Lagrangian model is demonstrated in Figures \ref{fig:Iceberg_calving}, which shows a tabular iceberg drifting away from an idealized ice shelf (see \citet{Stern2017} for more details).
+An example of this enhanced capability of the Lagrangian model is demonstrated in Figures \ref{fig:SST_snapshots}, which shows a tabular iceberg drifting away from an idealized ice shelf.% (see \citet{Stern2017} for more details).
 
 %This iceberg drifting simulation is described in a separate study \citep{Stern2017}.
-%Here, we instead focus comparing the Lagrangian model to existing Eularian model in a static ice shelf configuration. 
-However, before analyzing the improved capabilities of the Lagrangian ice-shelf model, it is necessary to thoroughly test and benchmark the Lagrangian ice-shelf model in a more familiar configuration.
-To do this we compare the Lagrangian ice-shelf-cavity model to existing Eularian model in a static ice-shelf configuration. 
+%Here, we instead focus comparing the Lagrangian model to existing Eulerian model in a static ice shelf configuration. 
+%We validate the Lagrangian ice-shelf model by simulating the flow beneath a static idealized ice shelf cavity,
+%, developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP) \citep{Asay-Davis2016}.
+%and comparing the results to the results obtained used an existing Eulerian model simulations with identical configuration. The results show that the two models are almost indistinguishable
+
+%However, before analyzing the improved capabilities of the Lagrangian ice-shelf model, it is necessary to thoroughly test and benchmark the Lagrangian ice-shelf model in a more familiar configuration.
+To do this we compare the Lagrangian ice-shelf-cavity model to existing Eulerian model in a static ice-shelf configuration.
 For this comparison, we use the model configuration developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP).
-The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, and (ii) to prove that the Lagrangian model can replicate the behavior of an Eularian ice-shelf model when modeling ocean cavities beneath static ice shelves.
-%In particular, we aim to show that for a static ice shelf, Lagrangian ice-shelf model gives the same results as an Eularian model in the same configuration (using the same ocean model). 
-Demonstrating that the Lagrangian model compares well to more traditional Eularian models is a prerequisite for using the Lagrangian model to move beyond the capabilities of the Eularian model, and increases our confidence in more complex Lagrangian simulations involving calving icebergs.
+
+The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, (ii) to validate the Lagrangian model by simulating the flow beneath a static idealized ice shelf cavity, and comparing it to an Eulerian ice-shelf model run in an identical configuration, and (iii) to demonstrate the enhanced capabilities of the Lagrangian ice-shelf model by simulating a large iceberg calving away from the idealized ice shelf.
+Modeling the ocean during and after a calving event, allows us to observe how the calving event affects the ocean near and beneath the ice shelf, and how changes in the ocean feedback onto the ice shelf.
+
+%In particular, we aim to show that for a static ice shelf, Lagrangian ice-shelf model gives the same results as an Eulerian model in the same configuration (using the same ocean model). 
+%Demonstrating that the Lagrangian model compares well to more traditional Eulerian models is a prerequisite for using the Lagrangian model to move beyond the capabilities of the Eulerian model, and increases our confidence in more complex Lagrangian simulations involving calving icebergs.
 %An analysis of an ice-shelf cavity with a tabular iceberg drifting away from the from the ice shelf is provided in a separate study \citep{Stern2017}.
 
-%Results from this static ice shelf experiment are compared to results using an existing Eularian ice shelf coupled to the same ocean model.
+%Results from this static ice shelf experiment are compared to results using an existing Eulerian ice shelf coupled to the same ocean model.
 The strong agreement between these two models implies that the Lagrangian ice shelf has been implemented correctly.
-This is a good starting point for moving beyond the capabilities of the Eularian model.
+This is a good starting point for moving beyond the capabilities of the Eulerian model.
 The Lagrangian model is then used to simulate a tabular iceberg calving away from the ice shelf and drifting into the open ocean.
@@
 
-%\sout{The goal of this study is to show that this Lagrangian ice-shelf model can replicate the results of an Eularian ice-shelf model when used in a static ice-shelf configuration (with all the elements being held stationary).
-}
-Although the ice elements do not move in the static ice-shelf experiment presented in this paper, this configuration is a relevant test for the Lagrangian model, as it tests the interpolation and aggregation between Eularian and Lagrangian grids, and also tests the coupling between the ocean and ice-shelf models.
-
-In this section we describe the fully dynamic Lagrangian ice-shelf model.
-We then focus on element packing and interpolation between the Eularian and Lagrangian grids, which are the parts of the model which are relevant to static ice simulations.
-A complete description of the KID model, including details of the momentum budget and element interactions can be found in \citet{Stern2017}.
+In this section we describe the Lagrangian ice-shelf model.
+A more complete description of the model including numerical methods and algorithms used to track the numerical bonds can be found in \citet{Stern2017}.
 
@@
 The elements also interact with other elements and can be `bonded' together by numerical bonds, which allow many elements to move together as a unit.
-By bonding many ice elements together, the model is able to form larger structures, such as tabular icebergs or ice shelves (Figures \ref{fig:Schematic}).
-% The interactive forces between elements aggregate to give the larger structures an effective rheology.
-
+By bonding many ice elements together, the model is able to form larger structures, such as tabular icebergs or ice shelves (Figure \ref{fig:Schematic}).
+
+\subsection{Equations of motion}
+The momentum equation for each element is given by 
+\begin{equation}
+\label{Iceberg_mom_eq}
+M \frac{D \vec{u}}{Dt}=\vec{F}_{A} + \vec{F}_{W}+ \vec{F}_{R}+\vec{F}_{C} +\vec{F}_{SS}+\vec{F}_{SI}+\vec{F}_{IA} ,
+\end{equation}
+where $\frac{D}{Dt}$ is the total (Lagrangian) derivative, $M$ is the mass of the element, $\vec{u}$ is the velocity of the element, and the terms on the right hand side give the forces on the element due to air drag $(\vec{F}_{A})$, water drag $(\vec{F}_{W})$, sea-ice drag $(\vec{F}_{SI})$, Coriolis force $(\vec{F}_{C})$, wave radiation force $(\vec{F}_{R})$, sea surface slope $(\vec{F}_{SS})$, and interactions with other elements ($\vec{F}_{IA}$).
+
+The forces on each element are set up such that in the absence of interactive forces, the ice elements follow the same equations used in iceberg drift models \citep{Bigg1997, Gladstone2001, Martin2010}).
+This ensures that when an element breaks away from an ice shelf and drifts in the open ocean, it is modeled as a freely drifting iceberg.
+When an element is connected to the ice shelf (or larger ice structure), it also experiences forces due to interactions with the elements around it.
+The details of these interactive forces between elements are described below.
+A complete description of the other forces acting on the iceberg is provided in \citet{Stern2017}.
+
+\subsection{Interactive Forces} 
+Interactive forces are applied between elements to prevent elements overlapping with neighboring elements, and prevent `bonded' elements from moving apart from one another (see Figures \ref{fig:Schematic}a).
+The interactive forces are modeled as damped elastic forces: For two elements $i$ and $j$ at positions $\vec{x}_{i}$ and $\vec{x}_{j}$, the elastic and damped components of the interactive force are given by
+\begin{equation}
+\label{F_elastic}
+(\vec{F_{e}})_{ij}= -\kappa_{e}  \bigg(d_{ij} -L_{ij} \bigg) M_{ij} \vec{r}_{ij},
+\end{equation}
+and 
+\begin{equation}
+\label{F_damping} 
+%(\vec{F_{d}})_{ij}=  M_{ij} \Bigg (-c_{r_{||}} P_{\vec{r}_{ij}}  - c_{r_{\perp}} P_{\vec{r}_{ij}^{\perp}} \Bigg ) \cdot (\vec{u_{i}} -\vec{u_{j}} ) 
+(\vec{F_{d}})_{ij}=   - M_{ij} c_{r_{||}} P_{\vec{r}_{ij}}  \cdot (\vec{u_{i}} -\vec{u_{j}} ), 
+\end{equation}
+respectively.
+Here $d_{ij} =  |\vec{x}_{i}-\vec{x}_{j} |$ is the distance between the elements, $\vec{r}_{ij}= \frac{(\vec{x_{i}} -\vec{x_{j}})}{|\vec{x_{i}} -\vec{x_{j}}|}$ is the directional unit vector between element.
+$L_{ij}$ is the average diameter of the two elements (assuming a circular shape for the elements), $\kappa_{e}$ is the spring constant, and $M_{ij}$ is the minimum of the masses of elements $i$ and $j$.
+$P_{\vec{r}_{ij}}$ is the projection matrix that projects onto $\vec{r}_{ij}$, and $c_{r_{||}}$ is the drag coefficient.
+We set $c_{r_{||}}=2\sqrt{\kappa_{e} }$, so that the elastic force is critically damped.
+The total interactive $\vec{F}_{IA}$ on an element is found by summing up the all the interactive forces with other elements.
+
+\subsection{Melt rates}
 The thickness and extent of the Lagrangian elements change due to melting when they are exposed to above-freezing ocean mixed-layer temperatures.
-The melt rates of the elements are prescribed using parametrizations developed for iceberg and ice-shelf decay \citep{Bigg1997, Holland1999, Gladstone2001, Martin2010}.
-The corresponding heat, salt and mass fluxes are passed to the ocean to simulate freshwater injection to the ocean surface.
-% In this study we focus on comparing the model to a Eularian model, so the melt rate of elements is determined using the three equation model for basal melt, which is a typical melting parametrization used beneath ice shelves \citep{Holland1999}.
+The melt rates of the elements in the interior of a large structure (such as an ice shelf or large icebergs) are parametrized using the three-equation model, which is a typically melt rate parametrization used to model basal melt beneath ice shelves \citep{Holland1999}.
+The melt rates of freely floating ice elements (not bonded to other elements) are parametrized using standard parametrizations for iceberg \citep{Bigg1997, Gladstone2001, Martin2010}.
+For elements at the edge of large structures (with edges partly exposes to the open ocean) the melt rates are computed using a weighted sum of the ice shelf and and iceberg melt rate parametrization, with the weights being proprotional to the fraction of the element's perimeter which exposed to the open ocean \citep{Stern2017}.
 
 \subsection{Initializing element geometry and packing}
-The elements in the Lagrangian model are shaped as equally-sized regular hexagons.
-We initialize the Lagrangian model by positioning the elements in a staggered lattice of equally-size hexagons, so that the elements fit together and perfectly tile the ice-shelf surface (Figures \ref{fig:Schematic}b).
+The elements in the Lagrangian model are shaped as equally-sized regular hexagons (although they are treated as circular for the purpose of element interactions).
+We initialize the Lagrangian model by positioning the elements in a staggered lattice of equally-size hexagons, so that the elements fit together and perfectly tile the ice-shelf surface (Figures \ref{fig:Schematic}).
 Hexagonal elements are used so that when adjacent pairs of elements are bonded together, the network of bonds form equilateral triangles, which gives rigidity to the larger structure \citep{Stern2017}.
-\textcolor{red}{???
-Maybe add some comments about accuracy of continuity of fields like pressure etc on the discrete elements???}
+By using hexagonal elements, which can be packed together without any gaps, the element initialization is perfectly space filling.
+This allows the model to simulate continuous ice shelves (without gaps or crevasses), and allows the results to be more easily comparable with Eularian ice shelf models.
+In this study, we only use hexagonal elements, however, other element geometries, can be used when less precision is needed.
 
 \subsection{Interpolation and aggregation onto the Lagrangian grid}
-When constructing ice shelves using the Lagrangian model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
+%When constructing ice shelves using the Lagrangian model, the collection of elements can be thought of as being a `Lagrangian grid' for the ice shelf.
 In this framework the nodes of the Lagrangian grid (elements) can move at every time step, altering the shape of the ice shelf.
-This is in contrast to the more traditional approach of modeling ice shelves on an Eularian grid, where the grid is fixed in time.
+This is in contrast to the more traditional approach of modeling ice shelves on an Eulerian grid, where the grid is fixed in time.
 Using a Lagrangian grid is a convenient framework for modeling breakable ice shelves since it allows pieces of the ice-shelf grid to break away from the ice shelf and become part of the iceberg grid \citep{Stern2017}.
 
-In the experiments presented in this study, the ice-shelf model is coupled to an ocean model, which is runs on a static Eularian grid.
+%In the experiments presented in this study, the ice-shelf model is coupled to an ocean model, which is runs on a static Eulerian grid. 
 At every time step, ice-shelf fields are passed from the ice-shelf model to the ocean model and from the ocean model to the ice-shelf model.
-Four ocean (mixed layer) fields are passed from the ocean model to the ice-shelf model: temperature, salinity and zonal and meridional velocities.
-These fields are interpolated onto the Lagrangian elements using a bilinear interpolation scheme.
-
-At the end of a ice-shelf model time step, ice-shelf fields are aggregated from the elements back onto the Eularian ocean grid, and are then passed from the ice-shelf model to the ocean model.
-The aggregation from the Lagrangian grid to the Eularian ocean grid is done in a way which is consistent with the shape of the elements.
-For the purposes of aggregation, we assume that the elements have surface areas that are shaped as regular hexagons.
-Element's properties are aggregated from the Lagrangian grid to the Eularian grid by exactly calculating the fraction of an element that is intersects each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
-\textcolor{red}{???
-This part is a bit hard to follow, it needs more explanation.
-Don't know whether a schematic could help.
-???}
-
-\subsection{Lagrangian vs Eularian ice-shelf model}
-In the next section, simulations using the Lagrangian ice-shelf model are compared to simulations using an Eularian ice-shelf model with an an identical configuration.
-While the internal framework and grids of the Eularian and Lagrangian ice-shelf models are quite different, both models are coupled to the ocean model using the same coupling structure.
-Five fields are passed from the ice-shelf models to ocean model: mass, surface area, temperature flux, salinity flux and mass flux.
-The Eularian model uses the same grid as the ocean model, while in the Lagrangian model these fields are aggregated onto the ocean model grid before being passed through the coupler.
+Fields which are passed from the ocean model to the Lagrangian ice shelf model have to be interpolated from the Eulerian grid onto the Lagrangian grid (i.e.: onto the elements).
+This is done using a bilinear interpolation scheme.
+Four ocean fields are passed from the ocean model to the ice-shelf model: temperature, salinity and zonal and meridional velocities.
+
+At the end of an ice-shelf model time step, ice-shelf fields are aggregated from the elements back onto the Eulerian ocean grid, and are then passed from the ice-shelf model to the ocean model. 
+The aggregation from the Lagrangian elements onto the Eulerian grid is done by calculating the fraction of each element's volume that lies in each ocean grid cell, and dividing the fields in proportion to this fraction.
+For example, the amount of ice mass aggregated onto a given ocean grid cell is found by summing up the masses of all elements which intersect that grid cell, only counting the part of an element's mass that  actually intersects the ocean grid cell.
+When calculating the intersection between an element and a grid cell, we assume that the elements have surface areas that are shaped as regular hexagons.
+Seven fields are passed from the ice-shelf models to ocean model: iceberg mass and surface area (used the upper-ocean pressure field), temperature flux, salinity flux and mass flux, and meridian and zonal velocity (used to calculate the momentum flux).
+
+%While the internal framework and grids of the Eulerian and Lagrangian ice-shelf models are quite different, both models are coupled to the ocean model using the same coupling structure.Five fields are passed from the ice-shelf models to ocean model: mass, surface area, temperature flux, salinity flux and mass flux.
+The Eulerian model uses the same grid as the ocean model, while in the Lagrangian model these fields are aggregated onto the ocean model grid before being passed through the coupler.
 Once in the ocean model, these fields and are used to: (i) apply a pressure to the ocean surface, \textcolor{red}{???
@@
 What if an ocean would be z-coordinate, what would be an equivalent of this condition???}(ii) alter the upper-ocean boundary condition to reflect that the ocean is covered by ice, \textcolor{red}{another ambiguous statement} and (iii) apply salt, temperature and mass fluxes associated with ice-shelf melting and freezing.
-
-Since the coupling with the ocean model is handled in the same way for both the Eularian and Lagrangian models and both models are coupled to the same ocean model, any differences between the two models in the static ice-shelf configuration (using the same melt rate parametrization) are likely due to the interpolation/aggregation between the ice and ocean grids.
-By accurately aggregating fields from the Lagrangian grid to Eularian ocean grids, we aim to make the Lagrangian ice-shelf model behave like the Eularian ice-shelf model in static ice-shelf simulations.
-%Apart from the step of aggregating between the Lagrangian and Eularian grids, the interaction between the Lagrangian ice-shelf model and ocean model is exactly the same as the interaction between an Eularian ice-shelf model and an ocean model.
+%
+%Since the coupling with the ocean model is handled in the same way for both the Eulerian and Lagrangian models and both models are coupled to the same ocean model, any differences between the two models in the static ice-shelf configuration (using the same melt rate parametrization) are likely due to the interpolation/aggregation between the ice and ocean grids.
+By accurately aggregating fields from the Lagrangian grid to Eulerian ocean grids, we aim to make the Lagrangian ice-shelf model behave like the Eulerian ice-shelf model in static ice-shelf simulations.
 
@@
 %\sout{The KID model is used to represent the ice shelf in an idealized ice-shelf cavity MOM6 ocean flow.
-The simulations are repeated using an Eularian ice shelf with an identical configuration.
-The details of the experimental setup for both the Lagrangian and Eularian models are presented here.}
+The simulations are repeated using an Eulerian ice shelf with an identical configuration.
+The details of the experimental setup for both the Lagrangian and Eulerian models are presented here.}
 %
@@
 \subsection{Ocean Model}
-The Lagrangian and Eularian ice shelves are coupled to the MOM6 ocean model \citep{Hallberg2013}. 
+The Lagrangian and Eulerian ice shelves are coupled to the MOM6 ocean model \citep{Hallberg2013}. 
 The ocean model is run using a hybrid vertical coordinate system which blends a sigma-level and a z-level coordinate \citep{Stern2017}, implemented using the ALE method \citep{White2009}.
@@
 
-\subsection{Lagrangian ice-shelf simulations:}
-%\subsection{Lagrangian and Eularian ice shelf simulations:}
+\subsection{Initializing Lagrangian elements:}
+%\subsection{Lagrangian and Eulerian ice shelf simulations:}
 The Lagrangian ice shelf is created using 10882 Lagrangian hexagonal elements with sides of length $S=0.98$ km .
@@
 Gaps along the boundaries are filled in using smaller elements so that the total ice-shelf area is preserved.
-The initial mass of the ice elements is determined by a preprocessing inversion step, which is the inverse of the aggregation procedure discussed in Section 2.3.
-
-%Figure \ref{fig:ISOMIP_mass_and_topog}c shows what the ice-shelf draft would be if the draft were calculated from the mass of elements in each ocean grid cell without spreading an element's mass across neighboring cells (i.e.: treating elements as point masses).
-Figure \ref{fig:ISOMIP_mass_and_topog}b shows the draft after spreading the mass across grid cells.
-When the mass spreading interpolation scheme is not used, grid artifacts seen in the ice-shelf draft (Figure \ref{fig:ISOMIP_mass_and_topog}c).
-The grid artifacts are much reduced when the mass spreading interpolation is used (Figure \ref{fig:ISOMIP_mass_and_topog}b).
-%
-\subsection{Eularian ice-shelf simulations:}
-The Eularian ice-shelf simulation is performed using an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, which is an optional module of the the MOM6 ocean model.
+The initial mass of the ice elements is determined using bilinear interpolation from a prescribed gridded ice mass field.
+
+\subsection{Eulerian ice-shelf:}
+We validate the Lagrangian ice shelf model by comparing the results to the results found using an Eularian ice shelf model in an identical static ice shelf configuration (see below).
+The Eulerian ice-shelf simulation is performed using an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, which is an optional module of the the MOM6 ocean model.
 The ice shelf is initialized on the same grid as the ocean model with a horizontal resolution of $\Delta x = 2$ km.
 The ice-shelf thickness field is initialized using the same ice-shelf draft used for the Lagrangian model (Figure \ref{fig:ISOMIP_mass_and_topog}).
-
-%\subsection{Eularian ice shelf simulation:}
-\subsection{Sub-ice-shelf melting}
-The melt rates in both the Lagrangian and Eularian ice-shelf simulations are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}.
-In both experiments the ice shelf is held stationary.
-In the Eularian code, this is achieved by setting the ice-shelf velocity to zero, while in Lagrangian ice shelf, the element velocities are set to zero.
-In both simulations, the ice shelf is thermodynamically active and is able to `melt' but has a time-invariant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
+The melt rates in the Eulerian ice-shelf simulation are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}, with the same parameters used to calculate the ice shelf melt rates in the Lagrangian model.
+
+\subsection{Static ice shelf simulation:}
+We test the Lagrangian ice shelf model by simulating the flow beneath the idealized ice shelf with the ice shelf being held statice (i.e.: elements are held stationary).
+In this simulation the ice shelf is thermodynamically active and is able to `melt' but has a time-invariant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
 In this setup, ice-shelf melting generates temperature and salinity fluxes into the ocean, but does not change the thickness of the ice shelf / ice elements.
-This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
-%The simulation is run for 5 years, and results are considered after the spinup period.
-
-\section{Results}
-\subsection{Results from the Lagrangian ice-shelf simulation}
-The results from the Lagrangian ice-shelf simulation fit within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
-The ocean temperatures inside the domain are warmer than the in-situ freezing point (Figure \ref{fig:static_solo_temp_v_v}a), and cause melting at the ice-shelf base (Figure  \ref{fig:static_solo_melt}c).
-The meltwater entering the domain is more buoyant than the water around it, and rises along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_v_v}).
+%This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
+A constant wind stress $\vec{\tau} = <\tau_{x},\tau_{y}> = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to the ocean surface.
+Note that this wind stress is was not applied in the original MISOMIP experiments \citep{Asay-Davis2016}.
+The model is spun up for 5 years, and the analysis is done on the second 5 years after the spinup.
+
+\subsection{Iceberg calving simulation:}
+In a second experiment, the Lagrangian ice shelf model is used to simulate a tabular iceberg detaching from the ice shelf, and drifting into the open ocean.
+The iceberg calving simulation is initialized using the final state of the static Lagrangian ice shelf simulation (i.e.: at time $t = 10 $ years).
+When initializing the calving event, we bypass the question of how to prescribe a physical calving law \citep{Benn2007, Alley2008, Levermann2012, Bassis2013} by manually breaking off a semi-circular iceberg.
+
+In the iceberg calving simulation, all ice elements initially within a 14.4~km radius of the center of the ice front to move freely while the other ice elements continue to be held stationary.
+Ice elements less than 12~km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
+A ring of elements whose distance, $d$, from the ice front center obeys $12 \textrm{ km} \leq   d \leq14.4 \textrm{ km}$, are allowed to move freely, but have all their bonds removed.
+Elements in this half annulus represent fragments of the ice shelf which calve into small pieces during the calving event.
+
+\textcolor{red}{Should these two simulations be included?}
+\subsubsection{Fixed iceberg velocity simulation}
+To aid in the analysis of the ocean response to iceberg calving, another iceberg calving simulation was preformed, using a fixed iceberg velocity.
+This fixed velocity iceberg simulation is identical to the iceberg calving simulation (Section 3.6), except that the velocity of the calving icebergs is prescribed as $\vec{v} = = < 0, 0.01 >$ m/s.
+Since the iceberg speed is prescribed, this simulation is not fully coupled.
+
+\subsubsection{Missing-Iceberg simulation}
+A simulation is preformed to help analyze how the changing ice shelf geometry affects the sub-ice-shelf circulation and hydrography.
+In this simulation, calving iceberg (with the same geometry as the iceberg simulations above) is removed at the start of the simulation, and the simulation is spun up from rest.
+The simulation is run for 10 years, so that it is easily comparable to the Static ice shelf simulation (described in Section 3.5).
+
+%\section{Results}
+\section{Static ice-shelf simulation results}
+\subsection{Static ice-shelf simulation}
+The results in the Lagrangian static ice-shelf simulation fit within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
+The ocean temperatures inside the domain are warmer than the in-situ freezing point (Figure \ref{fig:static_solo_temp_v_v}a), and cause melting at the ice-shelf base (Figure  \ref{fig:static_solo_melt}a).
+The meltwater entering the domain is more buoyant than the water around it, and rises along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_v_v}b,c).
 %As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_v_v}a).
 This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water, which provides the thermal energy required for continuous ice-shelf melt.
+Strong meridional jets are observed at the ice front along the flanks of the domain, fluxing water into the ice shelf cavity on the eastern flank and allowing water to leave the ice shelf cavity on the western side (Figure \ref{fig: meridional_velocity_snapshots}a).
+The meridional flow in the center of the ice front is much smaller, consistent with the dynamical barrier at the ice shelf front discussed in previous modeling and experimental studies \citep{Holland2001, Stern2014}.
 
 The highest melt rates are observed within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
-These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}d) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front (Figure  \ref{fig:static_solo_melt}c).
-
-%\subsubsection{Comparison with Eularian ice-shelf model}
-\subsection{Comparison of Lagrangian and Eularian ice-shelf models}
+These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}b) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front (Figure  \ref{fig:static_solo_melt}c).\\
+
+%\subsubsection{Comparison with Eulerian ice-shelf model}
+
+\subsection{Comparison of Lagrangian and Eulerian ice-shelf models}
 The Lagrangian ice-shelf model results are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration (see Section 3.4).
 To get a quantitative comparison, we compare the Lagrangian ice-shelf model results to a simulation using an Eulerian ice-shelf model with an identical configuration.
+Since the Lagrangian and Eularian ice shelf models are coupled to the same ocean model and the ice shelf models use the same parametrization for ice shelf melt, we expect the results of the two models to be the almost the same, with the only differences arising from the interpolation and aggregation schemes (see Section 2.6).
+This allows us to use the Eularian ice shelf model to validate the Lagrangian model.
+
 The results show that two simulations are almost indistinguishable.
-This is demonstrated, for example, in Figures \ref{fig:Bt_comparison}, which shows the time-averaged barotropic stream function of the Lagrangian (Figures \ref{fig:Bt_comparison}a) and Eularian (Figures \ref{fig:Bt_comparison}b) simulations, and the difference between the two (Figures \ref{fig:Bt_comparison}c).
-%For scale, we note that the differences between the barotropic stream functions in the two simulations, are two orders of magnitude smaller than the differences between two simulations using the same Eularian ice shelf with different vertical coordinate systems described in Section 3.2 (not shown).
-The difference between the Lagrangian and Eularian barotropic stream functions are two orders of magnitude smaller than typical differences observed between simulations using different models in the MISOMIP \citep{Asay-Davis2016}.
-The similarity of the Lagrangian and Eularian simulations are also reflected in the fact that the simulations have very similar ice-shelf melt rates and ocean temperature/salinity profiles (shown in Figures \ref{fig:Melt_comparison} and Figures \ref{fig:Salt_comparison} in the supplementary materials).
+This is demonstrated, for example, in Figures \ref{fig:Bt_comparison}, which shows the time-averaged barotropic stream function of the Lagrangian (Figures \ref{fig:Bt_comparison}a) and Eulerian (Figures \ref{fig:Bt_comparison}b) simulations, and the difference between the two (Figures \ref{fig:Bt_comparison}c).
+%For scale, we note that the differences between the barotropic stream functions in the two simulations, are two orders of magnitude smaller than the differences between two simulations using the same Eulerian ice shelf with different vertical coordinate systems described in Section 3.2 (not shown).
+The difference between the Lagrangian and Eulerian barotropic stream functions are two orders of magnitude smaller than typical differences observed between simulations using different models in the MISOMIP \citep{Asay-Davis2016}.
+The similarity of the Lagrangian and Eulerian simulations are also reflected in the fact that the simulations have very similar ice-shelf melt rates and ocean temperature/salinity profiles (shown in Figures \ref{fig:Melt_comparison} and Figures \ref{fig:Salt_comparison} in the supplementary materials).
 
@@
 
-%The good agreement between the Eularian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
+%The good agreement between the Eulerian and Lagrangian simulations is not too surprising since the two models are coupled to the same ocean model in exactly the same configuration.
 Recall that the role of the ice-shelf model in these simulations is to (i) apply a pressure to the ocean surface, (ii) provide melt fluxes to the ocean, and (iii) alter the upper ocean boundary condition below the ice shelf.
-The agreement between the Eularian and Lagrangian simulations is a confirmation that the Lagrangian model is able to simulate sub-ice-shelf cavities as well as the Eularian model does.
-This is a good starting point for moving beyond the capabilities of the Eularian model.
-
-\textcolor{red}{???
-This section is a bit thin.
-Perhaps it'd be worth looking at more fields and also discuss to under which circumstances differences between the KID and Eularian models can be larger and start affecting simulations and the results ???}
+The agreement between the Eulerian and Lagrangian simulations is a confirmation that the Lagrangian model is able to simulate sub-ice-shelf cavities as well as the Eulerian model does.
+This is a good starting point for moving beyond the capabilities of the Eulerian model.
+
+\section{Iceberg calving simulation results}
+The infrequency of large calving events together with the difficulty of placing observational instruments around tabular icebergs means that little is known about how calving icebergs affect ocean circulation around the iceberg and at the ice front.
+The Lagrangian ice shelf model developed in this study allows us for the first time to simulate an iceberg calving away from the ice shelf, and to study what effect this has on the ocean around the iceberg and beneath the ice shelf.
+Since the Lagrangian iceberg/ice shelf model is fully coupled to the ocean, the iceberg motion affects the ocean hydrography, and the changing ocean conditions feedback onto the ice.
+%The effect of iceberg calving on the ocean around the iceberg is discussed in \citep{Stern2017}.
+Here we focus on how the calving event affects the region close to the ice front and beneath the ice shelf.
+
+The results below show that the calving of a large tabular iceberg can cause significant changes to the ocean stratification and circulation around the iceberg and at the ice shelf front. 
+%The changes at the ice shelf front persist, even once the tabular iceberg has drifted away from the ice shelf cavity, eventually reaching a new equilibrium consistent with the new ice front geometry.
+Changing conditions at the ice front alter the temperature fluxes into the ice shelf cavity, which impacts the hydrography inside the ice shelf cavity, and drives changes to the ice-shelf melt rates across the entire ice shelf.
+Local changes to the ocean hydrography are also observed around the iceberg.
+A Taylor column is observed below the iceberg, which travels with the iceberg as it drifts into the open ocean.
+
+\subsection{At the ice front}
+%\subsubsection{Surface warming}
+After the iceberg calves, the large semi-circular tabular iceberg drifts to the northeast, driven primarily by the wind and Coriolis force.
+As this large iceberg and the smaller fragments moves through the water a warming of the sea surface temperature is observed around the iceberg and at the ice front (Figure \ref{fig:SST_snapshots}).
+The warm anomalies near the ice front persist and strengthen, even once the large iceberg fragment has drifted away.
+Part of this warmed surface water at the ice front is advected to west by the strong currents at the ice front (Figure \ref{fig:SST_snapshots}c).
+On the western side of the domain, most of this warm anomaly is advected northwards, while some of the warmth is forced southward, and is able to subduct beneath ice shelf on the western side of the ice shelf front.
+
+%\subsubsection{Sub-surface cooling}
+In addition to the surface warming, a subsurface cooling is also observed around the iceberg and at the ice front in the days following the calving event (Figure \ref{fig:Temperature_section_Collapse_yz}).
+The sub-subsurface cooling and warm surface temperature anomalies are accompanied by a freshening at depth and increase in surface salinity (not shown).
+Since the background stratification has positive temperature and salinity gradients (cold/fresh water above over warm/salty), the pattern of warm salty surface anomalies above cold fresh subsurface anomalies suggests that these changes are driven by enhanced vertical mixing.
+
+At the ice front, the subsurface negative temperature anomalies strengthen over time and within a month of the calving event, the negative anomalies occupy most of the water column close to the ice front (Figure \ref{fig:Temperature_section_Collapse_xz}).
+The zonal current along the ice front drives the cool anomaly to the west, causing an enhancement of the cool anomalies on the western side of the ice shelf front (Figure \ref{fig:Temperature_section_Collapse_xz}c).
+Most of the subsurface cooling occurs outside of the ice shelf cavity, as the dynamical barrier caused by the ice shelf inhibits exchange of water across the ice front. 
+However over time, an increasing amount of cooler water is able to enter the ice shelf cavity, and is advected below the ice shelf (Figure \ref{fig:Temperature_section_Collapse_yz}).
+
+%The cooler waters entering the ice shelf cavity mix with the water within the ice shelf cavity, causing the strength of the cool anomaly to be reduced towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
+
+%\subsubsection{Circulation Changes}
+The changing temperature flux into the ice shelf cavity in the center of the domain is partly driven by changing ocean velocities, observed at the ice front directly after the iceberg calves.
+The pre-calving meridional flow at the ice front is dominated by strong boundary currents moving water into and out of the ice shelf cavity along the flanks for the domain, while very little meridional velocity is observed in the center of the domain (as discussed in Section 4.1).
+After the iceberg calves, large meridional velocities are observed at the ice front (Figure \ref{fig:meridional_velocity_snapshots}).
+The structure and variability of the velocity field observed at the ice front after calving, suggest the elevated flow speed are driving by ocean instabilities that are triggered by the calving iceberg.
+These instabilities presumably a key driver of the enhanced vertical mixing described above.
+\textcolor{red}{[How do these instabilities work?]}
+%The motion near the ice front remains elevated while the tabular iceberg in the vicinityand then dissipate, presumably finding a new equilibrium.
+
+\subsection{Inside the ice shelf cavity }
+%\subsubsection{Melt rate response}
+The combination of cool sub-surface temperature anomalies and elevated ocean velocities at the ice front, results in a temperature flux across the ice front, as cool temperature anomalies to enter the ice shelf cavity (Figure \ref{fig:Temperature_section_Collapse_yz}).
+Once the cooler water has entered the ice shelf cavity, the anomalies spread southwards within the ice shelf cavity, eventually reaching all the way to the grounding line.
+As the cool water spreads into the cavity, it mixes with the water within the ice shelf cavity, causing a reduction in the strength of the anomaly towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
+
+The cooling of the water inside the ice shelf cavity after calving leads to a reduction of the melt rates at the base of the ice shelf (Figure \ref{fig:Melt_rate_snapshots}).
+The reduced melt rates occur over a wide area extending from the newly calved ice front, all the way towards the grounding line.
+The negative melt rate anomalies increase over time, as more cold water enters the ice shelf cavity.
+The strongest negative anomalies are observed near the ice front, while the strength of the negative melt rate anomalies are reduced towards the grounding.
+The reduction in melt rates are up to  0.5 m per year, which is small compared to the mean melt rates near the grounding line, but is a substantial fraction of the melt at intermediate depths (Figure \ref{fig:static_solo_melt}a).
+
+Near the ice front, the competing effects of warm surface water subducting beneath the ice shelf on the flanks of the domain, and the cool water entering the ice shelf in the enter of the domain, lead to a complex of pattern of positive and negative melt rate anomalies within 20 km of the ice front (Figure \ref{fig:static_solo_melt}).
+The strongest positive anomalies are observe on the western side of the ice shelf front, while the strongest negative melt rate anomalies are observed in the center of the domain.
+This is likely related to the geometry of the calving iceberg.
+
+The changes in ice shelf melt rates following the calving event are primarily driven by changing ocean temperatures at the base of the ice shelf.
+In contrast the ocean velocities, and hence the frictional velocity at the ice base, remain largely unchanged after the calving event (see Figure \ref{fig:ustar_calving} in the supplementary material), and do not play a large role in the changing melt rates.
+
+The presence of a northern boundary in our simulation mean that we are unable to entirely remove the iceberg from the domain and observe the system approaching a new equilibrium state.
+However, a comparison between the iceberg calving simulation and the missing-iceberg simulation (where the model was spun up with the iceberg removed from the start of the simulation) shows that after 60 days the hydrography inside the ice shelf cavity in the iceberg-calving simulation appears to be qualitatively similar to missing-iceberg simulation steady state (see Figure \ref{fig:broken_melt} in the supplementary material, for example).
+This suggests that the processes occurring at the ice front directly after calving are transient processes which allow the system to move towards a steady state that is largely controlled by the ice shelf geometry.
+Since the ice shelf geometry in our simulation is highly idealize, it is unclear whether the adjustment time scale seen here is relevant to real-world ice shelves.
+
+\subsection{Around the tabular iceberg}
+As the iceberg drifts through the water, it affects the ocean velocity and stratification in its immediate vicinity.
+As was seen near the ice front, the enhanced mixing around the iceberg causes warm salty anomalies around the iceberg near the surface, and cool fresh anomalies at depth (Figure \ref{fig:Taylor_column}a).
+%As the iceberg drifts aways from the ice shelf, these anomalies are observed most strongly directly around the iceberg, suggesting that the enhanced mixing around this iceberg is a locally driven process, created by the presence of the iceberg in the water column.
+As the iceberg drifts away from the ice shelf, the iceberg leaves a trail of warm surface anomalies in its wake that maps out the iceberg path of the iceberg (as discussed in \citet{Stern2017}) (Figure \ref{fig:SST_snapshots}c).
+Similarly, cool subsurface temperature anomalies are observed in the wake of the iceberg at depth (not shown).
+
+Strong barotropic ocean currents are observed directly below the iceberg as it drifts through the water (Figure \ref{fig:Taylor_column}b).
+The column of uniform velocity below the iceberg is evidence of the Taylor column that forms below the iceberg.
+The sudden changing in ocean thickness when moving from below the iceberg to the open ocean causes a dynamical barrier which separates the flow beneath the iceberg from the rest of water column (as was seen across the ice front).
+Similar Taylor columns have been observed above sea mounts [reference].
+Elevated largely barotropic flows are observed around the iceberg as it drifts.
+These currents are a result of complex interaction between the iceberg on the surrounding ocean.
+More work is needed (perhaps in a further idealized setting) to understand these ineractoins.
+
+Directly below the iceberg on the ocean floor, an increased dipycnal mixing is observed in the bottom boundary layer.
+This elevated mixing in the bottom boundary layer is likely a result of a barotropic adjustment driven by the iceberg motion.
+As the iceberg drifts through the water, the region of elevated dipycnal mixing shifts so that it remains directly below the iceberg.
+Similarly elevated rates in dipycnal mixing are observed at the bottom of the water column near the ice front.
 
@@
 In this framework, the ice shelf is constructed out of many Lagrangian elements, which are bonded together by numerical bonds.
-The collection of Lagrangian elements store the ice-shelf properties.
-Unlike Eularian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf.
-This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:Iceberg_calving}).
-This capability is currently not possible using more traditional Eularian models \citep{Stern2017}.
-%
-%A consequence of using a Lagrangian ice-shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eularian ocean grid in order to be passed to the ocean model.
+%The collection of Lagrangian elements store the ice-shelf properties.
+By breaking the bonds, we can use the Lagrangian model to simulate iceberg calving, and to observed the ocean response to large calving events (Figures  \ref{fig:SST_snapshots}).
+This capability is currently not possible using more traditional Eulerian models \citep{Stern2017}.
+
+% Unlike Eulerian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf. 
+%This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:SST_snapshots}).
+%
+%A consequence of using a Lagrangian ice-shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eulerian ocean grid in order to be passed to the ocean model.
 This is done by exactly calculation the fraction of each ice element that lies in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
 
-The framework capabilities are demonstrated by modeling the circulation beneath a (static) idealized ice shelf, which was developed as part of the MISOMIP inter-comparison project.
-The results from the Lagrangian ice-shelf model fit within our paradigm of understanding for circulation within ice-shelf cavities: buoyant meltwater that enters the ice-shelf cavity drives freshwater plumes at the ice-shelf base, which drives the circulation within the cavity.
+We validate the Lagrangian ice shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an existing Eulerian model simulations with identical configuration.
+The results from the static ice shelf simulation using the Lagrangian ice-shelf model fit within our paradigm of understanding for circulation within ice-shelf cavities: buoyant meltwater that enters the ice-shelf cavity drives freshwater plumes at the ice-shelf base, which drives the circulation within the cavity.
 The circulation, melt rates and ocean hydrography achieved using the Lagrangian ice shelf compare well with other simulations in the MISOMIP experiments.
-
-A direct comparison \sout{comparison} between the Lagrangian and a Eularian ice-shelf model coupled to the same ocean model shows that the results are extremely similar.
-Differences between the Lagrangian and Eularian ice shelves models (resulting from interpolation errors) are much smaller than the differences observed when changing the ocean vertical coordinate system (for example).
-Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eularian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
+Comparing the results to the results obtained using an Eularian model in an identical static configuration showed that the two models simulations are very similar.
+Small differences between the Lagrangian and Eulerian ice shelves models result from interpolation errors, but these errors are two orders of magnitude smaller than typical difference observe between simulations using different ocean models (for example).
+Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eulerian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
+
+The Lagrangian model is then used to simulate iceberg calving.
+In the iceberg calving experiment, enhanced ocean mixing is observed near the ice front and around the tabular iceberg after the iceberg detaches from the ice shelf.
+The enhanced mixed brings warm water to the surface, leading to a warming of sea surface temperatures around the iceberg and ice front.
+The mixing allow leads to a cooling of sub-surface waters near the ice front.
+These cooler waters enter the ice shelf cavity and lead to reduced melt rates at the base of the ice shelf in the months following the calving event.
 
@@
 Real-world ice shelves are non-Newtonian fluids which are able to flow, allowing the ice-shelf geometry to change over time.
-Much progress has been made in modeling ice-shelf flows in an Eularian framework \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
+Much progress has been made in modeling ice-shelf flows in an Eulerian framework \citep{Grosfeld2004, Goldberg2012, De_Rydt2006}.
 A challenge will be to develop models with similar ice dynamics in a Lagrangian framework.
@@
 The bond strength could also evolve dynamically as bonds get `damaged'.
-The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eularian ice-shelf studies \citep{Pralong2005, Borstad2012}.
+The evolution of bond damage could be tracked using damage mechanics, as has been done in some Eulerian ice-shelf studies \citep{Pralong2005, Borstad2012}.
 %
@@
 % in order to represent large breakable ice shelves and icebergs
+
+\section{To dos}
+\vspace{5mm}
+\subsection{Things to add:}
+\textcolor{red}{
+1) Time series showing variably quantities at points in the domain (e.g.: temperature flux, velocity, total melt...)\\
+2) Some aggregated numbers to emphasis some ideas (e.g.: Total change in melt volume and circulation....)\\
+3) Add some perspectives to the Conclusion/Discussion about whether we can trust the results shown here.\\
+}
+
+\subsection{New/Improvd figures}
+\textcolor{red}{
+1) Figure \ref{fig:Taylor_column}, domesticating below the iceberg (Temperature, velocity, kd (many v too)).
+2) Time series figure
+3) Ocean velocity snapshots xz 
+4) Ocean velocity snapshots yz (maybe)
+3) Late time figure  (maybe - see supp)
+}
+
+\subsection{Some other points to perhaps include}
+\textcolor{red}{
+1) The no-bonds simulation and the fixed velocity simulation both show the same surface warming and subsurface cooling signals, indicating that this is quite a robust feature.\\
+\\
+2) The fact that the warming/cooling is seen directly around the calving iceberg (see following video) indicates that the mechanism is a local mechanism rather than a global basin adjustment\\
+\\
+3) The changes in melt appear to tend towards the results from the Broken Shelf simulation, suggesting local processes around the iceberg causing warming/cooling, help the system to move between steady states, which are imposed by the large scale geometry and forcing.\\
+\\
+4) Looking at Kd shows largest mixing regions occur in places where there is open water.
+No enhanced Kd is observed below the iceberg (because it is too deep).
+This suggests that changes in mixing are caused by new regions being exposed to open water (i.e.: wind).\\
+\\
+5) A simulation using no sub-ice shelf friction has a very similar signal, suggesting that the signal is not caused my iceberg induced mixing.\\
+\\
+6) Is the enhanced mixing at the bottom of the water column around the iceberg related to the warming/cooling signal? Why is it there at all?\\
+\\}
+\subsection{Other questions:}
+\textcolor{red}{
+1) What is happening with the enhanced mixing exactly?
+It looks like it is driven by new area being exposed to open water.
+But does this make sense?
+When an iceberg moves, where does the water which takes its place come from?
+\\
+2) Does the surface warming and subsurface cooling have to be a result of enhanced mixing? Is it possible that mixing is occurring even though kd is small?
+Possibilities:\\
+}
 
@@
 
-\bibitem[Robinson et al (2012)]{Robinson2012}
-Robinson, N. J., M. J. M. Williams, P. J. Barrett, and A. R. Pyne (2010), Observations of flow and ice-ocean interaction beneath the McMurdo
-Ice Shelf, Antarctica, {\it J. Geophys. Res.}, 115, C03025
+\bibitem[Robinson and Williams (2012)]{Robinson2012}
+Robinson, N.
+J., and Williams, M.
+J.
+M.
+(2012).
+Iceberg-induced changes to polynya operation and regional oceanography in the southern Ross Sea, Antarctica, from in situ observations.
+{\it Antarctic Science}, 24(5), 514-526.
 
@@
  \clearpage
--
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
-\caption{ {Snapshots of a simulation where a Lagrangian ice-shelf calves a tabular iceberg viewed (a) from above and (b) from the side.
+
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
+%\caption{ {Snapshots of a simulation where a Lagrangian ice-shelf calves a tabular iceberg viewed (a) from above and (b) from the side.
 The snapshots is taken 30 days after calving.
@@
 The solid line in panel (a) shows the position of the grounding line.}}
-\end{center}
-\label{fig:Iceberg_calving}
+%\end{center}
+%\label{fig:Iceberg_calving}
+%\end{figure}
+% \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
+\caption{ {Snapshots of sea surface temperature anomalies in the iceberg calving simulation.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.
+The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:Temperature_section_Collapse_xz}, respectively}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:SST_snapshots}
 \end{figure}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Lagrangian_shelf_domain.png}
-\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eularian static ice-shelf simulations}}
+\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eulerian static ice-shelf simulations}}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_v_v.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
 \caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
 \caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration.
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_barotropic_sf.png}
+\caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration.
 Panel (c) shows the difference between panels (a) and (b).
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x20_anomaly.png}
+\caption{ {Snapshots of vertical sections of ocean temperature anomaly at $x$=40~km in the iceberg-calving experiment.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+In each panel, the base of the ice before calving and at the time of the snapshot are shown by the solid and dashed black lines, respectively.
+Positions that were not the ocean interior at in both snapshots are masked in grey.
+The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Temperature_section_Collapse_yz}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
+\caption{ {Snapshots of vertical sections of ocean temperature anomaly at $y$=300~km in the tabular-iceberg-calving experiment.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Temperature_section_Collapse_xz}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_melt_m_per_year_anomaly.png}
+\caption{ { Snapshots of the melt rate anomaly, at the ice-shelf base in the tabular iceberg calving simulation.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Melt_rate_snapshots}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x153.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\caption{ {Snapshots of vertical sections of meridional velocity anomaly at $y$=300~km in the tabular-iceberg-calving experiment.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+\end{center}
+\label{fig:meridional_velocity_snapshots}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+%\includegraphics[width=0.99\textwidth]{}
+\caption{ {Snapshots of vertical sections of ocean (i) temperature anomaly, (ii) meridional velocity,  and (iii) dipyncnal diffusivity at $y$=???~km in the tabular-iceberg-calving experiment.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+The position of the vertical transects is shown by the ???
+dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+\end{center}
+\label{fig:Taylor_column}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/.png}
+\caption{ {Time series of temperature fluxes, velocities, melt rates....}}
+\end{center}
+\label{fig:Time_Series}
+\end{figure}
  \clearpage
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_melt.png}
-\caption{ {Time-averaged melt rates in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration.
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_melt.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_melt.png}
+\caption{ {Time-averaged melt rates in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration.
 Panel (c) shows the difference between panels (a) and (b).
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
-\caption{ {Time-averaged vertical sections of salility in the (a) Lagrangian and (b) Eularian simulations in the static ice-shelf configuration at at $x$=54~km.
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_salt_layers.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\caption{ {Time-averaged vertical sections of salinity in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration at at $x$=54~km.
 Panel (c) shows the difference between panels (a) and (b).
@@
 
+  \begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Broken_Compare_melt_m_per_year_anomaly.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\caption{ {(a) Snapshot of the melt rate at the base of the ice shelf 60 days after the calving event in the tabular-iceberg-calving simulation.
+(b) Steady state melt rate of the simulation that was spun-up from rest with the semi-circular iceberg removed..}}
+\end{center}
+\label{fig:broken_melt}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_ustar_iceberg.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\caption{ {Snapshots of frictional velocity at the ice-shelf base in the tabular-iceberg-calving simulation. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.}}
+\end{center}
+\label{fig:ustar_calving}
+\end{figure}
+ \clearpage
+
  \end{document}

### 2018-05-27 Lagrangian_MISOMIP.tex
Updating Lagrangian_MISOMIP

@@
 \item The ocean circulation beneath a (static) Lagrangian ice shelf is almost indistinguishable from the circulation beneath an Eulerian ice-shelf model run in an identical configuration, which  provides a proof of concept for the Lagrangian model.
-\item Enhanced ocean mixing occurs near the ice front after a large calving event, which warms the ocean surface and cools the water column at depth.
+%\item Enhanced ocean mixing occurs near the ice front after a large calving event, which warms the ocean surface and cools the water column at depth.
 The cool sub-surface anomalies enter the ice shelf cavity and cause reduced basal melt in the period following the calving event.
+\item After an iceberg calves away from an ice shelf, a complex interaction is observed between the iceberg motion and ocean hydrography.
+This interaction leads to the formation of a Taylor column beneath the iceberg, a subsurface cooling at the ice front, and reduced melt rates within the ice shelf cavity.
 \end{itemize}
@@
 When calculating the intersection between an element and a grid cell, we assume that the elements have surface areas that are shaped as regular hexagons.
-Seven fields are passed from the ice-shelf models to ocean model: iceberg mass and surface area (used the upper-ocean pressure field), temperature flux, salinity flux and mass flux, and meridian and zonal velocity (used to calculate the momentum flux).
+Seven fields are passed from the ice-shelf models to ocean model: iceberg mass and surface area (used to calculate the upper-ocean pressure field), temperature flux, salinity flux and mass flux, and meridian and zonal velocity (used to calculate the momentum flux).
 
@@
 
- \section{Experiment Setup}
+ \section{Experiment setup}
 % the proof of concept for
@@
 
-\subsection{Ocean Model}
+\subsection{Ocean model}
 The Lagrangian and Eulerian ice shelves are coupled to the MOM6 ocean model \citep{Hallberg2013}. 
@@
 
-\subsection{Initializing Lagrangian elements:}
+%\subsection{Initializing Lagrangian elements:}
+\subsection{Lagrangian ice-shelf model:}
+The Lagrangian ice-shelf simulations are performed using the Kinematic Iceberg Dynamics (KID) model described in Section 2.
 %\subsection{Lagrangian and Eulerian ice shelf simulations:}
@@
 
-\subsection{Eulerian ice-shelf:}
-We validate the Lagrangian ice shelf model by comparing the results to the results found using an Eularian ice shelf model in an identical static ice shelf configuration (see below).
+\subsection{Eulerian ice-shelf model:}
 The Eulerian ice-shelf simulation is performed using an existing Eulerian ice-shelf cavity model \citep{Goldberg2012}, which is an optional module of the the MOM6 ocean model.
@@
 
-\subsection{Static ice shelf simulation:}
-We test the Lagrangian ice shelf model by simulating the flow beneath the idealized ice shelf with the ice shelf being held statice (i.e.: elements are held stationary).
-In this simulation the ice shelf is thermodynamically active and is able to `melt' but has a time-invariant thickness (as specified in the Ocean0 experiment in the MISOMIP \citep{Asay-Davis2016}).
-In this setup, ice-shelf melting generates temperature and salinity fluxes into the ocean, but does not change the thickness of the ice shelf / ice elements.
-%This can be thought to represent an ice shelf in dynamic equilibrium where the melt is exactly balanced ice-shelf advection.
+\section{Model validation}
+The Lagrangian ice shelf model is validated by comparing it to an existing Eularian ice shelf model in an identical static configuration.
+
+\subsection{Setup of static validation experiment:}
+The experimental setup for the model validation experiment is based on the Ocean0 MISOMIP experiment \citep{Asay-Davis2016}.
+In this experiment the ice shelves are thermodynamically active but have a time-invariant thickness.
+Temperature and salinity fluxes from ice shelf melt drive the circulation within the cavity.
+
 A constant wind stress $\vec{\tau} = <\tau_{x},\tau_{y}> = < 0.05, 0.05 >$  $\frac{N}{m^{2}}$ is applied to the ocean surface.
 Note that this wind stress is was not applied in the original MISOMIP experiments \citep{Asay-Davis2016}.
-The model is spun up for 5 years, and the analysis is done on the second 5 years after the spinup.
-
-\subsection{Iceberg calving simulation:}
-In a second experiment, the Lagrangian ice shelf model is used to simulate a tabular iceberg detaching from the ice shelf, and drifting into the open ocean.
-The iceberg calving simulation is initialized using the final state of the static Lagrangian ice shelf simulation (i.e.: at time $t = 10 $ years).
-When initializing the calving event, we bypass the question of how to prescribe a physical calving law \citep{Benn2007, Alley2008, Levermann2012, Bassis2013} by manually breaking off a semi-circular iceberg.
-
-In the iceberg calving simulation, all ice elements initially within a 14.4~km radius of the center of the ice front to move freely while the other ice elements continue to be held stationary.
-Ice elements less than 12~km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
-A ring of elements whose distance, $d$, from the ice front center obeys $12 \textrm{ km} \leq   d \leq14.4 \textrm{ km}$, are allowed to move freely, but have all their bonds removed.
-Elements in this half annulus represent fragments of the ice shelf which calve into small pieces during the calving event.
-
-\textcolor{red}{Should these two simulations be included?}
-\subsubsection{Fixed iceberg velocity simulation}
-To aid in the analysis of the ocean response to iceberg calving, another iceberg calving simulation was preformed, using a fixed iceberg velocity.
-This fixed velocity iceberg simulation is identical to the iceberg calving simulation (Section 3.6), except that the velocity of the calving icebergs is prescribed as $\vec{v} = = < 0, 0.01 >$ m/s.
-Since the iceberg speed is prescribed, this simulation is not fully coupled.
-
-\subsubsection{Missing-Iceberg simulation}
-A simulation is preformed to help analyze how the changing ice shelf geometry affects the sub-ice-shelf circulation and hydrography.
-In this simulation, calving iceberg (with the same geometry as the iceberg simulations above) is removed at the start of the simulation, and the simulation is spun up from rest.
-The simulation is run for 10 years, so that it is easily comparable to the Static ice shelf simulation (described in Section 3.5).
-
-%\section{Results}
-\section{Static ice-shelf simulation results}
-\subsection{Static ice-shelf simulation}
-The results in the Lagrangian static ice-shelf simulation fit within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
-The ocean temperatures inside the domain are warmer than the in-situ freezing point (Figure \ref{fig:static_solo_temp_v_v}a), and cause melting at the ice-shelf base (Figure  \ref{fig:static_solo_melt}a).
-The meltwater entering the domain is more buoyant than the water around it, and rises along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_v_v}b,c).
-%As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_v_v}a).
-This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water, which provides the thermal energy required for continuous ice-shelf melt.
-Strong meridional jets are observed at the ice front along the flanks of the domain, fluxing water into the ice shelf cavity on the eastern flank and allowing water to leave the ice shelf cavity on the western side (Figure \ref{fig: meridional_velocity_snapshots}a).
-The meridional flow in the center of the ice front is much smaller, consistent with the dynamical barrier at the ice shelf front discussed in previous modeling and experimental studies \citep{Holland2001, Stern2014}.
-
-The highest melt rates are observed within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
-These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}b) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
-Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front (Figure  \ref{fig:static_solo_melt}c).\\
-
-%\subsubsection{Comparison with Eulerian ice-shelf model}
-
-\subsection{Comparison of Lagrangian and Eulerian ice-shelf models}
-The Lagrangian ice-shelf model results are qualitatively similar to most of the simulations from the MISOMIP experiment \citep{Asay-Davis2016}, which use a similar configuration (see Section 3.4).
-To get a quantitative comparison, we compare the Lagrangian ice-shelf model results to a simulation using an Eulerian ice-shelf model with an identical configuration.
+
+The elements in the Lagrangian ice shelf simulation are held stationary so that the ice shelf is static and comparable to the Eularian simulation.
+The models are spun up for 5 years. The analysis is performed on year 6 to 10 of the simulations.
+
+\subsection{Results of validation experiment}
+
+The results of the static ice shelf simulations in both simulations are qualitatively similar to results presented in \citep{Asay-Davis2016}.
+Melting at the base of the ice shelf drives a circulation within the cavity and strong jets are observed at the ice front and along the sides of the domain (Figure \ref{fig:Bt_comparison}).
+A more complete description of the circulation is provided in the supplementarity material.
+
 Since the Lagrangian and Eularian ice shelf models are coupled to the same ocean model and the ice shelf models use the same parametrization for ice shelf melt, we expect the results of the two models to be the almost the same, with the only differences arising from the interpolation and aggregation schemes (see Section 2.6).
-This allows us to use the Eularian ice shelf model to validate the Lagrangian model.
-
 The results show that two simulations are almost indistinguishable.
-This is demonstrated, for example, in Figures \ref{fig:Bt_comparison}, which shows the time-averaged barotropic stream function of the Lagrangian (Figures \ref{fig:Bt_comparison}a) and Eulerian (Figures \ref{fig:Bt_comparison}b) simulations, and the difference between the two (Figures \ref{fig:Bt_comparison}c).
+This is demonstrated, for example, in Figure \ref{fig:Bt_comparison}, which shows the time-averaged barotropic stream function of the Lagrangian (Figures \ref{fig:Bt_comparison}a) and Eulerian (Figures \ref{fig:Bt_comparison}b) simulations, and the difference between the two (Figures \ref{fig:Bt_comparison}c).
 %For scale, we note that the differences between the barotropic stream functions in the two simulations, are two orders of magnitude smaller than the differences between two simulations using the same Eulerian ice shelf with different vertical coordinate systems described in Section 3.2 (not shown).
@@
 
-\section{Iceberg calving simulation results}
+%\section{Results}
+
+\section{Iceberg calving experiment}
+
 The infrequency of large calving events together with the difficulty of placing observational instruments around tabular icebergs means that little is known about how calving icebergs affect ocean circulation around the iceberg and at the ice front.
-The Lagrangian ice shelf model developed in this study allows us for the first time to simulate an iceberg calving away from the ice shelf, and to study what effect this has on the ocean around the iceberg and beneath the ice shelf.
+The Lagrangian ice-shelf model developed in this study allows us for the first time to simulate an iceberg calving away from the ice shelf, and to study what effect this has on the ocean around the iceberg and beneath the ice shelf.
 Since the Lagrangian iceberg/ice shelf model is fully coupled to the ocean, the iceberg motion affects the ocean hydrography, and the changing ocean conditions feedback onto the ice.
@@
 
+In this section, the Lagrangian ice shelf model is used to simulate a tabular iceberg detaching from the ice shelf, and drifting into the open ocean. 
 The results below show that the calving of a large tabular iceberg can cause significant changes to the ocean stratification and circulation around the iceberg and at the ice shelf front.
+
+\subsection{Setup of iceberg calving experiment:}
+The iceberg calving experiment is initialized using the final state of the static Lagrangian ice shelf simulation (i.e.: at time $t = 10 $ years).
+When initializing the calving event, we bypass the question of how to prescribe a physical calving law \citep{Benn2007, Alley2008, Levermann2012, Bassis2013} by manually breaking off a semi-circular iceberg.
+All ice elements initially within a 14.4~km radius of the center of the ice front are allowed to move freely while the other ice elements continue to be held stationary.
+Ice elements less than 12~km from the center of the ice front, are bonded together to form a semi-circular tabular iceberg.
+A ring of elements whose distance, $d$, from the ice front center obeys $12 \textrm{ km} \leq   d \leq14.4 \textrm{ km}$, are allowed to move freely, but have all their bonds removed.
+%Elements in this half annulus represent fragments of the ice shelf which calve into small pieces during the calving event.
+
+%\textcolor{red}{Should these two simulations be included?}
+%\subsubsubsection{Fixed iceberg velocity simulation}
+%To aid in the analysis of the ocean response to iceberg calving, another iceberg calving simulation was preformed, using a fixed iceberg velocity.
+This fixed velocity iceberg simulation is identical to the iceberg calving simulation (Section 3.6), except that the velocity of the calving icebergs is prescribed as $\vec{v} = = < 0, 0.01 >$ m/s.
+Since the iceberg speed is prescribed, this simulation is not fully coupled.
+%
+%\subsubsection{Missing-Iceberg simulation}
+%A simulation is preformed to help analyze how the changing ice shelf geometry affects the sub-ice-shelf circulation and hydrography.
+In this simulation, calving iceberg (with the same geometry as the iceberg simulations above) is removed at the start of the simulation, and the simulation is spun up from rest.
+The simulation is run for 10 years, so that it is easily comparable to the Static ice shelf simulation (described in Section 3.5).
+
+\subsection{Results of iceberg calving experiment}
+
 %The changes at the ice shelf front persist, even once the tabular iceberg has drifted away from the ice shelf cavity, eventually reaching a new equilibrium consistent with the new ice front geometry.
-Changing conditions at the ice front alter the temperature fluxes into the ice shelf cavity, which impacts the hydrography inside the ice shelf cavity, and drives changes to the ice-shelf melt rates across the entire ice shelf.
-Local changes to the ocean hydrography are also observed around the iceberg.
-A Taylor column is observed below the iceberg, which travels with the iceberg as it drifts into the open ocean.
-
-\subsection{At the ice front}
+%Changing conditions at the ice front alter the temperature fluxes into the ice shelf cavity, which impacts the hydrography inside the ice shelf cavity, and drives changes to the ice-shelf melt rates across the entire ice shelf.
+A current is also observed circling the iceberg in a clockwise direction as the iceberg drift northwards.
+The  drive local changes to the ocean hydrography around the iceberg, and also influence the basin-wide circulation.
+% A Taylor column is observed below the iceberg, which travels with the iceberg as it drifts into the open ocean.
+
+%\subsection{Ocean response to iceberg detatchment}
 %\subsubsection{Surface warming}
-After the iceberg calves, the large semi-circular tabular iceberg drifts to the northeast, driven primarily by the wind and Coriolis force.
-As this large iceberg and the smaller fragments moves through the water a warming of the sea surface temperature is observed around the iceberg and at the ice front (Figure \ref{fig:SST_snapshots}).
-The warm anomalies near the ice front persist and strengthen, even once the large iceberg fragment has drifted away.
-Part of this warmed surface water at the ice front is advected to west by the strong currents at the ice front (Figure \ref{fig:SST_snapshots}c).
-On the western side of the domain, most of this warm anomaly is advected northwards, while some of the warmth is forced southward, and is able to subduct beneath ice shelf on the western side of the ice shelf front.
-
-%\subsubsection{Sub-surface cooling}
-In addition to the surface warming, a subsurface cooling is also observed around the iceberg and at the ice front in the days following the calving event (Figure \ref{fig:Temperature_section_Collapse_yz}).
-The sub-subsurface cooling and warm surface temperature anomalies are accompanied by a freshening at depth and increase in surface salinity (not shown).
-Since the background stratification has positive temperature and salinity gradients (cold/fresh water above over warm/salty), the pattern of warm salty surface anomalies above cold fresh subsurface anomalies suggests that these changes are driven by enhanced vertical mixing.
-
-At the ice front, the subsurface negative temperature anomalies strengthen over time and within a month of the calving event, the negative anomalies occupy most of the water column close to the ice front (Figure \ref{fig:Temperature_section_Collapse_xz}).
+%After the iceberg calves, the large semi-circular tabular iceberg begins to drift away from the ice shelf (Figure \ref{fig:SST_snapshots}).
+The iceberg drifts towards the northeast, driven primarily by the wind and Coriolis force.
+As the iceberg drifts, it rotates in a counter-clockwise direction.
+After about 45 days, the iceberg collides with the eastern boundary of the domain and from their continues to drift northwards.
+
+\subsubsection{Ocean response to iceberg detachment}
+Immediately after the numerical bonds are broken, a large semi-circular tabular iceberg detaches from the ice shelf, and begins to drift northwards (Figure \ref{fig:SST_snapshots}).
+The northwards motion of the iceberg creates a region of open water at the new calving front, between the ice shelf and the tabular iceberg.
+The formation of a region of open ocean behind the iceberg causes a sudden stretching of the water column in the wake of the iceberg, which drives an upwelling throughout the water column.
+The negative background temperature gradient (cold over warm) means that this upwelling is observed as warm water anomaly beneath newly formed ice front (Figure \ref{fig:Temperature_section_Collapse_yz}a and \ref{fig:Temperature_section_Collapse_xz}a).
+The warming is observed throughout the water column, but is largest near the surface.
+Similarly, the upwelling leads to increased salinity beneath newly formed ice front (not shown).
+
+The calving event also drives an immediate change in circulation around the newly created ice front as the ocean adjusts to the topographic changes. 
+Since the Coriolis parameter is negative, a stretching of the water column behind the iceberg has to be accompanied by the creation of negative relative vorticity in order for potential vorticity (PV) to be conserved.
+The creation of negative relative vorticity along the newly calved ice front, gives rise to a pair of oppositely orientated ocean jets running along the ice front.
+A westward barotropic jet is created to the south of the calving front, and an eastward barotropic jet is created to the north of the calving front (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}b).
+The positive gradient in zonal velocity created by this pair of oppositely orientated jets yields the negative relative vorticity, needed to conserve PV.
+
+To the north of the iceberg, the iceberg detachment has the opposite effect on the ocean.
+The forward movement of the iceberg causes a squeezing of the water column directly in front of the iceberg.
+This shortening of the water column causes a downwelling in the water column in front of the iceberg, which is observed as a cool water anomaly in front of the iceberg (Figure \ref{fig:Temperature_section_Collapse_yz}a).
+The squeezing of the water column generates positive relative vorticity, so that the total PV is conserved.
+The positive relative vorticity creates an eastward and westward jet to the south and north of the northern edge of the iceberg (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}b).
+The stretching and squeezing of the water column to the south and north of the iceberg, both contribute to the eastward jet which forms directly beneath the iceberg which plays an important role in driving iceberg motion.
+%The eastward jets created beneath the iceberg merge into one combined jet, so that the flow beneath the iceberg is towards the east.
+
+ \textcolor{red}{(If you have time, check whether when the wind goes in the other direction, the jet beneath the iceberg moves in the other direction.)}
+%\begin{equation}
+%q = \frac{f + \zeta}{h}
+%\end{equation}
+\subsubsection{Iceberg motion}
+After the iceberg breaks away from the ice shelf, the motion of iceberg is primarily driven by the drag from ocean currents beneath the iceberg, wind drag and by Coriolis force.
+The eastward jet beneath the iceberg drives the iceberg towards the east (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}b), while the wind and Coriolis force drive the iceberg offshore.
+Initially, as the iceberg drifts eastward, it collides with the ice shelf, which hinders its motion (Figure \ref{fig:SST_snapshots}a).
+Only once the iceberg has drifted sufficiently far northwards to be clear of the ice shelf, does it begin to drift towards the east.
+Once this happens, the iceberg velocity quickly adjusts so that it is approximately equal to the ocean velocity below the iceberg.
+% \textcolor{red}{(check this is true)}.
+As the iceberg drifts northwards, it rotates in a counter-clockwise direction (Figure \ref{fig:SST_snapshots}).
+
+%The rotation is partly due to the semi-circular shape of the iceberg being guided by the semi-circular ice front, but is also observed in experiments using rectangular icebergs, where it is mainly caused by the Coriolis force.
+The iceberg continues to rotate even after it has moved entirely away from the ice shelf.
+The motion of the iceberg plays a large role in setting the direction of the ocean flow below and around the iceberg, since the ocean has to adjust to topographical changes so that PV is conserved.
+This is illustrated, for example, by the change in orientation of the ocean jets running beneath the iceberg that occurs as the iceberg rotates (Figure \ref{fig:u_velocity_horizontal}b).
+An important consequence of the controlling effect of iceberg topography is formation of a Taylor Column below the iceberg: the water column below the iceberg is constrained to move at the same speed as the iceberg above, since differential motion would force the water column out from under the iceberg, causing the water column to stretch, and generating PV.
+This means that the column of water beneath the iceberg is largely separated from the water around the iceberg and strong gradients in temperature, salinity and velocity can exist at the iceberg edge.
+In our experiment, a Taylor Column is clearly observed below the iceberg throughout the simulation (Figure \ref{fig:Taylor_column}).
+%(the changes in PV associated with the rotation of the jets are ultimately driven by the external force of the wind)
+
+Once the iceberg reaches the eastern side of the domain, it begins to interact the boundary of the domain and with the southward boundary current running along the edge of the domain (Figures \ref{fig:SST_snapshots}b and \ref{fig:v_velocity_horizontal}c).
+The presence of the iceberg along the eastern boundary impedes the southward boundary current, so that the current has to flow to the west of the iceberg (Figure \ref{fig:v_velocity_horizontal}b). 
+The diverted current follows the topographic contour created by the iceberg so that it sets up a  counter-clockwise circulation running around the iceberg (Figure \ref{fig:u_velocity_horizontal}c).
+The eastward jet which was previously positioned beneath the iceberg shifts to the south and becomes part of the flow directing the boundary current around the iceberg.
+This counter-clockwise circulation around the iceberg remains around the iceberg until the end of the simulation.
+Interestingly, the iceberg continues to move northward despite the fact that it is moving within a southward flowing boundary current (Figure \ref{fig:Taylor_column}b).
+This is partly due to the Taylor Column beneath the iceberg, which allows the northward velocity beneath the iceberg to be separated from the southward moving current around the iceberg.
+
+%The iceberg continues to rotate as it approaches the side of the domain, while the mean iceberg motion is directed to move parallel to the eastern boundary so that the iceberg motion is towards the north.
+
+%The diverting of the flow towards the west is aided by the westward current in front of the iceberg (discussed above).
+
+%\textcolor{red}{Mention: Similar Taylor columns have been observed above sea mounts [reference].}
+
+%\textcolor{red}{Possibly include: Directly below the iceberg on the ocean floor, an increased dipycnal mixing is observed in the bottom boundary layer.
+This elevated mixing in the bottom boundary layer is likely a result of a barotropic adjustment driven by the iceberg motion.
+As the iceberg drifts through the water, the region of elevated dipycnal mixing shifts so that it remains directly below the iceberg.
+Similarly elevated rates in dipycnal mixing are observed at the bottom of the water column near the ice front.
+}
+
+%\subsection{Changes in stratification}
+%\subsection{Stratification at the ice front and around the iceberg}
+\subsubsection{Surface warming and sub-surface cooling}
+%After the iceberg calves, the large semi-circular tabular iceberg drifts to the northeast, driven primarily by the wind and Coriolis force. 
+After the tabular iceberg detaches from the ice shelf, a warming is observed throughout the water column to the south of the iceberg (Figure \ref{fig:Temperature_section_Collapse_yz}a, as discussed above).
+This warming extends to the ocean surface, resulting in warm sea surface temperature (SST) anomalies at the newly calved ice front and around the southern side of the iceberg (Figure \ref{fig:SST_snapshots} and \ref{fig:Temperature_section_Collapse_xz}a  \textcolor{red}{- make sure it is clear in the Figure}).
+In the weeks following calving, part of this warm SST anomaly remains at the ice front, influencing the heat flux into the ice shelf cavity, and some the SST anomaly drifts with the iceberg into the open ocean.
+
+The warm SST anomalies at the ice front persist and strengthen, even once the tabular iceberg has drifted away, as water continues to upwell at the newly formed ice front.
+Some of this warmed surface water is advected to west by the westward jet at the ice front (Figure \ref{fig:SST_snapshots}c).
+Once these warmed surface waters reach the western side of the domain, most of this warm anomaly is advected northwards following the western boundary, while some of the warmth is forced southward, and is able to subduct beneath ice shelf on the western side of the ice shelf front.
+
+The SST anomalies that drift along with the iceberg are initially concentrated along the curved southern side of the iceberg.
+As the tabular iceberg drifts away from the ice shelf (and begins to rotate), the currents that develop around the iceberg advect this warm SST anomaly counter-clockwise around the perimeter of the iceberg so that by 15 days after calving, the SST around the most of the iceberg's perimeter is anomalously warm (Figure \ref{fig:SST_snapshots}).
+As the iceberg drifts further into the open ocean, the warmed surface waters around the iceberg's perimeter mix with the ambient surface water, leaving a trail of warmed surface water which maps out the wake of the iceberg.
+It is likely that as the iceberg drifts, the motion of the iceberg and strong sheer in horizontal velocity at the iceberg edges contribute to continued upwelling, leading to further increased surface warming.
+
+As discussed above, the downwelling on the northern side of the iceberg observed immediately after calving, leads to a cooling/freshening of the water column beneath and to the north of the iceberg (Figure \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:Temperature_section_Collapse_xz}).
+As the iceberg drifts away from the ice shelf, the cool water anomalies remain beneath the iceberg, traveling with the iceberg into the open ocean, leaving a trail of cool subsurface temperature anomalies which maps out the (subsurface) wake of the iceberg (not shown).
+The pattern of warm surface anomalies around the iceberg, and cool subsurface anomalies around the iceberg, is clearly visible throughout the simulation (Figure \ref{fig:Taylor_column}c), and suggests continued vertical mixing around the iceberg perimeter as it drifts into the open ocean.
+
+About 5 days after calving, as the iceberg begins to rotate counter clockwise, the jet to the north of the iceberg begins to drive the cool water anomaly towards the ice front (Figure \ref{fig:u_velocity_horizontal}b).
+The strong jet moving towards the ice front causes water to subduct beneath the ice front, leading to further cool sub-surface anomalies.
+Below the depth of the ice shelf, the cool water anomalies are stronger than the warm water anomalies caused by the initial water column stretching.
+The subsurface negative temperature anomalies strengthen over time and within a month of the calving event, the negative anomalies occupy most of the water column close to the ice front (Figure \ref{fig:Temperature_section_Collapse_xz}).
+This subsurface cooling at the ice front is the most prominent temperature response observed in our iceberg calving experiments.
+Similar subsurface cooling at the ice front was observed in other experiments using different sizes and shapes for the calving iceberg (not shown).
+
 The zonal current along the ice front drives the cool anomaly to the west, causing an enhancement of the cool anomalies on the western side of the ice shelf front (Figure \ref{fig:Temperature_section_Collapse_xz}c).
 Most of the subsurface cooling occurs outside of the ice shelf cavity, as the dynamical barrier caused by the ice shelf inhibits exchange of water across the ice front. 
-However over time, an increasing amount of cooler water is able to enter the ice shelf cavity, and is advected below the ice shelf (Figure \ref{fig:Temperature_section_Collapse_yz}).
+However over time, an increasing amount of cooler water is able to enter the ice shelf cavity, and is advected below the ice shelf (Figure \ref{fig:Temperature_section_Collapse_yz}c).
 
 %The cooler waters entering the ice shelf cavity mix with the water within the ice shelf cavity, causing the strength of the cool anomaly to be reduced towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
-
 %\subsubsection{Circulation Changes}
-The changing temperature flux into the ice shelf cavity in the center of the domain is partly driven by changing ocean velocities, observed at the ice front directly after the iceberg calves.
+%The changing temperature flux into the ice shelf cavity in the center of the domain is partly driven by changing ocean velocities, observed at the ice front directly after the iceberg calves.
 The pre-calving meridional flow at the ice front is dominated by strong boundary currents moving water into and out of the ice shelf cavity along the flanks for the domain, while very little meridional velocity is observed in the center of the domain (as discussed in Section 4.1).
@@
 
-\subsection{Inside the ice shelf cavity }
+\textcolor{red}{The sub-subsurface cooling and warm surface temperature anomalies discussed above are accompanied by a freshening at depth and increase in surface salinity (not shown).}\\
+%\textcolor{red}{Mention: cool subsurface temperature anomalies are observed in the wake of the iceberg at depth (not shown)}
+
+\subsubsection{Inside the ice shelf cavity }
 %\subsubsection{Melt rate response}
@@
 Near the ice front, the competing effects of warm surface water subducting beneath the ice shelf on the flanks of the domain, and the cool water entering the ice shelf in the enter of the domain, lead to a complex of pattern of positive and negative melt rate anomalies within 20 km of the ice front (Figure \ref{fig:static_solo_melt}).
-The strongest positive anomalies are observe on the western side of the ice shelf front, while the strongest negative melt rate anomalies are observed in the center of the domain.
+
+%The strongest positive anomalies are observe on the western side of the ice shelf front, while the strongest negative melt rate anomalies are observed in the center of the domain.
 This is likely related to the geometry of the calving iceberg.
-
-The changes in ice shelf melt rates following the calving event are primarily driven by changing ocean temperatures at the base of the ice shelf.
+%
+%The changes in ice shelf melt rates following the calving event are primarily driven by changing ocean temperatures at the base of the ice shelf.
 In contrast the ocean velocities, and hence the frictional velocity at the ice base, remain largely unchanged after the calving event (see Figure \ref{fig:ustar_calving} in the supplementary material), and do not play a large role in the changing melt rates.
 
+\subsubsection{Equilibrium hydrography}
 The presence of a northern boundary in our simulation mean that we are unable to entirely remove the iceberg from the domain and observe the system approaching a new equilibrium state.
-However, a comparison between the iceberg calving simulation and the missing-iceberg simulation (where the model was spun up with the iceberg removed from the start of the simulation) shows that after 60 days the hydrography inside the ice shelf cavity in the iceberg-calving simulation appears to be qualitatively similar to missing-iceberg simulation steady state (see Figure \ref{fig:broken_melt} in the supplementary material, for example).
+However, a comparison between the iceberg calving simulation and an `equilibrium-shelf simulation' (where the model was spun up with the iceberg removed from the start), shows that after 60 days the hydrography inside the ice shelf cavity in the iceberg-calving simulation appears to be qualitatively similar to equilibrium-shelf simulation steady state (see Figure \ref{fig:broken_melt} in the supplementary material, for example).
 This suggests that the processes occurring at the ice front directly after calving are transient processes which allow the system to move towards a steady state that is largely controlled by the ice shelf geometry.
-Since the ice shelf geometry in our simulation is highly idealize, it is unclear whether the adjustment time scale seen here is relevant to real-world ice shelves.
-
-\subsection{Around the tabular iceberg}
-As the iceberg drifts through the water, it affects the ocean velocity and stratification in its immediate vicinity.
+Since the ice shelf geometry in our simulation is highly idealized and is in a closed domain, it is unclear whether the adjustment time scale seen here is relevant to real-world ice shelves.
+
+%\subsection{Around the tabular iceberg}
+%As the iceberg drifts through the water, it affects the ocean velocity and stratification in its immediate vicinity.
 As was seen near the ice front, the enhanced mixing around the iceberg causes warm salty anomalies around the iceberg near the surface, and cool fresh anomalies at depth (Figure \ref{fig:Taylor_column}a).
 %As the iceberg drifts aways from the ice shelf, these anomalies are observed most strongly directly around the iceberg, suggesting that the enhanced mixing around this iceberg is a locally driven process, created by the presence of the iceberg in the water column.
-As the iceberg drifts away from the ice shelf, the iceberg leaves a trail of warm surface anomalies in its wake that maps out the iceberg path of the iceberg (as discussed in \citet{Stern2017}) (Figure \ref{fig:SST_snapshots}c).
+%As the iceberg drifts away from the ice shelf, the iceberg leaves a trail of warm surface anomalies in its wake that maps out the iceberg path of the iceberg (as discussed in \citet{Stern2017}) (Figure \ref{fig:SST_snapshots}c).
 Similarly, cool subsurface temperature anomalies are observed in the wake of the iceberg at depth (not shown).
 
-Strong barotropic ocean currents are observed directly below the iceberg as it drifts through the water (Figure \ref{fig:Taylor_column}b).
+%Strong barotropic ocean currents are observed directly below the iceberg as it drifts through the water (Figure \ref{fig:Taylor_column}b).
 The column of uniform velocity below the iceberg is evidence of the Taylor column that forms below the iceberg.
@@
 These currents are a result of complex interaction between the iceberg on the surrounding ocean.
-More work is needed (perhaps in a further idealized setting) to understand these ineractoins.
-
-Directly below the iceberg on the ocean floor, an increased dipycnal mixing is observed in the bottom boundary layer.
-This elevated mixing in the bottom boundary layer is likely a result of a barotropic adjustment driven by the iceberg motion.
-As the iceberg drifts through the water, the region of elevated dipycnal mixing shifts so that it remains directly below the iceberg.
-Similarly elevated rates in dipycnal mixing are observed at the bottom of the water column near the ice front.
+More work is needed (perhaps in a further idealized setting) to understand these interactions.
+
+%\textcolor{red}{Idea: create a layered movie with many layers focused around the bottom edge of the ice, to give increase resolution}
 
@@
 
-We validate the Lagrangian ice shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an existing Eulerian model simulations with identical configuration.
-The results from the static ice shelf simulation using the Lagrangian ice-shelf model fit within our paradigm of understanding for circulation within ice-shelf cavities: buoyant meltwater that enters the ice-shelf cavity drives freshwater plumes at the ice-shelf base, which drives the circulation within the cavity.
+We validate the Lagrangian ice shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an existing Eulerian model simulation with identical configuration.
+This comparison show that the results from Lagrangian and Eularian models are almost indistinguishable.
+This agreement confirms that the Lagrangian model is able to simulate sub-ice-shelf cavities as well as the Eulerian model. 
+Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eulerian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian models and represents a good benchmark test for new Lagrangian ice-shelf models.
+%
+%
+%This is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models. 
+%
+%
+%Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eulerian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
+%
+%Small differences between the Lagrangian and Eulerian ice shelves models result from interpolation errors, but these errors are two orders of magnitude smaller than typical difference observe between simulations using different ocean models (for example).
+%
+%The results from the static ice shelf simulation using the Lagrangian ice-shelf model fit within our paradigm of understanding for circulation within ice-shelf cavities: buoyant meltwater that enters the ice-shelf cavity drives freshwater plumes at the ice-shelf base, which drives the circulation within the cavity.
 The circulation, melt rates and ocean hydrography achieved using the Lagrangian ice shelf compare well with other simulations in the MISOMIP experiments.
-Comparing the results to the results obtained using an Eularian model in an identical static configuration showed that the two models simulations are very similar.
-Small differences between the Lagrangian and Eulerian ice shelves models result from interpolation errors, but these errors are two orders of magnitude smaller than typical difference observe between simulations using different ocean models (for example).
-Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eulerian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian ice-shelf models and represents a good benchmark test for new Lagrangian ice-shelf models.
-
-The Lagrangian model is then used to simulate iceberg calving.
-In the iceberg calving experiment, enhanced ocean mixing is observed near the ice front and around the tabular iceberg after the iceberg detaches from the ice shelf.
-The enhanced mixed brings warm water to the surface, leading to a warming of sea surface temperatures around the iceberg and ice front.
-The mixing allow leads to a cooling of sub-surface waters near the ice front.
-These cooler waters enter the ice shelf cavity and lead to reduced melt rates at the base of the ice shelf in the months following the calving event.
+%
+%Comparing the results to the results obtained using an Eularian model in an identical static configuration showed that the two models simulations are very similar.
+
+The Lagrangian model is then used to simulate a semi-circular iceberg detaching from the ice shelf.
+The results demonstrate that the calving of a large tabular iceberg can cause significant changes to the ocean stratification and circulation around the iceberg and at the ice front.
+A number of robust features were observe in this iceberg-calving simulation, which could have real-world analogues:
+
+\begin{itemize}
+\item As the iceberg detaches from the ice shelf, there is an immediate dynamical ocean response: a stretching of the water column directly behind the iceberg gives rise to ocean upwelling, which leads to a warm salty anomalies being created at the newly calved ice front.
+PV conservation implies that this ocean column stretching gives rise to the formation for pair of oppositely orientated jets which form directly behind berg.
+A similar (and oppositely signed) phenomenon occurs in front of the berg, where a squeezing of the water column leads to downwelling, a cooling/freshening of the water column and a pair of oppositely orientated jets being created along the front side of the iceberg.
+
+\item The iceberg topography has a controlling affect on the ocean below it. This is demonstrated by the shifting of ocean jets below the iceberg in response to the iceberg motion. It is also
+demonstrated by the Taylor forms directly below the iceberg.
+This Taylor column follows the iceberg as it drifts into the open ocean and leads to a separation between the ocean properties below the iceberg and the ambient ocean conditions.
+
+\item The calving and motion of the iceberg has a large and complex affect on ocean temperate and salinity around the iceberg and at the calving front.
+In our experiment, warmed water surrounds the iceberg as it drift away from the ice shelf and maps out a trail of warm surface anomalies in the wake of the iceberg.
+Similarly, cooler waters are observed below the iceberg and map out a trail of cool sub-surface anomalies in the iceberg wake.
+
+\item As the iceberg drifts away form the ice shelf, it interacts with the ocean current coming towards the ice shelf.
+The iceberg impedes the ocean current which is diverted around the iceberg and sets up a new circulation around the iceberg.
+In our simulation, the change in circulation directs a current towards the center of the ice shelf front.
+This water subduct causing large cool anomalies at the ice front.
+% The jets at the iceberg edge are consistent with the temperature / salinity front at the iceberg edge that form because of the Taylor column beneath the berg.
+
+\item Large changes in ocean properties which occur at the ice front following the iceberg calving can directly affect the temperature flux into the ice shelf cavity, which in turn alter the sub-ice shelf melt rates.
+In our experiment, the cool water subducting beneath the ice shelf lead to reduced melt rates beneath the ice shelf.
+This decrease in melt rate extends far into the ice shelf cavity.
+
+\item Once the iceberg has drifted far away from the ice shelf cavity, the conditions and melt rates within the ice-shelf cavity appear to be converge towards values similar to those in simulations run with the iceberg removed from the start.
+This result suggests that the melt rates inside the ice shelf cavity are largely controlled by the ice shelf geometry.
+The changes in ocean conditions caused by the interaction with the iceberg appear to be transient adjustment processes.
+\end{itemize}
+
+The results from this experiment demonstrate the complex interaction between a calving iceberg and the surrounding ocean, and suggests that iceberg-ocean interactions can significantly affect ocean currents and hydrography around calving sites, and can even feedback onto melt rates within the ice shelf cavity.
+More work is needed to  further understand these iceberg-ocean interactions, and to gauge how these dynamics might affect real-world ice shelf cavities.
+The Lagrangian ice shelf model presented in this study could be a useful tool to study these interactions using both idealized and real-world geometries.
 
@@
 
-\section{To dos}
-\vspace{5mm}
-\subsection{Things to add:}
-\textcolor{red}{
-1) Time series showing variably quantities at points in the domain (e.g.: temperature flux, velocity, total melt...)\\
-2) Some aggregated numbers to emphasis some ideas (e.g.: Total change in melt volume and circulation....)\\
-3) Add some perspectives to the Conclusion/Discussion about whether we can trust the results shown here.\\
-}
-
-\subsection{New/Improvd figures}
-\textcolor{red}{
-1) Figure \ref{fig:Taylor_column}, domesticating below the iceberg (Temperature, velocity, kd (many v too)).
-2) Time series figure
-3) Ocean velocity snapshots xz 
-4) Ocean velocity snapshots yz (maybe)
-3) Late time figure  (maybe - see supp)
-}
-
-\subsection{Some other points to perhaps include}
-\textcolor{red}{
-1) The no-bonds simulation and the fixed velocity simulation both show the same surface warming and subsurface cooling signals, indicating that this is quite a robust feature.\\
-\\
-2) The fact that the warming/cooling is seen directly around the calving iceberg (see following video) indicates that the mechanism is a local mechanism rather than a global basin adjustment\\
-\\
-3) The changes in melt appear to tend towards the results from the Broken Shelf simulation, suggesting local processes around the iceberg causing warming/cooling, help the system to move between steady states, which are imposed by the large scale geometry and forcing.\\
-\\
-4) Looking at Kd shows largest mixing regions occur in places where there is open water.
+%\section{To dos}
+%\vspace{5mm}
+%\subsection{Things to add:}
+%\textcolor{red}{
+%1) Time series showing variably quantities at points in the domain (e.g.: temperature flux, velocity, total melt...)\\
+%2) Some aggregated numbers to emphasis some ideas (e.g.: Total change in melt volume and circulation....)\\
+%3) Add some perspectives to the Conclusion/Discussion about whether we can trust the results shown here.\\
+%}
+
+%\subsection{New/Improvd figures}
+%\textcolor{red}{
+%1) Figure \ref{fig:Taylor_column}, domesticating below the iceberg (Temperature, velocity, kd (many v too)).
+%2) Time series figure
+%3) Ocean velocity snapshots xz 
+%4) Ocean velocity snapshots yz (maybe)
+%3) Late time figure  (maybe - see supp)
+%}
+%
+%\subsection{Some other points to perhaps include}
+%\textcolor{red}{
+%1) The no-bonds simulation and the fixed velocity simulation both show the same surface warming and subsurface cooling signals, indicating that this is quite a robust feature.\\
+%\\
+%2) The fact that the warming/cooling is seen directly around the calving iceberg (see following video) indicates that the mechanism is a local mechanism rather than a global basin adjustment\\
+%\\
+%3) The changes in melt appear to tend towards the results from the Broken Shelf simulation, suggesting local processes around the iceberg causing warming/cooling, help the system to move between steady states, which are imposed by the large scale geometry and forcing.\\
+%\\
+%4) Looking at Kd shows largest mixing regions occur in places where there is open water.
 No enhanced Kd is observed below the iceberg (because it is too deep).
 This suggests that changes in mixing are caused by new regions being exposed to open water (i.e.: wind).\\
-\\
-5) A simulation using no sub-ice shelf friction has a very similar signal, suggesting that the signal is not caused my iceberg induced mixing.\\
-\\
-6) Is the enhanced mixing at the bottom of the water column around the iceberg related to the warming/cooling signal? Why is it there at all?\\
-\\}
-\subsection{Other questions:}
-\textcolor{red}{
-1) What is happening with the enhanced mixing exactly?
+%\\
+%5) A simulation using no sub-ice shelf friction has a very similar signal, suggesting that the signal is not caused my iceberg induced mixing.\\
+%\\
+%6) Is the enhanced mixing at the bottom of the water column around the iceberg related to the warming/cooling signal? Why is it there at all?\\
+%\\}
+%\subsection{Other questions:}
+%\textcolor{red}{
+%1) What is happening with the enhanced mixing exactly?
 It looks like it is driven by new area being exposed to open water.
@@
 \\
-2) Does the surface warming and subsurface cooling have to be a result of enhanced mixing? Is it possible that mixing is occurring even though kd is small?
-Possibilities:\\
-}
+%2) Does the surface warming and subsurface cooling have to be a result of enhanced mixing? Is it possible that mixing is occurring even though kd is small?
+%Possibilities:\\
+%}
 
@@
 \end{thebibliography}
+
+\subsection{Supplementary matirial}
+\textcolor{red}{This must be moved to its own document.}
+\subsection{Static ice-shelf simulation}
+The results in the Lagrangian static ice-shelf simulation fit within the current understanding of ice-shelf cavity circulations based on ice-shelf observations \citep{MacAyeal1984, Lewis1986, Jacobs2011} and previous modeling efforts \citep{Determan1994, Holland2006, Losch2008}.
+The ocean temperatures inside the domain are warmer than the in-situ freezing point (Figure \ref{fig:static_solo_temp_v_v}a), and cause melting at the ice-shelf base (Figure  \ref{fig:static_solo_melt}a).
+The meltwater entering the domain is more buoyant than the water around it, and rises along the ice shelf as a cool fresh plume (Figure \ref{fig:static_solo_temp_v_v}b,c).
+%As the plume rises, it entrains ambient water causing a warming of the upper ocean (Figure \ref{fig:static_solo_temp_v_v}a).
+This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water, which provides the thermal energy required for continuous ice-shelf melt.
+Strong meridional jets are observed at the ice front along the flanks of the domain, fluxing water into the ice shelf cavity on the eastern flank and allowing water to leave the ice shelf cavity on the western side (Figure \ref{fig:Bt_comparison}a).
+The meridional flow in the center of the ice front is much smaller, consistent with the dynamical barrier at the ice shelf front discussed in previous modeling and experimental studies \citep{Holland2001, Stern2014}.
+
+The highest melt rates are observed within 100km of the grounding line (Figure  \ref{fig:static_solo_melt}a).
+These elevated melt rates are caused by the presence of warm water (Figure  \ref{fig:static_solo_melt}b) and increased ocean velocities (Figure  \ref{fig:static_solo_melt}c) near the grounding line, as well as the fact that freezing point of ice decreases with increasing pressure.
+Elevated melt rates are also seen near the ice front, caused by strong currents running along the ice-shelf front (Figure  \ref{fig:static_solo_melt}c).\\
 
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Lagrangian_shelf_domain.png}
-\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eulerian static ice-shelf simulations}}
-\end{center}
-\label{fig:ISOMIP_mass_and_topog}
-\end{figure}
- \clearpage
-
- \begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_v_v.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
-\caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model.
-Panels show cross sections of the (a) ocean temperature anomaly relative the the initial temperature, and (b) the meridional ocean velocity.
-Panel (c) again shows the meridional ocean velocity, and is zoomed into the region near the ice-shelf base (the zoomed-in region is indicated with a black box (b)).}}
-\end{center}
-\label{fig:static_solo_temp_v_v}
-\end{figure} 
- \clearpage
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-\caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6.
-The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean temperature and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
-Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
-\end{center}
-\label{fig:static_solo_melt}
-\end{figure} 
- \clearpage
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_mass_spread_mass.png}
+\caption{ {(a) Ocean bottom topography and (c) ice-shelf draft used to initialized the static ice shelf experiment simulation.
+The ice draft is calculated from the total mass in an ocean grid cell after the mass-spreading interpolation has been applied.
+Panel (b) shows the initial ice draft that would be calculated if the mass-spreading interpolation were not used (i.e.
+elements treated as point masses).
+The lower and upper black lines denote the grounding line and ice shelf front, respectively.
+This figure is reproduced from \citep{Stern2017}.
+} \label{fig:ISOMIP_mass_and_topog}}
+\end{center}
+\end{figure}
+ \clearpage
+
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Lagrangian_shelf_domain.png}
+%\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eulerian static ice-shelf simulations}}
+%\end{center}
+%\label{fig:ISOMIP_mass_and_topog}
+%\end{figure}
+% \clearpage
 
@@
 Panel (c) shows the difference between panels (a) and (b).
-The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
+The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.
+\textcolor{red}{Something is wrong with the units in this figure}}}
 \end{center}
@@
 The anomalies are relative to pre-calving temperatures.
-Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
+Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving.
 In each panel, the base of the ice before calving and at the time of the snapshot are shown by the solid and dashed black lines, respectively.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly_mask.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
 \caption{ {Snapshots of vertical sections of ocean temperature anomaly at $y$=300~km in the tabular-iceberg-calving experiment.
 The anomalies are relative to pre-calving temperatures.
-Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
-The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving.
+The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.
+\textcolor{red}{Should include the warming just after calving perhaps}}}
 \end{center}
@@
 \label{fig:Temperature_section_Collapse_xz}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_u.png}
+\caption{ {Snapshots of ocean zonal velocity at $z$=197.5~m(?) in the iceberg-calving experiment.
+Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving.
+\textcolor{red}{I should include an outline of the iceberg shape in this figure}}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:u_velocity_horizontal}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
+\caption{ {Panel b: Zonal velocity at ice front, 1 day after calving. \textcolor{red}{This figure still needs to be fixed}}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:v_velocity_vertical}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x10_anomaly_mask.png}
+\caption{ {Snapshots of vertical sections of ocean (i) zonal velocity, (ii) meridional velocity,  and (iii) temperature anomaly at $y$=60~km in the tabular-iceberg-calving experiment.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken 50 days after calving.
+The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:SST_snapshots}c.}}
+\end{center}
+\label{fig:Taylor_column}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_z40_.png}
+\caption{ {Snapshots of ocean meridional velocity at $z$=197.5~m in the iceberg-calving experiment.
+Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving.
+\textcolor{red}{I should include an outline of the iceberg shape in this figure}}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:v_velocity_horizontal}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x153.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t1_t15_t50.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x153.png}
 %\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
-\caption{ {Snapshots of vertical sections of meridional velocity anomaly at $y$=300~km in the tabular-iceberg-calving experiment.
-The anomalies are relative to pre-calving temperatures.
-Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
-The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment.
+Snapshots are taken (a) 0, (b) 1, and (c) 50 days after calving.
+The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.
+\textcolor{red}{Could show 1,14 and 50 days after calving to be consistent with the other Figures.
+But this figure is more interesting}}}
 \end{center}
 \label{fig:meridional_velocity_snapshots}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-%\includegraphics[width=0.99\textwidth]{}
-\caption{ {Snapshots of vertical sections of ocean (i) temperature anomaly, (ii) meridional velocity,  and (iii) dipyncnal diffusivity at $y$=???~km in the tabular-iceberg-calving experiment.
-The anomalies are relative to pre-calving temperatures.
-Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
-The position of the vertical transects is shown by the ???
-dashed lines in Figure \ref{fig:SST_snapshots}a.}}
-\end{center}
-\label{fig:Taylor_column}
-\end{figure}
- \clearpage
-
-\begin{figure}
-\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/.png}
-\caption{ {Time series of temperature fluxes, velocities, melt rates....}}
-\end{center}
-\label{fig:Time_Series}
 \end{figure}
@@
 \begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_v_v.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
+\caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model.
+Panels show cross sections of the (a) the steady-state ocean temperature, and (b) the meridional ocean velocity.
+Panel (c) again shows the meridional ocean velocity, and is zoomed into the region near the ice-shelf base (the zoomed-in region is indicated with a black box (b)).}}
+\end{center}
+\label{fig:static_solo_temp_v_v}
+\end{figure} 
+ \clearpage
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+\caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6.
+The three panels show 5 year time average of the (a) melt rate, (b) top-of-ocean temperature and (c) frictional velocity, $u^{*}$, at the base of the ice shelf.
+Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}}
+\end{center}
+\label{fig:static_solo_melt}
+\end{figure} 
+ \clearpage
+
+  \begin{figure}
+\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Broken_Compare_melt_m_per_year_anomaly.png}
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_salt_zold_x20_anomaly_mask.png}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\caption{ {Snapshots of vertical sections of ocean salinity anomaly at $x$=40~km in the iceberg-calving experiment.
+The anomalies are relative to pre-calving temperatures.
+Snapshots are taken (a) 1, (b) 15, and (c) 50 days after calving.
+In each panel, the base of the ice before calving and at the time of the snapshot are shown by the solid and dashed black lines, respectively.
+Positions that were not the ocean interior at in both snapshots are masked in grey.
+The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.}}
+\end{center}
+\label{fig:Salinity_section_Collapse_yz}
+\end{figure}
+ \clearpage
+
  \end{document}

### 2018-09-09 Lagrangian_MISOMIP.tex
Adding latest text

@@
 %\title{The effect of calving-size distribution on sea-ice formation around Antarctica}
-\title{Modeling ice-shelf cavities using Lagrangian elements}
+\title{Modeling ice-shelf cavities and tabular icebergs using Lagrangian elements}
 %\title{The effects of iceberg calving-size distribution in a global climate model}
@@
 In this study we present a novel model of an ice-shelf cavity below a breakable ice shelf constructed of Lagrangian elements.
-% In this Lagrangian ice shelf model, large pieces of the ice shelf can break away from the ice shelf and become tabular icebergs. 
-We validate the Lagrangian ice shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an Eulerian model simulations with identical configuration.
+% In this Lagrangian ice-shelf model, large pieces of the ice shelf can break away from the ice shelf and become tabular icebergs. 
+We validate the Lagrangian ice-shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an Eulerian model simulations with identical configuration.
 %simulating the circulation within a (static) idealized ice-shelf cavity, which was developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP). 
@@
 The Lagrangian model is then used to simulate the ocean's response to a tabular iceberg calving away from the ice shelf.
-The results show a calving iceberg can lead to large changes in the surrounding ocean.
-Changes in circulation patterns and enhanced vertical mixing are observed at the ice front and around the iceberg following the calving event.
-The vertical mixing at the ice front warms the ocean surface and cools the water column at depth, allowing cooler waters to enter the ice shelf cavity, which in turn leads to reduced melt rates within the cavity.
+The results show how an iceberg calving event and the subsequent iceberg drift affects the ocean conditions at the ice front and around the iceberg.
+At the ice front, the iceberg calving leads to a warming of the ocean surface and cooling of the water column at depth, allowing cooler waters to enter the ice-shelf cavity.
+This in turn leads to reduced melt rates within the cavity.
 A Taylor column is observed below the iceberg, which moves with the iceberg as it drifts into the open ocean.
-As the tabular iceberg drifts further from the ice shelf, the circulation within the ice shelf cavity tends towards a new steady state, consistent with the new ice shelf geometry.
+As the tabular iceberg drifts further from the ice shelf, the circulation within the ice-shelf cavity tends towards a new steady state, consistent with the new ice-shelf geometry.
 
@@
 %\item Enhanced ocean mixing occurs near the ice front after a large calving event, which warms the ocean surface and cools the water column at depth.
-The cool sub-surface anomalies enter the ice shelf cavity and cause reduced basal melt in the period following the calving event.
+The cool sub-surface anomalies enter the ice-shelf cavity and cause reduced basal melt in the period following the calving event.
 \item After an iceberg calves away from an ice shelf, a complex interaction is observed between the iceberg motion and ocean hydrography.
-This interaction leads to the formation of a Taylor column beneath the iceberg, a subsurface cooling at the ice front, and reduced melt rates within the ice shelf cavity.
+This interaction leads to the formation of a Taylor column beneath the iceberg, a subsurface cooling at the ice front, and reduced melt rates within the ice-shelf cavity.
 \end{itemize}
@@
 In these models, ice-shelf melting was represented through salinity and temperature fluxes, while the ice-shelf geometry remained unchanged.
-Later models of ice-shelf cavities allowed the ice-shelf geometry to evolve as the ice shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}.
+Later models of ice-shelf cavities allowed the ice-shelf geometry to evolve as the ice-shelf melted, permitting the study of coupled ocean-ice phenomena \citep{Gladish2012, Sergienko2013}.
 More recently, dynamic ice-shelf models have been coupled to the ocean cavity, allowing the study of grounding line migration which is of key importance for sea level rise projections \citep{Grosfeld2004, Goldberg2012, De_Rydt2006, Seroussi2017}.
@@
 %Here, we instead focus comparing the Lagrangian model to existing Eulerian model in a static ice shelf configuration. 
-%We validate the Lagrangian ice-shelf model by simulating the flow beneath a static idealized ice shelf cavity,
+%We validate the Lagrangian ice-shelf model by simulating the flow beneath a static idealized ice-shelf cavity,
 %, developed as part of the Marine Ice Ocean Modeling Inter-comparison Project (MISOMIP) \citep{Asay-Davis2016}.
@@
 
-The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, (ii) to validate the Lagrangian model by simulating the flow beneath a static idealized ice shelf cavity, and comparing it to an Eulerian ice-shelf model run in an identical configuration, and (iii) to demonstrate the enhanced capabilities of the Lagrangian ice-shelf model by simulating a large iceberg calving away from the idealized ice shelf.
+The goals of this study are (i) to introduce and describe the Lagrangian ice-shelf model, (ii) to validate the Lagrangian model by simulating the flow beneath a static idealized ice-shelf cavity, and comparing it to an Eulerian ice-shelf model run in an identical configuration, and (iii) to demonstrate the enhanced capabilities of the Lagrangian ice-shelf model by simulating a large iceberg calving away from the idealized ice shelf.
 Modeling the ocean during and after a calving event, allows us to observe how the calving event affects the ocean near and beneath the ice shelf, and how changes in the ocean feedback onto the ice shelf.
@@
 The melt rates of the elements in the interior of a large structure (such as an ice shelf or large icebergs) are parametrized using the three-equation model, which is a typically melt rate parametrization used to model basal melt beneath ice shelves \citep{Holland1999}.
-The melt rates of freely floating ice elements (not bonded to other elements) are parametrized using standard parametrizations for iceberg \citep{Bigg1997, Gladstone2001, Martin2010}.
-For elements at the edge of large structures (with edges partly exposes to the open ocean) the melt rates are computed using a weighted sum of the ice shelf and and iceberg melt rate parametrization, with the weights being proprotional to the fraction of the element's perimeter which exposed to the open ocean \citep{Stern2017}.
+The melt rates of freely floating ice elements (not bonded to other elements) are parametrized using standard parameterizations for iceberg melt \citep{Bigg1997, Gladstone2001, Martin2010}.
+For elements at the edge of large structures (with edges partly exposes to the open ocean) the melt rates are computed using a weighted sum of the ice shelf and and iceberg melt rate parametrization, with the weights being proportional to the fraction of the element's perimeter which exposed to the open ocean \citep{Stern2017}.
 
@@
 By using hexagonal elements, which can be packed together without any gaps, the element initialization is perfectly space filling.
-This allows the model to simulate continuous ice shelves (without gaps or crevasses), and allows the results to be more easily comparable with Eularian ice shelf models.
+This allows the model to simulate continuous ice shelves (without gaps or crevasses), and allows the results to be more easily comparable with Eularian ice-shelf models.
 In this study, we only use hexagonal elements, however, other element geometries, can be used when less precision is needed.
@@
 At every time step, ice-shelf fields are passed from the ice-shelf model to the ocean model and from the ocean model to the ice-shelf model.
-Fields which are passed from the ocean model to the Lagrangian ice shelf model have to be interpolated from the Eulerian grid onto the Lagrangian grid (i.e.: onto the elements).
+Fields which are passed from the ocean model to the Lagrangian ice-shelf model have to be interpolated from the Eulerian grid onto the Lagrangian grid (i.e.: onto the elements).
 This is done using a bilinear interpolation scheme.
@@
 The ice-shelf thickness field is initialized using the same ice-shelf draft used for the Lagrangian model (Figure \ref{fig:ISOMIP_mass_and_topog}).
-The melt rates in the Eulerian ice-shelf simulation are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}, with the same parameters used to calculate the ice shelf melt rates in the Lagrangian model.
+The melt rates in the Eulerian ice-shelf simulation are calculated using the 3 equation model for ice-shelf decay \citep{Holland1999}, with the same parameters used to calculate the ice-shelf melt rates in the Lagrangian model.
 
 \section{Model validation}
-The Lagrangian ice shelf model is validated by comparing it to an existing Eularian ice shelf model in an identical static configuration.
+The Lagrangian ice-shelf model is validated by comparing it to an existing Eularian ice-shelf model in an identical static configuration.
 
@@
 In this experiment the ice shelves are thermodynamically active but have a time-invariant thickness.
-Temperature and salinity fluxes from ice shelf melt drive the circulation within the cavity.
+Temperature and salinity fluxes from ice-shelf melt drive the circulation within the cavity.
 
@@
 
-Since the Lagrangian and Eularian ice shelf models are coupled to the same ocean model and the ice shelf models use the same parametrization for ice shelf melt, we expect the results of the two models to be the almost the same, with the only differences arising from the interpolation and aggregation schemes (see Section 2.6).
+Since the Lagrangian and Eularian ice-shelf models are coupled to the same ocean model and the ice-shelf models use the same parametrization for ice-shelf melt, we expect the results of the two models to be the almost the same, with the only differences arising from the interpolation and aggregation schemes (see Section 2.6).
 The results show that two simulations are almost indistinguishable.
@@
 %For scale, we note that the differences between the barotropic stream functions in the two simulations, are two orders of magnitude smaller than the differences between two simulations using the same Eulerian ice shelf with different vertical coordinate systems described in Section 3.2 (not shown).
-The difference between the Lagrangian and Eulerian barotropic stream functions are two orders of magnitude smaller than typical differences observed between simulations using different models in the MISOMIP \citep{Asay-Davis2016}.
-The similarity of the Lagrangian and Eulerian simulations are also reflected in the fact that the simulations have very similar ice-shelf melt rates and ocean temperature/salinity profiles (shown in Figures \ref{fig:Melt_comparison} and Figures \ref{fig:Salt_comparison} in the supplementary materials).
+The difference between the Lagrangian and Eulerian barotropic stream functions are two orders of magnitude smaller than typical differences observed between simulations using different models in the Ocean0 MISOMIP experiment \citep{Asay-Davis2016}.
+The similarity of the Lagrangian and Eulerian simulations are also reflected in the fact that the simulations have very similar ice-shelf melt rates and ocean temperature/salinity profiles (shown in Figures \ref{fig:Melt_comparison} and \ref{fig:Salt_comparison} in the supplementary materials).
 
@@
 The Lagrangian ice-shelf model developed in this study allows us for the first time to simulate an iceberg calving away from the ice shelf, and to study what effect this has on the ocean around the iceberg and beneath the ice shelf.
-Since the Lagrangian iceberg/ice shelf model is fully coupled to the ocean, the iceberg motion affects the ocean hydrography, and the changing ocean conditions feedback onto the ice.
+Since the Lagrangian iceberg/ice-shelf model is fully coupled to the ocean, the iceberg motion affects the ocean hydrography, and the changing ocean conditions feedback onto the ice.
 %The effect of iceberg calving on the ocean around the iceberg is discussed in \citep{Stern2017}.
@@
 
-In this section, the Lagrangian ice shelf model is used to simulate a tabular iceberg detaching from the ice shelf, and drifting into the open ocean. 
+In this section, the Lagrangian ice-shelf model is used to simulate a tabular iceberg detaching from the ice shelf, and drifting into the open ocean. 
 The results below show that the calving of a large tabular iceberg can cause significant changes to the ocean stratification and circulation around the iceberg and at the ice shelf front.
@@
 %\subsubsubsection{Fixed iceberg velocity simulation}
-%To aid in the analysis of the ocean response to iceberg calving, another iceberg calving simulation was preformed, using a fixed iceberg velocity.
-This fixed velocity iceberg simulation is identical to the iceberg calving simulation (Section 3.6), except that the velocity of the calving icebergs is prescribed as $\vec{v} = = < 0, 0.01 >$ m/s.
+%To aid in the analysis of the ocean response to iceberg calving, another iceberg-calving simulation was preformed, using a fixed iceberg velocity.
+This fixed velocity iceberg simulation is identical to the iceberg-calving simulation (Section 3.6), except that the velocity of the calving icebergs is prescribed as $\vec{v} = = < 0, 0.01 >$ m/s.
 Since the iceberg speed is prescribed, this simulation is not fully coupled.
@@
 %\subsubsection{Missing-Iceberg simulation}
-%A simulation is preformed to help analyze how the changing ice shelf geometry affects the sub-ice-shelf circulation and hydrography.
+%A simulation is preformed to help analyze how the changing ice-shelf geometry affects the sub-ice-shelf circulation and hydrography.
 In this simulation, calving iceberg (with the same geometry as the iceberg simulations above) is removed at the start of the simulation, and the simulation is spun up from rest.
@@
 
-%The changes at the ice shelf front persist, even once the tabular iceberg has drifted away from the ice shelf cavity, eventually reaching a new equilibrium consistent with the new ice front geometry.
-%Changing conditions at the ice front alter the temperature fluxes into the ice shelf cavity, which impacts the hydrography inside the ice shelf cavity, and drives changes to the ice-shelf melt rates across the entire ice shelf.
+%The changes at the ice shelf front persist, even once the tabular iceberg has drifted away from the ice-shelf cavity, eventually reaching a new equilibrium consistent with the new ice front geometry.
+%Changing conditions at the ice front alter the temperature fluxes into the ice-shelf cavity, which impacts the hydrography inside the ice-shelf cavity, and drives changes to the ice-shelf melt rates across the entire ice shelf.
 A current is also observed circling the iceberg in a clockwise direction as the iceberg drift northwards.
@@
 \subsubsection{Ocean response to iceberg detachment}
-Immediately after the numerical bonds are broken, a large semi-circular tabular iceberg detaches from the ice shelf, and begins to drift northwards (Figure \ref{fig:SST_snapshots}).
-The northwards motion of the iceberg creates a region of open water at the new calving front, between the ice shelf and the tabular iceberg.
+After the numerical bonds are broken, a large semi-circular tabular iceberg detaches from the ice shelf, and begins to drift northwards (Figure \ref{fig:SST_snapshots}).
+The detachment of the iceberg gives rise to a dynamical ocean response which is shown in the schematic in Figure \ref{fig:Schematic_of_calving}a and \ref{fig:Schematic_of_calving}b, and is described below.
+
+Immediately after calving, the northwards motion of the iceberg creates a region of open water at the new calving front, between the ice shelf and the tabular iceberg (Figure \ref{fig:SST_snapshots}a).
 The formation of a region of open ocean behind the iceberg causes a sudden stretching of the water column in the wake of the iceberg, which drives an upwelling throughout the water column.
@@
 
-The calving event also drives an immediate change in circulation around the newly created ice front as the ocean adjusts to the topographic changes. 
+The calving event also drives an immediate change in ocean currents at the newly created ice front as the ocean adjusts to the topographic changes. 
 Since the Coriolis parameter is negative, a stretching of the water column behind the iceberg has to be accompanied by the creation of negative relative vorticity in order for potential vorticity (PV) to be conserved.
 The creation of negative relative vorticity along the newly calved ice front, gives rise to a pair of oppositely orientated ocean jets running along the ice front.
-A westward barotropic jet is created to the south of the calving front, and an eastward barotropic jet is created to the north of the calving front (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}b).
+A westward barotropic jet is created to the south of the calving front, and an eastward barotropic jet is created to the north of the calving front (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}).
 The positive gradient in zonal velocity created by this pair of oppositely orientated jets yields the negative relative vorticity, needed to conserve PV.
@@
 The squeezing of the water column generates positive relative vorticity, so that the total PV is conserved.
-The positive relative vorticity creates an eastward and westward jet to the south and north of the northern edge of the iceberg (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}b).
+The positive relative vorticity creates an eastward and westward jet to the south and north of the northern edge of the iceberg (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}).
 The stretching and squeezing of the water column to the south and north of the iceberg, both contribute to the eastward jet which forms directly beneath the iceberg which plays an important role in driving iceberg motion.
@@
 After the iceberg breaks away from the ice shelf, the motion of iceberg is primarily driven by the drag from ocean currents beneath the iceberg, wind drag and by Coriolis force.
-The eastward jet beneath the iceberg drives the iceberg towards the east (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}b), while the wind and Coriolis force drive the iceberg offshore.
+The eastward jet beneath the iceberg drives the iceberg towards the east (Figures \ref{fig:u_velocity_horizontal}a and \ref{fig:v_velocity_vertical}), while the wind and Coriolis force drive the iceberg offshore.
 Initially, as the iceberg drifts eastward, it collides with the ice shelf, which hinders its motion (Figure \ref{fig:SST_snapshots}a).
@@
 Once the iceberg reaches the eastern side of the domain, it begins to interact the boundary of the domain and with the southward boundary current running along the edge of the domain (Figures \ref{fig:SST_snapshots}b and \ref{fig:v_velocity_horizontal}c).
-The presence of the iceberg along the eastern boundary impedes the southward boundary current, so that the current has to flow to the west of the iceberg (Figure \ref{fig:v_velocity_horizontal}b). 
+The presence of the iceberg along the eastern boundary impedes the southward boundary current, so that the current has to flow to the west of the iceberg (Figure \ref{fig:v_velocity_horizontal}c). 
 The diverted current follows the topographic contour created by the iceberg so that it sets up a  counter-clockwise circulation running around the iceberg (Figure \ref{fig:u_velocity_horizontal}c).
@@
 This is partly due to the Taylor Column beneath the iceberg, which allows the northward velocity beneath the iceberg to be separated from the southward moving current around the iceberg.
+The rotation of the iceberg and interaction with the boundary current are summarized in the schematics in Figure \ref{fig:Schematic_of_calving}c and \ref{fig:Schematic_of_calving}e.
 
@@
 After the tabular iceberg detaches from the ice shelf, a warming is observed throughout the water column to the south of the iceberg (Figure \ref{fig:Temperature_section_Collapse_yz}a, as discussed above).
-This warming extends to the ocean surface, resulting in warm sea surface temperature (SST) anomalies at the newly calved ice front and around the southern side of the iceberg (Figure \ref{fig:SST_snapshots} and \ref{fig:Temperature_section_Collapse_xz}a  \textcolor{red}{- make sure it is clear in the Figure}).
-In the weeks following calving, part of this warm SST anomaly remains at the ice front, influencing the heat flux into the ice shelf cavity, and some the SST anomaly drifts with the iceberg into the open ocean.
+This warming extends to the ocean surface, resulting in warm sea surface temperature (SST) anomalies at the newly calved ice front and around the southern side of the iceberg (Figure \ref{fig:SST_snapshots} and \ref{fig:Temperature_section_Collapse_xz}a).
+In the weeks following calving, part of this warm SST anomaly remains at the ice front, influencing the heat flux into the ice-shelf cavity, and some the SST anomaly drifts with the iceberg into the open ocean.
 
@@
 Similar subsurface cooling at the ice front was observed in other experiments using different sizes and shapes for the calving iceberg (not shown).
+The sub-subsurface cooling and warm surface temperature anomalies discussed above are accompanied by a freshening at depth and increase in surface salinity (not shown).
 
 The zonal current along the ice front drives the cool anomaly to the west, causing an enhancement of the cool anomalies on the western side of the ice shelf front (Figure \ref{fig:Temperature_section_Collapse_xz}c).
-Most of the subsurface cooling occurs outside of the ice shelf cavity, as the dynamical barrier caused by the ice shelf inhibits exchange of water across the ice front. 
-However over time, an increasing amount of cooler water is able to enter the ice shelf cavity, and is advected below the ice shelf (Figure \ref{fig:Temperature_section_Collapse_yz}c).
-
-%The cooler waters entering the ice shelf cavity mix with the water within the ice shelf cavity, causing the strength of the cool anomaly to be reduced towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
+Most of the subsurface cooling occurs outside of the ice-shelf cavity, as the dynamical barrier caused by the ice shelf inhibits exchange of water across the ice front. 
+However over time, an increasing amount of cooler water is able to enter the ice-shelf cavity, and is advected below the ice shelf (Figure \ref{fig:Temperature_section_Collapse_yz}c).
+
+The surface warming at the ice front and around the iceberg, as well as the subsurface cooling at the ice front, are summarized in the schematics in Figure \ref{fig:Schematic_of_calving}c, \ref{fig:Schematic_of_calving}d and \ref{fig:Schematic_of_calving}e.
+%The cooler waters entering the ice-shelf cavity mix with the water within the ice-shelf cavity, causing the strength of the cool anomaly to be reduced towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
 %\subsubsection{Circulation Changes}
-%The changing temperature flux into the ice shelf cavity in the center of the domain is partly driven by changing ocean velocities, observed at the ice front directly after the iceberg calves.
-The pre-calving meridional flow at the ice front is dominated by strong boundary currents moving water into and out of the ice shelf cavity along the flanks for the domain, while very little meridional velocity is observed in the center of the domain (as discussed in Section 4.1).
+%The changing temperature flux into the ice-shelf cavity in the center of the domain is partly driven by changing ocean velocities, observed at the ice front directly after the iceberg calves.
+The pre-calving meridional flow at the ice front is dominated by strong boundary currents moving water into and out of the ice-shelf cavity along the flanks for the domain, while very little meridional velocity is observed in the center of the domain (as discussed in Section 4.1).
 After the iceberg calves, large meridional velocities are observed at the ice front (Figure \ref{fig:meridional_velocity_snapshots}).
@@
 
-\textcolor{red}{The sub-subsurface cooling and warm surface temperature anomalies discussed above are accompanied by a freshening at depth and increase in surface salinity (not shown).}\\
 %\textcolor{red}{Mention: cool subsurface temperature anomalies are observed in the wake of the iceberg at depth (not shown)}
 
-\subsubsection{Inside the ice shelf cavity }
+\subsubsection{Inside the ice-shelf cavity }
 %\subsubsection{Melt rate response}
-The combination of cool sub-surface temperature anomalies and elevated ocean velocities at the ice front, results in a temperature flux across the ice front, as cool temperature anomalies to enter the ice shelf cavity (Figure \ref{fig:Temperature_section_Collapse_yz}).
-Once the cooler water has entered the ice shelf cavity, the anomalies spread southwards within the ice shelf cavity, eventually reaching all the way to the grounding line.
-As the cool water spreads into the cavity, it mixes with the water within the ice shelf cavity, causing a reduction in the strength of the anomaly towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
-
-The cooling of the water inside the ice shelf cavity after calving leads to a reduction of the melt rates at the base of the ice shelf (Figure \ref{fig:Melt_rate_snapshots}).
+The combination of cool sub-surface temperature anomalies and elevated ocean velocities at the ice front, results in a temperature flux across the ice front, as cool temperature anomalies to enter the ice-shelf cavity (Figure \ref{fig:Temperature_section_Collapse_yz}, Figure \ref{fig:Schematic_of_calving}f).
+Once the cooler water has entered the ice-shelf cavity, the anomalies spread southwards within the ice-shelf cavity, eventually reaching all the way to the grounding line.
+As the cool water spreads into the cavity, it mixes with the water within the ice-shelf cavity, causing a reduction in the strength of the anomaly towards the grounding line (Figure \ref{fig:Temperature_section_Collapse_yz}c).
+
+The cooling of the water inside the ice-shelf cavity after calving leads to a reduction of the melt rates at the base of the ice shelf (Figure \ref{fig:Melt_rate_snapshots}).
 The reduced melt rates occur over a wide area extending from the newly calved ice front, all the way towards the grounding line.
-The negative melt rate anomalies increase over time, as more cold water enters the ice shelf cavity.
+The negative melt rate anomalies increase over time, as more cold water enters the ice-shelf cavity.
 The strongest negative anomalies are observed near the ice front, while the strength of the negative melt rate anomalies are reduced towards the grounding.
@@
 
-Near the ice front, the competing effects of warm surface water subducting beneath the ice shelf on the flanks of the domain, and the cool water entering the ice shelf in the enter of the domain, lead to a complex of pattern of positive and negative melt rate anomalies within 20 km of the ice front (Figure \ref{fig:static_solo_melt}).
+Near the ice front, the competing effects of warm surface water subducting beneath the ice shelf on the flanks of the domain, and the cool water entering the ice shelf in the enter of the domain, lead to a complex of pattern of positive and negative melt rate anomalies within 20 km of the ice front (Figure \ref{fig:Melt_rate_snapshots}).
 
@@
 %
-%The changes in ice shelf melt rates following the calving event are primarily driven by changing ocean temperatures at the base of the ice shelf.
+%The changes in ice-shelf melt rates following the calving event are primarily driven by changing ocean temperatures at the base of the ice shelf.
 In contrast the ocean velocities, and hence the frictional velocity at the ice base, remain largely unchanged after the calving event (see Figure \ref{fig:ustar_calving} in the supplementary material), and do not play a large role in the changing melt rates.
@@
 The presence of a northern boundary in our simulation mean that we are unable to entirely remove the iceberg from the domain and observe the system approaching a new equilibrium state.
-However, a comparison between the iceberg calving simulation and an `equilibrium-shelf simulation' (where the model was spun up with the iceberg removed from the start), shows that after 60 days the hydrography inside the ice shelf cavity in the iceberg-calving simulation appears to be qualitatively similar to equilibrium-shelf simulation steady state (see Figure \ref{fig:broken_melt} in the supplementary material, for example).
-This suggests that the processes occurring at the ice front directly after calving are transient processes which allow the system to move towards a steady state that is largely controlled by the ice shelf geometry.
-Since the ice shelf geometry in our simulation is highly idealized and is in a closed domain, it is unclear whether the adjustment time scale seen here is relevant to real-world ice shelves.
+However, a comparison between the iceberg-calving simulation and an `equilibrium-shelf simulation' (where the model was spun up with the iceberg removed from the start), shows that after 60 days the hydrography inside the ice-shelf cavity in the iceberg-calving simulation appears to be qualitatively similar to equilibrium-shelf simulation steady state (see Figure \ref{fig:broken_melt} in the supplementary material, for example).
+This suggests that the processes occurring at the ice front directly after calving are transient processes which allow the system to move towards a steady state that is largely controlled by the ice-shelf geometry.
+Since the ice-shelf geometry in our simulation is highly idealized and is in a closed domain, it is unclear whether the adjustment time scale seen here is relevant to real-world ice shelves.
 
@@
 
+\section{Summary}
+
+%The Lagrangian model is then used to simulate a semi-circular iceberg detaching from the ice shelf. 
+The simulations presented above demonstrate that the calving of a large tabular iceberg can cause significant changes to the ocean stratification and circulation around the iceberg and at the ice front.
+Although the idealized geometry of the simulations makes it difficult to compare the results directly to real-world observations, a number of robust features were observe in this iceberg-calving simulation, which could have real-world analogues.
+
+\begin{enumerate}
+\item \textbf{Dynamical response of ocean to iceberg calving:}\\
+As the iceberg detaches from the ice shelf, there is an immediate dynamical ocean response: a stretching of the water column directly behind the iceberg gives rise to ocean upwelling, which leads to a warm salty anomalies being created at the newly calved ice front.
+PV conservation implies that this ocean column stretching gives rise to the formation for pair of oppositely orientated jets which form directly behind iceberg.
+A similar (and oppositely signed) phenomenon occurs in front of the iceberg, where a squeezing of the water column leads to downwelling, a cooling/freshening of the water column and a pair of oppositely orientated jets being created along the front side of the iceberg (see schematic in Figure \ref{fig:Schematic_of_calving}a, \ref{fig:Schematic_of_calving}b).
+
+\item \textbf{Controlling influence of iceberg topography:}\\
+The iceberg topography has a controlling affect on the ocean below it.
+This is demonstrated by the shifting of ocean jets below the iceberg in response to the iceberg motion.
+It is also demonstrated by the Taylor forms directly below the iceberg.
+This Taylor column follows the iceberg as it drifts into the open ocean and leads to a separation between the ocean properties below the iceberg and the ambient ocean conditions.
+
+\item\textbf{Localized changes in ocean hydrography around the iceberg:}\\
+The calving and motion of the iceberg has a large and complex affect on ocean temperate and salinity around the iceberg and at the calving front.
+In our experiment, warmed water surrounds the iceberg as it drift away from the ice shelf and maps out a trail of warm surface anomalies in the wake of the iceberg.
+Similarly, cooler waters are observed below the iceberg and map out a trail of cool sub-surface anomalies in the iceberg wake.
+
+\item \textbf{Interaction between iceberg and ocean currents:}\\
+As the iceberg drifts away form the ice shelf, it interacts with the ocean current coming towards the ice shelf.
+The iceberg impedes the ocean current which is diverted around the iceberg and sets up a new circulation around the iceberg.
+In our simulation, the change in circulation directs a current towards the center of the ice shelf front.
+This water subduct causing large cool anomalies at the ice front (see schematic in Figure \ref{fig:Schematic_of_calving}).
+% The jets at the iceberg edge are consistent with the temperature / salinity front at the iceberg edge that form because of the Taylor column beneath the berg.
+
+\item \textbf{Iceberg calving can affect sub-ice shelf temperatures and melt rates:}\\
+Large changes in ocean properties which occur at the ice front following the iceberg calving can directly affect the temperature flux into the ice-shelf cavity, which in turn alter the sub-ice-shelf melt rates.
+In our experiment, the cool water subducting beneath the ice shelf lead to reduced melt rates beneath the ice shelf.
+This decrease in melt rate extends far into the ice-shelf cavity.
+
+\item \textbf{Controlling influence of the ice-shelf geometry:}\\
+Once the iceberg has drifted far away from the ice-shelf cavity, the conditions and melt rates within the ice-shelf cavity appear to be converge towards values similar to those in simulations run with the iceberg removed from the start.
+This result suggests that the melt rates inside the ice-shelf cavity are largely controlled by the ice-shelf geometry.
+The changes in ocean conditions caused by the interaction with the iceberg appear to be transient adjustment processes.
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusion}
+
+This study presents a new Lagrangian framework for modeling sub-ice-shelf cavities.
+In this framework, the ice shelf is constructed out of many Lagrangian elements, which are bonded together by numerical bonds.
 %In order to accurately project future sea level, it is likely that we will need to develop fully-coupled global general climate models (GCM's) with dynamic ice-shelf cavities which are able to melt, break and interact with the ocean in physically realistic ways.
 This will require us to create models of ice shelf cavities with capabilities that can not currently be simulated by the current generation of ice-shelf models.
-
-This study presents a new Lagrangian framework for modeling sub-ice-shelf cavities.
-In this framework, the ice shelf is constructed out of many Lagrangian elements, which are bonded together by numerical bonds.
+%
+%
+% Unlike Eulerian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf. 
+%This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:SST_snapshots}).
+%
+%A consequence of using a Lagrangian ice-shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eulerian ocean grid in order to be passed to the ocean model.
+This is done by exactly calculation the fraction of each ice element that lies in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
+
 %The collection of Lagrangian elements store the ice-shelf properties.
@@
 
-% Unlike Eulerian grids, the nodes (elements) can move at every time step, altering the shape of the ice shelf. 
-%This allows us to use the Lagrangian ice-shelf model to large pieces of the ice-shelf breaking away from the ice shelf to becoming tabular icebergs that are fully embedded in the ocean (Figures  \ref{fig:SST_snapshots}).
-%
-%A consequence of using a Lagrangian ice-shelf model is all variables need to be interpolated from the Lagrangian grid onto the Eulerian ocean grid in order to be passed to the ocean model.
-This is done by exactly calculation the fraction of each ice element that lies in each ocean grid cell, and dividing the element's properties between the ocean grid cell in proportion to that fraction.
-
-We validate the Lagrangian ice shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an existing Eulerian model simulation with identical configuration.
+We validate the Lagrangian ice-shelf model by simulating the flow beneath a (static) idealized ice shelf, and comparing the results to an existing Eulerian model simulation with identical configuration.
 This comparison show that the results from Lagrangian and Eularian models are almost indistinguishable.
@@
 Demonstrating that the Lagrangian ice-shelf model is able to reproduce the results of an Eulerian ice-shelf model in the same static ice-shelf configuration is a prerequisite developing more advanced Lagrangian models and represents a good benchmark test for new Lagrangian ice-shelf models.
+
+The Lagrangian ice shelf model is then used to simulate a tabular iceberg calving away from an ice shelf.
+The results from this experiment demonstrate the complex interaction between a calving iceberg and the surrounding ocean, and suggests that iceberg-ocean interactions can significantly affect ocean currents and hydrography around calving sites, and can even feedback onto melt rates within the ice-shelf cavity.
+More work is needed to  further understand these iceberg-ocean interactions, and to gauge how these dynamics might affect real-world ice shelf cavities.
+The Lagrangian ice-shelf model presented in this study could be a useful tool to study these interactions using both idealized and real-world geometries.
+
 %
@@
 
-The Lagrangian model is then used to simulate a semi-circular iceberg detaching from the ice shelf.
-The results demonstrate that the calving of a large tabular iceberg can cause significant changes to the ocean stratification and circulation around the iceberg and at the ice front.
-A number of robust features were observe in this iceberg-calving simulation, which could have real-world analogues:
-
-\begin{itemize}
-\item As the iceberg detaches from the ice shelf, there is an immediate dynamical ocean response: a stretching of the water column directly behind the iceberg gives rise to ocean upwelling, which leads to a warm salty anomalies being created at the newly calved ice front.
-PV conservation implies that this ocean column stretching gives rise to the formation for pair of oppositely orientated jets which form directly behind berg.
-A similar (and oppositely signed) phenomenon occurs in front of the berg, where a squeezing of the water column leads to downwelling, a cooling/freshening of the water column and a pair of oppositely orientated jets being created along the front side of the iceberg.
-
-\item The iceberg topography has a controlling affect on the ocean below it. This is demonstrated by the shifting of ocean jets below the iceberg in response to the iceberg motion. It is also
-demonstrated by the Taylor forms directly below the iceberg.
-This Taylor column follows the iceberg as it drifts into the open ocean and leads to a separation between the ocean properties below the iceberg and the ambient ocean conditions.
-
-\item The calving and motion of the iceberg has a large and complex affect on ocean temperate and salinity around the iceberg and at the calving front.
-In our experiment, warmed water surrounds the iceberg as it drift away from the ice shelf and maps out a trail of warm surface anomalies in the wake of the iceberg.
-Similarly, cooler waters are observed below the iceberg and map out a trail of cool sub-surface anomalies in the iceberg wake.
-
-\item As the iceberg drifts away form the ice shelf, it interacts with the ocean current coming towards the ice shelf.
-The iceberg impedes the ocean current which is diverted around the iceberg and sets up a new circulation around the iceberg.
-In our simulation, the change in circulation directs a current towards the center of the ice shelf front.
-This water subduct causing large cool anomalies at the ice front.
-% The jets at the iceberg edge are consistent with the temperature / salinity front at the iceberg edge that form because of the Taylor column beneath the berg.
-
-\item Large changes in ocean properties which occur at the ice front following the iceberg calving can directly affect the temperature flux into the ice shelf cavity, which in turn alter the sub-ice shelf melt rates.
-In our experiment, the cool water subducting beneath the ice shelf lead to reduced melt rates beneath the ice shelf.
-This decrease in melt rate extends far into the ice shelf cavity.
-
-\item Once the iceberg has drifted far away from the ice shelf cavity, the conditions and melt rates within the ice-shelf cavity appear to be converge towards values similar to those in simulations run with the iceberg removed from the start.
-This result suggests that the melt rates inside the ice shelf cavity are largely controlled by the ice shelf geometry.
-The changes in ocean conditions caused by the interaction with the iceberg appear to be transient adjustment processes.
-\end{itemize}
-
-The results from this experiment demonstrate the complex interaction between a calving iceberg and the surrounding ocean, and suggests that iceberg-ocean interactions can significantly affect ocean currents and hydrography around calving sites, and can even feedback onto melt rates within the ice shelf cavity.
-More work is needed to  further understand these iceberg-ocean interactions, and to gauge how these dynamics might affect real-world ice shelf cavities.
-The Lagrangian ice shelf model presented in this study could be a useful tool to study these interactions using both idealized and real-world geometries.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\subsection{Supplementary matirial}
+ \clearpage
+
+\section{Supplementary material}
 \textcolor{red}{This must be moved to its own document.}
@@
 This injection of positive buoyancy at depth drives a clockwise circulation outside of the ice-shelf cavity (Figure \ref{fig:Bt_comparison}a), providing the ice-shelf cavity with a continuous supply of warm water, which provides the thermal energy required for continuous ice-shelf melt.
-Strong meridional jets are observed at the ice front along the flanks of the domain, fluxing water into the ice shelf cavity on the eastern flank and allowing water to leave the ice shelf cavity on the western side (Figure \ref{fig:Bt_comparison}a).
+Strong meridional jets are observed at the ice front along the flanks of the domain, fluxing water into the ice-shelf cavity on the eastern flank and allowing water to leave the ice-shelf cavity on the western side (Figure \ref{fig:Bt_comparison}a).
 The meridional flow in the center of the ice front is much smaller, consistent with the dynamical barrier at the ice shelf front discussed in previous modeling and experimental studies \citep{Holland2001, Stern2014}.
@@
 In this schematic the ice elements (purple dots) are initialized in a staggered lattice covering the surface area of the iceberg.
-For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (red hexagons).
-For purposed of element interactions, the ice elements are assumed to be circular (black circles).
+For the purpose of mass aggregation, the ice elements are assumed to have hexagonal shape (red hexagons).
+For the purpose of element interactions, the ice elements are assumed to be circular (black circles).
 Elements are initially bonded to adjacent elements using numerical bonds (magenta lines).
@@
 An ocean grid has been included (dashed cyan lines).
+\textcolor{red}{Still need to update this figure to include the super imposed hexagons.
+Also, perhaps we want to remove some of the text in the caption?
+(e.g.: remove from the words "In this schematic the ice elements").}
 %The background photo in the larger schematic is an areal photograph of iceberg PIIB (Area= 42 $\textrm{km}^{2}$) taken in Baffin Bay in 2012.
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
-\caption{ {Snapshots of sea surface temperature anomalies in the iceberg calving simulation.
+\caption{ {Snapshots of sea surface temperature anomalies in the iceberg-calving simulation.
 The anomalies are relative to pre-calving temperatures.
@@
 Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.
-The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:Temperature_section_Collapse_xz}, respectively}}
+The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz} and \ref{fig:meridional_velocity_snapshots}, respectively.}}
 \end{center}
@@
 \caption{ {(a) Ocean bottom topography and (c) ice-shelf draft used to initialized the static ice shelf experiment simulation.
-The ice draft is calculated from the total mass in an ocean grid cell after the mass-spreading interpolation has been applied.
-Panel (b) shows the initial ice draft that would be calculated if the mass-spreading interpolation were not used (i.e.
+The ice draft is calculated from the total mass of ice intersecting each ocean grid cell (see Section 2.6).
+Panel (b) shows the initial ice draft that would be calculated if the mass aggregation onto the Eularian grid was not used (i.e.
 elements treated as point masses).
@@
 \begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Diagrams/Iceberg_scehmatic_with_red.pdf}
+\caption{ {{\small Schematic illustrating how the ocean hydrography is affected by iceberg calving.
+Cool and warm water anomalies are indicated in blue and red, respectively, and ocean currents are shown using arrows.
+
+Stage 1, iceberg detachment (a, b): as the iceberg detaches, water column stretching behind the iceberg causes warm water anomalies behind the iceberg.
+The conservation of PV caused by this stretching gives rise to a pair zonal jets behind and below the iceberg.
+Similarly, the contracting water column in front of the iceberg creates cool anomalies, and drives a zonal jet in front and below the iceberg.
+
+Stage 2, iceberg rotation (c, d): as the iceberg drifts away from the ice shelf, it rotates causing the jets around it to change direction.
+The newly orientated jet in front of the iceberg drives water towards to ice shelf, which subducts at the ice front, causing subsurface cooling.
+
+Stage 3, cooling below the ice shelf (e, f): as the iceberg moves away from the ice shelf, it interacts with the boundary currents, which are diverted by the presence of the iceberg.
+At the ice front, the cool water anomalies are advected into the ice-shelf cavity, eventually leading to reduced melt rates throughout the cavity.
+
+The warm water surface anomalies behind the iceberg after calving (panel a), move with the iceberg as it drifts (panel b), and entirely surround the iceberg as it continues to drift into the open ocean (panel c).
+
+}
+
+}}
+\end{center}
+%FIgure created by \end{center}
+\label{fig:Schematic_of_calving}
+\end{figure}
+ \clearpage
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x20_anomaly.png}
@@
 The position of the vertical transects is shown by the blue dashed lines in Figure \ref{fig:SST_snapshots}a.
-\textcolor{red}{Should include the warming just after calving perhaps}}}
+}}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
-\caption{ {Panel b: Zonal velocity at ice front, 1 day after calving. \textcolor{red}{This figure still needs to be fixed}}}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
+\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_u_cropped.png}
+
+\caption{ {Snapshot of vertical section of zonal velocity at $x$=40~km in the iceberg-calving experiment 1 day after calving.
+The position of the vertical transects is shown by the black dashed line in Figure \ref{fig:SST_snapshots}a.
+An eastward jet is observed beneath the iceberg, and westward jets are observed to the north and south of the iceberg.}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x10_anomaly_mask.png}
-\caption{ {Snapshots of vertical sections of ocean (i) zonal velocity, (ii) meridional velocity,  and (iii) temperature anomaly at $y$=60~km in the tabular-iceberg-calving experiment.
+\caption{ {Snapshots of vertical sections of ocean (a) zonal velocity, (b) meridional velocity,  and (c) temperature anomaly at $x$=60~km in the tabular-iceberg-calving experiment.
 The anomalies are relative to pre-calving temperatures.
 Snapshots are taken 50 days after calving.
-The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:SST_snapshots}c.}}
+%The position of the vertical transects is shown by the dashed lines in Figure \ref{fig:SST_snapshots}c. 
+\textcolor{red}{Should we add the position to Figure 2a?}}}
 \end{center}
@@
 \includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_melt_m_per_year_anomaly.png}
-\caption{ { Snapshots of the melt rate anomaly, at the ice-shelf base in the tabular iceberg calving simulation.
-The anomalies are relative to pre-calving temperatures.
+\caption{ { Snapshots of the melt rate anomaly, at the ice-shelf base in the tabular iceberg-calving simulation.
+The anomalies are relative to pre-calving melt rates.
 Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.
@@
 %\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
-\caption{ {Time-averaged vertical sections of salinity in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration at at $x$=54~km.
+\caption{ {Time-averaged vertical sections of salinity at  $x$=40~km in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration.
 Panel (c) shows the difference between panels (a) and (b).
-The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.}}
+The time averages are taken over 5 years of model time, beginning at the end of the 5 year spin up period.
+The position of the vertical transects is shown by the black dashed lines in Figure \ref{fig:SST_snapshots}a.
+}}
 \end{center}

### 2018-09-09 Lagrangian_MISOMIP.tex
Upadate

@@
 Grid cells with ice mass $> 10^{4}$ kg are plotted in white, with grey shading indicating thinner ice.
-The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz} and \ref{fig:meridional_velocity_snapshots}, respectively.}}
+The black and blue dashed line in panel (a) shows the location of the vertical transects shown in Figures \ref{fig:Temperature_section_Collapse_yz} and \ref{fig:v_velocity_vertical}, and \ref{fig:Temperature_section_Collapse_xz}, respectively.}}
 \end{center}
@@
 
-\begin{figure}
-\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t1_t15_t50.png}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x153.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
-\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment.
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
+%\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment.
 Snapshots are taken (a) 0, (b) 1, and (c) 50 days after calving.
@@
 But this figure is more interesting}}}
-\end{center}
-\label{fig:meridional_velocity_snapshots}
-\end{figure}
- \clearpage
+%\end{center}
+%\label{fig:meridional_velocity_snapshots}
+%\end{figure}
+% \clearpage
 

### 2018-10-26 Lagrangian_MISOMIP.tex
Made paths to figures relative

@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Two_panel_schematic_shelf.png}
+\includegraphics[width=0.99\textwidth]{Figures/Two_panel_schematic_shelf.png}
 \caption{ {Schematic showing how ice shelves and tabular icebergs are constructed using Lagrangian elements. 
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
+%\includegraphics[width=0.99\textwidth]{Figures/side_and_top_view_ALE_z_Mixed_Melt_Collapse_temp_layers_x12.png}
 %\caption{ {Snapshots of a simulation where a Lagrangian ice-shelf calves a tabular iceberg viewed (a) from above and (b) from the side.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_anomaly.png}
 \caption{ {Snapshots of sea surface temperature anomalies in the iceberg-calving simulation.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_D_mass_spread_mass.png}
+\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_solo_D_mass_spread_mass.png}
 \caption{ {(a) Ocean bottom topography and (c) ice-shelf draft used to initialized the static ice shelf experiment simulation.
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Lagrangian_shelf_domain.png}
+%\includegraphics[width=0.99\textwidth]{Figures/Lagrangian_shelf_domain.png}
 %\caption{ {Ocean bottom topography and ice-shelf draft used in the Lagrangian and Eulerian static ice-shelf simulations}}
@@
 \begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_barotropic_sf.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
+\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_comparison_barotropic_sf.png}
 \caption{ {Time-averaged barotropic stream function in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration.
@@
 \begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Diagrams/Iceberg_scehmatic_with_red.pdf}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_barotropic_sf.png}
+\includegraphics[width=0.99\textwidth]{Diagrams/Iceberg_scehmatic_with_red.pdf}
 \caption{ {{\small Schematic illustrating how the ocean hydrography is affected by iceberg calving.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x20_anomaly.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x20_anomaly.png}
 \caption{ {Snapshots of vertical sections of ocean temperature anomaly at $x$=40~km in the iceberg-calving experiment.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly_mask.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly_mask.png}
+%\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x149_anomaly.png}
 \caption{ {Snapshots of vertical sections of ocean temperature anomaly at $y$=300~km in the tabular-iceberg-calving experiment.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_u.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_u.png}
 \caption{ {Snapshots of ocean zonal velocity at $z$=197.5~m(?) in the iceberg-calving experiment.
@@
 \begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_u_cropped.png}
+%\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_temp_u_v_calved.png}
+\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_u_cropped.png}
 
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_temp_zold_x10_anomaly_mask.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_temp_zold_x10_anomaly_mask.png}
 \caption{ {Snapshots of vertical sections of ocean (a) zonal velocity, (b) meridional velocity,  and (c) temperature anomaly at $x$=60~km in the tabular-iceberg-calving experiment.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_z40_.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_v_z40_.png}
 \caption{ {Snapshots of ocean meridional velocity at $z$=197.5~m in the iceberg-calving experiment.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_melt_m_per_year_anomaly.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_melt_m_per_year_anomaly.png}
 \caption{ { Snapshots of the melt rate anomaly, at the ice-shelf base in the tabular iceberg-calving simulation.
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
+%\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_v_layers_x149_mask_t0_t1_t50.png}
 %\caption{ {Snapshots of vertical sections of meridional velocity at $y$=300~km in the tabular-iceberg-calving experiment.
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_Iceberg_calving.png}
+%\includegraphics[width=0.99\textwidth]{Figures/fixed_drift_bond_Iceberg_calving.png}
 %\caption{ {Need to update this Figure. Also, I should try using orientation with the Bonds.}}
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/fixed_drift_bond_salt_layers.png}
+%\includegraphics[width=0.99\textwidth]{Figures/fixed_drift_bond_salt_layers.png}
 %\caption{ {}}
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_u_layers.png}
+%\includegraphics[width=0.99\textwidth]{Figures/snapshots_fixed_01_u_layers.png}
 %\caption{ {Need to update this Figure. }}
@@
 %\begin{center}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_fixed_01_v_layers.png}
+%\includegraphics[width=0.99\textwidth]{Figures/snapshots_fixed_01_v_layers.png}
 %\caption{ {Need to update this Figure. }}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_melt.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_melt.png}
+\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_comparison_melt.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_melt.png}
 \caption{ {Time-averaged melt rates in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_comparison_salt_layers.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_comparison_salt_layers.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
 \caption{ {Time-averaged vertical sections of salinity at  $x$=40~km in the (a) Lagrangian and (b) Eulerian simulations in the static ice-shelf configuration.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_temp_v_v.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_temp_v_v.png}
+\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_temp_v_v.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_solo_temp_v_v.png}
 \caption{ {Snapshots of the static ice-shelf experiment taken after 5 years of model simulation, using the Lagrangian ice-shelf model coupled to the MOM6 ocean model.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+\includegraphics[width=0.99\textwidth]{Figures/Wind_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg.png}
 \caption{ {Results of the static ice-shelf experiment using the Lagrangian ice-shelf model coupled to MOM6.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Broken_Compare_melt_m_per_year_anomaly.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Broken_Compare_melt_m_per_year_anomaly.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
 \caption{ {(a) Snapshot of the melt rate at the base of the ice shelf 60 days after the calving event in the tabular-iceberg-calving simulation.
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_ustar_iceberg.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_ustar_iceberg.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
 \caption{ {Snapshots of frictional velocity at the ice-shelf base in the tabular-iceberg-calving simulation. Snapshots are taken (a) 7, (b) 15, and (c) 50 days after calving.}}
@@
 \begin{center}
-\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_Wind_Wind_Collapse_salt_zold_x20_anomaly_mask.png}
-%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_comparison_salt_layers.png}
+\includegraphics[width=0.99\textwidth]{Figures/snapshots_Wind_Wind_Collapse_salt_zold_x20_anomaly_mask.png}
+%\includegraphics[width=0.99\textwidth]{Figures/ALE_z_static_shelf_comparison_salt_layers.png}
 \caption{ {Snapshots of vertical sections of ocean salinity anomaly at $x$=40~km in the iceberg-calving experiment.
